### 2020-03-08 docs/paper/paper.tex
* Paper organization

\documentclass[draft, a4, 10pt, onecolumn]{IEEEtran}

\usepackage{color,soul}

\begin{document}

\title{\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}}

\author{Zelaci Aimen, Ahmet Yaşlı, Cem Kalyoncu, and Hüseyin Ademgil}

\maketitle

\begin{abstract}
Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches. However, the potential number of combinations possible for a single application is huge. This issue combined by the speed of PCF numerical simulation techniques causes the task to take significant amount of time. As stated in the previous works, artificial neural networks (ANN) can predict the result of numerical simulations much faster. However, there are two issues with the methods proposed previously. Namely, the required number of samples for training and generality of the designed network. In this paper, we have proposed the use of generative adversarial networks (GAN) to fabricate additional data to be used in training and a unique ANN design that can work with wider range of configurations.
\end{abstract}

\section{Introduction}

\hl{Importance of PCF and SPR, written by AY or HA}

\hl{Importance of ANN, deep neural networks, GAN}

\hl{Literature survey}

\hl{Short explanation of GAN/ANN}

This paper is organized as follows. Section \ref{sec:prop} details the use of GAN to generate additional training samples for ANN as well as the proposed neural network architecture. Photonic crystal fiber design that is used for testing is described in details in section \ref{sec:pcf}. Detailed analysis of the experimental results are discussed in section \ref{sec:exp}. Finally, concluding remarks are made in section \ref{sec:conc}.

\section{Proposed method}
\label{sec:prop}

\hl{Details of the overall architecture}

\subsection{Artificial neural network design}
\label{ssec:ann}

\hl{Particulars of ANN design}

\hl{Explanations for Adam optimizer and batch normalization}

\subsection{Generative Adversarial networks}
\label{ssec:gan}

\hl{Explain GAN}

\hl{Explain how GAN is used in this design}

\section{Photonic crystal fiber design}
\label{sec:pcf}

\hl{PCF design details, written by AY}

\section{Experiments}
\label{sec:exp}

\subsection{Experimental setup}

\hl{Details of the dataset, machine that is used to run simulations}

\hl{Metrics used in the comparisons}

\subsection{Performance of ANN}

\hl{Performance of ANN design alone, compared to the other method}

\subsection{Performance boost of GAN}

\hl{Experiments regarding to the GAN}

\subsection{Computational performance}

\hl{Training and execution time of ANN versus simulation method}

\section{Conclusion}
\label{sec:conc}

\hl{about the improved speed}

\hl{reduced amount of training samples}

\hl{increased generality of the system}

Machine learning approaches has an inherit strength on top of classical simulation methods: they could model hidden parameters in a system which we have no knowledge about. Therefore, not only ANN can improve the speed of PCF simulation, but also accuracy of the simulations. However, this final claim requires further analysis and experimentation.

\end{document}

### 2020-03-10 docs/paper/paper.tex
*update: paper.tex

@@
 \usepackage{color,soul}
+\usepackage{tikz}
+\usepackage{pgfplots}
+\usepackage[english]{babel}
+\usepackage{graphicx}
 
@@
 \label{ssec:ann}
-
-\hl{Particulars of ANN design}
-
-\hl{Explanations for Adam optimizer and batch normalization}
+The ANN model is a fully-connected feed-forward MLP (Multi Layer Perceptron), consisting of an input layer, an output layer, and 5 hidden layers, 50 neurons for each hidden layer.
+Taking ReLU (Rectified Linear Unit) as the activation function, Adam (Diederik P.
+Kingma, Jimmy Ba, 22 Dec 2014 ) as the optimizer and the mean suqared error as the loss/cost function.
+To reduce overfitting we use the Early stopping method [reference], that is by saving checkpoints where the best validation mean squared error occurred as we iterate.
+To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used [reference].
 
@@
 
-\hl{Explain GAN}
-
-\hl{Explain how GAN is used in this design}
+GANs consist of two neural networks, as shown in figure (3).
+The first of which called a discriminator, that gives an estimate of the probability that a given input is real or generated (fake).
+Whereas the second network is referred to as the generator, which outputs data samples from a random noise vector called a latent variable usually given the symbol $z$ supplied at its input.
+The error between the discriminator’s output and the actual labels (The real data samples vectors all labeled as 1: the probability of being real) would then be measured by the means of a chosen metric.
+Introduced by Arjovsky et al [reference] the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
+Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty [reference].
+The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.
+GANs power emerges from the fact that discover insights or structures embedded within the data, which enables it generate it samples within an acceptable error.
+Therefore, in this work we will try to supplement our original training with the generated samples to improve the ANN model accuracy on predicting the confinement loss of the PCF.
 
@@
 
-\hl{Details of the dataset, machine that is used to run simulations}
+A labeled data-set of only 432 samples was collected in this work, through simulations using FV-FEM.
+The length of the data-set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent.
+The data-set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
+The labels are the confinement loss of the PCF.
+The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for 3 different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36) [35]).
+Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing.
+This data was preprocessed before fed in the networks.
+The indices of refraction  are very close, which made it quiet difficult for the neural networks to differentiate between them, after many trials, the best choice was to take only the tens digit of ${134, 135, 136}$, giving ${4, 5, 6}$.
+Finally, we transform the confinement loss to the log scale.
 
@@
 
-\hl{Performance of ANN design alone, compared to the other method}
+We train the ANN model for more than 2000 epochs, starting from the original data-set.
+Then we augment the data by 1000 generated samples from our WGAN-GP, which will be demonstrated in the next section.
+The following table summarizes the hyper-parameters chosen for the ANN model:\\
+\begin{tabular}{||c c c c c||}
+\hline
+Length of the training data-set & Learning rate&Batch size & $\beta_{1}$ & $\beta_{2}$\\ [0.5ex] 
+\hline\hline
+336 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
+\hline
+\hline\hline
+1000+336 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
+\hline
+\hline\hline
+2000 + 336 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
+\hline
+\hline\hline
+3000 + 336 & $ 2.5\times10^{-04} $ & 16  & 0.9 & 0.999 \\
+\hline
+\end{tabular}\\
+	 \newline
+	 The MSE on the training sets ranged from 0.0030 to 0.0050. For all data sets the MSE on the training sets decreased in an acceptable manner, as shown in the following figure.
+\begin{figure}[h]
+    \begin{tikzpicture}[scale=.6]
+		\begin{axis}[
+		xlabel=$Epochs$, % \hertz requires SIunits
+		ylabel=$Training \space MSE$,
+		title={Training MSE of the ANN model},
+		grid=both,
+		minor grid style={gray!25},
+		major grid style={gray!25},
+		width=1.1\linewidth,
+		no marks]
+		\addplot[line width=1pt,solid,color=blue] %
+		table{tr_loss_ann.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{}
+\end{figure}\\
+    \newline
+    Next, we plot the predictions the ANN model made after training using only the original data-set.
+    \newpage
+\begin{figure}[h]
+			\begin{tikzpicture}[scale=.6]
+			\begin{axis}[
+			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, % \hertz requires SIunits
+			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
+			title={Length of the training dataset = 336 + 0},
+			grid=both,
+			minor grid style={gray!25},
+			major grid style={gray!25},
+			width=1.1\linewidth]
+			\addplot[
+			only marks,
+			mark size=2.9pt, mark=o, color=red, fill=red] %
+			table{dataset_336.txt};
+			\addlegendentry{$Predicted$}
+			\addplot[line width=1pt,solid,color=blue]  %
+			table{y.txt};
+			\addlegendentry{$Actual$}
+			\end{axis}
+			\end{tikzpicture}
+			\caption{}
+\end{figure}
+As you can see, the ANN made somewhat good predictions of the low values of the confinement loss.
+A close inspection into the data samples collected shows that points are concentrated in the low values interval, i.e the ANN picked up the pattern quiet easily.
+However, in the higher values interval, the ANN could not see a pattern because points are distant from each other to some extent, even though we transformed the confinement loss to the log scale to actually minimize these distances.
 

### 2020-03-10 docs/paper/paper.tex
update: paper

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 
@@
 
-\author{Zelaci Aimen, Ahmet Yaşlı, Cem Kalyoncu, and Hüseyin Ademgil}
+\author{Aimen Zelaci, Ahmet Yaşlı, Cem Kalyoncu, and Hüseyin Ademgil}
 
@@
 Namely, the required number of samples for training and generality of the designed network.
-In this paper, we have proposed the use of generative adversarial networks (GAN) to fabricate additional data to be used in training and a unique ANN design that can work with wider range of configurations.
+In this paper, we have proposed the use of generative adversarial networks (GAN) to augment the real data set to then train a  ANN model.
+
 \end{abstract}
@@
 
-\hl{Importance of ANN, deep neural networks, GAN}
+Machine learning techniques are coming to the forefront of many fields.
+Especially deep learning [ref], surpassing human performance in a variety of fields, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
+However, this flexibility does not stop here because Artificial Neural Networks can compute any function at all (Universality theorem)[ref].
+No matter what the function is, there is to be a ANN so that for every possible vector X, the value f(X) (or some close approximation) is output from the network [ref].
+This fact propelled researchers to widen the applications of ANNs even further, including the study of nanophotonic structures [ref], optimization of photonic crystal nanocavities [ref], and more recently in a similar work to this paper, computing optical properties of a photonic crystal fiber [ref].
+Perhaps one of the challenges that deep learning models face is that they benefit from large amounts of data to train, which is quite costly to acquire [ref].
+One of the solutions to overcome this issue is to artificially expand the original real data set by the means of generative networks.
+Introduced by Goodfellow et al., Generative Adversarial Networks (GANs) [ref], proved to be very impressive in tasks such as synthetic data generation [ref], Synthetically Augment data for deep learning based image segmentation [ref].
+GANs power comes from the fact that they discover insights and structures within distributions that allows them to make good approximations to the real data set.
+In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
+Our aim to eventually surpass the simulations performed using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate the sensor performance.
+A time comparison between the performance of the ANN and classic simulation techniques has been made here [ref].
+Furtheremore, a time comparaison is also made in this paper in section $4$.
 
@@
 
-\hl{Details of the overall architecture}
+We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected.
+Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
+Previous works [ref, ref], demonstrated that random data augmentation actually had weakened the performance of the model.
+Hence, active researches are ongoing to find ways to optimally sample the generated data [ref], in other words to filter out the "good" generated data after training the GAN.
+In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
+In the following sub-sections we discuss the networks architectures.
 
@@
 The ANN model is a fully-connected feed-forward MLP (Multi Layer Perceptron), consisting of an input layer, an output layer, and 5 hidden layers, 50 neurons for each hidden layer.
-Taking ReLU (Rectified Linear Unit) as the activation function, Adam (Diederik P.
-Kingma, Jimmy Ba, 22 Dec 2014 ) as the optimizer and the mean suqared error as the loss/cost function.
+Taking ReLU (Rectified Linear Unit) as the activation function, Adam [ref] as the optimizer and the mean squared error as the loss/cost function.
 To reduce overfitting we use the Early stopping method [reference], that is by saving checkpoints where the best validation mean squared error occurred as we iterate.
-To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used [reference].
+To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used [ref].
 
-\subsection{Generative Adversarial networks}
+\subsection{Generative Adversarial network design}
 \label{ssec:gan}
 
-GANs consist of two neural networks, as shown in figure (3).
+GANs consist of two neural networks, as shown in figure (num).
 The first of which called a discriminator, that gives an estimate of the probability that a given input is real or generated (fake).
@@
 The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.
-GANs power emerges from the fact that discover insights or structures embedded within the data, which enables it generate it samples within an acceptable error.
-Therefore, in this work we will try to supplement our original training with the generated samples to improve the ANN model accuracy on predicting the confinement loss of the PCF.
-
+The WGAN-GP architecture chosen in this work is as follows: both the Critic and the generator networks are a fully-connected feed-forward MLP, having 4 hidden layers, with $ minibatchsize\times2^{number of layers} $ neurons for each hidden layer in the critic network, whereas $ minibatchsize\times2^{2} $ neurons for each hidden layer in the generator network.
+The input vector for the Critic network consists of the $six$ parameters discussed earlier for the ANN model, in addition the corresponding loss value, giving a total of seven inputs.
+The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the critic network.
+LeakyReLU and ReLU were chosen as the activation functions for the Critic and Generator respectively and Adam as the optimizer for both networks.
+Finally Batch Normalization technique was applied to the Generator.
+\newpage
 \section{Photonic crystal fiber design}
@@
 \end{tabular}\\
-	 \newline
+\newpage
 The MSE on the training sets ranged from 0.0030 to 0.0050. For all data sets the MSE on the training sets decreased in an acceptable manner, as shown in the following figure.
@@
 		\begin{axis}[
-		xlabel=$Epochs$, % \hertz requires SIunits
+		xlabel=$Epochs$, 
 		ylabel=$Training \space MSE$,
@@
 			\begin{axis}[
-			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, % \hertz requires SIunits
+			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
 			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
@@
 
-\hl{Experiments regarding to the GAN}
+During training the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in figure(num).
+In this sub-section we discuss the results of augmenting the real data set with Synthetic data.
+Figure(num) demonstrates the predictions made by the ANN model after training with different sizes of the Synthetic data set.
+This might seem paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data.
+There are several reasons that is driving our ANN model predictions in the wrong way.
+Even though our WGAN-GP seemed well trained, there still a domain gap between the real data and the generated data, or the expansion of data is growing in the wrong direction to that of entirely containing the real data.
+Furthermore, the generated data might lack realism.
+Or the sampling strategy adopted is poor[ref, ref, ref].
+After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved we set out to accomplish at the beginning, to train an ANN model and make accurate prediction on a never-seen-before data.
 
+\begin{figure}[ht]
+    \begin{subfigure}{.5\textwidth}
+			\begin{tikzpicture}
+			\begin{axis}[
+			xlabel=$Epochs$, 
+			ylabel=$ Training $ $ MSE $,
+			title={Training loss function of the Critic network},
+			grid=both,
+			minor grid style={gray!25},
+			major grid style={gray!25},
+			width=1.1\linewidth]
+			\addplot[line width=1pt,solid,color=blue]  %
+			table{wgan_tr_loss.txt};
+			\end{axis}
+			\end{tikzpicture}
+\end{subfigure}
+    \begin{subfigure}{.5\textwidth}
+			\begin{tikzpicture}
+			\begin{axis}[
+			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
+			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
+			title={Length of the training dataset = 336 + 1000},
+			grid=both,
+			minor grid style={gray!25},
+			major grid style={gray!25},
+			width=1.1\linewidth]
+			\addplot[
+			only marks,
+			mark size=2.9pt, mark=o, color=red, fill=red] %
+			table{dataset_1000.txt};
+			\addlegendentry{$Predicted$}
+			\addplot[line width=1pt,solid,color=blue]  %
+			table{y.txt};
+			\addlegendentry{$Actual$}
+			\end{axis}
+			\end{tikzpicture}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+			\begin{tikzpicture}
+			\begin{axis}[
+			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, % \hertz requires SIunits
+			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
+			title={Length of the training dataset = 336 + 2000},
+			grid=both,
+			minor grid style={gray!25},
+			major grid style={gray!25},
+			width=1.1\linewidth]
+			\addplot[
+			only marks,
+			mark size=2.9pt, mark=o, color=red, fill=red] %
+			table{dataset_2000.txt};
+			\addlegendentry{$Predicted$}
+			\addplot[line width=1pt,solid,color=blue]  %
+			table{y.txt};
+			\addlegendentry{$Actual$}
+			\end{axis}
+			\end{tikzpicture}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+			\begin{tikzpicture}
+			\begin{axis}[
+			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, % \hertz requires SIunits
+			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
+			title={Length of the training dataset = 336 + 3000},
+			grid=both,
+			minor grid style={gray!25},
+			major grid style={gray!25},
+			width=1.1\linewidth]
+			\addplot[
+			only marks,
+			mark size=2.9pt, mark=o, color=red, fill=red] %
+			table{dataset_3000.txt};
+			\addlegendentry{$Predicted$}
+			\addplot[line width=1pt,solid,color=blue]  %
+			table{y.txt};
+			\addlegendentry{$Actual$}
+			\end{axis}
+			\end{tikzpicture}
+\end{subfigure}
+\caption{}
+\end{figure}
+\newpage
+It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in figure(num).
+\begin{figure}
+    \begin{subfigure}{.5\textwidth}
+			\begin{tikzpicture}
+			\begin{axis}[
+			title={$n_{analyte=1.33}$},
+			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
+			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
+			grid=both,
+			minor grid style={gray!25},
+			major grid style={gray!25},
+			width=1.1\linewidth]
+			\addplot[
+			only marks,
+			mark size=2.9pt, mark=o, color=red, fill=red] %
+			table[x={X},y={Y_REAL}]{133.txt};
+			\addlegendentry{$Actual$}
+			\addplot[smooth, 
+			line width=1pt,solid,color=blue]  %
+			table[x={X},y={Predictions}]{133.txt};
+			\addlegendentry{$Predictions$}
+			\end{axis}
+			\end{tikzpicture}
+\end{subfigure}
+ \begin{subfigure}{.5\textwidth}
+			\begin{tikzpicture}
+			\begin{axis}[
+			title={$n_{analyte=1.34}$},
+			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
+			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
+			grid=both,
+			minor grid style={gray!25},
+			major grid style={gray!25},
+			width=1.1\linewidth]
+			\addplot[
+			only marks,
+			mark size=2.9pt, mark=o, color=red, fill=red] %
+			table[x={X},y={Y_REAL}]{134.txt};
+			\addlegendentry{$Actual$}
+			\addplot[smooth,
+			line width=1pt,solid,color=blue]  %
+			table[x={X},y={Predictions}]{134.txt};
+			\addlegendentry{$Predictions$}
+			\end{axis}
+			\end{tikzpicture}
+\end{subfigure}
+ \begin{subfigure}{.5\textwidth}
+			\begin{tikzpicture}
+			\begin{axis}[
+			title={$n_{analyte=1.35}$},
+		    xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
+			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
+			grid=both,
+			minor grid style={gray!25},
+			major grid style={gray!25},
+			width=1.1\linewidth]
+			\addplot[
+			only marks,
+			mark size=2.9pt, mark=o, color=red, fill=red] %
+			table[x={X},y={Y_REAL}]{135.txt};
+			\addlegendentry{$Actual$}
+			\addplot[smooth,line width=1pt,solid,color=blue]  %
+			table[x={X},y={Predictions}]{135.txt};
+			\addlegendentry{$Predictions$}
+			\end{axis}
+			\end{tikzpicture}
+\end{subfigure}
+\caption{}
+\end{figure}
+\newpage
 \subsection{Computational performance}

### 2020-03-11 docs/paper/paper.tex
Introduction preface Fixed filenames

@@
 
+In this paper we propose the use of artificial neural networks (ANN) to compute the loss in photonic crystal fibers in a wide range of configurations.
+Additionally, in order to minimize the required amount of samples to train the ANN, we employed generative adversarial networks (GAN).
+As discussed in the experiments section, this setup significantly reduces the error in the prediction compared to the state-of-the-art methods used in the literature.
+
 \hl{Importance of PCF and SPR, written by AY or HA}
 
-Machine learning techniques are coming to the forefront of many fields.
-Especially deep learning [ref], surpassing human performance in a variety of fields, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
-However, this flexibility does not stop here because Artificial Neural Networks can compute any function at all (Universality theorem)[ref].
-No matter what the function is, there is to be a ANN so that for every possible vector X, the value f(X) (or some close approximation) is output from the network [ref].
-This fact propelled researchers to widen the applications of ANNs even further, including the study of nanophotonic structures [ref], optimization of photonic crystal nanocavities [ref], and more recently in a similar work to this paper, computing optical properties of a photonic crystal fiber [ref].
-Perhaps one of the challenges that deep learning models face is that they benefit from large amounts of data to train, which is quite costly to acquire [ref].
-One of the solutions to overcome this issue is to artificially expand the original real data set by the means of generative networks.
-Introduced by Goodfellow et al., Generative Adversarial Networks (GANs) [ref], proved to be very impressive in tasks such as synthetic data generation [ref], Synthetically Augment data for deep learning based image segmentation [ref].
-GANs power comes from the fact that they discover insights and structures within distributions that allows them to make good approximations to the real data set.
-In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
+Machine learning techniques are coming to the forefront of many fields [ref], surpassing the human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
+Additionally, ANN can approximate any function (Universality theorem)[ref].
+This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures [ref], optimization of photonic crystal nanocavities [ref], and more recently, computing optical properties of a photonic crystal fiber [ref].
+
+One of the most difficult challenges that deep learning models face is that they benefit from large amounts of data to train, which may be costly to acquire [ref].
+One of the solutions to overcome this issue is to artificially expand the original dataset by the means of generative networks.
+Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [ref], proved to be successful in tasks such as synthetic data generation [ref] and synthetically augment the data for deep learning based systems [ref].
+
+\hl{Will be moved to methodology} 
+hl{GAN power comes from the fact that they discover insights and structures within distributions that allows them to make good approximations to the real data set.} \hl{This is exactly how ANN works too.} In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
 Our aim to eventually surpass the simulations performed using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate the sensor performance.
@@
 \hl{Literature survey}
-
-\hl{Short explanation of GAN/ANN}
 

### 2020-03-12 main.py
update: data_handler: networks

@@ -1,27 +1,0 @@
-import data_handler
-import networks
-
-# Size of data augmentation
-AUGMENT_SIZE = 1000
-
-# Load Original data
-# OUR SPR PHOTONIC SENSOR
-#tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='data.xlsx')
-
-# THEIR PCF DATA
-tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_pcf_data()
-
-# Augment data after training the wgan
-# To augment our data use fname = 'gen_data.txt'
-# To augment their data use fname = 'gen_data_pcf.txt'
-#tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, AUGMENT_SIZE, fname='gen_data_pcf.txt')
-
-# Save / Checkpoint directory
-save_dir = r'.\trained-nets\model1.h5'
-chkdir = r'.\trained-weights\weights1.hdf5'
-
-if __name__ == '__main__':
-    #print(tr_data[-1])
-    #networks.generate_and_save_data(training=False)
-    networks.train_wgan(tr_data,tr_labels, epochs=200)
-    #networks.train_model(EPOCHS, tr_data, tr_labels, va_data, va_labels, save_dir, chkdir)

### 2020-03-12 src/data_handler.py

@@ -1,0 +1,102 @@
+import scipy as sp
+import pandas as pd
+import matplotlib.pyplot as plt
+
+def load_pcf_data(fname='.\data\pcf_data1.xlsx'):
+    df_1 = pd.read_excel(fname)
+    datafile_1 = df_1.values
+
+    tr_data = datafile_1[:1000,2:6].reshape(1000,4)
+    tr_labels = datafile_1[:1000,-1].reshape(1000,1)
+
+    va_data = datafile_1[1000:1050,2:6].reshape(50,4)
+    va_labels = datafile_1[1000:1050, -1].reshape(50, 1)
+
+    test_data =datafile_1[1050:,2:6]
+    test_labels =datafile_1[1050:,-1]
+
+    return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
+
+def load_data(fname='.\data\data.xlsx'):
+    data =pd.read_excel(fname)
+    df = data.values
+
+    df = df.reshape(9,3,16,7)
+    sp.random.shuffle(df)
+    df = df.reshape(432,7)
+
+    analytes = df[:,0]
+    analytes = (analytes*100)%10
+    x = df[:, 1:6]
+    
+    x = x.reshape(432,5)
+    analytes = analytes.reshape(432,1)
+    
+    x = sp.concatenate((analytes, x), axis=1)
+    x /= 10
+
+    y = df[:, -1]
+    y = y * (10**8)
+    y = sp.log10(y)
+    #Assert shape
+    x = x.reshape(9,3,16,6)
+    y = y.reshape(9,3,16,1)
+
+    tr_data = x[:7].reshape(7 * 16 * 3, 6)
+    tr_labels = y[:7].reshape(7 * 16 * 3, 1)
+
+    va_data = x[-2].reshape(1*16*3,6)
+    va_labels = y[-2].reshape(1*16*3,1)
+
+    test_data = x[-1].reshape(1*16*3,6)
+    test_labels = y[-1].reshape(1*16*3,1)
+
+    return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
+
+# Augment data
+def augment_data(tr_data, tr_labels, size=1000, fname='.\gen_data\gen_data.txt'):
+    generated_data = pd.read_csv(fname).values
+
+    #OUR data
+    if(fname=='gen_data'):
+        gen_x = generated_data[:size, :6]
+       
+    #THEIR data
+    if(fname=='gen_data_pcf'):
[…]

### 2020-03-12 src/main.py

@@ -1,0 +1,52 @@
+from src import networks, data_handler
+from src.networks import Wgan
+
+# Size of data augmentation
+AUGMENT_SIZE = 1000
+
+# Load Original data
+# OUR SPR PHOTONIC SENSOR
+tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
+
+# THEIR PCF DATA
+#tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_pcf_data()
+
+# Augment data after training the wgan
+# To augment our data use fname = '.\gen_data\gen_data.txt'
+# To augment their data use fname = '.\gen_data\gen_data_pcf.txt'
+#tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, AUGMENT_SIZE, fname='.\gen_data\gen_data_pcf.txt')
+
+# Save / Checkpoint directory
+save_dir = r'.\trained-nets\model1.h5'
+chkdir = r'.\trained-weights\weights1.hdf5'
+
+if __name__ == '__main__':
+    # TRAIN WGAN
+    wgan = Wgan(BATCH_SIZE = 12,
+                noise_dim = 7,
+                num_critic_input = 7,
+                n_critic = 5,
+                grad_penalty_weight = 10,
+                num_examples_to_generate = 8)
+    generator = wgan.make_generator_model(num_layers=4)
+    critic = wgan.make_critic_model(num_layers=4)
+    #wgan.train_wgan(tr_data,tr_labels,epochs = 200, generator=generator, critic=critic)
+
+    # TRAIN ANN MODEL
+    ann_model = networks.make_model(num_layers=5,
+                                    num_inputs=6,
+                                    num_outputs=1,
+                                    num_neurons=50)
+
+    networks.train_model(model = ann_model,
+                         epochs=2000,
+                         tr_data=tr_data,
+                         tr_labels=tr_labels,
+                         va_data=va_data,
+                         va_labels=va_labels,
+                         save_dir=save_dir,
+                         chkdir=chkdir)
+    # TEST
+    networks.test_model(model=ann_model,
+                        test_data=test_data,
+                        test_labels=test_labels)

### 2020-03-12 src/networks.py

@@ -1,0 +1,321 @@
+# Load libraries
+from __future__ import absolute_import, division, print_function, unicode_literals
+from tensorflow import keras
+from tensorflow.keras import layers
+import scipy as sp
+import tensorflow as tf
+import matplotlib.pyplot as plt
+import time
+import os
+from scipy.interpolate import UnivariateSpline
+
+# Enable Tensorflow eager execution. This line must be at the top of the script.
+tf.compat.v1.enable_eager_execution()
+
+############################### ANN MODEL ##########################################
+####################################################################################
+####################################################################################
+
+def make_model(num_layers=5, num_neurons=50, num_inputs=6, num_outputs=1):
+    model = tf.keras.Sequential()
+
+    # INPUT layer
+    model.add(layers.Dense(num_neurons, input_shape=(num_inputs,)))
+    model.add(layers.ReLU())
+
+    # Hidden layers
+    for _ in range(num_layers):
+        model.add(layers.Dense(num_neurons))
+        model.add(layers.BatchNormalization())
+        model.add(layers.ReLU())
+
+    # OUTPUT layer
+    model.add(layers.Dense(num_outputs))
+    model.add(layers.ReLU())
+
+    return model
+
+def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, chkdir):
+
+    # Proceed training of a saved model
+    # model = keras.models.load_model(save_dir)
+
+    # TensorBoard log directory
+    logdir = r'.\logs\scalars\{}'.format(time.time())
+
+    # CALLBACKS
+    # TensorBoard
+    tensorboard_callback = keras.callbacks.TensorBoard(log_dir=logdir)
+
+    # Save the best va_loss file
+    checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=1,
+                                                   save_best_only=True)
+
+    data_size = int(len(tr_data))
+    # Learning rate / Minibatch size
+    lr = 1e-4
+    batch_size = 8
+    if data_size >= 2000:
+        lr = 2e-4
+        batch_size = 16
+    if data_size >= 3000:
+        lr = 20e-4 / 8
+        batch_size = 20
+
+    # Define optimizers
+    Adam = keras.optimizers.Adam(learning_rate=lr, beta_1=0.9, beta_2=0.999)
+    RMSprop = keras.optimizers.RMSprop(learning_rate=1e-2, rho=0.9)
+    # Train
[…]

### 2020-03-12 src/main.py
fix: load_model

@@ -21,6 +21,8 @@ save_dir = r'.\trained-nets\model1.h5'
 chkdir = r'.\trained-weights\weights1.hdf5'
 
 if __name__ == '__main__':
+    # PLEASE TRAIN the ANN and WGAN seperately !
+
     # TRAIN WGAN
     wgan = Wgan(BATCH_SIZE = 12,
                 noise_dim = 7,
@@ -47,6 +49,10 @@ if __name__ == '__main__':
                          save_dir=save_dir,
                          chkdir=chkdir)
     # TEST
+    # LOAD_TYPE = load the whole model or load the best checkpoint(load weights)
+    ann_model = networks.load_model(model=ann_model,
+                                    load_type='load_weights',
+                                    dir=r'.\trained-weights\weights1')
     networks.test_model(model=ann_model,
                         test_data=test_data,
                         test_labels=test_labels)

### 2020-03-12 src/networks.py

@@ -93,9 +93,7 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
     ############# Graphs ######################
     ###########################################
 
-def load_model(load_type,dir):
-    model = make_model()
-
+def load_model(model,load_type,dir):
     if load_type == 'load_weights':
         model.load_weights(dir)
 

### 2020-03-12 src/networks.py
Update networks.py

@@ -8,7 +8,10 @@ import matplotlib.pyplot as plt
 import time
 import os
 from scipy.interpolate import UnivariateSpline
+from tensorflow.python.client import device_lib
 
+# Print CPUs / GPUs available
+print(device_lib.list_local_devices())
 # Enable Tensorflow eager execution. This line must be at the top of the script.
 tf.compat.v1.enable_eager_execution()
 

### 2020-03-13 src/main.py
Update main.py

@@ -1,5 +1,5 @@
-from src import networks, data_handler
-from src.networks import Wgan
+import networks, data_handler
+from networks import Wgan
 
 # Size of data augmentation
 AUGMENT_SIZE = 1000

### 2020-03-14 docs/paper/paper.tex
update: abstract: Comp-performance

@@
 \usepackage{subcaption}
-
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,      
+    urlcolor=cyan,
+}
+\urlstyle{same}  
 \begin{document}
@@
 \begin{abstract}
-Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches.
-However, the potential number of combinations possible for a single application is huge.
-This issue combined by the speed of PCF numerical simulation techniques causes the task to take significant amount of time.
-As stated in the previous works, artificial neural networks (ANN) can predict the result of numerical simulations much faster.
-However, there are two issues with the methods proposed previously.
-Namely, the required number of samples for training and generality of the designed network.
-In this paper, we have proposed the use of generative adversarial networks (GAN) to augment the real data set to then train a  ANN model.
+Our aim is to surpass the performance of the simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate a Surface Plasmon Reasonance (SPR) based Photonic Crystal Fiber (PCF) sensor performance, using deep learning.
+By these simulation techniques one must calculate the confinement loss for a specific wavelength and a particular set of geometric properties of the PCF sensor, then repeat the process for different analytes.
+In order to find the best fit distribution we have to make as much calculations per wavelength as possible to ensure the correct location of the peak value of the confinement loss.
+This process is then repeated for different geometric set that consists of more than 6 elements to find the best set that maximizes the distance between confinement loss distributions, in other words to find the best PCF sensor.
+Thus this way is not only time costing, consuming hours to days, but also inaccurate sometimes.
+In contrast, a deep neural network model does all of this astonishingly in under a second.
 
@@
 Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [ref], proved to be successful in tasks such as synthetic data generation [ref] and synthetically augment the data for deep learning based systems [ref].
-
-\hl{Will be moved to methodology} 
-hl{GAN power comes from the fact that they discover insights and structures within distributions that allows them to make good approximations to the real data set.} \hl{This is exactly how ANN works too.} In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
-Our aim to eventually surpass the simulations performed using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate the sensor performance.
-A time comparison between the performance of the ANN and classic simulation techniques has been made here [ref].
-Furtheremore, a time comparaison is also made in this paper in section $4$.
+In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
 
@@
 Whereas the second network is referred to as the generator, which outputs data samples from a random noise vector called a latent variable usually given the symbol $z$ supplied at its input.
-The error between the discriminator’s output and the actual labels (The real data samples vectors all labeled as 1: the probability of being real) would then be measured by the means of a chosen metric.
+The error between the discriminator's output and the actual labels (The real data samples vectors all labelled as 1: the probability of being real) would then be measured by the means of a chosen metric.
 Introduced by Arjovsky et al [reference] the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
@@
 
-A labeled data-set of only 432 samples was collected in this work, through simulations using FV-FEM.
+A labelled data-set of only 432 samples was collected in this work, through simulations using FV-FEM.
 The length of the data-set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent.
@@
 Then we augment the data by 1000 generated samples from our WGAN-GP, which will be demonstrated in the next section.
-The following table summarizes the hyper-parameters chosen for the ANN model:\\
-\begin{tabular}{||c c c c c||}
+The following table summarizes the hyper-parameters chosen for the ANN model:
+\begin{table}[h]
+\centering
+\scalebox{1.5}{
+    \begin{tabular}{|l|l|l|l|l|}
     \hline
-Length of the training data-set & Learning rate&Batch size & $\beta_{1}$ & $\beta_{2}$\\ [0.5ex] 
-\hline\hline
+Length of the training data-set & Learning rate&Batch size & $\beta_{1}$ & $\beta_{2}$\\
+\hline
 336 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
 \hline
-\hline\hline
 1000+336 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
 \hline
-\hline\hline
 2000 + 336 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
 \hline
-\hline\hline
 3000 + 336 & $ 2.5\times10^{-04} $ & 16  & 0.9 & 0.999 \\
 \hline
-\end{tabular}\\
+    \end{tabular}
+}
+\caption{Hyper-parameters chosen for the ANN model}
+\end{table}
+
 \newpage
@@
 
+This work had been conduct on a  laptop having: Intel(R) Core(TM) i7-5600 CPU @2.60GHz (4 CPUs) and 8GB RAM. The code for this work is available at: \url{https://github.com/Aimen-Zelaci/SPRPCF_ANN/}.
+\newline
+The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, batch size, data set size, epochs and framework used to code the model.
+In this work we fixed the number of epochs and executed training using Tensorflow/Keras and Pytorch frameworks, by varying the mini-btach size and the data set size, as demonstrated in Table(num).
+It is worth mentioning the differences between using full batch or mini-batch.
+In full batch training the whole data set is passed to the model for each iteration.
+In contrast, mini-batch training, the data set is split into small mini-batches of equal sizes.
+Previous works have firmly proved the advantages of using the correct mini-batch size as oppose to large batch sizes[ref].
+Training runtime is longer using mini-batches.
+However, mini-batches allow for more frequent gradient calculations, that results in more stable and reliable training [ref].
+Perhaps one of the main downsides of using large batch size is the poor generalization resulting in a phenomena know as the "generalization gap"[ref].
+Active research is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime [ref].
+A closely related recent work (Machine learning approach for computing optical properties of a photonic crystal fiber, SUNNY CHUGH, AAMIR GULISTAN, SOUVIK GHOSH, AND B.M.A.
+RAHMAN, DEC 2019), conducted their expirements using full batch to train the model.
+In this works we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications.
+Finally, we compared the performance of the ANN/WGAN models using CPU and GPU.
+As Table (num) demonstrates, GPU based training outperformes that of CPU based.
+With the emergence of Cloud Computing technology, one can rent GPU based instances of high specs with pennies on the dollar.
+
+\begin{table}[h]
+\begin{tabular}{lllll}
+    & data set size & mini batch size & Time elapsed (sec) \\
+Mini batches    &336 + 0 & 8 & 136 & \\
+    &336 + 1000 & 8 & 388 & \\
+    &336 + 2000 & 16 & 563  & \\ 
+    &336 + 3000 & 20 & 958  & \\
+\end{tabular}
+\begin{tabular}{lllll}
+   & data set size & Time elapsed (sec) \\
+Full batch    &336 + 0 &  96 & \\
+    &336 + 1000 &  162 & \\
+    &336 + 2000 &  165 & \\ 
+    &336 + 3000 &  263 & \\
+\end{tabular}
+\caption{Training performance using Tensorflow/Keras}
+\end{table}
+\begin{table}[h]
+\begin{tabular}{lllll}
+ & data set size & mini batch size & Time elapsed (sec) \\
+Mini batches    & 336 + 0 & 8 & 359 & \\
+    & 336 + 1000 & 8 & 1348  & \\
+    & 336 + 2000 & 16 & 1379  & \\ 
+    & 336 + 3000 & 20 & 1504 & \\
+\end{tabular}
+\begin{tabular}{lllll}
+   &data set size & Time (sec) \\
+   Full batch &336 + 0 &  14  & \\
+    & 336 + 1000 &  57  & \\
+    & 336 + 2000 &  107  & \\ 
+    & 336 + 3000 &  195  & \\
+\end{tabular}
+\caption{Training performance using Pytorch}
+\end{table}
+
+\hl{WGAN EXCUTION WITH GPU VS CPU BY CEM}
+
+Next, we compare the testing runtime of the ANN model to that of simulation methods used to compute the confinement loss for 3 different analytes and 16 wavelenghts, i.e a total of 48 values of the confinement loss, demonstrated in Table(num).
+
+\begin{table}[h]
+\centering
+\scalebox{1.2}{\begin{tabular}{l|l}
+      & Time elapsed & \\
+      \hline
+    ANN &  0.79 sec & \\
+    \hline
+    Simulation &  7872 sec = 2.18 hours  & \\
+\end{tabular}
+}
+\caption{ANN vs Simulation test runtime performance}
+\end{table}
+\newpage
+
 \section{Conclusion}

### 2020-03-15 docs/paper/paper.tex
update docs: ref-list: graphs

@@
 \begin{abstract}
-Our aim is to surpass the performance of the simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate a Surface Plasmon Reasonance (SPR) based Photonic Crystal Fiber (PCF) sensor performance, using deep learning.
+Our aim is to surpass the performance of the simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate a Surface Plasmon Reasonance (SPR) based Photonic Crystal Fiber (PCF) sensor performance, using deep learning models.
 By these simulation techniques one must calculate the confinement loss for a specific wavelength and a particular set of geometric properties of the PCF sensor, then repeat the process for different analytes.
 In order to find the best fit distribution we have to make as much calculations per wavelength as possible to ensure the correct location of the peak value of the confinement loss.
-This process is then repeated for different geometric set that consists of more than 6 elements to find the best set that maximizes the distance between confinement loss distributions, in other words to find the best PCF sensor.
-Thus this way is not only time costing, consuming hours to days, but also inaccurate sometimes.
-In contrast, a deep neural network model does all of this astonishingly in under a second.
+Simulation methods are not only time costing and daunting, consuming hours to days, but also inaccurate sometimes.
+In contrast, a deep neural network model astonishingly performs calculations in under a second, quiet accurately.
 
@@
 
-In this paper we propose the use of artificial neural networks (ANN) to compute the loss in photonic crystal fibers in a wide range of configurations.
-Additionally, in order to minimize the required amount of samples to train the ANN, we employed generative adversarial networks (GAN).
-As discussed in the experiments section, this setup significantly reduces the error in the prediction compared to the state-of-the-art methods used in the literature.
-
 \hl{Importance of PCF and SPR, written by AY or HA}
 
-Machine learning techniques are coming to the forefront of many fields [ref], surpassing the human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
-Additionally, ANN can approximate any function (Universality theorem)[ref].
-This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures [ref], optimization of photonic crystal nanocavities [ref], and more recently, computing optical properties of a photonic crystal fiber [ref].
+Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing the human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
+Artificial Neural Networks can approximate any function by virtue of the Universality theorem: No matter what the input is there is to be a guaranteed ANN architecture that computes the desired outputs.
+This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures [1], optimization of photonic crystal nanocavities [2], and more recently, computing optical properties of a photonic crystal fiber [3].
 
-One of the most difficult challenges that deep learning models face is that they benefit from large amounts of data to train, which may be costly to acquire [ref].
-One of the solutions to overcome this issue is to artificially expand the original dataset by the means of generative networks.
-Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [ref], proved to be successful in tasks such as synthetic data generation [ref] and synthetically augment the data for deep learning based systems [ref].
+One of the most difficult challenges that deep learning models face is that they benefit from large amounts of data to train, which may be costly to acquire.
+One of the solutions to overcome this issue is to artificially expand the original training dataset by the means of generative networks.
+Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [4], proved to be successful in data generation [5, 6, 7, 8, 9].
 In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
@@
 Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
-Previous works [ref, ref], demonstrated that random data augmentation actually had weakened the performance of the model.
-Hence, active researches are ongoing to find ways to optimally sample the generated data [ref], in other words to filter out the "good" generated data after training the GAN.
+Previous works [10, 11], demonstrated that random data augmentation actually had weakened the performance of the model.
+Hence, active researches are ongoing to find ways to optimally sample the generated data [12], in other words to filter out the "good" generated data after training the GAN.
 In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
 In the following sub-sections we discuss the networks architectures.
+Before we proceed, it is worth mentioning that the choices made for the parameters of the networks are by no means a robust set of rules, rather, they are rules of thumb and heuristics, as no such rules have been yet developed for ANN models.
 
@@
 \label{ssec:ann}
-The ANN model is a fully-connected feed-forward MLP (Multi Layer Perceptron), consisting of an input layer, an output layer, and 5 hidden layers, 50 neurons for each hidden layer.
-Taking ReLU (Rectified Linear Unit) as the activation function, Adam [ref] as the optimizer and the mean squared error as the loss/cost function.
-To reduce overfitting we use the Early stopping method [reference], that is by saving checkpoints where the best validation mean squared error occurred as we iterate.
-To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used [ref].
+The ANN model is a fully-connected feed-forward MLP (Multi Layer Perceptron), consisting of an input layer, an output layer, 5 hidden layers, and 50 neurons for each hidden layer.
+Taking ReLU (Rectified Linear Unit) as the activation function, Adam [13] as the optimizer and the mean squared error as the loss/cost function.
+To reduce over fitting we use the Early stopping method, by saving checkpoints where the best validation mean squared error occurred as we iterate before the model starts to over fit.
+To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm [14] was used.
 
@@
 The error between the discriminator's output and the actual labels (The real data samples vectors all labelled as 1: the probability of being real) would then be measured by the means of a chosen metric.
-Introduced by Arjovsky et al [reference] the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
-Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty [reference].
+Introduced by Arjovsky et al [15] the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
+Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty [16].
 The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.
 The WGAN-GP architecture chosen in this work is as follows: both the Critic and the generator networks are a fully-connected feed-forward MLP, having 4 hidden layers, with $ minibatchsize\times2^{number of layers} $ neurons for each hidden layer in the critic network, whereas $ minibatchsize\times2^{2} $ neurons for each hidden layer in the generator network.
-The input vector for the Critic network consists of the $six$ parameters discussed earlier for the ANN model, in addition the corresponding loss value, giving a total of seven inputs.
+The input vector for the Critic network consists of the six parameters discussed earlier for the ANN model, in addition the corresponding loss value, giving a total of seven inputs.
 The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the critic network.
@@
 Finally Batch Normalization technique was applied to the Generator.
-\newpage
+
 \section{Photonic crystal fiber design}
@@
 \hline
-1000+336 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
+336 + 1000 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
 \hline
-2000 + 336 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
+336 + 2000 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
 \hline
-3000 + 336 & $ 2.5\times10^{-04} $ & 16  & 0.9 & 0.999 \\
+336 + 3000 & $ 2.5\times10^{-04} $ & 16  & 0.9 & 0.999 \\
 \hline
@@
 \newpage
-The MSE on the training sets ranged from 0.0030 to 0.0050. For all data sets the MSE on the training sets decreased in an acceptable manner, as shown in the following figure.
+The MSE on the training sets ranged from 0.0030 to 0.0050.
+For all data sets the MSE on the training sets decreased in an acceptable manner.
+Next, we plot the predictions the ANN model made after training using only the original.
+As shown in the following figure data-set.
+
 \begin{figure}[h]
-    \begin{tikzpicture}[scale=.6]
+	\hspace*{-0.07\textwidth}
+	\begin{subfigure}{.5\textwidth}
+    \begin{tikzpicture}
 		\begin{axis}[
@@
 	\end{tikzpicture}
-	\caption{}
-\end{figure}\\
-    \newline
-    Next, we plot the predictions the ANN model made after training using only the original data-set.
-    \newpage
-\begin{figure}[h]
-			\begin{tikzpicture}[scale=.6]
+	\end{subfigure}\hspace{0.1\textwidth}
+	\begin{subfigure}{.5\textwidth}
+	\begin{tikzpicture}
 			\begin{axis}[
+			legend pos=north west,
 			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
@@
 			\end{tikzpicture}
+	\end{subfigure}
 	\caption{}
-\end{figure}
+\end{figure}\\
+
+    \newpage
 As you can see, the ANN made somewhat good predictions of the low values of the confinement loss.
@@
 Furthermore, the generated data might lack realism.
-Or the sampling strategy adopted is poor[ref, ref, ref].
+Or the sampling strategy adopted is poor.
 After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved we set out to accomplish at the beginning, to train an ANN model and make accurate prediction on a never-seen-before data.
 
-\begin{figure}[ht]
+\hspace{-0.07\textwidth}
+\begin{figure}[h]
     \begin{subfigure}{.5\textwidth}
@@
 			\end{tikzpicture}
-\end{subfigure}
+\end{subfigure}\hspace{0.05\textwidth}
     \begin{subfigure}{.5\textwidth}
@@
 			\begin{axis}[
+			legend pos=north west,
 			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
@@
 			\begin{axis}[
-			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, % \hertz requires SIunits
+			legend pos=north west,
+			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
 			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
@@
 			\end{tikzpicture}
-\end{subfigure}
+\end{subfigure}\hspace{0.05\textwidth}
 \begin{subfigure}{.5\textwidth}
@@
 			\begin{axis}[
-			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, % \hertz requires SIunits
+			legend pos=north west,
+			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
 			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
@@
 It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in figure(num).
+
 \begin{figure}
@@
 			\end{tikzpicture}
-\end{subfigure}
+\end{subfigure}\hspace{0.05\textwidth}
  \begin{subfigure}{.5\textwidth}
@@
 In contrast, mini-batch training, the data set is split into small mini-batches of equal sizes.
-Previous works have firmly proved the advantages of using the correct mini-batch size as oppose to large batch sizes[ref].
+Previous works [17, 18] have firmly proved the advantages of using the correct mini-batch size as oppose to large batch sizes.
 Training runtime is longer using mini-batches.
-However, mini-batches allow for more frequent gradient calculations, that results in more stable and reliable training [ref].
-Perhaps one of the main downsides of using large batch size is the poor generalization resulting in a phenomena know as the "generalization gap"[ref].
-Active research is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime [ref].
+However, mini-batches allow for more frequent gradient calculations, that results in more stable and reliable training.
+Perhaps one of the main downsides of using large batch size is the poor generalization resulting in a phenomena know as the "generalization gap".
+Active research [19] is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime.
 A closely related recent work (Machine learning approach for computing optical properties of a photonic crystal fiber, SUNNY CHUGH, AAMIR GULISTAN, SOUVIK GHOSH, AND B.M.A.
 RAHMAN, DEC 2019), conducted their expirements using full batch to train the model.
-In this works we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications.
+In this works we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications to fit our purposes.
 Finally, we compared the performance of the ANN/WGAN models using CPU and GPU.

### 2020-03-15 src/data_handler.py
update: Time-performance

@@ -28,10 +28,10 @@ def load_data(fname='.\data\data.xlsx'):
     analytes = df[:,0]
     analytes = (analytes*100)%10
     x = df[:, 1:6]
-    
+
     x = x.reshape(432,5)
     analytes = analytes.reshape(432,1)
-    
+
     x = sp.concatenate((analytes, x), axis=1)
     x /= 10
 
@@ -55,18 +55,23 @@ def load_data(fname='.\data\data.xlsx'):
 
 # Augment data
 def augment_data(tr_data, tr_labels, size=1000, fname='.\gen_data\gen_data.txt'):
-    generated_data = pd.read_csv(fname).values
+
+    #generated_data = pd.read_csv(fname).values
+    generated_data = sp.genfromtxt('fname', delimiter='\t\t')
+
+    if(size == 0):
+        return [tr_data, tr_labels]
 
     #OUR data
     if(fname=='gen_data'):
         gen_x = generated_data[:size, :6]
-       
+
     #THEIR data
     if(fname=='gen_data_pcf'):
         gen_x = generated_data[:size, :4]
-        
+
     gen_y = generated_data[:size, -1]
-    
+
     # Concatenate arrays
     tr_labels = sp.concatenate((tr_labels, gen_y), axis=0)
     tr_data = sp.concatenate((tr_data, gen_x), axis=0)

### 2020-03-15 src/main.py

@@ -1,5 +1,6 @@
 import networks, data_handler
 from networks import Wgan
+import time
 
 # Size of data augmentation
 AUGMENT_SIZE = 1000
@@ -24,6 +25,7 @@ if __name__ == '__main__':
     # PLEASE TRAIN the ANN and WGAN seperately !
 
     # TRAIN WGAN
+    start = time.time()
     wgan = Wgan(BATCH_SIZE = 12,
                 noise_dim = 7,
                 num_critic_input = 7,
@@ -33,6 +35,7 @@ if __name__ == '__main__':
     generator = wgan.make_generator_model(num_layers=4)
     critic = wgan.make_critic_model(num_layers=4)
     #wgan.train_wgan(tr_data,tr_labels,epochs = 200, generator=generator, critic=critic)
+    print('Training time for the wgan is: {} sec'.format(time.time() - start))
 
     # TRAIN ANN MODEL
     ann_model = networks.make_model(num_layers=5,
@@ -40,19 +43,27 @@ if __name__ == '__main__':
                                     num_outputs=1,
                                     num_neurons=50)
 
-    networks.train_model(model = ann_model,
-                         epochs=2000,
-                         tr_data=tr_data,
-                         tr_labels=tr_labels,
-                         va_data=va_data,
-                         va_labels=va_labels,
-                         save_dir=save_dir,
-                         chkdir=chkdir)
+    for augment_size in [0,1000,2000,3000]:
+        tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, augment_size, fname='.\gen_data\gen_data.txt')
+        start = time.time()
+        networks.train_model(model = ann_model,
+                             epochs=2000,
+                             tr_data=tr_data,
+                             tr_labels=tr_labels,
+                             va_data=va_data,
+                             va_labels=va_labels,
+                             save_dir=r'.\trained-nets\model{}.h5'.format(augment_size),
+                             chkdir=r'.\trained-weights\weights.hdf5'.format(augment_size)
+                             )
+        print('Training time for data set length {} is : {} sec'.format(336+augment_size, time.time() - start))
+
     # TEST
     # LOAD_TYPE = load the whole model or load the best checkpoint(load weights)
+    start = time.time()
     ann_model = networks.load_model(model=ann_model,
                                     load_type='load_weights',
                                     dir=r'.\trained-weights\weights1')
     networks.test_model(model=ann_model,
                         test_data=test_data,
                         test_labels=test_labels)
+    print('Test time is: {}'.format(time.time() - start))

### 2020-03-15 src/main.py
fix

@@ -34,7 +34,7 @@ if __name__ == '__main__':
                 num_examples_to_generate = 8)
     generator = wgan.make_generator_model(num_layers=4)
     critic = wgan.make_critic_model(num_layers=4)
-    #wgan.train_wgan(tr_data,tr_labels,epochs = 200, generator=generator, critic=critic)
+    wgan.train_wgan(tr_data,tr_labels,epochs = 2000, generator=generator, critic=critic)
     print('Training time for the wgan is: {} sec'.format(time.time() - start))
 
     # TRAIN ANN MODEL

### 2020-03-15 src/networks.py

@@ -83,7 +83,7 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
     plt.plot(va_labels, va_labels, 'r')       #
     plt.grid()                                #
     plt.title('epochs {}; '                   #
-              'length of dataset {}\n ; '     # 
+              'length of dataset {}\n ; '     #
               'TR LOSS {}\n; Test MSE {}'     #
               .format(epochs,                 #
                       int(len(tr_data)),      #
@@ -176,10 +176,11 @@ class Wgan(object):
         for _ in range(num_layers):
             model.add(layers.Dense(self.BATCH_SIZE * (2 ** 2)))
             model.add(layers.BatchNormalization())
-            model.add(layers.LeakyReLU())
+            model.add(layers.ReLU())
 
         # OUTPUT layer
-        model.add(layers.Dense(self.noise_dim, activation='relu'))
+        model.add(layers.Dense(self.noise_dim))
+        model.add(layers.ReLU())
 
         return model
 

### 2020-03-15 src/data_handler.py
update: putting-all-together

@@ -54,31 +54,28 @@ def load_data(fname='.\data\data.xlsx'):
     return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
 
 # Augment data
-def augment_data(tr_data, tr_labels, size=1000, fname='.\gen_data\gen_data.txt'):
+def augment_data(tr_data, tr_labels, size, fname='.\gen_data\gen_data.txt'):
 
-    #generated_data = pd.read_csv(fname).values
-    generated_data = sp.genfromtxt('fname', delimiter='\t\t')
+    generated_data = pd.read_csv(fname).values
+
+    start_slice = size-1000
+    print(len(tr_data))
 
     if(size == 0):
         return [tr_data, tr_labels]
 
     #OUR data
-    if(fname=='gen_data'):
-        gen_x = generated_data[:size, :6]
+    gen_x = generated_data[start_slice:size, :6].reshape(1000,6)
 
     #THEIR data
     if(fname=='gen_data_pcf'):
-        gen_x = generated_data[:size, :4]
+        gen_x = generated_data[start_slice:size, :4].reshape(1000,4)
 
-    gen_y = generated_data[:size, -1]
+    gen_y = generated_data[start_slice:size, -1].reshape(1000,1)
 
     # Concatenate arrays
     tr_labels = sp.concatenate((tr_labels, gen_y), axis=0)
     tr_data = sp.concatenate((tr_data, gen_x), axis=0)
-
-    # Assert shape
-    tr_data = sp.array([x.reshape(6, ) for x in tr_data]).reshape(int(len(tr_data)), 6)
-    tr_labels = sp.array([y.reshape(1, ) for y in tr_labels]).reshape(int(len(tr_data)))
 
     return [tr_data, tr_labels]
 

### 2020-03-15 src/main.py

@@ -24,7 +24,7 @@ chkdir = r'.\trained-weights\weights1.hdf5'
 if __name__ == '__main__':
     # PLEASE TRAIN the ANN and WGAN seperately !
 
-    # TRAIN WGAN
+    # 1. TRAIN WGAN
     start = time.time()
     wgan = Wgan(BATCH_SIZE = 12,
                 noise_dim = 7,
@@ -34,10 +34,20 @@ if __name__ == '__main__':
                 num_examples_to_generate = 8)
     generator = wgan.make_generator_model(num_layers=4)
     critic = wgan.make_critic_model(num_layers=4)
-    wgan.train_wgan(tr_data,tr_labels,epochs = 2000, generator=generator, critic=critic)
-    print('Training time for the wgan is: {} sec'.format(time.time() - start))
 
-    # TRAIN ANN MODEL
+    wgan.train_wgan(tr_data,tr_labels,epochs = 2000, generator=generator, critic=critic)
+
+    print('Training run time for the wgan is: {} sec'.format(time.time() - start))
+
+    # 2. GENERATE DATA
+    #########################################################################################
+    start = time.time()                                                                     #
+    # WILL SAVE TO gen_data\gen_data2.txt // Data already generated in gen_data\gen_data.txt#
+    wgan.generate_and_save_data(iterations = 1000,training=False, generator=generator)      #
+    print('Generation run time is: {} sec'.format(time.time() - start))                     #
+    #########################################################################################
+
+    # 3. TRAIN ANN MODEL/Augment data
     ann_model = networks.make_model(num_layers=5,
                                     num_inputs=6,
                                     num_outputs=1,
@@ -53,17 +63,17 @@ if __name__ == '__main__':
                              va_data=va_data,
                              va_labels=va_labels,
                              save_dir=r'.\trained-nets\model{}.h5'.format(augment_size),
-                             chkdir=r'.\trained-weights\weights.hdf5'.format(augment_size)
+                             chkdir=r'.\trained-weights\weights{}.hdf5'.format(augment_size)
                              )
-        print('Training time for data set length {} is : {} sec'.format(336+augment_size, time.time() - start))
+        print('Training run time for data set length {} is : {} sec'.format(336+augment_size, time.time() - start))
 
-    # TEST
+    # 4. TEST
     # LOAD_TYPE = load the whole model or load the best checkpoint(load weights)
     start = time.time()
     ann_model = networks.load_model(model=ann_model,
                                     load_type='load_weights',
[…]

### 2020-03-15 src/networks.py

@@ -74,27 +74,10 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
                      validation_data=(va_data, va_labels), callbacks=[tensorboard_callback, checkpointer])
     # Post training
     model.save(save_dir)
-    loss = hist.history['loss']
-    epochsArr = sp.arange(epochs)
-    predictions = model.predict([va_data])
-    MSE = sp.square(sp.subtract(va_labels, predictions)).mean()
-    ### Plot predictions vs validation ########
-    plt.scatter(va_labels, predictions)       #
-    plt.plot(va_labels, va_labels, 'r')       #
-    plt.grid()                                #
-    plt.title('epochs {}; '                   #
-              'length of dataset {}\n ; '     #
-              'TR LOSS {}\n; Test MSE {}'     #
-              .format(epochs,                 #
-                      int(len(tr_data)),      #
-                      loss[-1], MSE))         #
-    plt.show()                                #
-    ### TR loss vs epochs #####################
-    plt.plot(epochsArr, loss, 'r')            #
-    plt.grid()                                #
-    plt.show()                                #
-    ############# Graphs ######################
-    ###########################################
+    #loss = hist.history['loss']
+    #epochsArr = sp.arange(epochs)
+    #predictions = model.predict([va_data])
+    #MSE = sp.square(sp.subtract(va_labels, predictions)).mean()
 
 def load_model(model,load_type,dir):
     if load_type == 'load_weights':
@@ -300,19 +283,20 @@ class Wgan(object):
 
             print('Time for epoch {} is {} sec'.format(epoch + 1, time.time() - start))
 
-    def generate_and_save_data(self,training, generator):
-        seed = tf.random.normal([self.num_examples_to_generate, self.noise_dim])
-        predictions = generator(seed, training=training)
-        if (training == False):
-            for p in predictions:
-                # Noise filter
-                ones = sum(int(o >= 1.0) for o in p[:6])
-                zeros = sum(int(z < 0.1) for z in p)
-                # sp.savetxt(r'gen_data_pcf.txt', p, delimiter=',')
-                if(ones == 0 and zeros == 0):
-                    file = open('gen_data_pcf.txt', 'a+')
-                    file.write('{},{},{},{},{}\n'.format(p[0], p[1], p[2], p[3], p[4]))
-                    file.close()
+    def generate_and_save_data(self,iterations,training, generator):
+        for _ in range(iterations):
[…]

### 2020-03-15 src/data_handler.py
fix: logging

@@ -59,7 +59,6 @@ def augment_data(tr_data, tr_labels, size, fname='.\gen_data\gen_data.txt'):
     generated_data = pd.read_csv(fname).values
 
     start_slice = size-1000
-    print(len(tr_data))
 
     if(size == 0):
         return [tr_data, tr_labels]

### 2020-03-15 src/main.py

@@ -2,9 +2,6 @@ import networks, data_handler
 from networks import Wgan
 import time
 
-# Size of data augmentation
-AUGMENT_SIZE = 1000
-
 # Load Original data
 # OUR SPR PHOTONIC SENSOR
 tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
@@ -37,14 +34,14 @@ if __name__ == '__main__':
 
     wgan.train_wgan(tr_data,tr_labels,epochs = 2000, generator=generator, critic=critic)
 
-    print('Training run time for the wgan is: {} sec'.format(time.time() - start))
+    print('\n*****\nTraining run time for the wgan is: {} sec\n****\n'.format(time.time() - start))
 
     # 2. GENERATE DATA
     #########################################################################################
     start = time.time()                                                                     #
     # WILL SAVE TO gen_data\gen_data2.txt // Data already generated in gen_data\gen_data.txt#
-    wgan.generate_and_save_data(iterations = 1000,training=False, generator=generator)      #
-    print('Generation run time is: {} sec'.format(time.time() - start))                     #
+    wgan.generate_and_save_data(iterations = 1000,training=False, generator=generator)       #
+    print('\n*****\nGeneration run time is: {} sec\n*****'.format(time.time() - start))
     #########################################################################################
 
     # 3. TRAIN ANN MODEL/Augment data
@@ -55,6 +52,7 @@ if __name__ == '__main__':
 
     for augment_size in [0,1000,2000,3000]:
         tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, augment_size, fname='.\gen_data\gen_data.txt')
+        print('\n\n Training on {} samples \n\n'.format(int(len(tr_data))))
         start = time.time()
         networks.train_model(model = ann_model,
                              epochs=2000,
@@ -65,15 +63,15 @@ if __name__ == '__main__':
                              save_dir=r'.\trained-nets\model{}.h5'.format(augment_size),
                              chkdir=r'.\trained-weights\weights{}.hdf5'.format(augment_size)
                              )
-        print('Training run time for data set length {} is : {} sec'.format(336+augment_size, time.time() - start))
+        print('\n*****\nTraining run time for data set length {} is : {} sec\n*****'.format(336+augment_size, time.time() - start))
 
     # 4. TEST
     # LOAD_TYPE = load the whole model or load the best checkpoint(load weights)
     start = time.time()
[…]

### 2020-03-15 src/networks.py

@@ -51,7 +51,7 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
     tensorboard_callback = keras.callbacks.TensorBoard(log_dir=logdir)
 
     # Save the best va_loss file
-    checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=1,
+    checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=0,
                                                    save_best_only=True)
 
     data_size = int(len(tr_data))
@@ -70,8 +70,8 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
     RMSprop = keras.optimizers.RMSprop(learning_rate=1e-2, rho=0.9)
     # Train
     model.compile(optimizer=Adam, loss='mean_squared_error', batch_size=batch_size)
-    hist = model.fit(tr_data, tr_labels, epochs=epochs, verbose=2,
-                     validation_data=(va_data, va_labels), callbacks=[tensorboard_callback, checkpointer])
+    hist = model.fit(tr_data, tr_labels, epochs=epochs, verbose=0,
+                     validation_data=(va_data, va_labels), callbacks=[checkpointer])
     # Post training
     model.save(save_dir)
     #loss = hist.history['loss']
@@ -94,7 +94,7 @@ def test_model(model, test_data, test_labels, len_tr_data=0):
 
     plt.scatter(test_labels, predictions, label='Predictions', c='red', alpha=0.5)
     plt.plot(test_labels, test_labels, label='Actual', c='green', alpha=0.7)
-    legend = plt.legend(loc='left center', shadow=True, fontsize='large')
+    legend = plt.legend(loc='upper left', shadow=True, fontsize='large')
     legend.get_frame().set_facecolor('C7')
     plt.ylabel('Prediction Log10(loss)')
     plt.xlabel('Actual Log10(loss)')
@@ -104,15 +104,13 @@ def test_model(model, test_data, test_labels, len_tr_data=0):
 
     wavelength = sp.arange(500,820,20)
     for i in [0,16,32]:
-        print(len(predictions[i:i+16]))
-        print(len(wavelength))
         spl = UnivariateSpline(wavelength, predictions[i:i+16])
         wavelength_smoothed = sp.linspace(500,820,500)
         pr_smoothed = spl(wavelength_smoothed)
[…]

### 2020-03-15 src/main.py
fix: gan-checkpoints

@@ -40,7 +40,7 @@ if __name__ == '__main__':
     #########################################################################################
     start = time.time()                                                                     #
     # WILL SAVE TO gen_data\gen_data2.txt // Data already generated in gen_data\gen_data.txt#
-    wgan.generate_and_save_data(iterations = 1000,training=False, generator=generator)       #
+    wgan.generate_and_save_data(iterations = 1000,training=False, generator=generator, critic=critic)       #
     print('\n*****\nGeneration run time is: {} sec\n*****'.format(time.time() - start))
     #########################################################################################
 

### 2020-03-15 src/networks.py

@@ -274,13 +274,19 @@ class Wgan(object):
             # Generate and save data
             # generate_and_save_data(generator,seed,training=False)
             # Plot generated data vs wavelength each 200 epoch
-            if (epoch + 1) % 200 == 0:
+            if (epoch + 1) % 2 == 0:
                 # data_handler.plot_wgan(epoch + 1)
                 checkpoint.save(file_prefix=checkpoint_prefix)
 
             print('Time for epoch {} is {} sec'.format(epoch + 1, time.time() - start))
 
-    def generate_and_save_data(self,iterations,training, generator):
+    def generate_and_save_data(self,iterations,training, generator, critic):
+        checkpoint_dir = './training_checkpoints'
+        checkpoint = tf.train.Checkpoint(generator_optimizer=self.generator_optimizer,
+                                         discriminator_optimizer=self.critic_optimizer,
+                                         generator=generator,
+                                         discriminator=critic)
+        checkpoint.restore(tf.train.latest_checkpoint(checkpoint_dir))
         for _ in range(iterations):
             seed = tf.random.normal([self.num_examples_to_generate, self.noise_dim])
             predictions = generator(seed, training=training)

### 2020-03-16 docs/paper/paper.tex
updata: comp-performance

@@
     & data set size & mini batch size & Time elapsed (sec) \\
-Mini batches    &336 + 0 & 8 & 136 & \\
-    &336 + 1000 & 8 & 388 & \\
-    &336 + 2000 & 16 & 563  & \\ 
-    &336 + 3000 & 20 & 958  & \\
+Mini batches    &336 + 0 & 8 & 214 & \\
+    &336 + 1000 & 8 & 744 & \\
+    &336 + 2000 & 16 & 685  & \\ 
+    &336 + 3000 & 20 & 861  & \\
 \end{tabular}
@@
    & data set size & Time elapsed (sec) \\
-Full batch    &336 + 0 &  96 & \\
-    &336 + 1000 &  162 & \\
-    &336 + 2000 &  165 & \\ 
-    &336 + 3000 &  263 & \\
+Full batch    &336 + 0 &  23 & \\
+    &336 + 1000 &  34 & \\
+    &336 + 2000 &  45 & \\ 
+    &336 + 3000 &  57 & \\
 \end{tabular}
-\caption{Training performance using Tensorflow/Keras}
+\caption{Training performance using Tensorflow(Keras)}
 \end{table}
@@
  & data set size & mini batch size & Time elapsed (sec) \\
-Mini batches    & 336 + 0 & 8 & 359 & \\
-    & 336 + 1000 & 8 & 1348  & \\
-    & 336 + 2000 & 16 & 1379  & \\ 
-    & 336 + 3000 & 20 & 1504 & \\
+Mini batches    & 336 + 0 & 8 & 1315 & \\
+    & 336 + 1000 & 8 & 6453  & \\
+    & 336 + 2000 & 16 & 4751  & \\ 
+    & 336 + 3000 & 20 & 5132 & \\
 \end{tabular}
@@
    &data set size & Time (sec) \\
-   Full batch &336 + 0 &  14  & \\
-    & 336 + 1000 &  57  & \\
-    & 336 + 2000 &  107  & \\ 
-    & 336 + 3000 &  195  & \\
+   Full batch &336 + 0 &  36  & \\
+    & 336 + 1000 &  98  & \\
+    & 336 + 2000 &  195  & \\ 
+    & 336 + 3000 &  336  & \\
 \end{tabular}

### 2020-03-16 src/main.py
update: test-runtime

@@ -71,7 +71,8 @@ if __name__ == '__main__':
     ann_model = networks.load_model(model=ann_model,
                                     load_type='load_weights',
                                     dir=r'.\trained-weights\weights1000.hdf5')
-    networks.test_model(model=ann_model,
+    predictions = networks.test_model(model=ann_model,
                         test_data=test_data,
-                        test_labels=test_labels)
+                        test_labels=test_labels,
+                        plot = False)
     print('\n*****\nTest run time of the ANN model is: {}\n*****\n'.format(time.time() - start))

### 2020-03-16 src/networks.py

@@ -69,9 +69,9 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
     Adam = keras.optimizers.Adam(learning_rate=lr, beta_1=0.9, beta_2=0.999)
     RMSprop = keras.optimizers.RMSprop(learning_rate=1e-2, rho=0.9)
     # Train
-    model.compile(optimizer=Adam, loss='mean_squared_error', batch_size=batch_size)
+    model.compile(optimizer=Adam, loss='mean_squared_error')
     hist = model.fit(tr_data, tr_labels, epochs=epochs, verbose=0,
-                     validation_data=(va_data, va_labels), callbacks=[checkpointer])
+                     validation_data=(va_data, va_labels), callbacks=[checkpointer], batch_size=batch_size)
     # Post training
     model.save(save_dir)
     #loss = hist.history['loss']
@@ -88,35 +88,37 @@ def load_model(model,load_type,dir):
 
     return model
 
-def test_model(model, test_data, test_labels, len_tr_data=0):
+def test_model(model, test_data, test_labels, len_tr_data=0, plot=True):
     predictions = model.predict([test_data])
     #MSE = sp.square(sp.subtract(test_labels, predictions)).mean()
-
-    plt.scatter(test_labels, predictions, label='Predictions', c='red', alpha=0.5)
-    plt.plot(test_labels, test_labels, label='Actual', c='green', alpha=0.7)
-    legend = plt.legend(loc='upper left', shadow=True, fontsize='large')
-    legend.get_frame().set_facecolor('C7')
-    plt.ylabel('Prediction Log10(loss)')
-    plt.xlabel('Actual Log10(loss)')
-    plt.grid()
-    plt.title('Length of TR dataset 336 + {}'.format(len_tr_data))
-    plt.show()
-
-    wavelength = sp.arange(500,820,20)
-    for i in [0,16,32]:
-        spl = UnivariateSpline(wavelength, predictions[i:i+16])
-        wavelength_smoothed = sp.linspace(500,820,500)
-        pr_smoothed = spl(wavelength_smoothed)
-        spl.set_smoothing_factor(0.5)
-        plt.plot(wavelength_smoothed, pr_smoothed, label='Predictions', c='black', lw=2)
-        plt.scatter(wavelength, test_labels[i:i+16], label='Actual', c='red', alpha=0.7,marker='o')
+    if plot == True:
[…]

### 2020-03-17 docs/paper/paper.tex
update: test-runtime
update-doc: ANN/GAN-arch

@@
 \begin{abstract}
-Our aim is to surpass the performance of the simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate a Surface Plasmon Reasonance (SPR) based Photonic Crystal Fiber (PCF) sensor performance, using deep learning models.
-By these simulation techniques one must calculate the confinement loss for a specific wavelength and a particular set of geometric properties of the PCF sensor, then repeat the process for different analytes.
-In order to find the best fit distribution we have to make as much calculations per wavelength as possible to ensure the correct location of the peak value of the confinement loss.
+Our aim is to propose a deep learning approach that surpasses simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) used to design, optimise and evaluate a Surface Plasmon Reasonance (SPR) based Photonic Crystal Fiber (PCF) sensor performance.
+Through these simulation techniques one must calculate the confinement loss for a specific wavelength and a particular set of geometric properties of the PCF sensor, then repeat the process for different analytes.
+To eventually find the best set of geometric properties that maximises the distance between the confinement loss distributions of different analytes, and thus find the most sensible PCF sensor.
+In order to find these distributions we have to make as much calculations per wavelength as possible to ensure the correct location of the peak value of the confinement loss.
 Simulation methods are not only time costing and daunting, consuming hours to days, but also inaccurate sometimes.
-In contrast, a deep neural network model astonishingly performs calculations in under a second, quiet accurately.
+In contrast, a deep neural network model astonishingly performs these calculations in milliseconds to seconds, quiet accurately, when it is well trained with an accurate data set.
 
@@
 \label{ssec:ann}
-The ANN model is a fully-connected feed-forward MLP (Multi Layer Perceptron), consisting of an input layer, an output layer, 5 hidden layers, and 50 neurons for each hidden layer.
-Taking ReLU (Rectified Linear Unit) as the activation function, Adam [13] as the optimizer and the mean squared error as the loss/cost function.
+The ANN model is a fully-connected feed-forward MLP (Multi Layer Perceptron).
+Table(num) summarizes the details of the model consisting of an input layer.
 To reduce over fitting we use the Early stopping method, by saving checkpoints where the best validation mean squared error occurred as we iterate before the model starts to over fit.
 To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm [14] was used.
+
+\begin{table}[h]
+\centering
+\scalebox{1.1}{
+    \begin{tabular}{|l|l|}
+    \hline
+Number of hidden layers & 5  \\
+\hline
+Number of neurons per hidden layers & 50  \\
+\hline
+Activation function & Rectified Linear Unit (ReLU)  \\
+\hline
+Optimizer & Adam[13]  \\
+\hline
+Loss function& Mean Squared Error (MSE) \\
+\hline
+    \end{tabular}
+}
+\caption{Detailes of the ANN model}
+\end{table}
 
@@
 Whereas the second network is referred to as the generator, which outputs data samples from a random noise vector called a latent variable usually given the symbol $z$ supplied at its input.
-The error between the discriminator's output and the actual labels (The real data samples vectors all labelled as 1: the probability of being real) would then be measured by the means of a chosen metric.
+The error at the discriminator's output would then be measured by the means of a chosen metric.
 Introduced by Arjovsky et al [15] the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
@@
 The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.
-The WGAN-GP architecture chosen in this work is as follows: both the Critic and the generator networks are a fully-connected feed-forward MLP, having 4 hidden layers, with $ minibatchsize\times2^{number of layers} $ neurons for each hidden layer in the critic network, whereas $ minibatchsize\times2^{2} $ neurons for each hidden layer in the generator network.
-The input vector for the Critic network consists of the six parameters discussed earlier for the ANN model, in addition the corresponding loss value, giving a total of seven inputs.
-The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the critic network.
-LeakyReLU and ReLU were chosen as the activation functions for the Critic and Generator respectively and Adam as the optimizer for both networks.
-Finally Batch Normalization technique was applied to the Generator.
+In this work, both the Critic and the generator are fully connected feed forward MLP models.
+Tables(num, num) summarize the details of both networks.
+The input vector to the Critic network consists of the six parameters discussed earlier for the ANN model, in addition to the corresponding confinement loss value, giving a total of seven inputs.
+The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the Critic.
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|l|}
+\hline
+Number of hidden layers & 4  \\
+\hline
+Number of neurons per hidden layers & $ minibatchsize\times2^{number of layers} $  \\
+\hline
+Activation function & Leaky Rectified Linear Unit (LeakyReLU)  \\
+\hline
+Optimizer & Adam[13]  \\
+\hline
+    \end{tabular}
+\caption{Details of the Critic model}    
+\end{table}
+
+\begin{table}[h]
+\centering
+ \begin{tabular}{|l|l|}
+    \hline
+Number of hidden layers & 4  \\
+\hline
+Number of neurons per hidden layers & $ minibatchsize\times2^{2} $  \\
+\hline
+Activation function & Rectified Linear Unit (ReLU)  \\
+\hline
+Optimizer & Adam[13]  \\
+\hline
+Normalization & Batch Normalization[14] \\
+\hline
+    \end{tabular}
+\caption{Details of the Generator model}
+\end{table}
 
@@
 
-We train the ANN model for more than 2000 epochs, starting from the original data-set.
-Then we augment the data by 1000 generated samples from our WGAN-GP, which will be demonstrated in the next section.
+We train the ANN model for more than 2000 epochs, starting from the original data set.
+Then we augment the latter set by 1000 generated samples by our WGAN-GP, which will be demonstrated in the next subsection.
 The following table summarizes the hyper-parameters chosen for the ANN model:
@@
     \hline
-Length of the training data-set & Learning rate&Batch size & $\beta_{1}$ & $\beta_{2}$\\
+Length of the training data-set & Learning rate& Mini batch size & $\beta_{1}$ & $\beta_{2}$\\
 \hline
-336 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
+336 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
 \hline
-336 + 1000 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
+336 + 1000 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
 \hline
@@
 \hline
-336 + 3000 & $ 2.5\times10^{-04} $ & 16  & 0.9 & 0.999 \\
+336 + 3000 & $ 2.5\times10^{-04} $ & 20  & 0.9 & 0.999 \\
 \hline
@@
     \newpage
-As you can see, the ANN made somewhat good predictions of the low values of the confinement loss.
-A close inspection into the data samples collected shows that points are concentrated in the low values interval, i.e the ANN picked up the pattern quiet easily.
-However, in the higher values interval, the ANN could not see a pattern because points are distant from each other to some extent, even though we transformed the confinement loss to the log scale to actually minimize these distances.
 
@@
 
-During training the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in figure(num).
-In this sub-section we discuss the results of augmenting the real data set with Synthetic data.
-Figure(num) demonstrates the predictions made by the ANN model after training with different sizes of the Synthetic data set.
-This might seem paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data.
+During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in figure(num).
+In this sub-section we discuss the results of augmenting the real data set with generated samples.
+Figure(num) demonstrates the predictions made by the ANN model after training with different sizes of the data set.
+This might look paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data.
 There are several reasons that is driving our ANN model predictions in the wrong way.
@@
 Or the sampling strategy adopted is poor.
-After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved we set out to accomplish at the beginning, to train an ANN model and make accurate prediction on a never-seen-before data.
+But the most convincing reason is the limited original data set size of 336 samples, used to train the WGAN model in the first place.
+After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved what we set out to accomplish at the beginning, to increase the accuracy of the ANN model by artificially expanding the original set.
 
@@
 
-This work had been conduct on a  laptop having: Intel(R) Core(TM) i7-5600 CPU @2.60GHz (4 CPUs) and 8GB RAM. The code for this work is available at: \url{https://github.com/Aimen-Zelaci/SPRPCF_ANN/}.
+This work had been conduct on a  laptop:
+
+\begin{itemize}
+\item Intel(R) Core(TM) i7-5600 CPU @2.60GHz (4 CPUs)
+\item 8GB RAM
+\item No GPU on board
+\end{itemize}
+
+For comparaison purposes we ran the expirements on a machine with GPU on board:
+
+\hl{CEM PC SPECS}
+
+Epirements conducted on the latter machine will be labeled as GPU based, whereas on the former as CPU based.
+
+By taking advantage of Cloud Computing technology, one does not have to spend large amounts of money to obtain high-specs machine, rather, rent readily available deep learning instances in the cloud for pennies on the dollar.
+
+The code for this work is available at: \url{https://github.com/Aimen-Zelaci/SPRPCF_ANN/}.
 \newline
-The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, batch size, data set size, epochs and framework used to code the model.
-In this work we fixed the number of epochs and executed training using Tensorflow/Keras and Pytorch frameworks, by varying the mini-btach size and the data set size, as demonstrated in Table(num).
-It is worth mentioning the differences between using full batch or mini-batch.
-In full batch training the whole data set is passed to the model for each iteration.
-In contrast, mini-batch training, the data set is split into small mini-batches of equal sizes.
-Previous works [17, 18] have firmly proved the advantages of using the correct mini-batch size as oppose to large batch sizes.
-Training runtime is longer using mini-batches.
-However, mini-batches allow for more frequent gradient calculations, that results in more stable and reliable training.
+The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, mini batch size, data set size, number of epochs, the framework used to code the model, and of course the specifications of the machine.
+In this work we fixed the number of epochs to 2000 and executed training using Tensorflow(Keras) and Pytorch frameworks.
+As demonstrated in Table(num).
+It is worth mentioning the differences between training with full batch or mini batches.
+In full batch training, the whole data set is passed to the model for each iteration.
+In contrast, mini-batch-training, the data set is split into small mini batches of equal sizes, then passed to the model seperately, thus for each epoch there will be exactly length  of the data set devided by the mini batch size steps, and hence slowing down the training process.
+Previous works [17, 18] have firmly proved the advantages of using the correct mini batch size as oppose to large batch sizes.
+Mini batches allow for more frequent gradient calculations, that results in more stable and reliable training.
 Perhaps one of the main downsides of using large batch size is the poor generalization resulting in a phenomena know as the "generalization gap".
 Active research [19] is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime.
-A closely related recent work (Machine learning approach for computing optical properties of a photonic crystal fiber, SUNNY CHUGH, AAMIR GULISTAN, SOUVIK GHOSH, AND B.M.A.
-RAHMAN, DEC 2019), conducted their expirements using full batch to train the model.
-In this works we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications to fit our purposes.
-Finally, we compared the performance of the ANN/WGAN models using CPU and GPU.
-As Table (num) demonstrates, GPU based training outperformes that of CPU based.
-With the emergence of Cloud Computing technology, one can rent GPU based instances of high specs with pennies on the dollar.
+A closely related recent work (Machine learning approach for computing optical properties of a photonic crystal fiber, Sunny Chugh, Aamir Gulistan, Souvik Ghosh, AND B.M.A.
+Rahman, DEC 2019), conducted their expirements using full batch to train the model.
+In this work we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications to fit our purposes.
+Finally, we compare the performance of the WGAN model, using Tensorflow(Keras) framework, of CPU based to that of GPU based.
 
@@
 \end{tabular}
-\caption{Training performance using Tensorflow(Keras)}
+\caption{Training performance using Tensorflow(Keras). CPU based training.}
 \end{table}
@@
 \begin{tabular}{lllll}
-   &data set size & Time (sec) \\
+   &data set size & Time elapsed (sec) \\
    Full batch &336 + 0 &  36  & \\
@@
 \end{tabular}
-\caption{Training performance using Pytorch}
+\caption{Training performance using Pytorch. CPU based training.}
 \end{table}
@@
 Next, we compare the testing runtime of the ANN model to that of simulation methods used to compute the confinement loss for 3 different analytes and 16 wavelenghts, i.e a total of 48 values of the confinement loss, demonstrated in Table(num).
+This result is absolutely staggering.
+The ANN model calculated 16 confinement losses in just 0.17 seconds, while simulations took about 2 hours.
+Therefore, a well trained ANN model can be used to accurately find the best PCF geometric properties set that maximisez the distance between the confinement loss distributions of each analyte in a matter of seconds to minutes.
+Hence, accelerate the search for the best PCF sensor.
 
@@
       \hline
-    ANN &  0.79 sec & \\
+    ANN &  0.17 sec & \\
     \hline

### 2020-03-17 src/networks.py

@@ -62,7 +62,7 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
         lr = 2e-4
         batch_size = 16
     if data_size >= 3000:
-        lr = 20e-4 / 8
+        lr = 2.5e-4
         batch_size = 20
 
     # Define optimizers

### 2020-03-17 docs/paper/paper.tex
fix: doc

@@
 \label{ssec:ann}
-The ANN model is a fully-connected feed-forward MLP (Multi Layer Perceptron).
-Table(num) summarizes the details of the model consisting of an input layer.
+The ANN model is a fully-connected feed-forward Multi Layer Perceptron (MLP) model.
+Table(num) summarizes the details of the model.
 To reduce over fitting we use the Early stopping method, by saving checkpoints where the best validation mean squared error occurred as we iterate before the model starts to over fit.
@@
 
-A labelled data-set of only 432 samples was collected in this work, through simulations using FV-FEM.
-The length of the data-set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent.
-The data-set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
+A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM.
+This length of the data set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent.
+This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
 The labels are the confinement loss of the PCF.
-The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for 3 different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36) [35]).
+The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36) [35]).
 Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing.
@@
 The indices of refraction  are very close, which made it quiet difficult for the neural networks to differentiate between them, after many trials, the best choice was to take only the tens digit of ${134, 135, 136}$, giving ${4, 5, 6}$.
-Finally, we transform the confinement loss to the log scale.
+Finally, we transform the confinement loss to the log scale, for the purpose of shortening the distance between the confinement loss points
 
@@
 We train the ANN model for more than 2000 epochs, starting from the original data set.
-Then we augment the latter set by 1000 generated samples by our WGAN-GP, which will be demonstrated in the next subsection.
+Then we augment the latter set by 1000 generated samples by our WGAN-GP, which will be demonstrated in the next subsection, and train again with the new augmented data set.
 The following table summarizes the hyper-parameters chosen for the ANN model:
@@
 The MSE on the training sets ranged from 0.0030 to 0.0050.
-For all data sets the MSE on the training sets decreased in an acceptable manner.
+For all training data sets the MSE decreased in an acceptable manner.
 Next, we plot the predictions the ANN model made after training using only the original.
@@
 
-During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in figure(num).
-In this sub-section we discuss the results of augmenting the real data set with generated samples.
+During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in Figure(num).
+In this subsection we discuss the results of augmenting the real data set with generated samples.
 Figure(num) demonstrates the predictions made by the ANN model after training with different sizes of the data set.
 This might look paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data.
-There are several reasons that is driving our ANN model predictions in the wrong way.
+There are several reasons for why our ANN model is driven in the wrong direction.
 Even though our WGAN-GP seemed well trained, there still a domain gap between the real data and the generated data, or the expansion of data is growing in the wrong direction to that of entirely containing the real data.
@@
 Or the sampling strategy adopted is poor.
-But the most convincing reason is the limited original data set size of 336 samples, used to train the WGAN model in the first place.
-After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved what we set out to accomplish at the beginning, to increase the accuracy of the ANN model by artificially expanding the original set.
+But the most convincing reason is the limited original training data set size of 336 samples, used to train the WGAN model in the first place.
+After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved what we set out to accomplish at the beginning, to improve the accuracy of the ANN model by artificially expanding the original set.
 
@@
 \newpage
-It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in figure(num).
+It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(num).
 

### 2020-03-17 docs/paper/paper.tex
fix: doc

@@
 
-Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing the human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
+Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
 Artificial Neural Networks can approximate any function by virtue of the Universality theorem: No matter what the input is there is to be a guaranteed ANN architecture that computes the desired outputs.
@@
 Hence, active researches are ongoing to find ways to optimally sample the generated data [12], in other words to filter out the "good" generated data after training the GAN.
-In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
+In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables, and the confinement loss.
 In the following sub-sections we discuss the networks architectures.
@@
 The indices of refraction  are very close, which made it quiet difficult for the neural networks to differentiate between them, after many trials, the best choice was to take only the tens digit of ${134, 135, 136}$, giving ${4, 5, 6}$.
-Finally, we transform the confinement loss to the log scale, for the purpose of shortening the distance between the confinement loss points
+Finally, we transform the confinement loss to the log scale, for the purpose of shortening the distances between the confinement loss points.
 
@@
 For all training data sets the MSE decreased in an acceptable manner.
-Next, we plot the predictions the ANN model made after training using only the original.
-As shown in the following figure data-set.
+Next, we plot the predictions the ANN model made on the test set, after training using only the original set.
+As shown in the following figure.
 
@@
 It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(num).
-
+The most important result in these experiments is that the ANN model predicted the correct location of the peak value of the confinement loss distributions for the three different analytes used. 
 \begin{figure}
@@
 This result is absolutely staggering.
-The ANN model calculated 16 confinement losses in just 0.17 seconds, while simulations took about 2 hours.
+The ANN model calculated 48 confinement losses in just 0.17 seconds, while simulations took about 2 hours.
 Therefore, a well trained ANN model can be used to accurately find the best PCF geometric properties set that maximisez the distance between the confinement loss distributions of each analyte in a matter of seconds to minutes.

### 2020-03-18 docs/paper/paper.tex
fix: num_layers: new-tf

@@
 \begin{abstract}
-Our aim is to propose a deep learning approach that surpasses simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) used to design, optimise and evaluate a Surface Plasmon Reasonance (SPR) based Photonic Crystal Fiber (PCF) sensor performance.
+Our aim is to propose a deep learning approach that surpasses simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) used to design, optimise and evaluate a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR) structure performance, proposed in our recent work.
 Through these simulation techniques one must calculate the confinement loss for a specific wavelength and a particular set of geometric properties of the PCF sensor, then repeat the process for different analytes.
@@
 Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [4], proved to be successful in data generation [5, 6, 7, 8, 9].
-In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
+In this paper we focus on determining one of the propagation features of a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), proposed in our recent work [21], that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
 
@@
     \hline
-Number of hidden layers & 5  \\
+Number of hidden layers & 6  \\
 \hline
@@
 \hline
-Number of hidden layers & 4  \\
+Number of hidden layers & 5  \\
 \hline
@@
     \hline
-Number of hidden layers & 4  \\
+Number of hidden layers & 5 \\
 \hline

### 2020-03-18 src/data_handler.py

@@ -6,6 +6,8 @@ def load_pcf_data(fname='.\data\pcf_data1.xlsx'):
     df_1 = pd.read_excel(fname)
     datafile_1 = df_1.values
 
+    sp.random.shuffle(datafile_1)
+
     tr_data = datafile_1[:1000,2:6].reshape(1000,4)
     tr_labels = datafile_1[:1000,-1].reshape(1000,1)
 
@@ -51,7 +53,12 @@ def load_data(fname='.\data\data.xlsx'):
     test_data = x[-1].reshape(1*16*3,6)
     test_labels = y[-1].reshape(1*16*3,1)
 
+    # Save shuffled data frame
+    df = pd.DataFrame(df, index = None)
+    df.to_excel(r'.\data\shuffled_df.xlsx')
+
     return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
+
 
 # Augment data
 def augment_data(tr_data, tr_labels, size, fname='.\gen_data\gen_data.txt'):

### 2020-03-18 src/main.py

@@ -29,8 +29,8 @@ if __name__ == '__main__':
                 n_critic = 5,
                 grad_penalty_weight = 10,
                 num_examples_to_generate = 8)
-    generator = wgan.make_generator_model(num_layers=4)
-    critic = wgan.make_critic_model(num_layers=4)
+    generator = wgan.make_generator_model(num_layers=5)
+    critic = wgan.make_critic_model(num_layers=5)
 
     wgan.train_wgan(tr_data,tr_labels,epochs = 2000, generator=generator, critic=critic)
 
@@ -45,14 +45,16 @@ if __name__ == '__main__':
     #########################################################################################
 
     # 3. TRAIN ANN MODEL/Augment data
-    ann_model = networks.make_model(num_layers=5,
+    for augment_size in [0,1000,2000,3000]:
+
+        ann_model = networks.make_model(num_layers=6,
                                     num_inputs=6,
                                     num_outputs=1,
                                     num_neurons=50)
-
-    for augment_size in [0,1000,2000,3000]:
         tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, augment_size, fname='.\gen_data\gen_data.txt')
+
         print('\n\n Training on {} samples \n\n'.format(int(len(tr_data))))
+
         start = time.time()
         networks.train_model(model = ann_model,
                              epochs=2000,

### 2020-03-18 src/networks.py

@@ -19,15 +19,15 @@ tf.compat.v1.enable_eager_execution()
 ####################################################################################
 ####################################################################################
 
-def make_model(num_layers=5, num_neurons=50, num_inputs=6, num_outputs=1):
+def make_model(num_layers=6, num_neurons=50, num_inputs=6, num_outputs=1):
     model = tf.keras.Sequential()
 
-    # INPUT layer
+    # 1st layer
     model.add(layers.Dense(num_neurons, input_shape=(num_inputs,)))
     model.add(layers.ReLU())
 
     # Hidden layers
-    for _ in range(num_layers):
+    for _ in range(num_layers - 1):
         model.add(layers.Dense(num_neurons))
         model.add(layers.BatchNormalization())
         model.add(layers.ReLU())
@@ -147,16 +147,16 @@ class Wgan(object):
         self.critic_optimizer = critic_optimizer
         self.generator_optimizer = generator_optimizer
 
-    def make_generator_model(self, num_layers = 4):
+    def make_generator_model(self, num_layers = 5):
         model = tf.keras.Sequential()
 
-        # INPUT layer
+        # 1st layer
         model.add(layers.Dense(self.BATCH_SIZE * (2 ** 2), input_shape=(self.noise_dim,)))
         model.add(layers.BatchNormalization())
         model.add(layers.LeakyReLU())
 
         # HIDDEN layers
-        for _ in range(num_layers):
+        for _ in range(num_layers - 1):
             model.add(layers.Dense(self.BATCH_SIZE * (2 ** 2)))
             model.add(layers.BatchNormalization())
             model.add(layers.ReLU())
@@ -167,16 +167,16 @@ class Wgan(object):
 
         return model
 
-    def make_critic_model(self, num_layers = 4):
+    def make_critic_model(self, num_layers = 5):
         model = tf.keras.Sequential()
 
-        # INPUT layer
+        # 1st layer
         model.add(layers.Dense(self.BATCH_SIZE * (2 ** 2), input_shape=(self.num_critic_input,)))
         model.add(layers.LeakyReLU())
 
         # HIDDEN LAYERS
         i = 2
-        for _ in range(num_layers):
+        for _ in range(num_layers - 1):
             model.add(layers.Dense(self.BATCH_SIZE * (2 ** i)))
             model.add(layers.LeakyReLU())
             i-=1

### 2020-03-18 src/tf_ann.py

@@ -1,0 +1,117 @@
+from __future__ import print_function
+import data_handler
+# Import MNIST data
+import tensorflow.compat.v1 as tf
+import scipy as sp
+import time
+import matplotlib.pyplot as plt
+from tensorflow.python.client import device_lib
+
+tf.disable_eager_execution()
+
+# Print CPUs / GPUs available
+print(device_lib.list_local_devices())
+
+
+# Load data
+tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
+
+# Augment
+
+#tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, 1000, fname='.\gen_data\gen_data.txt')
+
+# Parameters
+learning_rate = 0.0001
+training_epochs = 200
+batch_size = 8
+
+# Network Parameters
+n_hidden = 50
+n_input = 6
+n_outputs = 1
+num_hidden_layers = 6
+
+# Initializers
+sigma = 1
+weight_initializer = tf.variance_scaling_initializer(mode="fan_avg", distribution="uniform", scale=sigma)
+bias_initializer = tf.zeros_initializer()
+
+
+def initializer():
+    weights = {
+        'h1': tf.Variable(weight_initializer([n_input, n_hidden])),
+        'out': tf.Variable(weight_initializer([n_hidden, n_outputs]))
+    }
+    biases = {
+        'b1': tf.Variable(bias_initializer([n_hidden])),
+        'out': tf.Variable(bias_initializer([n_outputs]))
+    }
+
+    # Create hidden layers
+    for i in range(1,num_hidden_layers):
+        weights['h{}'.format(i+1)] = tf.Variable(weight_initializer([n_hidden, n_hidden]))
+        biases['b{}'.format(i+1)] = tf.Variable(bias_initializer([n_outputs]))
+
+    return [weights, biases]
+
+weights, biases = initializer()
+
+# Create model
+def multilayer_perceptron(x, weights, biases):
+    in_x = tf.add(tf.matmul(x, weights['h1']), biases['b1'])
+    in_x = tf.nn.relu(in_x)
+    in_x = tf.layers.batch_normalization(in_x)
+
+    for i in range(1,num_hidden_layers):
+        in_x = tf.add(tf.matmul(in_x, weights['h{}'.format(i+1)]), biases['b{}'.format(i+1)])
+        in_x = tf.nn.relu(in_x)
+        in_x = tf.layers.batch_normalization(in_x)
+
[…]

### 2020-03-18 src/tf_ann.py
fix: remove-comment

@@ -1,6 +1,5 @@
 from __future__ import print_function
 import data_handler
-# Import MNIST data
 import tensorflow.compat.v1 as tf
 import scipy as sp
 import time

### 2020-03-18 src/data_handler.py
update: save-generated with pandas

@@ -1,4 +1,5 @@
 import scipy as sp
+import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 
@@ -80,8 +81,8 @@ def augment_data(tr_data, tr_labels, size, fname='.\gen_data\gen_data.txt'):
     gen_y = generated_data[start_slice:size, -1].reshape(1000,1)
 
     # Concatenate arrays
-    tr_labels = sp.concatenate((tr_labels, gen_y), axis=0)
-    tr_data = sp.concatenate((tr_data, gen_x), axis=0)
+    tr_labels = np.concatenate((tr_labels, gen_y), axis=0)
+    tr_data = np.concatenate((tr_data, gen_x), axis=0)
 
     return [tr_data, tr_labels]
 

### 2020-03-18 src/main.py

@@ -3,7 +3,7 @@ from networks import Wgan
 import time
 
 # Load Original data
-# OUR SPR PHOTONIC SENSOR
+# OUR SPR BASED PHOTONIC SENSOR
 tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
 
 # THEIR PCF DATA
@@ -12,7 +12,6 @@ tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.lo
 # Augment data after training the wgan
 # To augment our data use fname = '.\gen_data\gen_data.txt'
 # To augment their data use fname = '.\gen_data\gen_data_pcf.txt'
-#tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, AUGMENT_SIZE, fname='.\gen_data\gen_data_pcf.txt')
 
 # Save / Checkpoint directory
 save_dir = r'.\trained-nets\model1.h5'
@@ -20,15 +19,16 @@ chkdir = r'.\trained-weights\weights1.hdf5'
 
 if __name__ == '__main__':
     # PLEASE TRAIN the ANN and WGAN seperately !
-
     # 1. TRAIN WGAN
     start = time.time()
+    print('\n*****\nTraining The WGAN  \n****\n')
     wgan = Wgan(BATCH_SIZE = 12,
                 noise_dim = 7,
                 num_critic_input = 7,
                 n_critic = 5,
                 grad_penalty_weight = 10,
                 num_examples_to_generate = 8)
+
     generator = wgan.make_generator_model(num_layers=5)
     critic = wgan.make_critic_model(num_layers=5)
 
@@ -38,9 +38,10 @@ if __name__ == '__main__':
 
     # 2. GENERATE DATA
     #########################################################################################
+    print('\n*****\n GENERATING DATA ... \n****\n')
     start = time.time()                                                                     #
     # WILL SAVE TO gen_data\gen_data2.txt // Data already generated in gen_data\gen_data.txt#
-    wgan.generate_and_save_data(iterations = 1000,training=False, generator=generator, critic=critic)       #
+    wgan.generate_and_save_data(iterations = 1000, training=False, generator=generator, critic=critic)
     print('\n*****\nGeneration run time is: {} sec\n*****'.format(time.time() - start))
     #########################################################################################
 
@@ -53,7 +54,7 @@ if __name__ == '__main__':
                                     num_neurons=50)
[…]

### 2020-03-18 src/networks.py

@@ -2,7 +2,9 @@
 from __future__ import absolute_import, division, print_function, unicode_literals
 from tensorflow import keras
 from tensorflow.keras import layers
+import numpy as np
 import scipy as sp
+import pandas as pd
 import tensorflow as tf
 import matplotlib.pyplot as plt
 import time
@@ -70,12 +72,12 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
     RMSprop = keras.optimizers.RMSprop(learning_rate=1e-2, rho=0.9)
     # Train
     model.compile(optimizer=Adam, loss='mean_squared_error')
-    hist = model.fit(tr_data, tr_labels, epochs=epochs, verbose=0,
+    hist = model.fit(tr_data, tr_labels, epochs=epochs, verbose=1,
                      validation_data=(va_data, va_labels), callbacks=[checkpointer], batch_size=batch_size)
     # Post training
     model.save(save_dir)
     #loss = hist.history['loss']
-    #epochsArr = sp.arange(epochs)
+    #epochsArr = np.arange(epochs)
     #predictions = model.predict([va_data])
     #MSE = sp.square(sp.subtract(va_labels, predictions)).mean()
 
@@ -289,6 +291,9 @@ class Wgan(object):
                                          generator=generator,
                                          discriminator=critic)
         checkpoint.restore(tf.train.latest_checkpoint(checkpoint_dir))
+
+        _df = sp.zeros(7).reshape(1,7)
+
         for _ in range(iterations):
             seed = tf.random.normal([self.num_examples_to_generate, self.noise_dim])
             predictions = generator(seed, training=training)
@@ -299,9 +304,10 @@ class Wgan(object):
                     zeros = sum(int(z < 0.1) for z in p)
                     # sp.savetxt(r'gen_data_pcf.txt', p, delimiter=',')
                     if(ones == 0 and zeros == 0):
-                        file = open(r'.\gen_data\gen_data2.txt', 'a+')
-                        file.write('{},{},{},{},{}\n'.format(p[0], p[1], p[2], p[3], p[4], p[5], p[6]))
-                        file.close()
+                        _df = np.concatenate((_df,tf.reshape(p,[1, 7])), axis=0)
+        _df = pd.DataFrame(_df, index=None)
+        _df = _df.drop(0, axis=0)
+        _df.to_csv('.\gen_data\gen_data2.txt', index=False)
 
     @staticmethod
     def critic_loss(real_output, fake_output):

### 2020-03-19 src/tf_ann.py
fix: tf_ann: discard-biases for BN

@@ -53,11 +53,12 @@ def initializer():
 
     return [weights, biases]
 
-weights, biases = initializer()
+# We are going to use Batch Normalization, therefore we don't need the biases
+weights, _ = initializer()
 
 # Create model
 def multilayer_perceptron(x, weights, biases):
-    in_x = tf.add(tf.matmul(x, weights['h1']), biases['b1'])
+    in_x = tf.matmul(x, weights['h1'])
     in_x = tf.nn.relu(in_x)
     in_x = tf.layers.batch_normalization(in_x)
 
@@ -66,7 +67,7 @@ def multilayer_perceptron(x, weights, biases):
         in_x = tf.nn.relu(in_x)
         in_x = tf.layers.batch_normalization(in_x)
 
-    out_layer = tf.matmul(in_x, weights['out']) + biases['out']
+    out_layer = tf.matmul(in_x, weights['out'])
     out_layer = tf.nn.relu(out_layer)
 
     return out_layer
@@ -75,7 +76,7 @@ def multilayer_perceptron(x, weights, biases):
 X = tf.placeholder("float", [None, n_input], name='X')
 Y = tf.placeholder("float", [None, n_outputs], name='Y')
 
-out = multilayer_perceptron(X, weights, biases)
+out = multilayer_perceptron(X, weights, _)
 
 # Define loss and optimizer
 loss_op = tf.losses.mean_squared_error(Y, out)

### 2020-03-20 src/networks.py
fix: smoothing-factor

@@ -107,10 +107,9 @@ def test_model(model, test_data, test_labels, len_tr_data=0, plot=True):
         wavelength = sp.arange(500,820,20)
         for i in [0,16,32]:
             spl = UnivariateSpline(wavelength, predictions[i:i+16])
-            wavelength_smoothed = sp.linspace(500,820,500)
-            pr_smoothed = spl(wavelength_smoothed)
-            spl.set_smoothing_factor(0.5)
-            plt.plot(wavelength_smoothed, pr_smoothed, label='Predictions', c='black', lw=2)
+            wavelength_smoothed = sp.linspace(500,820,100)
+            spl.set_smoothing_factor(0.0)
+            plt.scatter(wavelength, predictions[i:i+16], label='Predictions', c='black', lw=2)
             plt.scatter(wavelength, test_labels[i:i+16], label='Actual', c='red', alpha=0.7,marker='o')
             legend = plt.legend(loc='upper left', shadow=True, fontsize='large')
             legend.get_frame().set_facecolor('C7')

### 2020-03-20 src/networks.py
fix: plot*

@@ -94,7 +94,7 @@ def test_model(model, test_data, test_labels, len_tr_data=0, plot=True):
     predictions = model.predict([test_data])
     #MSE = sp.square(sp.subtract(test_labels, predictions)).mean()
     if plot == True:
-        plt.scatter(test_labels, predictions, label='Predictions', c='red', alpha=0.5)
+        plt.plot(test_labels, predictions, label='Predictions', c='red', alpha=0.5)
         plt.plot(test_labels, test_labels, label='Actual', c='green', alpha=0.7)
         legend = plt.legend(loc='upper left', shadow=True, fontsize='large')
         legend.get_frame().set_facecolor('C7')
@@ -109,7 +109,7 @@ def test_model(model, test_data, test_labels, len_tr_data=0, plot=True):
             spl = UnivariateSpline(wavelength, predictions[i:i+16])
             wavelength_smoothed = sp.linspace(500,820,100)
             spl.set_smoothing_factor(0.0)
-            plt.scatter(wavelength, predictions[i:i+16], label='Predictions', c='black', lw=2)
+            plt.scatter(wavelength_smoothed, spl(wavelength_smoothed), label='Predictions', c='black', lw=2)
             plt.scatter(wavelength, test_labels[i:i+16], label='Actual', c='red', alpha=0.7,marker='o')
             legend = plt.legend(loc='upper left', shadow=True, fontsize='large')
             legend.get_frame().set_facecolor('C7')

### 2020-03-20 src/networks.py
fix: plot*xd

@@ -94,7 +94,7 @@ def test_model(model, test_data, test_labels, len_tr_data=0, plot=True):
     predictions = model.predict([test_data])
     #MSE = sp.square(sp.subtract(test_labels, predictions)).mean()
     if plot == True:
-        plt.plot(test_labels, predictions, label='Predictions', c='red', alpha=0.5)
+        plt.scatter(test_labels, predictions, label='Predictions', c='red', alpha=0.5)
         plt.plot(test_labels, test_labels, label='Actual', c='green', alpha=0.7)
         legend = plt.legend(loc='upper left', shadow=True, fontsize='large')
         legend.get_frame().set_facecolor('C7')
@@ -109,7 +109,7 @@ def test_model(model, test_data, test_labels, len_tr_data=0, plot=True):
             spl = UnivariateSpline(wavelength, predictions[i:i+16])
             wavelength_smoothed = sp.linspace(500,820,100)
             spl.set_smoothing_factor(0.0)
-            plt.scatter(wavelength_smoothed, spl(wavelength_smoothed), label='Predictions', c='black', lw=2)
+            plt.plot(wavelength_smoothed, spl(wavelength_smoothed), label='Predictions', c='black', lw=2)
             plt.scatter(wavelength, test_labels[i:i+16], label='Actual', c='red', alpha=0.7,marker='o')
             legend = plt.legend(loc='upper left', shadow=True, fontsize='large')
             legend.get_frame().set_facecolor('C7')

### 2020-03-21 src/tf_ann.py
updata: full-batch-tr

@@ -15,13 +15,16 @@ print(device_lib.list_local_devices())
 # Load data
 tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
 
+
 # Augment
 
-#tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, 1000, fname='.\gen_data\gen_data.txt')
+for _ in [1000]:
+    tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, _, fname='.\gen_data\gen_data.txt')
 
+print(tr_labels[0])
 # Parameters
-learning_rate = 0.0001
-training_epochs = 200
+learning_rate = 0.001
+training_epochs = 2000
 batch_size = 8
 
 # Network Parameters
@@ -36,38 +39,35 @@ weight_initializer = tf.variance_scaling_initializer(mode="fan_avg", distributio
 bias_initializer = tf.zeros_initializer()
 
 
-def initializer():
-    weights = {
-        'h1': tf.Variable(weight_initializer([n_input, n_hidden])),
-        'out': tf.Variable(weight_initializer([n_hidden, n_outputs]))
-    }
-    biases = {
-        'b1': tf.Variable(bias_initializer([n_hidden])),
-        'out': tf.Variable(bias_initializer([n_outputs]))
-    }
+weights = {
+    'h1': tf.Variable(weight_initializer([n_input, n_hidden])),
+    'out': tf.Variable(weight_initializer([n_hidden, n_outputs]))
+}
+biases = {
+    'b1': tf.Variable(bias_initializer([n_hidden])),
+    'out': tf.Variable(bias_initializer([n_outputs]))
+}
 
-    # Create hidden layers
-    for i in range(1,num_hidden_layers):
-        weights['h{}'.format(i+1)] = tf.Variable(weight_initializer([n_hidden, n_hidden]))
-        biases['b{}'.format(i+1)] = tf.Variable(bias_initializer([n_outputs]))
+# Create hidden layers
+for i in range(1,num_hidden_layers):
+    weights['h{}'.format(i+1)] = tf.Variable(weight_initializer([n_hidden, n_hidden]))
+    biases['b{}'.format(i+1)] = tf.Variable(bias_initializer([n_outputs]))
 
-    return [weights, biases]
-
-# We are going to use Batch Normalization, therefore we don't need the biases
-weights, _ = initializer()
 
[…]

### 2020-03-21 src/tf_ann.py
update: full-batch-tr

@@ -11,17 +11,13 @@ tf.disable_eager_execution()
 # Print CPUs / GPUs available
 print(device_lib.list_local_devices())
 
-
 # Load data
 tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
 
-
 # Augment
-
-for _ in [1000]:
+for _ in [1000, 2000, 3000]:
     tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, _, fname='.\gen_data\gen_data.txt')
 
-print(tr_labels[0])
 # Parameters
 learning_rate = 0.001
 training_epochs = 2000

### 2020-03-21 docs/paper/paper.tex
update: exp-setup-section

@@
 The labels are the confinement loss of the PCF.
-The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36) [35]).
+The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36)).
 Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing.
+By slicing the data set this way we are guiding the network to learn an entirely new set of geometric properties, and this is the reason what made the task impossible, since we only have nine configurations, as we discussed at the beginning of this subsection.
+In contrast, randomly shuffling the data set as a whole is an easy task in this situation, and the ANN model would make great predictions on the test set, however a sense of generality towards new geometric sets will be lost.
+
 This data was preprocessed before fed in the networks.

### 2020-03-21 docs/paper/paper.tex
update: add-figures

@@
 Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [4], proved to be successful in data generation [5, 6, 7, 8, 9].
-In this paper we focus on determining one of the propagation features of a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), proposed in our recent work [21], that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
+In this paper we focus on determining one of the propagation features of a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), proposed in our recent work [21], that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1).
+
+\begin{figure}
+\centering
+\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{mainalgo.png}
+\caption{}
+\end{figure}
 
@@
 The ANN model is a fully-connected feed-forward Multi Layer Perceptron (MLP) model.
-Table(num) summarizes the details of the model.
+Table(1) summarizes the details of the model.
 To reduce over fitting we use the Early stopping method, by saving checkpoints where the best validation mean squared error occurred as we iterate before the model starts to over fit.
@@
 
-GANs consist of two neural networks, as shown in figure (num).
+GANs consist of two neural networks, as shown in Figure (2).
 The first of which called a discriminator, that gives an estimate of the probability that a given input is real or generated (fake).
@@
 In this work, both the Critic and the generator are fully connected feed forward MLP models.
-Tables(num, num) summarize the details of both networks.
+Tables(2, 3) summarize the details of both networks.
 The input vector to the Critic network consists of the six parameters discussed earlier for the ANN model, in addition to the corresponding confinement loss value, giving a total of seven inputs.
 The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the Critic.
+
+\begin{figure}
+\centering
+\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{GAN.png}
+\caption{}
+\end{figure}
+
 \begin{table}[h]
@@
 }
-\caption{Hyper-parameters chosen for the ANN model}
+\caption{Hyper-parameters chosen for the ANN model, where $\beta_{1}$ and $\beta_{2}$ are a part of Adam parameters}
 \end{table}
@@
 
-During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in Figure(num).
+During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in Figure(4).
 In this subsection we discuss the results of augmenting the real data set with generated samples.
-Figure(num) demonstrates the predictions made by the ANN model after training with different sizes of the data set.
+Figure(4) demonstrates the predictions made by the ANN model after training with different sizes of the data set.
 This might look paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data.
@@
 \newpage
-It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(num).
+It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(5).
 The most important result in these experiments is that the ANN model predicted the correct location of the peak value of the confinement loss distributions for the three different analytes used. 
@@
 In this work we fixed the number of epochs to 2000 and executed training using Tensorflow(Keras) and Pytorch frameworks.
-As demonstrated in Table(num).
+As demonstrated in Tables(5,6).
 It is worth mentioning the differences between training with full batch or mini batches.

### 2020-03-21 src/networks.py
progress-bar

@@ -9,6 +9,7 @@ import tensorflow as tf
 import matplotlib.pyplot as plt
 import time
 import os
+from tqdm import tqdm
 from scipy.interpolate import UnivariateSpline
 from tensorflow.python.client import device_lib
 
@@ -21,7 +22,7 @@ tf.compat.v1.enable_eager_execution()
 ####################################################################################
 ####################################################################################
 
-def make_model(num_layers=6, num_neurons=50, num_inputs=6, num_outputs=1):
+def make_model(num_layers=6, num_neurons=50, num_inputs=6, num_outputs=1, batch_norm=True):
     model = tf.keras.Sequential()
 
     # 1st layer
@@ -31,7 +32,8 @@ def make_model(num_layers=6, num_neurons=50, num_inputs=6, num_outputs=1):
     # Hidden layers
     for _ in range(num_layers - 1):
         model.add(layers.Dense(num_neurons))
-        model.add(layers.BatchNormalization())
+        if batch_norm == True:
+            model.add(layers.BatchNormalization())
         model.add(layers.ReLU())
 
     # OUTPUT layer
@@ -73,7 +75,7 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
     # Train
     model.compile(optimizer=Adam, loss='mean_squared_error')
     hist = model.fit(tr_data, tr_labels, epochs=epochs, verbose=1,
-                     validation_data=(va_data, va_labels), callbacks=[checkpointer], batch_size=batch_size)
+                     validation_data=(va_data, va_labels), callbacks=[checkpointer], batch_size=data_size)
     # Post training
     model.save(save_dir)
     #loss = hist.history['loss']
@@ -148,7 +150,7 @@ class Wgan(object):
         self.critic_optimizer = critic_optimizer
         self.generator_optimizer = generator_optimizer
 
-    def make_generator_model(self, num_layers = 5):
+    def make_generator_model(self, num_layers = 5, batch_norm=True):
         model = tf.keras.Sequential()
 
         # 1st layer
@@ -159,7 +161,8 @@ class Wgan(object):
         # HIDDEN layers
         for _ in range(num_layers - 1):
             model.add(layers.Dense(self.BATCH_SIZE * (2 ** 2)))
-            model.add(layers.BatchNormalization())
+            if batch_norm == True:
+                model.add(layers.BatchNormalization())
             model.add(layers.ReLU())
 
         # OUTPUT layer
[…]

### 2020-03-22 src/data_handler.py
update**

@@ -9,21 +9,54 @@ def load_pcf_data(fname='.\data\pcf_data1.xlsx'):
 
     sp.random.shuffle(datafile_1)
 
-    tr_data = datafile_1[:1000,2:6].reshape(1000,4)
+    tr_data = datafile_1[:1000, 2:6].reshape(1000,4)
     tr_labels = datafile_1[:1000,-1].reshape(1000,1)
 
-    va_data = datafile_1[1000:1050,2:6].reshape(50,4)
+    va_data = datafile_1[1000:1050, 2:6].reshape(50,4)
     va_labels = datafile_1[1000:1050, -1].reshape(50, 1)
 
-    test_data =datafile_1[1050:,2:6]
+    test_data =datafile_1[1050:, 2:6]
     test_labels =datafile_1[1050:,-1]
 
     return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
 
+def handle_data(x, y, shuffle_tr=True):
+    x = x.reshape(9,3,16,6)
+    y = y.reshape(9,3,16,1)
+
+    tr_data = x[:7].reshape(7 * 16 * 3, 6)
+    tr_labels = y[:7].reshape(7 * 16 * 3, 1)
+
+    if shuffle_tr == True:
+        merge = np.concatenate((tr_data,tr_labels), axis=1)
+        sp.random.shuffle(merge)
+        tr_data = merge[:,:6].reshape(7 * 16 * 3, 6)
+        tr_labels = merge[:,-1].reshape(7 * 16 * 3, 1)
+
+    va_data = x[-2].reshape(1*16*3,6)
+    va_labels = y[-2].reshape(1*16*3,1)
+
+    test_data = x[-1].reshape(1*16*3,6)
+    test_labels = y[-1].reshape(1*16*3,1)
+
+    return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
+
+
 def load_data(fname='.\data\data.xlsx'):
     data =pd.read_excel(fname)
-    df = data.values
+    print(data.head())
 
+    if fname == 'shuffled_df.xlsx':
+            data = data.drop('Unnamed',axis=1)
+            print(data.head())
+            df = data.values
+            df = df.reshape(432,7)
+            x = df[:,:6]
+            y = df[:,-1]
+            # The training data is already shuffled, set shuffle_tr=False
+            return handle_data(x,y, shuffle_tr=False)
+
+    df = data.values
[…]

### 2020-03-22 src/main.py

@@ -2,80 +2,86 @@ import networks, data_handler
 from networks import Wgan
 import time
 
-# Load Original data
-# OUR SPR BASED PHOTONIC SENSOR
-tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
+wgan = Wgan(BATCH_SIZE = 12,
+            noise_dim = 7,
+            num_critic_input = 7,
+            n_critic = 5,
+            grad_penalty_weight = 10,
+            num_examples_to_generate = 8)
 
-# THEIR PCF DATA
-#tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_pcf_data()
+generator = wgan.make_generator_model(num_layers=5, batch_norm=True)
+critic = wgan.make_critic_model(num_layers=5)
 
-# Augment data after training the wgan
-# To augment our data use fname = '.\gen_data\gen_data.txt'
-# To augment their data use fname = '.\gen_data\gen_data_pcf.txt'
+ann_model = networks.make_model(num_layers=6,
+                                num_inputs=6,
+                                num_outputs=1,
+                                num_neurons=50,
+                                batch_norm=True)
+def train_wgan():
+    start = time.time()
 
-# Save / Checkpoint directory
-save_dir = r'.\trained-nets\model1.h5'
-chkdir = r'.\trained-weights\weights1.hdf5'
+    tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
+
+    print('\n*****\nTraining The WGAN  \n****\n')
+    wgan.train_wgan(tr_data,tr_labels,epochs = 2000, generator=generator, critic=critic)
+    print('\n*****\nTraining run time for the wgan is: {} sec\n****\n'.format(time.time() - start))
+
+def generate_data():
+    print('\n*****\n GENERATING DATA ... \n****\n')
+    start = time.time()
+    # WILL SAVE TO gen_data\gen_data2.txt // Data already generated in gen_data\gen_data.txt#
+    wgan.generate_and_save_data(iterations = 1000, training=False, generator=generator, critic=critic)
+    print('\n*****\nGeneration run time is: {} sec\n*****'.format(time.time() - start))
+
+def train_ann_model():
+    start = time.time()
+    # Load the same data used to train the WGAN
[…]

### 2020-03-22 src/networks.py

@@ -28,22 +28,19 @@ def make_model(num_layers=6, num_neurons=50, num_inputs=6, num_outputs=1, batch_
     # 1st layer
     model.add(layers.Dense(num_neurons, input_shape=(num_inputs,)))
     model.add(layers.ReLU())
-
     # Hidden layers
     for _ in range(num_layers - 1):
         model.add(layers.Dense(num_neurons))
         if batch_norm == True:
             model.add(layers.BatchNormalization())
         model.add(layers.ReLU())
-
     # OUTPUT layer
     model.add(layers.Dense(num_outputs))
     model.add(layers.ReLU())
 
     return model
 
-def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, chkdir):
-
+def train_model(model,epochs ,tr_data, tr_labels, va_data, va_labels, save_dir, chkdir,learning_rate = 1e-3, batch_size = 32):
     # Proceed training of a saved model
     # model = keras.models.load_model(save_dir)
 
@@ -58,30 +55,16 @@ def train_model(model,epochs, tr_data, tr_labels, va_data, va_labels, save_dir, 
     checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=0,
                                                    save_best_only=True)
 
-    data_size = int(len(tr_data))
-    # Learning rate / Minibatch size
-    lr = 1e-4
-    batch_size = 8
-    if data_size >= 2000:
-        lr = 2e-4
-        batch_size = 16
-    if data_size >= 3000:
-        lr = 2.5e-4
-        batch_size = 20
-
     # Define optimizers
-    Adam = keras.optimizers.Adam(learning_rate=lr, beta_1=0.9, beta_2=0.999)
+    Adam = keras.optimizers.Adam(learning_rate=learning_rate, beta_1=0.9, beta_2=0.999)
     RMSprop = keras.optimizers.RMSprop(learning_rate=1e-2, rho=0.9)
     # Train
     model.compile(optimizer=Adam, loss='mean_squared_error')
     hist = model.fit(tr_data, tr_labels, epochs=epochs, verbose=1,
-                     validation_data=(va_data, va_labels), callbacks=[checkpointer], batch_size=data_size)
+                     validation_data=(va_data, va_labels), callbacks=[checkpointer, tensorboard_callback], batch_size=batch_size)
     # Post training
     model.save(save_dir)
     #loss = hist.history['loss']
[…]

### 2020-03-22 src/data_handler.py
fix: minor-mistake

@@ -42,21 +42,18 @@ def handle_data(x, y, shuffle_tr=True):
     return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
 
 
-def load_data(fname='.\data\data.xlsx'):
+def load_data(fname):
     data =pd.read_excel(fname)
+    df = data.values
     print(data.head())
 
-    if fname == 'shuffled_df.xlsx':
-            data = data.drop('Unnamed',axis=1)
-            print(data.head())
-            df = data.values
-            df = df.reshape(432,7)
-            x = df[:,:6]
-            y = df[:,-1]
-            # The training data is already shuffled, set shuffle_tr=False
-            return handle_data(x,y, shuffle_tr=False)
+    if fname == r'.\data\shuffled_df.xlsx':
+        df = df.reshape(432,7)
+        x = df[:,:6]
+        y = df[:,-1]
+        # The training data is already shuffled, set shuffle_tr=False
+        return handle_data(x,y, shuffle_tr=False)
 
-    df = data.values
     df = df.reshape(9,3,16,7)
     sp.random.shuffle(df)
     df = df.reshape(432,7)
@@ -76,6 +73,7 @@ def load_data(fname='.\data\data.xlsx'):
     y = sp.log10(y).reshape(432,1)
     #Assert shape
 
+    df = np.concatenate((x,y), axis=1)
     # Save shuffled data frame
     df = pd.DataFrame(df, columns=['Analytes','lambda','Pitch','d1','d2','d3','loss'])
     df.to_excel(r'.\data\shuffled_df.xlsx', index = False)

### 2020-03-22 docs/paper/paper.tex
add: important-idea

@@
 In this paper we focus on determining one of the propagation features of a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), proposed in our recent work [21], that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1).
+In this work we will start by building a feed forward ANN model that learns the confinement loss given only the geometric properties of a sensor with fixed pattern and geometrical shape of the cladding air holes.
+For different types of sensors, Convolutional and Reccurent neural networks can be of great advantage, to discover the spatial properties of the sensors.
+The latter will be conducted in future work.
 

### 2020-03-22 docs/paper/paper.tex
add: important-idea

--- 2020-03-21 docs/paper/paper.tex
@@
 
+\hl{This Idea is very important}
+In this work we built a feed forward ANN model that learned the confinement loss given the geometric properties of a SPR-based PCF sensor with fixed pattern and geometrical shape of the cladding air holes.
+For different types of sensors, Convolutional and Reccurent neural networks can be of great advantage, to discover the spatial insights of variety of patterns and  geometrical shape of the cladding air holes.
+The latter will be conducted in future work.
+
 Machine learning approaches has an inherit strength on top of classical simulation methods: they could model hidden parameters in a system which we have no knowledge about.

### 2020-03-22 docs/paper/paper.tex
add: important-idea

@@
 In this paper we focus on determining one of the propagation features of a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), proposed in our recent work [21], that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1).
+We will fix the pattern and geometrical shape of the cladding air holes, and vary the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$.
+Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional neural networks.
 

### 2020-03-23 docs/paper/paper.tex
* Few fixes in wording

--- 2020-03-22 docs/paper/paper.tex
@@
 \usepackage{subcaption}
-\usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,
-    linkcolor=blue,
-    filecolor=magenta,      
-    urlcolor=cyan,
-}
-\urlstyle{same}  
+
 \begin{document}
@@
 \begin{abstract}
-Our aim is to propose a deep learning approach that surpasses simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) used to design, optimise and evaluate a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR) structure performance, proposed in our recent work.
-Through these simulation techniques one must calculate the confinement loss for a specific wavelength and a particular set of geometric properties of the PCF sensor, then repeat the process for different analytes.
-To eventually find the best set of geometric properties that maximises the distance between the confinement loss distributions of different analytes, and thus find the most sensible PCF sensor.
-In order to find these distributions we have to make as much calculations per wavelength as possible to ensure the correct location of the peak value of the confinement loss.
-Simulation methods are not only time costing and daunting, consuming hours to days, but also inaccurate sometimes.
-In contrast, a deep neural network model astonishingly performs these calculations in milliseconds to seconds, quiet accurately, when it is well trained with an accurate data set.
+Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches.
+However, the potential number of combinations possible for a single application is huge.
+This issue combined by the speed of PCF numerical simulation techniques causes the task to take significant amount of time.
+As stated in the previous works, artificial neural networks (ANN) can predict the result of numerical simulations much faster.
+However, there are two issues with the methods proposed previously.
+Namely, the required number of samples for training and generality of the designed network.
+In this paper, we have proposed the use of generative adversarial networks (GAN) to augment the real data set to then train a  ANN model.
 
@@
 
+In this paper we propose the use of artificial neural networks (ANN) to compute the loss in photonic crystal fibers in a wide range of configurations.
+Additionally, in order to minimize the required amount of samples to train the ANN, we employed generative adversarial networks (GAN).
+As discussed in the experiments section, this setup significantly reduces the error in the prediction compared to the state-of-the-art methods used in the literature.
+
 \hl{Importance of PCF and SPR, written by AY or HA}
 
-Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
-Artificial Neural Networks can approximate any function by virtue of the Universality theorem: No matter what the input is there is to be a guaranteed ANN architecture that computes the desired outputs.
-This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures [1], optimization of photonic crystal nanocavities [2], and more recently, computing optical properties of a photonic crystal fiber [3].
+Machine learning techniques are coming to the forefront of many fields [ref], surpassing the human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
+Additionally, ANN can approximate any function (Universality theorem)[ref].
+This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures [ref], optimization of photonic crystal nanocavities [ref], and more recently, computing optical properties of a photonic crystal fiber [ref].
 
-One of the most difficult challenges that deep learning models face is that they benefit from large amounts of data to train, which may be costly to acquire.
-One of the solutions to overcome this issue is to artificially expand the original training dataset by the means of generative networks.
-Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [4], proved to be successful in data generation [5, 6, 7, 8, 9].
-In this paper we focus on determining one of the propagation features of a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), proposed in our recent work [21], that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1).
-In this work we will start by building a feed forward ANN model that learns the confinement loss given only the geometric properties of a sensor with fixed pattern and geometrical shape of the cladding air holes.
-For different types of sensors, Convolutional and Reccurent neural networks can be of great advantage, to discover the spatial properties of the sensors.
-The latter will be conducted in future work.
+One of the most difficult challenges that deep learning models face is that they benefit from large amounts of data to train, which may be costly to acquire [ref].
+One of the solutions to overcome this issue is to artificially expand the original dataset by the means of generative networks.
+Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [ref], proved to be successful in tasks such as synthetic data generation [ref] and synthetically augment the data for deep learning based systems [ref].
 
-\begin{figure}
-\centering
-\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{mainalgo.png}
-\caption{}
-\end{figure}
+\hl{Will be moved to methodology} 
+hl{GAN power comes from the fact that they discover insights and structures within distributions that allows them to make good approximations to the real data set.} \hl{This is exactly how ANN works too.} In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model.
+Our aim to eventually surpass the simulations performed using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate the sensor performance.
+A time comparison between the performance of the ANN and classic simulation techniques has been made here [ref].
+Furtheremore, a time comparaison is also made in this paper in section $4$.
 
@@
 
-We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected.
+In this section details of the proposed method is discussed.
+At the start, a GAN is trained to generate additional data by using training samples.
+These generated samples are filtered to ensure they fall within the applicable range.
+Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network network.
+The details of the proposed ANN architecture and the GAN is discussed in the following subsections.
+
+\hl{will be split into the subsections.} We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected.
 Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
-Previous works [10, 11], demonstrated that random data augmentation actually had weakened the performance of the model.
-Hence, active researches are ongoing to find ways to optimally sample the generated data [12], in other words to filter out the "good" generated data after training the GAN.
-In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables, and the confinement loss.
+Previous works [ref, ref], demonstrated that random data augmentation actually had weakened the performance of the model.
+Hence, active researches are ongoing to find ways to optimally sample the generated data [ref], in other words to filter out the "good" generated data after training the GAN.
+In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
 In the following sub-sections we discuss the networks architectures.
-Before we proceed, it is worth mentioning that the choices made for the parameters of the networks are by no means a robust set of rules, rather, they are rules of thumb and heuristics, as no such rules have been yet developed for ANN models.
 
@@
 \label{ssec:ann}
-The ANN model is a fully-connected feed-forward Multi Layer Perceptron (MLP) model.
-Table(1) summarizes the details of the model.
-To reduce over fitting we use the Early stopping method, by saving checkpoints where the best validation mean squared error occurred as we iterate before the model starts to over fit.
-To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm [14] was used.
+The ANN model employed in this research is a fully-connected feed-forward MLP (Multi Layer Perceptron) consisting of an input layer, an output layer, and 5 hidden layers.
+Each hidden layer consists of 50 neurons and uses Rectified Linear Unit (ReLU) activation function.
 
-\begin{table}[h]
-\centering
-\scalebox{1.1}{
-    \begin{tabular}{|l|l|}
-    \hline
-Number of hidden layers & 6  \\
-\hline
-Number of neurons per hidden layers & 50  \\
-\hline
-Activation function & Rectified Linear Unit (ReLU)  \\
-\hline
-Optimizer & Adam[13]  \\
-\hline
-Loss function& Mean Squared Error (MSE) \\
-\hline
-    \end{tabular}
-}
-\caption{Detailes of the ANN model}
-\end{table}
+Adam [ref] as the optimizer and the mean squared error as the loss/cost function.
+To reduce overfitting we use the Early stopping method [reference], that is by saving checkpoints where the best validation mean squared error occurred as we iterate.
+To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used [ref].
 
@@
 
-GANs consist of two neural networks, as shown in Figure (2).
+GANs consist of two neural networks, as shown in figure (num).
 The first of which called a discriminator, that gives an estimate of the probability that a given input is real or generated (fake).
 Whereas the second network is referred to as the generator, which outputs data samples from a random noise vector called a latent variable usually given the symbol $z$ supplied at its input.
-The error at the discriminator's output would then be measured by the means of a chosen metric.
-Introduced by Arjovsky et al [15] the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
-Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty [16].
+The error between the discriminator’s output and the actual labels (The real data samples vectors all labeled as 1: the probability of being real) would then be measured by the means of a chosen metric.
+Introduced by Arjovsky et al [reference] the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
+Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty [reference].
 The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.
-In this work, both the Critic and the generator are fully connected feed forward MLP models.
-Tables(2, 3) summarize the details of both networks.
-The input vector to the Critic network consists of the six parameters discussed earlier for the ANN model, in addition to the corresponding confinement loss value, giving a total of seven inputs.
-The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the Critic.
-
-\begin{figure}
-\centering
-\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{GAN.png}
-\caption{}
-\end{figure}
-
-\begin{table}[h]
-\centering
-\begin{tabular}{|l|l|}
-\hline
-Number of hidden layers & 5  \\
-\hline
-Number of neurons per hidden layers & $ minibatchsize\times2^{number of layers} $  \\
-\hline
-Activation function & Leaky Rectified Linear Unit (LeakyReLU)  \\
-\hline
-Optimizer & Adam[13]  \\
-\hline
-    \end{tabular}
-\caption{Details of the Critic model}    
-\end{table}
-
-\begin{table}[h]
-\centering
- \begin{tabular}{|l|l|}
-    \hline
-Number of hidden layers & 5 \\
-\hline
-Number of neurons per hidden layers & $ minibatchsize\times2^{2} $  \\
-\hline
-Activation function & Rectified Linear Unit (ReLU)  \\
-\hline
-Optimizer & Adam[13]  \\
-\hline
-Normalization & Batch Normalization[14] \\
-\hline
-    \end{tabular}
-\caption{Details of the Generator model}
-\end{table}
-
+The WGAN-GP architecture chosen in this work is as follows: both the Critic and the generator networks are a fully-connected feed-forward MLP, having 4 hidden layers, with $ minibatchsize\times2^{number of layers} $ neurons for each hidden layer in the critic network, whereas $ minibatchsize\times2^{2} $ neurons for each hidden layer in the generator network.
+The input vector for the Critic network consists of the $six$ parameters discussed earlier for the ANN model, in addition the corresponding loss value, giving a total of seven inputs.
+The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the critic network.
+LeakyReLU and ReLU were chosen as the activation functions for the Critic and Generator respectively and Adam as the optimizer for both networks.
+Finally Batch Normalization technique was applied to the Generator.
+\newpage
 \section{Photonic crystal fiber design}
@@
 
-A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM.
-This length of the data set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent.
-This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
+A labeled data-set of only 432 samples was collected in this work, through simulations using FV-FEM.
+The length of the data-set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent.
+The data-set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
 The labels are the confinement loss of the PCF.
-The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36)).
+The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for 3 different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36) [35]).
 Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing.
-By slicing the data set this way we are guiding the network to learn an entirely new set of geometric properties, and this is the reason what made the task impossible, since we only have nine configurations, as we discussed at the beginning of this subsection.
-In contrast, randomly shuffling the data set as a whole is an easy task in this situation, and the ANN model would make great predictions on the test set, however a sense of generality towards new geometric sets will be lost.
-
 This data was preprocessed before fed in the networks.
 The indices of refraction  are very close, which made it quiet difficult for the neural networks to differentiate between them, after many trials, the best choice was to take only the tens digit of ${134, 135, 136}$, giving ${4, 5, 6}$.
-Finally, we transform the confinement loss to the log scale, for the purpose of shortening the distances between the confinement loss points.
+Finally, we transform the confinement loss to the log scale.
 
@@
 
-We train the ANN model for more than 2000 epochs, starting from the original data set.
-Then we augment the latter set by 1000 generated samples by our WGAN-GP, which will be demonstrated in the next subsection, and train again with the new augmented data set.
-The following table summarizes the hyper-parameters chosen for the ANN model:
-\begin{table}[h]
-\centering
-\scalebox{1.5}{
-    \begin{tabular}{|l|l|l|l|l|}
+We train the ANN model for more than 2000 epochs, starting from the original data-set.
+Then we augment the data by 1000 generated samples from our WGAN-GP, which will be demonstrated in the next section.
+The following table summarizes the hyper-parameters chosen for the ANN model:\\
+\begin{tabular}{||c c c c c||}
 \hline
-Length of the training data-set & Learning rate& Mini batch size & $\beta_{1}$ & $\beta_{2}$\\
+Length of the training data-set & Learning rate&Batch size & $\beta_{1}$ & $\beta_{2}$\\ [0.5ex] 
+\hline\hline
+336 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
 \hline
-336 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
+\hline\hline
+1000+336 & $ 1\times10^{-04} $ & 12 & 0.9 & 0.999 \\
 \hline
-336 + 1000 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
+\hline\hline
+2000 + 336 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
 \hline
-336 + 2000 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
+\hline\hline
+3000 + 336 & $ 2.5\times10^{-04} $ & 16  & 0.9 & 0.999 \\
 \hline
-336 + 3000 & $ 2.5\times10^{-04} $ & 20  & 0.9 & 0.999 \\
-\hline
-    \end{tabular}
-}
-\caption{Hyper-parameters chosen for the ANN model, where $\beta_{1}$ and $\beta_{2}$ are a part of Adam parameters}
-\end{table}
-
+\end{tabular}\\
 \newpage
-The MSE on the training sets ranged from 0.0030 to 0.0050.
-For all training data sets the MSE decreased in an acceptable manner.
-Next, we plot the predictions the ANN model made on the test set, after training using only the original set.
-As shown in the following figure.
-
+The MSE on the training sets ranged from 0.0030 to 0.0050. For all data sets the MSE on the training sets decreased in an acceptable manner, as shown in the following figure.
 \begin{figure}[h]
-	\hspace*{-0.07\textwidth}
-	\begin{subfigure}{.5\textwidth}
-    \begin{tikzpicture}
+    \begin{tikzpicture}[scale=.6]
 		\begin{axis}[
@@
 	\end{tikzpicture}
-	\end{subfigure}\hspace{0.1\textwidth}
-	\begin{subfigure}{.5\textwidth}
-	\begin{tikzpicture}
+	\caption{}
+\end{figure}\\
+    \newline
+    Next, we plot the predictions the ANN model made after training using only the original data-set.
+    \newpage
+\begin{figure}[h]
+			\begin{tikzpicture}[scale=.6]
 			\begin{axis}[
-			legend pos=north west,
 			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
@@
 			\end{tikzpicture}
-	\end{subfigure}
 			\caption{}
-\end{figure}\\
-
-    \newpage
+\end{figure}
+As you can see, the ANN made somewhat good predictions of the low values of the confinement loss.
+A close inspection into the data samples collected shows that points are concentrated in the low values interval, i.e the ANN picked up the pattern quiet easily.
+However, in the higher values interval, the ANN could not see a pattern because points are distant from each other to some extent, even though we transformed the confinement loss to the log scale to actually minimize these distances.
 
@@
 
-During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in Figure(4).
-In this subsection we discuss the results of augmenting the real data set with generated samples.
-Figure(4) demonstrates the predictions made by the ANN model after training with different sizes of the data set.
-This might look paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data.
-There are several reasons for why our ANN model is driven in the wrong direction.
+During training the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in figure(num).
+In this sub-section we discuss the results of augmenting the real data set with Synthetic data.
+Figure(num) demonstrates the predictions made by the ANN model after training with different sizes of the Synthetic data set.
+This might seem paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data.
+There are several reasons that is driving our ANN model predictions in the wrong way.
 Even though our WGAN-GP seemed well trained, there still a domain gap between the real data and the generated data, or the expansion of data is growing in the wrong direction to that of entirely containing the real data.
 Furthermore, the generated data might lack realism.
-Or the sampling strategy adopted is poor.
-But the most convincing reason is the limited original training data set size of 336 samples, used to train the WGAN model in the first place.
-After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved what we set out to accomplish at the beginning, to improve the accuracy of the ANN model by artificially expanding the original set.
+Or the sampling strategy adopted is poor[ref, ref, ref].
+After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved we set out to accomplish at the beginning, to train an ANN model and make accurate prediction on a never-seen-before data.
 
-\hspace{-0.07\textwidth}
-\begin{figure}[h]
+\begin{figure}[ht]
     \begin{subfigure}{.5\textwidth}
@@
 			\end{tikzpicture}
-\end{subfigure}\hspace{0.05\textwidth}
+\end{subfigure}
     \begin{subfigure}{.5\textwidth}
@@
 			\begin{axis}[
-			legend pos=north west,
 			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
@@
 			\begin{axis}[
-			legend pos=north west,
-			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
+			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, % \hertz requires SIunits
 			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
@@
 			\end{tikzpicture}
-\end{subfigure}\hspace{0.05\textwidth}
+\end{subfigure}
 \begin{subfigure}{.5\textwidth}
@@
 			\begin{axis}[
-			legend pos=north west,
-			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
+			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, % \hertz requires SIunits
 			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
@@
 \newpage
-It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(5).
-The most important result in these experiments is that the ANN model predicted the correct location of the peak value of the confinement loss distributions for the three different analytes used. 
+It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in figure(num).
 \begin{figure}
@@
 			\end{tikzpicture}
-\end{subfigure}\hspace{0.05\textwidth}
+\end{subfigure}
  \begin{subfigure}{.5\textwidth}
@@
 
-This work had been conduct on a  laptop:
-
-\begin{itemize}
-\item Intel(R) Core(TM) i7-5600 CPU @2.60GHz (4 CPUs)
-\item 8GB RAM
-\item No GPU on board
-\end{itemize}
-
-For comparaison purposes we ran the expirements on a machine with GPU on board:
-
-\hl{CEM PC SPECS}
-
-Epirements conducted on the latter machine will be labeled as GPU based, whereas on the former as CPU based.
-
-By taking advantage of Cloud Computing technology, one does not have to spend large amounts of money to obtain high-specs machine, rather, rent readily available deep learning instances in the cloud for pennies on the dollar.
-
-The code for this work is available at: \url{https://github.com/Aimen-Zelaci/SPRPCF_ANN/}.
-\newline
-The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, mini batch size, data set size, number of epochs, the framework used to code the model, and of course the specifications of the machine.
-In this work we fixed the number of epochs to 2000 and executed training using Tensorflow(Keras) and Pytorch frameworks.
-As demonstrated in Tables(5,6).
-It is worth mentioning the differences between training with full batch or mini batches.
-In full batch training, the whole data set is passed to the model for each iteration.
-In contrast, mini-batch-training, the data set is split into small mini batches of equal sizes, then passed to the model seperately, thus for each epoch there will be exactly length  of the data set devided by the mini batch size steps, and hence slowing down the training process.
-Previous works [17, 18] have firmly proved the advantages of using the correct mini batch size as oppose to large batch sizes.
-Mini batches allow for more frequent gradient calculations, that results in more stable and reliable training.
-Perhaps one of the main downsides of using large batch size is the poor generalization resulting in a phenomena know as the "generalization gap".
-Active research [19] is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime.
-A closely related recent work (Machine learning approach for computing optical properties of a photonic crystal fiber, Sunny Chugh, Aamir Gulistan, Souvik Ghosh, AND B.M.A.
-Rahman, DEC 2019), conducted their expirements using full batch to train the model.
-In this work we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications to fit our purposes.
-Finally, we compare the performance of the WGAN model, using Tensorflow(Keras) framework, of CPU based to that of GPU based.
-
-\begin{table}[h]
-\begin{tabular}{lllll}
-    & data set size & mini batch size & Time elapsed (sec) \\
-Mini batches    &336 + 0 & 8 & 214 & \\
-    &336 + 1000 & 8 & 744 & \\
-    &336 + 2000 & 16 & 685  & \\ 
-    &336 + 3000 & 20 & 861  & \\
-\end{tabular}
-\begin{tabular}{lllll}
-   & data set size & Time elapsed (sec) \\
-Full batch    &336 + 0 &  23 & \\
-    &336 + 1000 &  34 & \\
-    &336 + 2000 &  45 & \\ 
-    &336 + 3000 &  57 & \\
-\end{tabular}
-\caption{Training performance using Tensorflow(Keras). CPU based training.}
-\end{table}
-\begin{table}[h]
-\begin{tabular}{lllll}
- & data set size & mini batch size & Time elapsed (sec) \\
-Mini batches    & 336 + 0 & 8 & 1315 & \\
-    & 336 + 1000 & 8 & 6453  & \\
-    & 336 + 2000 & 16 & 4751  & \\ 
-    & 336 + 3000 & 20 & 5132 & \\
-\end{tabular}
-\begin{tabular}{lllll}
-   &data set size & Time elapsed (sec) \\
-   Full batch &336 + 0 &  36  & \\
-    & 336 + 1000 &  98  & \\
-    & 336 + 2000 &  195  & \\ 
-    & 336 + 3000 &  336  & \\
-\end{tabular}
-\caption{Training performance using Pytorch. CPU based training.}
-\end{table}
-
-\hl{WGAN EXCUTION WITH GPU VS CPU BY CEM}
-
-Next, we compare the testing runtime of the ANN model to that of simulation methods used to compute the confinement loss for 3 different analytes and 16 wavelenghts, i.e a total of 48 values of the confinement loss, demonstrated in Table(num).
-This result is absolutely staggering.
-The ANN model calculated 48 confinement losses in just 0.17 seconds, while simulations took about 2 hours.
-Therefore, a well trained ANN model can be used to accurately find the best PCF geometric properties set that maximisez the distance between the confinement loss distributions of each analyte in a matter of seconds to minutes.
-Hence, accelerate the search for the best PCF sensor.
-
-\begin{table}[h]
-\centering
-\scalebox{1.2}{\begin{tabular}{l|l}
-      & Time elapsed & \\
-      \hline
-    ANN &  0.17 sec & \\
-    \hline
-    Simulation &  7872 sec = 2.18 hours  & \\
-\end{tabular}
-}
-\caption{ANN vs Simulation test runtime performance}
-\end{table}
-\newpage
-
 \section{Conclusion}

### 2020-03-24 src/networks.py
fix: mistake: <0

@@ -167,7 +167,7 @@ class Wgan(object):
             model.add(layers.Dense(self.BATCH_SIZE * (2 ** i)))
             model.add(layers.LeakyReLU())
             i-=1
-            if i == 0:
+            if i < 0:
                 i = 0
         # OUTPUT layer
         model.add(layers.Dense(1, activation='linear'))

### 2020-03-24 src/networks.py
update: tensorboard-gan

@@ -24,7 +24,6 @@ tf.compat.v1.enable_eager_execution()
 
 def make_model(num_layers=6, num_neurons=50, num_inputs=6, num_outputs=1, batch_norm=True):
     model = tf.keras.Sequential()
-
     # 1st layer
     model.add(layers.Dense(num_neurons, input_shape=(num_inputs,)))
     model.add(layers.ReLU())
@@ -43,18 +42,14 @@ def make_model(num_layers=6, num_neurons=50, num_inputs=6, num_outputs=1, batch_
 def train_model(model,epochs ,tr_data, tr_labels, va_data, va_labels, save_dir, chkdir,learning_rate = 1e-3, batch_size = 32):
     # Proceed training of a saved model
     # model = keras.models.load_model(save_dir)
-
     # TensorBoard log directory
     logdir = r'.\logs\scalars\{}'.format(time.time())
-
     # CALLBACKS
     # TensorBoard
     tensorboard_callback = keras.callbacks.TensorBoard(log_dir=logdir)
-
     # Save the best va_loss file
     checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=0,
                                                    save_best_only=True)
-
     # Define optimizers
     Adam = keras.optimizers.Adam(learning_rate=learning_rate, beta_1=0.9, beta_2=0.999)
     RMSprop = keras.optimizers.RMSprop(learning_rate=1e-2, rho=0.9)
@@ -106,8 +101,6 @@ def test_model(model, test_data, test_labels, len_tr_data=0, plot=True):
 
     return predictions
 
-
-
     ############################### WGAN ###############################################
     ####################################################################################
     ####################################################################################
@@ -123,7 +116,6 @@ class Wgan(object):
                       critic_optimizer = tf.keras.optimizers.Adam(2e-4, beta_1=0.5, beta_2=0.9),
                       generator_optimizer = tf.keras.optimizers.Adam(2e-4, beta_1=0.5, beta_2=0.9)
                         ):
-
         self.BATCH_SIZE = BATCH_SIZE
         self.noise_dim = noise_dim
         self.num_critic_input = num_critic_input
@@ -132,22 +124,22 @@ class Wgan(object):
         self.num_examples_to_generate = num_examples_to_generate
         self.critic_optimizer = critic_optimizer
         self.generator_optimizer = generator_optimizer
+        self.checkpoint_dir = './training_checkpoints'
[…]

### 2020-03-25 src/data_handler.py
add: FLAGS!

@@ -82,7 +82,10 @@ def load_data(fname):
 
 
 # Augment data
-def augment_data(tr_data, tr_labels, size, fname='.\gen_data\gen_data2.txt'):
+def augment_data(tr_data, tr_labels, flags):
+    size = flags.augment_size
+    fname = flags.gen_data_dir
+
     generated_data = pd.read_csv(fname).values
     #start_slice = size-1000
 

### 2020-03-25 src/initializer.py

@@ -1,0 +1,44 @@
+import tensorflow.compat.v1 as tf
+import json
+
+FLAGS = tf.flags.FLAGS
+
+with open('hyper_params.json', 'r') as f:
+    params_dict = json.load(f)
+
+wgan_flags = params_dict[0]
+ann_flags  = params_dict[1]
+data_flags = params_dict[2]
+
+tf.flags.DEFINE_integer('wgan_batch_size', wgan_flags['BATCH_SIZE'], 'batch size, default: 12')
+tf.flags.DEFINE_integer('noise_dim', wgan_flags['noise_dim'], 'z_dimension, default:7')
+tf.flags.DEFINE_integer('num_critic_input', wgan_flags['num_critic_input'], 'number of inputs to the critic, default:7')
+tf.flags.DEFINE_integer('n_critic', wgan_flags['n_critic'], 'Critic iterations, default:5')
+tf.flags.DEFINE_integer('grad_penalty_weight', wgan_flags['grad_penalty_weight'], 'Gradient penalty weight, default:10')
+tf.flags.DEFINE_integer('num_examples_to_generate', wgan_flags['num_examples_to_generate'], 'number of examples to generate, default:8')
+tf.flags.DEFINE_integer('wgan_epochs', wgan_flags['epochs'], 'WGAN epochs,default:2000')
+
+tf.flags.DEFINE_integer('gen_num_layers', wgan_flags['gen_num_layers'], 'Generator number of hidden layers,default:5')
+tf.flags.DEFINE_integer('cr_num_layers', wgan_flags['cr_num_layers'], 'Critic number of hidden layers,default:5')
+
+tf.flags.DEFINE_string('gen_batch_norm', wgan_flags['gen_batch_norm'], 'Generator batch normalization')
+
+tf.flags.DEFINE_integer('num_layers',ann_flags['num_layers'],'number of hidden layers of the ANN model, default:6')
+tf.flags.DEFINE_integer('num_inputs', ann_flags['num_inputs'], 'number of inputs to the ANN , default:6')
+tf.flags.DEFINE_integer('num_outputs', ann_flags['num_outputs'], 'number of outputs of the ANN ,default:1')
+tf.flags.DEFINE_integer('num_neurons', ann_flags['num_neurons'], 'number of neurons in the ANN, default:50')
+tf.flags.DEFINE_float('lr', ann_flags['learning_rate'], 'ANN learning rate, default:1e-3')
[…]

### 2020-03-25 src/main.py

@@ -1,78 +1,54 @@
-import networks, data_handler
+import tensorflow.compat.v1 as tf
+import networks, data_handler, initializer
 from networks import Wgan
 import time
 
-wgan = Wgan(BATCH_SIZE = 12,
-            noise_dim = 7,
-            num_critic_input = 7,
-            n_critic = 5,
-            grad_penalty_weight = 10,
-            num_examples_to_generate = 8)
+FLAGS = initializer.init()
 
-generator = wgan.make_generator_model(num_layers=5, batch_norm=True)
-critic = wgan.make_critic_model(num_layers=5)
+wgan = Wgan(FLAGS)
 
-ann_model = networks.make_model(num_layers=6,
-                                num_inputs=6,
-                                num_outputs=1,
-                                num_neurons=50,
-                                batch_norm=True)
+generator = wgan.make_generator_model()
+critic = wgan.make_critic_model()
+
+ann_model = networks.make_model(FLAGS)
+
 def train_wgan():
     start = time.time()
-
-    tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
-
-    print('\n*****\nTraining The WGAN  \n****\n')
-    wgan.train_wgan(tr_data,tr_labels,epochs = 2000, generator=generator, critic=critic)
-    print('\n*****\nTraining run time for the wgan is: {} sec\n****\n'.format(time.time() - start))
+    tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname=FLAGS.data)
+    wgan.train_wgan(tr_data,tr_labels, generator=generator, critic=critic)
 
 def generate_data():
-    print('\n*****\n GENERATING DATA ... \n****\n')
-    start = time.time()
     # WILL SAVE TO gen_data\gen_data2.txt // Data already generated in gen_data\gen_data.txt#
-    wgan.generate_and_save_data(iterations = 1000, training=False, generator=generator, critic=critic)
-    print('\n*****\nGeneration run time is: {} sec\n*****'.format(time.time() - start))
+    wgan.generate_and_save_data(iterations = 10, training=False, generator=generator, critic=critic)
 
 def train_ann_model():
-    start = time.time()
     # Load the same data used to train the WGAN
-    tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\shuffled_df.xlsx')
[…]

### 2020-03-25 src/networks.py

@@ -22,15 +22,20 @@ tf.compat.v1.enable_eager_execution()
 ####################################################################################
 ####################################################################################
 
-def make_model(num_layers=6, num_neurons=50, num_inputs=6, num_outputs=1, batch_norm=True):
+def make_model(flags):
     model = tf.keras.Sequential()
+    num_inputs = flags.num_inputs
+    num_neurons = flags.num_neurons
+    num_layers = flags.num_layers
+    num_outputs = flags.num_outputs
+    batch_norm = flags.batch_norm
     # 1st layer
     model.add(layers.Dense(num_neurons, input_shape=(num_inputs,)))
     model.add(layers.ReLU())
     # Hidden layers
     for _ in range(num_layers - 1):
         model.add(layers.Dense(num_neurons))
-        if batch_norm == True:
+        if batch_norm == "True":
             model.add(layers.BatchNormalization())
         model.add(layers.ReLU())
     # OUTPUT layer
@@ -39,7 +44,14 @@ def make_model(num_layers=6, num_neurons=50, num_inputs=6, num_outputs=1, batch_
 
     return model
 
-def train_model(model,epochs ,tr_data, tr_labels, va_data, va_labels, save_dir, chkdir,learning_rate = 1e-3, batch_size = 32):
+def train_model(model ,tr_data, tr_labels, va_data, va_labels, flags):
+    start = time.time()
+    print('\n\n Training the ANN model on {} samples \n\n'.format(int(len(tr_data))))
+    epochs = flags.epochs
+    lr = flags.lr
+    batch_size = flags.ANN_batch_size
+    save_dir = flags.save_dir
+    chkdir = flags.chkdir
     # Proceed training of a saved model
     # model = keras.models.load_model(save_dir)
     # TensorBoard log directory
@@ -51,7 +63,8 @@ def train_model(model,epochs ,tr_data, tr_labels, va_data, va_labels, save_dir, 
     checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=0,
                                                    save_best_only=True)
     # Define optimizers
-    Adam = keras.optimizers.Adam(learning_rate=learning_rate, beta_1=0.9, beta_2=0.999)
+    Adam = keras.optimizers.Adam(learning_rate=
+        lr, beta_1=0.9, beta_2=0.999)
     RMSprop = keras.optimizers.RMSprop(learning_rate=1e-2, rho=0.9)
     # Train
[…]

### 2020-03-25 src/initializer.py
add: train and test flags

@@ -10,6 +10,12 @@ wgan_flags = params_dict[0]
 ann_flags  = params_dict[1]
 data_flags = params_dict[2]
 
+
+tf.flags.DEFINE_bool('train_wgan', False,'train wgan, defaul:True')
+tf.flags.DEFINE_bool('generate', False,'generate data, defaul:True')
+tf.flags.DEFINE_bool('train_ann', False,'train ann, defaul:True')
+tf.flags.DEFINE_bool('test_ann', False,'test ann, defaul:True')
+
 tf.flags.DEFINE_integer('wgan_batch_size', wgan_flags['BATCH_SIZE'], 'batch size, default: 12')
 tf.flags.DEFINE_integer('noise_dim', wgan_flags['noise_dim'], 'z_dimension, default:7')
 tf.flags.DEFINE_integer('num_critic_input', wgan_flags['num_critic_input'], 'number of inputs to the critic, default:7')

### 2020-03-25 src/main.py

@@ -50,18 +50,20 @@ def test_model():
 
 def main(_):
     # 1. TRAIN WGAN
-    train_wgan()
+    if FLAGS.train_wgan:
+        train_wgan()
 
     # 2. GENERATE DATA
-    generate_data()
+    if FLAGS.generate:
+        generate_data()
 
     # 3. TRAIN ANN MODEL/Augment data
-    train_ann_model()
+    if FLAGS.train_ann:
+        train_ann_model()
 
     # 4. TEST
-    test_model()
+    if FLAGS.test_ann:
+        test_model()
 
 if __name__ == '__main__':
     tf.app.run()
-
-

### 2020-03-25 src/initializer.py
fix: gen_iterations

@@ -23,10 +23,8 @@ tf.flags.DEFINE_integer('n_critic', wgan_flags['n_critic'], 'Critic iterations, 
 tf.flags.DEFINE_integer('grad_penalty_weight', wgan_flags['grad_penalty_weight'], 'Gradient penalty weight, default:10')
 tf.flags.DEFINE_integer('num_examples_to_generate', wgan_flags['num_examples_to_generate'], 'number of examples to generate, default:8')
 tf.flags.DEFINE_integer('wgan_epochs', wgan_flags['epochs'], 'WGAN epochs,default:2000')
-
 tf.flags.DEFINE_integer('gen_num_layers', wgan_flags['gen_num_layers'], 'Generator number of hidden layers,default:5')
 tf.flags.DEFINE_integer('cr_num_layers', wgan_flags['cr_num_layers'], 'Critic number of hidden layers,default:5')
-
 tf.flags.DEFINE_string('gen_batch_norm', wgan_flags['gen_batch_norm'], 'Generator batch normalization')
 
 tf.flags.DEFINE_integer('num_layers',ann_flags['num_layers'],'number of hidden layers of the ANN model, default:6')
@@ -39,10 +37,12 @@ tf.flags.DEFINE_integer('ANN_batch_size', ann_flags['batch_size'], 'ANN batch si
 tf.flags.DEFINE_string('batch_norm', ann_flags['batch_norm'], 'ANN batch norm,default:True')
 tf.flags.DEFINE_string('save_dir', ann_flags['save_dir'], 'ANN save directory, default:model1000.h5')
 tf.flags.DEFINE_string('chkdir',ann_flags['chkdir'],'ANN checkpoint directory, default:weights1000.hdf5')
-tf.flags.DEFINE_string('gen_data_dir', ann_flags['gen_data_dir'], 'generated data directory,default:gen_data/gen_data.txt')
 tf.flags.DEFINE_string('model_to_test', ann_flags['model_to_test'], 'Test model directory')
-tf.flags.DEFINE_integer('augment_size', ann_flags['augment_size'], 'data augmentation size, default:1000')
 
+tf.flags.DEFINE_integer('augment_size', ann_flags['augment_size'], 'data augmentation size, default:1000')
+tf.flags.DEFINE_integer('gen_iterations', wgan_flags['gen_iterations'], 'iteration of data generation, default:1000')
+
[…]

### 2020-03-25 src/main.py

@@ -1,3 +1,4 @@
+#! /usr/bin/python3
 import tensorflow.compat.v1 as tf
 import networks, data_handler, initializer
 from networks import Wgan
@@ -19,7 +20,7 @@ def train_wgan():
 
 def generate_data():
     # WILL SAVE TO gen_data\gen_data2.txt // Data already generated in gen_data\gen_data.txt#
-    wgan.generate_and_save_data(iterations = 10, training=False, generator=generator, critic=critic)
+    wgan.generate_and_save_data(iterations = FLAGS.gen_iterations, training=False, generator=generator, critic=critic)
 
 def train_ann_model():
     # Load the same data used to train the WGAN

### 2020-03-25 src/data_handler.py
fix: data

@@ -3,35 +3,17 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 
-def load_pcf_data(fname='.\data\pcf_data1.xlsx'):
-    df_1 = pd.read_excel(fname)
-    datafile_1 = df_1.values
-
-    sp.random.shuffle(datafile_1)
-
-    tr_data = datafile_1[:1000, 2:6].reshape(1000,4)
-    tr_labels = datafile_1[:1000,-1].reshape(1000,1)
-
-    va_data = datafile_1[1000:1050, 2:6].reshape(50,4)
-    va_labels = datafile_1[1000:1050, -1].reshape(50, 1)
-
-    test_data =datafile_1[1050:, 2:6]
-    test_labels =datafile_1[1050:,-1]
-
-    return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
-
-def handle_data(x, y, shuffle_tr=True):
+def split_data(x, y):
     x = x.reshape(9,3,16,6)
     y = y.reshape(9,3,16,1)
 
     tr_data = x[:7].reshape(7 * 16 * 3, 6)
     tr_labels = y[:7].reshape(7 * 16 * 3, 1)
 
-    if shuffle_tr == True:
-        merge = np.concatenate((tr_data,tr_labels), axis=1)
-        sp.random.shuffle(merge)
-        tr_data = merge[:,:6].reshape(7 * 16 * 3, 6)
-        tr_labels = merge[:,-1].reshape(7 * 16 * 3, 1)
+    merge = np.concatenate((tr_data,tr_labels), axis=1)
+    sp.random.shuffle(merge)
+    tr_data = merge[:,:6].reshape(7 * 16 * 3, 6)
+    tr_labels = merge[:,-1].reshape(7 * 16 * 3, 1)
 
     va_data = x[-2].reshape(1*16*3,6)
     va_labels = y[-2].reshape(1*16*3,1)
@@ -52,33 +34,28 @@ def load_data(fname):
         x = df[:,:6]
         y = df[:,-1]
         # The training data is already shuffled, set shuffle_tr=False
-        return handle_data(x,y, shuffle_tr=False)
+        return split_data(x,y)
 
     df = df.reshape(9,3,16,7)
     sp.random.shuffle(df)
     df = df.reshape(432,7)
-
     analytes = df[:,0]
     analytes = (analytes*100)%10
     x = df[:, 1:6]
-
     x = x.reshape(432,5)
[…]

### 2020-03-25 src/main.py

@@ -25,7 +25,6 @@ def generate_data():
 def train_ann_model():
     # Load the same data used to train the WGAN
     tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname=FLAGS.shuffled_data)
-
     # Augment data. To train with only the original real samples, set augment_size = 0.
     # For different augmentations, change the batch_size/ learning_rate accordingly.
     tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, FLAGS)
@@ -53,15 +52,12 @@ def main(_):
     # 1. TRAIN WGAN
     if FLAGS.train_wgan:
         train_wgan()
-
     # 2. GENERATE DATA
     if FLAGS.generate:
         generate_data()
-
     # 3. TRAIN ANN MODEL/Augment data
     if FLAGS.train_ann:
         train_ann_model()
-
     # 4. TEST
     if FLAGS.test_ann:
         test_model()

### 2020-03-25 src/networks.py

@@ -1,4 +1,3 @@
-# Load libraries
 from __future__ import absolute_import, division, print_function, unicode_literals
 from tensorflow import keras
 from tensorflow.keras import layers
@@ -78,7 +77,6 @@ def train_model(model ,tr_data, tr_labels, va_data, va_labels, flags):
 def load_model(model,load_type,dir):
     if load_type == 'load_weights':
         model.load_weights(dir)
-
     if load_type == 'load_model':
         model = keras.models.load_model(dir)
 
@@ -130,7 +128,7 @@ class Wgan(object):
         self.n_critic = flags.n_critic
         self.grad_penalty_weight = flags.grad_penalty_weight
         self.num_examples_to_generate = flags.num_examples_to_generate
-        self.epochs = flags.epochs
+        self.epochs = flags.wgan_epochs
         self.critic_optimizer = tf.keras.optimizers.Adam(2e-4, beta_1=0.5, beta_2=0.9)
         self.generator_optimizer = tf.keras.optimizers.Adam(2e-4, beta_1=0.5, beta_2=0.9)
         self.checkpoint_dir = './training_checkpoints'

### 2020-03-25 src/main.py
remove: linux-exe

@@ -1,4 +1,3 @@
-#! /usr/bin/python3
 import tensorflow.compat.v1 as tf
 import networks, data_handler, initializer
 from networks import Wgan

### 2020-03-26 docs/paper/paper.tex

--- 2020-03-22 docs/paper/paper.tex
@@
 \usepackage{hyperref}
-\hypersetup{
-    colorlinks=true,
-    linkcolor=blue,
-    filecolor=magenta,      
-    urlcolor=cyan,
-}
-\urlstyle{same}  
+
 \begin{document}
@@
 \begin{abstract}
-Our aim is to propose a deep learning approach that surpasses simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) used to design, optimise and evaluate a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR) structure performance, proposed in our recent work.
-Through these simulation techniques one must calculate the confinement loss for a specific wavelength and a particular set of geometric properties of the PCF sensor, then repeat the process for different analytes.
-To eventually find the best set of geometric properties that maximises the distance between the confinement loss distributions of different analytes, and thus find the most sensible PCF sensor.
-In order to find these distributions we have to make as much calculations per wavelength as possible to ensure the correct location of the peak value of the confinement loss.
-Simulation methods are not only time costing and daunting, consuming hours to days, but also inaccurate sometimes.
-In contrast, a deep neural network model astonishingly performs these calculations in milliseconds to seconds, quiet accurately, when it is well trained with an accurate data set.
+Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches.
+However, the potential number of combinations possible for a single application is very large.
+This issue combined by the speed of the commonly used Full Vectorial Finite Element Method (FV-FEM) causes the task to take significant amount of time.
+As stated in the previous works, artificial neural networks (ANN) can predict the result of numerical simulations much faster.
+However, there are two issues with the methods proposed previously.
+Namely, the required number of samples for training and generality of the designed network.
+In this paper, we  propose the use of generative adversarial networks (GAN) to augment the real data set to train a ANN model.
+Experimental analysis suggest that the proposed combination not only accurately predicts the confinement loss even with limited amount of data, but also can work in wider range of methods and geometric configurations.
+Finally, the proposed method is shown to predict the confinement loss over a range of analytes and wavelengths in a completely new set of geometric configuration.
 
@@
 \label{sec:prop}
+
+In this section details of the proposed method is discussed.
+At the start, a GAN is trained to generate additional data by using training samples.
+These generated samples are filtered to ensure they fall within the applicable range.
+Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network network.
+The details of the proposed ANN architecture and the GAN is discussed in the following subsections.
+
+\hl{will be split into the subsections.} We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected.
+Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
+Previous works [ref, ref], demonstrated that random data augmentation actually had weakened the performance of the model.
+Hence, active researches are ongoing to find ways to optimally sample the generated data [ref], in other words to filter out the "good" generated data after training the GAN.
+In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
+In the following sub-sections we discuss the networks architectures.
+
+\subsection{Artificial neural network design}
+\label{ssec:ann}
+The ANN model employed in this research is a fully-connected feed-forward MLP (Multi Layer Perceptron) consisting of an input layer, an output layer, and 5 hidden layers.
+Each hidden layer consists of 50 neurons and uses Rectified Linear Unit (ReLU) activation function.
+
+Adam [ref] as the optimizer and the mean squared error as the loss/cost function.
+To reduce overfitting we use the Early stopping method [reference], that is by saving checkpoints where the best validation mean squared error occurred as we iterate.
+To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used [ref].
 
@@
 	\caption{}
-\end{figure}\\
+\end{figure}
 
@@
 \centering
-\scalebox{1.2}{\begin{tabular}{l|l}
-      & Time elapsed & \\
+\begin{tabular}{l|l}
+      & Time elapsed \\
       \hline
-    ANN &  0.17 sec & \\
+    ANN &  0.17 sec \\
     \hline
-    Simulation &  7872 sec = 2.18 hours  & \\
+    Simulation &  7872 sec = 2.18 hours  \\
 \end{tabular}
-}
+
 \caption{ANN vs Simulation test runtime performance}

### 2020-03-26 docs/paper/paper.tex
Cleanup
update: ref-list

@@
 \usepackage{hyperref}
+\usepackage{cite}
 
@@
 Finally, the proposed method is shown to predict the confinement loss over a range of analytes and wavelengths in a completely new set of geometric configuration.
-
 \end{abstract}
@@
 Artificial Neural Networks can approximate any function by virtue of the Universality theorem: No matter what the input is there is to be a guaranteed ANN architecture that computes the desired outputs.
-This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures [1], optimization of photonic crystal nanocavities [2], and more recently, computing optical properties of a photonic crystal fiber [3].
+This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a photonic crystal fiber \cite{chugh2019machine}.
 
@@
 One of the solutions to overcome this issue is to artificially expand the original training dataset by the means of generative networks.
-Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [4], proved to be successful in data generation [5, 6, 7, 8, 9].
+Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) \cite{goodfellow2014generative}, proved to be successful in data generation \cite{schlegl2017unsupervised, zheng2017unlabeled, frid2018synthetic, tanaka2019data, perez2017effectiveness}.
+
 In this paper we focus on determining one of the propagation features of a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), proposed in our recent work [21], that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1).
@@
 Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
-Previous works [ref, ref], demonstrated that random data augmentation actually had weakened the performance of the model.
-Hence, active researches are ongoing to find ways to optimally sample the generated data [ref], in other words to filter out the "good" generated data after training the GAN.
+Previous works \cite{ravuri2019seeing, shmelkov2018good}, demonstrated that random data augmentation actually had weakened the performance of the model.
+Hence, active researches are ongoing to find ways to optimally sample the generated data \cite{bhattarai2019sampling}, in other words to filter out the "good" generated data after training the GAN.
 In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
@@
 
-Adam [ref] as the optimizer and the mean squared error as the loss/cost function.
-To reduce overfitting we use the Early stopping method [reference], that is by saving checkpoints where the best validation mean squared error occurred as we iterate.
-To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used [ref].
+Adam \cite{kingma2014adam} as the optimizer and the mean squared error as the loss/cost function.
+To reduce overfitting we use the Early stopping method, that is by saving checkpoints where the best validation mean squared error occurred as we iterate.
+To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used \cite{ioffe2015batch}.
 
@@
 Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
-Previous works [10, 11], demonstrated that random data augmentation actually had weakened the performance of the model.
-Hence, active researches are ongoing to find ways to optimally sample the generated data [12], in other words to filter out the "good" generated data after training the GAN.
+Previous works \cite{ravuri2019seeing, shmelkov2018good}, demonstrated that random data augmentation actually had weakened the performance of the model.
+Hence, active researches are ongoing to find ways to optimally sample the generated data \cite{bhattarai2019sampling}, in other words to filter out the "good" generated data after training the GAN.
 In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables, and the confinement loss.
@@
 To reduce over fitting we use the Early stopping method, by saving checkpoints where the best validation mean squared error occurred as we iterate before the model starts to over fit.
-To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm [14] was used.
+To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm \cite{ioffe2015batch} was used.
 
@@
 \hline
-Optimizer & Adam[13]  \\
+Optimizer & Adam\cite{kingma2014adam}  \\
 \hline
@@
 The error at the discriminator's output would then be measured by the means of a chosen metric.
-Introduced by Arjovsky et al [15] the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
-Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty [16].
+Introduced by Arjovsky et al \cite{arjovsky2017wasserstein} the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
+Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty \cite{gulrajani2017improved}.
 The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.
@@
 \hline
-Normalization & Batch Normalization[14] \\
+Normalization & Batch Normalization\cite{ioffe2015batch} \\
 \hline
@@
 In contrast, mini-batch-training, the data set is split into small mini batches of equal sizes, then passed to the model seperately, thus for each epoch there will be exactly length  of the data set devided by the mini batch size steps, and hence slowing down the training process.
-Previous works [17, 18] have firmly proved the advantages of using the correct mini batch size as oppose to large batch sizes.
+Previous works \cite{masters2018revisiting, keskar2016large} have firmly proved the advantages of using the correct mini batch size as oppose to large batch sizes.
 Mini batches allow for more frequent gradient calculations, that results in more stable and reliable training.
 Perhaps one of the main downsides of using large batch size is the poor generalization resulting in a phenomena know as the "generalization gap".
-Active research [19] is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime.
-A closely related recent work (Machine learning approach for computing optical properties of a photonic crystal fiber, Sunny Chugh, Aamir Gulistan, Souvik Ghosh, AND B.M.A.
-Rahman, DEC 2019), conducted their expirements using full batch to train the model.
+Active research \cite{hoffer2017train} is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime.
+A closely related recent work \cite{chugh2019machine}, conducted their expirements using full batch to train the model.
 In this work we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications to fit our purposes.
@@
 
-Next, we compare the testing runtime of the ANN model to that of simulation methods used to compute the confinement loss for 3 different analytes and 16 wavelenghts, i.e a total of 48 values of the confinement loss, demonstrated in Table(num).
+Next, we compare the testing runtime of the ANN model to that of simulation methods used to compute the confinement loss for 3 different analytes and 16 wavelenghts, i.e a total of 48 values of the confinement loss, demonstrated in Table(7).
 This result is absolutely staggering.
@@
 
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,references}	
 \end{document}

### 2020-03-28 src/networks.py
fix: start time

@@ -235,6 +235,7 @@ class Wgan(object):
         self.train_loss_cr = train_loss_cr
 
     def train_wgan(self,tr_data, tr_labels, generator, critic):
+        start_tr = time.time()
         print('\n*****\nTraining The WGAN  \n****\n')
         epochs = self.epochs
         # Continue training
@@ -262,7 +263,7 @@ class Wgan(object):
 
             print('Time for epoch {} is {} sec'.format(epoch + 1, time.time() - start))
 
-        print('\n*****\nTraining run time for the wgan is: {} sec\n****\n'.format(time.time() - start))
+        print('\n*****\nTraining run time for the wgan is: {} sec\n****\n'.format(time.time() - start_tr))
 
     def generate_and_save_data(self,iterations,training, generator, critic):
         print('\n*****\n GENERATING DATA ... \n****\n')

### 2020-03-29 src/networks.py
fix: error-gp

@@ -175,11 +175,11 @@ class Wgan(object):
         return model
 
     def gradient_penalty(self,model,x_real, x_fake):
-        alpha = tf.compat.v1.random_uniform(shape=[self.BATCH_SIZE, self.num_critic_input], minval=0., maxval=1.)
-        diff = x_real - x_fake
+        alpha = tf.compat.v1.random_uniform(shape=[self.BATCH_SIZE, 1], minval=0., maxval=1.)
+        diff = x_fake - x_real
         interpolates = x_real + (alpha * diff)
         gradients = tf.gradients(model(interpolates), [interpolates])[0]
-        slopes = tf.sqrt(tf.reduce_sum(tf.square(gradients)))
+        slopes = tf.sqrt(tf.compat.v1.reduce_sum(tf.square(gradients), reduction_indices=[1]))
         gp = tf.reduce_mean((slopes - 1.) ** 2)
         return gp
 
@@ -194,8 +194,8 @@ class Wgan(object):
             critic_loss = self.critic_loss(real_output, fake_output)
             gp =self. gradient_penalty(critic, data, generated_data)
             critic_loss += self.grad_penalty_weight * gp
-            self.train_loss_cr(critic_loss)
-            tf.summary.scalar('loss', self.train_loss_cr.result(), step=epoch)
+            #self.train_loss_cr(critic_loss)
+            #tf.summary.scalar('loss', self.train_loss_cr.result(), step=epoch)
         gradients_of_critic = cr_tape.gradient(critic_loss, critic.trainable_variables)
         self.critic_optimizer.apply_gradients(zip(gradients_of_critic, critic.trainable_variables))
 
@@ -206,8 +206,8 @@ class Wgan(object):
             generated_data = generator(noise, training=True)
             fake_output = critic(generated_data, training=True)
             gen_loss = self.generator_loss(fake_output)
-            self.train_loss_gen(gen_loss)
-            tf.summary.scalar('loss', self.train_loss_gen.result(), step=epoch)
+            #self.train_loss_gen(gen_loss)
+            #tf.summary.scalar('loss', self.train_loss_gen.result(), step=epoch)
         gradients_of_generator = gen_tape.gradient(gen_loss, generator.trainable_variables)
         self.generator_optimizer.apply_gradients(zip(gradients_of_generator, generator.trainable_variables))
 

### 2020-03-30 src/data_handler.py
Disabled GPU Set threads to 16 Fixed filenames

@@ -29,7 +29,7 @@ def load_data(fname):
     df = data.values
     print(data.head())
 
-    if fname == r'.\data\shuffled_df.xlsx':
+    if fname == r'./data/shuffled_df.xlsx':
         df = df.reshape(432,7)
         x = df[:,:6]
         y = df[:,-1]
@@ -53,7 +53,7 @@ def load_data(fname):
     df = np.concatenate((x,y), axis=1)
     # Save shuffled data frame
     df = pd.DataFrame(df, columns=['Analytes','lambda','Pitch','d1','d2','d3','loss'])
-    df.to_excel(r'.\data\shuffled_df.xlsx', index = False)
+    df.to_excel(r'./data/shuffled_df.xlsx', index = False)
 
     return split_data(x,y)
 
@@ -79,7 +79,7 @@ def augment_data(tr_data, tr_labels, flags):
 
 # Plot wgan progress
 def plot_wgan(epoch, fname):
-    real_data_fname = r'.\data\data.xlsx'
+    real_data_fname = r'./data/data.xlsx'
     x_real, y_real ,_,__,___,____ = load_data(real_data_fname)
 
     data = pd.read_csv(fname).values

### 2020-03-30 src/main.py

@@ -3,6 +3,8 @@ import networks, data_handler, initializer
 from networks import Wgan
 import time
 
+tf.config.experimental.set_visible_devices([], 'GPU')
+tf.config.threading.set_inter_op_parallelism_threads(16)
 FLAGS = initializer.init()
 
 wgan = Wgan(FLAGS)
@@ -11,7 +13,6 @@ generator = wgan.make_generator_model()
 critic = wgan.make_critic_model()
 
 ann_model = networks.make_model(FLAGS)
-
 def train_wgan():
     start = time.time()
     tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname=FLAGS.data)

### 2020-03-31 docs/paper/paper.tex
Few changes

@@
 Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
-Artificial Neural Networks can approximate any function by virtue of the Universality theorem: No matter what the input is there is to be a guaranteed ANN architecture that computes the desired outputs.
+Additionally, ANN can approximate any function proven by Universality theorem \cite{HORNIK1991251}.
 This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a photonic crystal fiber \cite{chugh2019machine}.
@@
 
-In this paper we focus on determining one of the propagation features of a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), proposed in our recent work [21], that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1).
+In this paper, we focus on estimating confinement loss, one of the propagation features of multi-channel Photonic Crystal Fiber (PCF) sensors, using artificial neural networks.
+Specifically, we have based our system on Surface Plasmon Resonance (SPR).
+
+\hl{CK: Continuing from here...}
+
+\hl{and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1).
 We will fix the pattern and geometrical shape of the cladding air holes, and vary the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$.
 Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional neural networks.
+}
 

### 2020-04-01 docs/paper/paper.tex
* System architecture diagram * Few fixes to the text

@@
-\documentclass[draft, a4, 10pt, onecolumn]{IEEEtran}
+\documentclass[draft, a4, 10pt]{IEEEtran}
 
@@
 \usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows, shapes.arrows, decorations.markings, calc}
 \usepackage{pgfplots}
+
 \usepackage[english]{babel}
@@
 \usepackage{cite}
+
+%for flowcharts
+\tikzstyle{testing} = [
+	thick,
+	->,
+	>=stealth
+]
+\tikzstyle{training} = [
+	thick, 
+	decoration={
+		markings,
+		mark=at position 1 with {
+			\arrow[semithick]{open triangle 60}
+		}
+	},
+	double distance=1.4pt, 
+	shorten >= 5.5pt,
+	preaction = {decorate},
+	postaction = {
+		draw,
+		line width=1.4pt,
+		white,
+		shorten >= 4.5pt
+	}
+]
+
+\tikzstyle{data} = [
+	cylinder, 
+	shape border rotate=90, 
+	draw,
+	minimum width=1.5cm, 
+	minimum height=1.2cm,
+	text centered, 
+	draw=black, 
+	line width=0.3mm,
+	shape aspect=.1
+]
+
+\tikzstyle{operation} = [
+	rectangle, 
+	rounded corners,
+	minimum width=2cm, 
+	minimum height=1.2cm,
+	text centered, 
+	draw=black, 
+	line width=0.6mm,
+]
+
+\tikzstyle{sample} = [
+	rectangle, 
+	minimum width=1.2cm, 
+	minimum height=1.2cm,
+	text centered, 
+	draw=black,
+	line width=0.3mm,
+]
+
+\tikzstyle{filter} = [
+	trapezium, 
+	trapezium left angle=70, 
+	trapezium right angle=110, 
+	minimum width=1.5cm, 
+	minimum height=1cm, 
+	text centered, 
+	draw=black, 
+	line width=0.5mm
+]
 
@@
 Specifically, we have based our system on Surface Plasmon Resonance (SPR).
+However, in the experiments section we have demonstrated that the designed system is generic enough to apply to multiple PCF designs.
+Perhaps the most important contribution that augments the success of the proposed method is the use of GAN phase, where the available data is expanded to be used in the training phase.
 
-\hl{CK: Continuing from here...}
+\hl{!! Literature survey !!}
 
-\hl{and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model, as demonstrated in Figure(1).
-We will fix the pattern and geometrical shape of the cladding air holes, and vary the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$.
-Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional neural networks.
-}
+\hl{Use of ANN in PCF}
 
-\begin{figure}
-\centering
-\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{mainalgo.png}
-\caption{}
-\end{figure}
-
-\hl{Literature survey}
+\hl{SPR in PCF}
 
@@
 Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network network.
-The details of the proposed ANN architecture and the GAN is discussed in the following subsections.
+This architecture is illustrated in Figure \ref{fig:overall} The The details of the proposed ANN architecture and the GAN is discussed in the following subsections.
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[node distance=2cm]
+\node (collected) [data] {Collected samples};
+\node (GAN) [operation,below of=collected,xshift=-2cm] {GAN};
+\node (filter) [filter, below of=GAN, text width=2.4cm] {\baselineskip=10pt Filter out-of-range samples\par};
+\node (generated) [data, below of=filter] {Generated samples};
+\node (ann) [operation,below of=generated,xshift=2cm] {ANN};
+\node (testsample) [sample, right of=generated,xshift=2cm,yshift=-1cm, text width=1.2cm] {\baselineskip=10pt Test\par};
+\node (output) [sample, below of=testsample,yshift=-0cm, text width=1.2cm] {\baselineskip=10pt Output\par};
+
+\draw [training] (collected) -- (GAN);
+\draw [training] (GAN) -- (filter);
+\draw [training] (filter) -- (generated);
+\draw [training] (generated) -- (ann);
+\draw [training] (collected) -- (ann);
+\draw [testing] (testsample.west) to [bend right=45] ($(ann.north east)-(0.5,0)$);
+\draw [testing] ($(ann.south east)-(0.5,0)$) to [bend right=45] (output.west);
+	\end{tikzpicture}
+	\caption{System architecture}
+	\label{fig:overall}
+\end{figure}
 
@@
 \label{sec:pcf}
+
+\hl{We will fix the pattern and geometrical shape of the cladding air holes, and vary the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$.
+Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional neural networks.
+}
 

### 2020-04-02 src/basic_tf_ann.py
add: optimized wgan: MPEs/MSEs

@@ -1,12 +1,14 @@
 from __future__ import print_function
-import data_handler
-import tensorflow.compat.v1 as tf
-import scipy as sp
 import time
+import data_handler
+import initializer
 import matplotlib.pyplot as plt
+import tensorflow.compat.v1 as tf
 from tensorflow.python.client import device_lib
 
 tf.disable_eager_execution()
+
+FLAGS = initializer.init()
 
 # Print CPUs / GPUs available
 print(device_lib.list_local_devices())
@@ -15,25 +17,23 @@ print(device_lib.list_local_devices())
 tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
 
 # Augment
-for _ in [1000, 2000, 3000]:
-    tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, _, fname='.\gen_data\gen_data.txt')
+tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, FLAGS)
 
 # Parameters
-learning_rate = 0.001
-training_epochs = 2000
-batch_size = 8
+learning_rate = FLAGS.lr
+training_epochs = FLAGS.epochs
+batch_size = FLAGS.ANN_batch_size
 
 # Network Parameters
-n_hidden = 50
-n_input = 6
-n_outputs = 1
-num_hidden_layers = 6
+n_hidden = FLAGS.num_neurons
+n_input = FLAGS.num_inputs
+n_outputs = FLAGS.num_outputs
+num_hidden_layers = FLAGS.num_layers
 
 # Initializers
 sigma = 1
 weight_initializer = tf.variance_scaling_initializer(mode="fan_avg", distribution="uniform", scale=sigma)
 bias_initializer = tf.zeros_initializer()
-
 
 weights = {
     'h1': tf.Variable(weight_initializer([n_input, n_hidden])),
@@ -45,28 +45,29 @@ biases = {
 }
 
 # Create hidden layers
-for i in range(1,num_hidden_layers):
-    weights['h{}'.format(i+1)] = tf.Variable(weight_initializer([n_hidden, n_hidden]))
-    biases['b{}'.format(i+1)] = tf.Variable(bias_initializer([n_outputs]))
+for i in range(1, num_hidden_layers):
+    weights['h{}'.format(i + 1)] = tf.Variable(weight_initializer([n_hidden, n_hidden]))
[…]

### 2020-04-02 src/data_handler.py

@@ -3,59 +3,82 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 
+
 def split_data(x, y):
-    x = x.reshape(9,3,16,6)
-    y = y.reshape(9,3,16,1)
+    x = x.reshape(9, 3, 16, 6)
+    y = y.reshape(9, 3, 16, 1)
 
     tr_data = x[:7].reshape(7 * 16 * 3, 6)
     tr_labels = y[:7].reshape(7 * 16 * 3, 1)
 
-    merge = np.concatenate((tr_data,tr_labels), axis=1)
+    merge = np.concatenate((tr_data, tr_labels), axis=1)
     sp.random.shuffle(merge)
-    tr_data = merge[:,:6].reshape(7 * 16 * 3, 6)
-    tr_labels = merge[:,-1].reshape(7 * 16 * 3, 1)
+    tr_data = merge[:, :6].reshape(7 * 16 * 3, 6)
+    tr_labels = merge[:, -1].reshape(7 * 16 * 3, 1)
 
-    va_data = x[-2].reshape(1*16*3,6)
-    va_labels = y[-2].reshape(1*16*3,1)
+    va_data = x[-2].reshape(1 * 16 * 3, 6)
+    va_labels = y[-2].reshape(1 * 16 * 3, 1)
 
-    test_data = x[-1].reshape(1*16*3,6)
-    test_labels = y[-1].reshape(1*16*3,1)
+    test_data = x[-1].reshape(1 * 16 * 3, 6)
+    test_labels = y[-1].reshape(1 * 16 * 3, 1)
 
     return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
 
 
 def load_data(fname):
-    data =pd.read_excel(fname)
+    data = pd.read_excel(fname)
     df = data.values
     print(data.head())
 
     if fname == r'./data/shuffled_df.xlsx':
-        df = df.reshape(432,7)
-        x = df[:,:6]
-        y = df[:,-1]
+        df = df.reshape(432, 7)
+        x = df[:, :6]
+        y = df[:, -1]
         # The training data is already shuffled, set shuffle_tr=False
-        return split_data(x,y)
+        return split_data(x, y)
 
-    df = df.reshape(9,3,16,7)
+    df = df.reshape(9, 3, 16, 7)
     sp.random.shuffle(df)
-    df = df.reshape(432,7)
-    analytes = df[:,0]
-    analytes = (analytes*100)%10
[…]

### 2020-04-02 src/initializer.py

@@ -1,4 +1,6 @@
 import tensorflow.compat.v1 as tf
+import os
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '3'
 import json
 
 FLAGS = tf.flags.FLAGS
@@ -6,45 +8,50 @@ FLAGS = tf.flags.FLAGS
 with open('hyper_params.json', 'r') as f:
     params_dict = json.load(f)
 
+# params_dict = json.loads(params_dict)
 wgan_flags = params_dict[0]
-ann_flags  = params_dict[1]
+ann_flags = params_dict[1]
 data_flags = params_dict[2]
 
-
-tf.flags.DEFINE_bool('train_wgan', False,'train wgan, defaul:True')
-tf.flags.DEFINE_bool('generate', False,'generate data, defaul:True')
-tf.flags.DEFINE_bool('train_ann', False,'train ann, defaul:True')
-tf.flags.DEFINE_bool('test_ann', False,'test ann, defaul:True')
+tf.flags.DEFINE_bool('train_wgan', False, 'train wgan, defaul:True')
+tf.flags.DEFINE_bool('generate', False, 'generate data, defaul:True')
+tf.flags.DEFINE_bool('train_ann', False, 'train ann, defaul:True')
+tf.flags.DEFINE_bool('test_ann', False, 'test ann, defaul:True')
 
 tf.flags.DEFINE_integer('wgan_batch_size', wgan_flags['BATCH_SIZE'], 'batch size, default: 12')
 tf.flags.DEFINE_integer('noise_dim', wgan_flags['noise_dim'], 'z_dimension, default:7')
 tf.flags.DEFINE_integer('num_critic_input', wgan_flags['num_critic_input'], 'number of inputs to the critic, default:7')
 tf.flags.DEFINE_integer('n_critic', wgan_flags['n_critic'], 'Critic iterations, default:5')
 tf.flags.DEFINE_integer('grad_penalty_weight', wgan_flags['grad_penalty_weight'], 'Gradient penalty weight, default:10')
-tf.flags.DEFINE_integer('num_examples_to_generate', wgan_flags['num_examples_to_generate'], 'number of examples to generate, default:8')
+tf.flags.DEFINE_integer('num_examples_to_generate', wgan_flags['num_examples_to_generate'],
+                        'number of examples to generate, default:8')
 tf.flags.DEFINE_integer('wgan_epochs', wgan_flags['epochs'], 'WGAN epochs,default:2000')
[…]

### 2020-04-02 src/main.py

@@ -1,35 +1,43 @@
+import os
 import tensorflow.compat.v1 as tf
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '3'
 import networks, data_handler, initializer
-from networks import Wgan
-import time
+from networks import Wgan_optim
 
-tf.config.experimental.set_visible_devices([], 'GPU')
+# tf.config.experimental.set_visible_devices([], 'GPU')
 tf.config.threading.set_inter_op_parallelism_threads(16)
 FLAGS = initializer.init()
+run_config = tf.ConfigProto()
+run_config.gpu_options.allow_growth = True
+sess = tf.Session(config=run_config)
 
-wgan = Wgan(FLAGS)
 
-generator = wgan.make_generator_model()
-critic = wgan.make_critic_model()
-
-ann_model = networks.make_model(FLAGS)
 def train_wgan():
-    start = time.time()
     tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname=FLAGS.data)
-    wgan.train_wgan(tr_data,tr_labels, generator=generator, critic=critic)
+    wgan = Wgan_optim(sess, FLAGS, tr_data, tr_labels)
+    sess.run(tf.global_variables_initializer())
+    wgan.train_wgan()
+
 
 def generate_data():
     # WILL SAVE TO gen_data\gen_data2.txt // Data already generated in gen_data\gen_data.txt#
-    wgan.generate_and_save_data(iterations = FLAGS.gen_iterations, training=False, generator=generator, critic=critic)
+    wgan = Wgan_optim(sess, FLAGS, [], [])
+    sess.run(tf.global_variables_initializer())
+    wgan.generate_data()
+
 
 def train_ann_model():
+    ann_model = networks.make_model(FLAGS)
     # Load the same data used to train the WGAN
-    tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname=FLAGS.shuffled_data)
+    # SPR-based PCF
+    tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname=FLAGS.data)
+    # PCF data
+    # tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_pcf_data(fname=FLAGS.pcf_data)
     # Augment data. To train with only the original real samples, set augment_size = 0.
     # For different augmentations, change the batch_size/ learning_rate accordingly.
[…]

### 2020-04-02 src/networks.py

@@ -1,25 +1,36 @@
 from __future__ import absolute_import, division, print_function, unicode_literals
 from tensorflow import keras
 from tensorflow.keras import layers
+from datetime import datetime
 import numpy as np
 import scipy as sp
 import pandas as pd
-import tensorflow as tf
+import tensorflow.compat.v1 as tf
+import os
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '3'
 import matplotlib.pyplot as plt
 import time
-import os
+import logging
 from tqdm import tqdm
 from scipy.interpolate import UnivariateSpline
 from tensorflow.python.client import device_lib
 
 # Print CPUs / GPUs available
 print(device_lib.list_local_devices())
-# Enable Tensorflow eager execution. This line must be at the top of the script.
-tf.compat.v1.enable_eager_execution()
+# disable Tensorflow eager execution. This line must be at the top of the script.
+tf.disable_eager_execution()
+
+# init logger
+logger = logging.getLogger(__name__)
+logger.setLevel(logging.INFO)
+formatter = logging.Formatter('%(asctime)s:%(name)s:%(message)s')
+stream_handler = logging.StreamHandler()
+stream_handler.setFormatter(formatter)
+logger.addHandler(stream_handler)
+
 
 ############################### ANN MODEL ##########################################
-####################################################################################
-####################################################################################
+
 
 def make_model(flags):
     model = tf.keras.Sequential()
@@ -28,13 +39,19 @@ def make_model(flags):
     num_layers = flags.num_layers
     num_outputs = flags.num_outputs
     batch_norm = flags.batch_norm
+    logger.info('\n[*] Number of inputs: {}'.format(num_inputs))
+    logger.info('\n[*] Number of hidden nodes: {}'.format(num_neurons))
+    logger.info('\n[*] Number of hidden layers: {}'.format(num_layers))
+    logger.info('\n[*] Number of outputs: {}'.format(num_outputs))
+    logger.info('\n[*] Batch Normalization: {}'.format(batch_norm))
     # 1st layer
     model.add(layers.Dense(num_neurons, input_shape=(num_inputs,)))
+    # model.add(layers.BatchNormalization())
     model.add(layers.ReLU())
     # Hidden layers
     for _ in range(num_layers - 1):
[…]

### 2020-04-03 docs/paper/paper.tex
Methodology reorder GAN is almost finished

@@
-\documentclass[draft, a4, 10pt]{IEEEtran}
+\documentclass[draft, 10pt]{IEEEtran}
 
@@
 However, there are two issues with the methods proposed previously.
-Namely, the required number of samples for training and generality of the designed network.
-In this paper, we  propose the use of generative adversarial networks (GAN) to augment the real data set to train a ANN model.
-Experimental analysis suggest that the proposed combination not only accurately predicts the confinement loss even with limited amount of data, but also can work in wider range of methods and geometric configurations.
-Finally, the proposed method is shown to predict the confinement loss over a range of analytes and wavelengths in a completely new set of geometric configuration.
+Namely, the required number of samples for training and the overall accuracy of these methods.
+In this paper, we  propose the use of generative adversarial networks (GAN) to augment the real data set to train an ANN model.
+Experimental analysis suggest that the proposed combination not only accurately predicts the confinement loss even with limited amount of data but also GAN can be used to improve existing methods in the literature.
+Finally, it is shown that this system can predict the confinement loss over a range of analytes and wavelengths in a completely new set of geometric configuration.
 \end{abstract}
@@
 However, in the experiments section we have demonstrated that the designed system is generic enough to apply to multiple PCF designs.
-Perhaps the most important contribution that augments the success of the proposed method is the use of GAN phase, where the available data is expanded to be used in the training phase.
+The most important contribution of this research is the use of GAN phase, where the available data is expanded to be used in the training phase.
 
@@
 These generated samples are filtered to ensure they fall within the applicable range.
-Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network network.
-This architecture is illustrated in Figure \ref{fig:overall} The The details of the proposed ANN architecture and the GAN is discussed in the following subsections.
+Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network.
+This architecture is illustrated in Figure \ref{fig:overall}.
+The details of the proposed ANN architecture and the GAN is discussed in the following subsections.
 
@@
 
+\node (legendtrain) [right of=GAN,xshift=2cm] {};
+\node (legendtrainend) [below of=legendtrain,yshift=1cm] {Training};
+\node (legendtest) [below of=legendtrainend,yshift=1cm] {};
+\node (legendtestend) [below of=legendtest,yshift=1cm] {Testing};
+
 \draw [training] (collected) -- (GAN);
@@
 \draw [testing] ($(ann.south east)-(0.5,0)$) to [bend right=45] (output.west);
+
+\draw [training] (legendtrain) -- (legendtrainend);
+\draw [testing] (legendtest) -- (legendtestend);
+
 	\end{tikzpicture}
@@
 
-\hl{will be split into the subsections.} We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected.
-Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
-Previous works \cite{ravuri2019seeing, shmelkov2018good}, demonstrated that random data augmentation actually had weakened the performance of the model.
-Hence, active researches are ongoing to find ways to optimally sample the generated data \cite{bhattarai2019sampling}, in other words to filter out the "good" generated data after training the GAN.
-In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
-In the following sub-sections we discuss the networks architectures.
+\subsection{Generative adversarial network design}
+\label{ssec:gan}
+
+Generative adversarial networks are introduced in \cite{goodfellow2014generative}.
+We have employed GAN to augment the number of samples that are used in training.
+A GAN is composed of two neural networks: estimator and discriminator.
+The aim of the generator is to transform fully randomized data into data that follows the distribution of the original dataset.
+Discriminator assesses the performance of the generator and provides feedback for training.
+Instead of directly training generator, it is trained through this feedback.
+This paradigm avoids over-fitting the data in the generator side.
+
+It is possible to use different metrics for training in GAN [references here], for this project we have selected WGAN Wasserstein distance metric.
+This variant has been proposed by Arjovsky et al in \cite{arjovsky2017wasserstein}.
+In this system, discriminator is named as critic and it measures the distance between the generated data and the real data.
+The parameters to these networks are given in Table \ref{tbl:gandetails}.
+The reason behind choosing WGAN over other methods is to be able to determine a stopping criteria.
+In a regular GAN system, training is stopped when the generated data is deemed viable by an observer.
+Since GAN is often used in generation of image, video or audio, using a human in the loop is effective.
+However, in our problem, it is not viable for a human to judge the generated data.
+Automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which in turn degrades the performance.
+WGAN uses an adaptive stopping criteria that does not have the issue mentioned above.
+
+Previous works \cite{ravuri2019seeing, shmelkov2018good}, demonstrated that it is possible for random data augmentation to weaken the performance of the model.
+Hence, it is important to sample the generated data in way to prevent performance degradation \cite{bhattarai2019sampling}.
+In this method, we use a simple condition to discard the values that fall out of the desired range for both the independent variables ($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
+
+\hl{CK: continue here.}
+
+Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty \cite{gulrajani2017improved}.
+The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.
+
+In this work, both the Critic and the generator are fully connected feed forward MLP models.
+Tables(2, 3) summarize the details of both networks.
+The input vector to the Critic network consists of the six parameters discussed earlier for the ANN model, in addition to the corresponding confinement loss value, giving a total of seven inputs.
+The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the Critic.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{GAN.png}
+	\caption{}
+\end{figure}
+
+\begin{table}
+	\centering
+	\begin{tabular}{l|l|l}
+		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} \\\hline
+		Hidden layers & 5 & 5 \\
+		Neurons & $ batchsize~2^{2} $ & $batchsize~2^{layers}$ \\
+		Activation & ReLU & Leaky ReLU \\
+		Optimizer & Adam [ref] & Adam [ref] \\
+		Normalization & - & Batch \cite{ioffe2015batch} \\
+	\end{tabular}
+	\caption{Details of WGAN model}
+	\label{tbl:gandetails}
+\end{table}
 
@@
 \label{ssec:ann}
-The ANN model employed in this research is a fully-connected feed-forward MLP (Multi Layer Perceptron) consisting of an input layer, an output layer, and 5 hidden layers.
-Each hidden layer consists of 50 neurons and uses Rectified Linear Unit (ReLU) activation function.
 
@@
 \label{ssec:ann}
-The ANN model is a fully-connected feed-forward Multi Layer Perceptron (MLP) model.
-Table(1) summarizes the details of the model.
-To reduce over fitting we use the Early stopping method, by saving checkpoints where the best validation mean squared error occurred as we iterate before the model starts to over fit.
-To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm \cite{ioffe2015batch} was used.
+The ANN model employed in this research is a fully-connected feed-forward MLP (Multi Layer Perceptron) consisting of an input layer, an output layer, and 5 hidden layers.
+Each hidden layer consists of 50 neurons and uses Rectified Linear Unit (ReLU) activation function.
+Table \ref{tbl:anndetails} summarizes the details of the model.
+Due to the nature of the problem, over-fitting is an important issue.
+We have used early stopping method [ref] to reduce over-fitting.
+\hl{This method works by saving checkpoints where the best validation mean squared error occurred as it iterates before the model starts to over-fit.} To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm \cite{ioffe2015batch} was used.
 
@@
 \centering
-\scalebox{1.1}{
     \begin{tabular}{|l|l|}
@@
     \end{tabular}
-}
 \caption{Detailes of the ANN model}
-\end{table}
-
-\subsection{Generative Adversarial network design}
-\label{ssec:gan}
-
-GANs consist of two neural networks, as shown in Figure (2).
-The first of which called a discriminator, that gives an estimate of the probability that a given input is real or generated (fake).
-Whereas the second network is referred to as the generator, which outputs data samples from a random noise vector called a latent variable usually given the symbol $z$ supplied at its input.
-The error at the discriminator's output would then be measured by the means of a chosen metric.
-Introduced by Arjovsky et al \cite{arjovsky2017wasserstein} the Wasserstein distance metric (or the earth mover distance) proved to be very effective, instead of discriminating whether an input is real or generated, the discriminator provides a criticism of how far the generated data from the real data is, hence the discriminator network is referred to as the critic in the WGANs.
-Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty \cite{gulrajani2017improved}.
-The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.
-In this work, both the Critic and the generator are fully connected feed forward MLP models.
-Tables(2, 3) summarize the details of both networks.
-The input vector to the Critic network consists of the six parameters discussed earlier for the ANN model, in addition to the corresponding confinement loss value, giving a total of seven inputs.
-The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the Critic.
-
-\begin{figure}
-\centering
-\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{GAN.png}
-\caption{}
-\end{figure}
-
-\begin{table}[h]
-\centering
-\begin{tabular}{|l|l|}
-\hline
-Number of hidden layers & 5  \\
-\hline
-Number of neurons per hidden layers & $ minibatchsize\times2^{number of layers} $  \\
-\hline
-Activation function & Leaky Rectified Linear Unit (LeakyReLU)  \\
-\hline
-Optimizer & Adam[13]  \\
-\hline
-    \end{tabular}
-\caption{Details of the Critic model}    
-\end{table}
-
-\begin{table}[h]
-\centering
- \begin{tabular}{|l|l|}
-    \hline
-Number of hidden layers & 5 \\
-\hline
-Number of neurons per hidden layers & $ minibatchsize\times2^{2} $  \\
-\hline
-Activation function & Rectified Linear Unit (ReLU)  \\
-\hline
-Optimizer & Adam[13]  \\
-\hline
-Normalization & Batch Normalization\cite{ioffe2015batch} \\
-\hline
-    \end{tabular}
-\caption{Details of the Generator model}
+\label{tbl:anndetails}
 \end{table}

### 2020-04-04 docs/paper/paper.tex
WGAN writing is finished

@@
 In this section details of the proposed method is discussed.
-At the start, a GAN is trained to generate additional data by using training samples.
+Training of the system contains two phases: a GAN phase and regression training phase.
+At the start of the training, a GAN is trained to generate additional data by using training samples.
 These generated samples are filtered to ensure they fall within the applicable range.
 Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network.
+At the end of the training, the ANN that is trained for the regression task will be used to decide the output of a particular input parameters.
 This architecture is illustrated in Figure \ref{fig:overall}.
@@
 We have employed GAN to augment the number of samples that are used in training.
-A GAN is composed of two neural networks: estimator and discriminator.
+A GAN is composed of two neural networks: generator and discriminator.
 The aim of the generator is to transform fully randomized data into data that follows the distribution of the original dataset.
@@
 In this system, discriminator is named as critic and it measures the distance between the generated data and the real data.
-The parameters to these networks are given in Table \ref{tbl:gandetails}.
 The reason behind choosing WGAN over other methods is to be able to determine a stopping criteria.
@@
 WGAN uses an adaptive stopping criteria that does not have the issue mentioned above.
+Additionally, we have selected to incorporate Gradient penalty to improve WGAN proposed in \cite{gulrajani2017improved}.
+This improved WGAN system converges in a stable manner without having to fine tune hyper-parameters of the system.
+The flowchart of this system is given in Figure \ref{fig:gan}.
+
+In this work, both the Critic and the generator are fully connected feed forward MLP models.
+The details of the networks are given in Table \ref{tbl:gandetails}.
+The output from this system should be input and output pairs that will be used to train ANN part of the system.
+In our PCF system we have 6 input parameters and a single output parameter making a total of 7 parameters that will be used in the GAN phase.
+In Section \ref{sec:exp}, we have experimented using a different PCF system with different inputs, resulting a different number of parameters for the system.
+The generator is supplied with the same number of parameters as its expected output, that is 7 for our PCF system.
+These parameters are generated using Gaussian noise and is called latent variable.
+Once the training phase is complete, the generator and the filter is used to augment the number of training samples that are available for ANN.
 
@@
 Hence, it is important to sample the generated data in way to prevent performance degradation \cite{bhattarai2019sampling}.
-In this method, we use a simple condition to discard the values that fall out of the desired range for both the independent variables ($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
-
-\hl{CK: continue here.}
-
-Throughout this paper we will use yet the improved WGAN, the WGAN with Gradient penalty \cite{gulrajani2017improved}.
-The improved WGAN converges in a stable manner with least efforts made to tune the hyper- parameters of both networks constituting the GAN, which can be very daunting.
-
-In this work, both the Critic and the generator are fully connected feed forward MLP models.
-Tables(2, 3) summarize the details of both networks.
-The input vector to the Critic network consists of the six parameters discussed earlier for the ANN model, in addition to the corresponding confinement loss value, giving a total of seven inputs.
-The generator is supplied with random noise vector having a dimension of $7$, and outputs a vector that resembles that of the input to the Critic.
+In the proposed system, we have included a filtering step for the generated data.
+This step uses a simple condition to discard the values that fall out of the desired range, for both the independent variables ($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
 
@@
 	\centering
-	\includegraphics[trim= 0 0 0 0, clip, width=0.9\textwidth]{GAN.png}
-	\caption{}
+	\begin{tikzpicture}
+
+	\end{tikzpicture}
+	\caption{WGAN architecture}
+	\label{fig:gan}
 \end{figure}
@@
 		Hidden layers & 5 & 5 \\
-		Neurons & $ batchsize~2^{2} $ & $batchsize~2^{layers}$ \\
+		Neurons & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ \\
 		Activation & ReLU & Leaky ReLU \\
@@
 \end{table}
+
+\hl{CK: continue here.}
 

### 2020-04-04 docs/paper/paper.tex
WGAN graph

@@
 	rectangle, 
+	minimum width=1.2cm, 
+	minimum height=1.2cm,
+	text centered, 
+	draw=black,
+	line width=0.3mm,
+]
+
+\tikzstyle{metric} = [
+	diamond, 
 	minimum width=1.2cm, 
@@
 	\centering
-	\begin{tikzpicture}
+	\begin{tikzpicture}[node distance=2cm]
+		\node(latent) 	[filter,text width=1.4cm] 		{\baselineskip=10pt Noise generator\par};
+		\node(generator)[operation,below of=latent] 	{Generator};
+		\node(generated)[data, below of=generator,
+						 text width=1.4cm]				{\baselineskip=10pt Generated samples\par};
+		\node(collected)[data, right of=generated,
+						 xshift=1cm,text width=1.4cm]	{\baselineskip=10pt Collected samples\par};
+		\node(critic)	[operation,below of=generated,
+						 xshift=1.5cm]					{Critic};
+		\node(metric)   [metric,below of=critic,
+						 text width=1.4cm, yshift=-.2cm]{\baselineskip=10pt{}Wasserstein distance\par};
 
+		\draw [training] (latent) -- (generator) node [pos=.5, right, xshift=0.1cm] (z) {Latent variable};
+		\draw [training] (generator) -- (generated);
+		\draw [training] (generated) -| (critic);
+		\draw [training] (collected) -| (critic);
+		\draw [training] (critic) -- (metric);
+		\draw [testing]  (metric.east) - ++(1,0) |-  (critic.east);
+		\draw [testing]  (metric.west) - ++(-2.2,0) |-  (generator.west);
 	\end{tikzpicture}
-	\caption{WGAN architecture}
+	\caption{WGAN training}
 	\label{fig:gan}

### 2020-04-07 docs/paper/paper.tex
* ANN * Started working on experiments

@@
 Instead of directly training generator, it is trained through this feedback.
-This paradigm avoids over-fitting the data in the generator side.
+This paradigm avoids over-fitting the data.
 
@@
 
-		\draw [training] (latent) -- (generator) node [pos=.5, right, xshift=0.1cm] (z) {Latent variable};
+		\draw [training] (latent) -- (generator) node [pos=.5, left, xshift=-0.1cm] (z) {Latent variable};
 		\draw [training] (generator) -- (generated);
@@
 		Activation & ReLU & Leaky ReLU \\
-		Optimizer & Adam [ref] & Adam [ref] \\
+		Optimizer & Adam \cite{kingma2014adam} & Adam \cite{kingma2014adam} \\
 		Normalization & - & Batch \cite{ioffe2015batch} \\
@@
 
-\hl{CK: continue here.}
-
 \subsection{Artificial neural network design}
@@
 
-Adam \cite{kingma2014adam} as the optimizer and the mean squared error as the loss/cost function.
-To reduce overfitting we use the Early stopping method, that is by saving checkpoints where the best validation mean squared error occurred as we iterate.
-To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used \cite{ioffe2015batch}.
+The ANN model employed in this research is a fully-connected feed-forward Multi Layer Perceptron (MLP) consists of an input layer, an output layer, and 5 hidden layers.
+Each hidden layer contains 50 neurons and uses Rectified Linear Unit (ReLU) activation function.
+Table \ref{tbl:anndetails} summarizes the details of this model.
+We have adopted Adam \cite{kingma2014adam} as the optimizer and the mean squared error as the loss/cost function.
 
-We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected.
-Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
-Previous works \cite{ravuri2019seeing, shmelkov2018good}, demonstrated that random data augmentation actually had weakened the performance of the model.
-Hence, active researches are ongoing to find ways to optimally sample the generated data \cite{bhattarai2019sampling}, in other words to filter out the "good" generated data after training the GAN.
-In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables, and the confinement loss.
-In the following sub-sections we discuss the networks architectures.
-Before we proceed, it is worth mentioning that the choices made for the parameters of the networks are by no means a robust set of rules, rather, they are rules of thumb and heuristics, as no such rules have been yet developed for ANN models.
+Due to the nature of the problem, over-fitting is an important issue.
+We have used early stopping method to reduce over-fitting.
+In this method, it is possible to terminate and go back to a previous state if overall validation error increases.
+Thus instead of being forced into a worse classifier, training is terminated earlier.
+In addition, we use Batch Normalization algorithm \cite{ioffe2015batch} to accelerate training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.
 
-\subsection{Artificial neural network design}
-\label{ssec:ann}
-The ANN model employed in this research is a fully-connected feed-forward MLP (Multi Layer Perceptron) consisting of an input layer, an output layer, and 5 hidden layers.
-Each hidden layer consists of 50 neurons and uses Rectified Linear Unit (ReLU) activation function.
-Table \ref{tbl:anndetails} summarizes the details of the model.
-Due to the nature of the problem, over-fitting is an important issue.
-We have used early stopping method [ref] to reduce over-fitting.
-\hl{This method works by saving checkpoints where the best validation mean squared error occurred as it iterates before the model starts to over-fit.} To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm \cite{ioffe2015batch} was used.
+In proposed system, the ANN is trained using the samples from the original dataset and the augmented samples generated by the GAN phase.
+Please note that the samples that are selected to be used in training is not used in the training phase.
 
-\begin{table}[h]
+\begin{table}
 \centering
-    \begin{tabular}{|l|l|}
+    \begin{tabular}{l|l}
+		Hidden layers & 6  \\
 		\hline
-Number of hidden layers & 6  \\
-\hline
-Number of neurons per hidden layers & 50  \\
+		Neurons per hidden layer & 50  \\
 		\hline
@@
 		Loss function& Mean Squared Error (MSE) \\
-\hline
     \end{tabular}
@@
 \label{sec:pcf}
+
+A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM.
+This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
+The labels are the confinement loss of the PCF.
+The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36)).
 
@@
 
-A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM.
-This length of the data set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent.
-This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
-The labels are the confinement loss of the PCF.
-The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36)).
-Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing.
+In order to prove the effectiveness of the proposed setup, we have performed multiple experiments over two datasets.
+We have built the first dataset that is used in the experiments.
+This is \hl{an SPR PCF configuration ...
+and collected using FV-FEM.} Details of this dataset is explained in Section \ref{sec:pcf}.
+Seven configurations were randomly selected for training both the GAN and the ANN, one configuration was held out for validation, and the last one is used for testing.
+Slicing the data this way allowed us to guide the network to predict the loss on a completely different configuration.
+
+Additionally, we have used the dataset that has been used in [paper0].
+\hl{This dataset contains 1000 samples.
+Inputs to this data is ....
+and outputs are ....} We have only used confinement loss for the output.
+
+\hl{CK: continue here.}
+
 By slicing the data set this way we are guiding the network to learn an entirely new set of geometric properties, and this is the reason what made the task impossible, since we only have nine configurations, as we discussed at the beginning of this subsection.

### 2020-04-07 docs/paper/paper.tex
* More work on experimental results * Added normalization information for ANN * Combined GAN and ANN details into a single table

@@
 Additionally, ANN can approximate any function proven by Universality theorem \cite{HORNIK1991251}.
-This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a photonic crystal fiber \cite{chugh2019machine}.
+This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a photonic crystal fiber \cite{paper0}.
 
@@
 Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network.
-At the end of the training, the ANN that is trained for the regression task will be used to decide the output of a particular input parameters.
+At the end of the training, the ANN that is trained for the regression task will be used to decide the containment loss  of a set of input parameters.
 This architecture is illustrated in Figure \ref{fig:overall}.
-The details of the proposed ANN architecture and the GAN is discussed in the following subsections.
+The details of the proposed GAN and ANN architecture is discussed in the following subsections.
 
@@
 In this work, both the Critic and the generator are fully connected feed forward MLP models.
-The details of the networks are given in Table \ref{tbl:gandetails}.
+The details of the networks are given in Table \ref{tbl:anndetails}.
 The output from this system should be input and output pairs that will be used to train ANN part of the system.
@@
 
-\begin{table}
+\begin{table*}
 	\centering
-	\begin{tabular}{l|l|l}
-		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} \\\hline
-		Hidden layers & 5 & 5 \\
-		Neurons & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ \\
-		Activation & ReLU & Leaky ReLU \\
-		Optimizer & Adam \cite{kingma2014adam} & Adam \cite{kingma2014adam} \\
-		Normalization & - & Batch \cite{ioffe2015batch} \\
+	\begin{tabular}{l|l|l|l}
+		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} & \textbf{Regressor} \\\hline
+		Hidden layers & 5 & 5 & 6 \\
+		Neurons in hidden layers & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ & 50 \\
+		Activation function & ReLU & Leaky ReLU & ReLU \\
+		Optimizer & Adam \cite{kingma2014adam} & Adam & Adam \\
+		Input normalization & Z-score & Z-score & Z-score \\
+		Layer normalization & - & Batch \cite{ioffe2015batch} & Batch \\
+		Loss function & MSE & MSE & MSE \\
 	\end{tabular}
-	\caption{Details of WGAN model}
-	\label{tbl:gandetails}
-\end{table}
+	\caption{Details of ANN models}
+	\label{tbl:anndetails}
+\end{table*}
 
@@
 The ANN model employed in this research is a fully-connected feed-forward Multi Layer Perceptron (MLP) consists of an input layer, an output layer, and 5 hidden layers.
+The ANN is designed and trained to estimate containment loss in a regression configuration.
+We have applied $log_{10}$ to confinement loss in order to keep its numeric stability across a wide range.
 Each hidden layer contains 50 neurons and uses Rectified Linear Unit (ReLU) activation function.
 Table \ref{tbl:anndetails} summarizes the details of this model.
-We have adopted Adam \cite{kingma2014adam} as the optimizer and the mean squared error as the loss/cost function.
+We have adopted Adam \cite{kingma2014adam} as the optimizer and the mean squared error (MSE) as the loss/cost function.
 
@@
 In proposed system, the ANN is trained using the samples from the original dataset and the augmented samples generated by the GAN phase.
-Please note that the samples that are selected to be used in training is not used in the training phase.
-
-\begin{table}
-\centering
-    \begin{tabular}{l|l}
-		Hidden layers & 6  \\
-		\hline
-		Neurons per hidden layer & 50  \\
-		\hline
-		Activation function & Rectified Linear Unit (ReLU)  \\
-		\hline
-		Optimizer & Adam\cite{kingma2014adam}  \\
-		\hline
-		Loss function& Mean Squared Error (MSE) \\
-    \end{tabular}
-	\caption{Detailes of the ANN model}
-	\label{tbl:anndetails}
-\end{table}
+Additionally, we use z-score normalization (standardization).
+The parameters to the normalizer is calculated through training samples and it is applied to all samples that will be used with the regressor.
+This includes testing and training samples.
+Please note that the samples that are selected to be used in training is not used in the training phase and any normalization that is applied to them are applied during testing phase.
 
@@
 Slicing the data this way allowed us to guide the network to predict the loss on a completely different configuration.
+Please note that we have applied $log_{10}$ to confinement loss to scale it.
 
-Additionally, we have used the dataset that has been used in [paper0].
+Additionally, we have used the dataset that has been used in \cite{paper0}.
 \hl{This dataset contains 1000 samples.
 Inputs to this data is ....
-and outputs are ....} We have only used confinement loss for the output.
+and outputs are ....} We have only used log of confinement loss as the output.
+
+We have used mean square error as in the comparisons.
+All algorithms are implemented using TensorFlow library in Python and experiments are performed on laptop with Intel i7-5600 CPU and 8GB of RAM.
+TensorFlow library is set to use only CPU for the experiments.
+
+We have performed \hl{this and that experiments} which are discussed in the following sections.
 
 \hl{CK: continue here.}
-
-By slicing the data set this way we are guiding the network to learn an entirely new set of geometric properties, and this is the reason what made the task impossible, since we only have nine configurations, as we discussed at the beginning of this subsection.
-In contrast, randomly shuffling the data set as a whole is an easy task in this situation, and the ANN model would make great predictions on the test set, however a sense of generality towards new geometric sets will be lost.
-
-This data was preprocessed before fed in the networks.
-The indices of refraction  are very close, which made it quiet difficult for the neural networks to differentiate between them, after many trials, the best choice was to take only the tens digit of ${134, 135, 136}$, giving ${4, 5, 6}$.
-Finally, we transform the confinement loss to the log scale, for the purpose of shortening the distances between the confinement loss points.
-
-\hl{Metrics used in the comparisons}
 
@@
 Active research \cite{hoffer2017train} is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime.
-A closely related recent work \cite{chugh2019machine}, conducted their expirements using full batch to train the model.
+A closely related recent work \cite{paper0}, conducted their expirements using full batch to train the model.
 In this work we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications to fit our purposes.

### 2020-04-08 src/data_handler.py
add: kfolds_split

@@ -2,27 +2,40 @@ import scipy as sp
 import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
+from sklearn.preprocessing import StandardScaler
+import initializer
 
+FLAGS = initializer.init()
 
-def split_data(x, y):
-    x = x.reshape(9, 3, 16, 6)
-    y = y.reshape(9, 3, 16, 1)
+def split_data(x, y, kf=False):
+    if kf:
+        x = x.reshape(8, 3, 16, 6)
+        y = y.reshape(8, 3, 16, 1)
+    else:
+        x = x.reshape(9, 3, 16, 6)
+        y = y.reshape(9, 3, 16, 1)
+
+    if FLAGS.k_fold and not kf:
+        return [x,y]
 
     tr_data = x[:7].reshape(7 * 16 * 3, 6)
     tr_labels = y[:7].reshape(7 * 16 * 3, 1)
-
+    #Shuffle tr data
     merge = np.concatenate((tr_data, tr_labels), axis=1)
     sp.random.shuffle(merge)
     tr_data = merge[:, :6].reshape(7 * 16 * 3, 6)
     tr_labels = merge[:, -1].reshape(7 * 16 * 3, 1)
 
-    va_data = x[-2].reshape(1 * 16 * 3, 6)
-    va_labels = y[-2].reshape(1 * 16 * 3, 1)
-
-    test_data = x[-1].reshape(1 * 16 * 3, 6)
-    test_labels = y[-1].reshape(1 * 16 * 3, 1)
-
-    return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
+    if kf:
+        va_data = x[-1].reshape(1 * 16 * 3, 6)
+        va_labels = y[-1].reshape(1 * 16 * 3, 1)
+        return [tr_data, tr_labels, va_data, va_labels]
+    else:
+        va_data = x[-2].reshape(1 * 16 * 3, 6)
+        va_labels = y[-2].reshape(1 * 16 * 3, 1)
+        test_data = x[-1].reshape(1 * 16 * 3, 6)
+        test_labels = y[-1].reshape(1 * 16 * 3, 1)
+        return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
 
 
 def load_data(fname):
@@ -35,18 +48,21 @@ def load_data(fname):
         x = df[:, :6]
         y = df[:, -1]
         # The training data is already shuffled, set shuffle_tr=False
[…]

### 2020-04-08 src/initializer.py

@@ -13,11 +13,13 @@ wgan_flags = params_dict[0]
 ann_flags = params_dict[1]
 data_flags = params_dict[2]
 
+tf.flags.DEFINE_bool('k_fold', False, 'Use Kfold')
 tf.flags.DEFINE_bool('train_wgan', False, 'train wgan, defaul:True')
 tf.flags.DEFINE_bool('generate', False, 'generate data, defaul:True')
 tf.flags.DEFINE_bool('train_ann', False, 'train ann, defaul:True')
 tf.flags.DEFINE_bool('test_ann', False, 'test ann, defaul:True')
 
+tf.flags.DEFINE_integer('save_step',wgan_flags['save_step'], 'Wgan save step')
 tf.flags.DEFINE_integer('wgan_batch_size', wgan_flags['BATCH_SIZE'], 'batch size, default: 12')
 tf.flags.DEFINE_integer('noise_dim', wgan_flags['noise_dim'], 'z_dimension, default:7')
 tf.flags.DEFINE_integer('num_critic_input', wgan_flags['num_critic_input'], 'number of inputs to the critic, default:7')

### 2020-04-08 src/networks.py

@@ -67,8 +67,22 @@ def train_model(model, tr_data, tr_labels, va_data, va_labels, flags):
     epochs = flags.epochs
     lr = flags.lr
     batch_size = flags.ANN_batch_size
-    save_dir = flags.save_dir
-    chkdir = flags.chkdir
+    if flags.k_fold:
+        cur_time = datetime.now().strftime("%Y%m%d-%H%M")
+        if not os.path.isdir('./trained-kf-models/{}'.format(cur_time)):
+            os.makedirs('./trained-kf-models/{}'.format(cur_time))
+
+        if not os.path.isdir('./trained-kf-weights/{}'.format(cur_time)):
+            os.makedirs('./trained-kf-weights/{}'.format(cur_time))
+
+        save_dir = "./trained-kf-models/{}/model.h5".format(cur_time)
+        chkdir = "./trained-kf-weights/{}/weights.hdf5".format(cur_time)
+        flags.model_to_test = chkdir
+
+    if not flags.k_fold:
+        save_dir = flags.save_dir
+        chkdir = flags.chkdir
+
     logger.info('\n[*] learning rate: {}'.format(lr))
     logger.info('\n[*] Batch size: {}'.format(batch_size))
     logger.info('\n[*] Epoch: {}'.format(epochs))
@@ -110,6 +124,34 @@ def load_model(model, load_type, dir):
 def test_model(model, test_data, test_labels, augment_size=0, plot=True):
     start = time.time()
     predictions = model.predict([test_data])
+    print(predictions.shape)
+    MSE = np.square(np.subtract(test_labels.reshape(int(len(test_labels)), 1), predictions)).mean()
+    wavelength = sp.arange(500, 820, 20)
+    cur_time = datetime.now().strftime("%Y%m%d-%H%M")
+
+    if not os.path.isdir('./kfold-predictions-vs-wavelength/{}'.format(cur_time)):
+        os.makedirs('./kfold-predictions-vs-wavelength/{}'.format(cur_time))
+
+    if not os.path.isdir('./kfold-predictions-vs-labels/{}'.format(cur_time)):
+        os.makedirs('./kfold-predictions-vs-labels/{}'.format(cur_time))
+
+    if not os.path.isdir('./kfold-MSEs'.format(cur_time)):
+        os.makedirs('./kfold-MSEs'.format(cur_time))
+
[…]

### 2020-04-08 src/networks.py
add: batch_norm

@@ -46,7 +46,8 @@ def make_model(flags):
     logger.info('\n[*] Batch Normalization: {}'.format(batch_norm))
     # 1st layer
     model.add(layers.Dense(num_neurons, input_shape=(num_inputs,)))
-    # model.add(layers.BatchNormalization())
+    if batch_norm:
+     model.add(layers.BatchNormalization())
     model.add(layers.ReLU())
     # Hidden layers
     for _ in range(num_layers - 1):

### 2020-04-09 docs/paper/paper.tex
* Small fixes

@@
 		Optimizer & Adam \cite{kingma2014adam} & Adam & Adam \\
-		Input normalization & Z-score & Z-score & Z-score \\
+		Input normalization & None & Z-score (for collected samples) & Z-score \\
 		Layer normalization & - & Batch \cite{ioffe2015batch} & Batch \\
-		Loss function & MSE & MSE & MSE \\
+		Loss function & -Critic(generated) & Critic(generated) - Critic(collected) & MSE \\
 	\end{tabular}
@@
 
-We have performed \hl{this and that experiments} which are discussed in the following sections.
+In the following subsections, we have performed experiments to show the performance of the base ANN system by its own comparing with the state-of-the-art method in the literature, improvement gained by employing GAN phase, and finally the computational cost of the overall system compared to the simulator.
+All numeric comparison results are average of 10 executions.
 

### 2020-04-12 docs/paper/paper.tex
* Rearranged some figures * Fixed some wording

@@
 Namely, the required number of samples for training and the overall accuracy of these methods.
-In this paper, we  propose the use of generative adversarial networks (GAN) to augment the real data set to train an ANN model.
+In this paper, we  propose the use of generative adversarial networks (GAN) to augment the real dataset to train an ANN model.
 Experimental analysis suggest that the proposed combination not only accurately predicts the confinement loss even with limited amount of data but also GAN can be used to improve existing methods in the literature.
@@
 
-Machine Learning (ML) techniques are coming to the forefront of many fields, surpassing human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
+Machine Learning (ML) techniques are becoming a common tool in many fields, surpassing human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
 Additionally, ANN can approximate any function proven by Universality theorem \cite{HORNIK1991251}.
@@
 	\centering
+	\caption{Details of ANN models}
 	\begin{tabular}{l|l|l|l}
@@
 	\end{tabular}
-	\caption{Details of ANN models}
 	\label{tbl:anndetails}
@@
 
-A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM.
-This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
+A labelled dataset of only 432 samples was collected in this work, through simulations using FV-FEM.
+This dataset consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
 The labels are the confinement loss of the PCF.
@@
 
+\def\dszero{Zero}
+
 In order to prove the effectiveness of the proposed setup, we have performed multiple experiments over two datasets.
@@
 This is \hl{an SPR PCF configuration ...
-and collected using FV-FEM.} Details of this dataset is explained in Section \ref{sec:pcf}.
+and collected using FV-FEM.} Details of this dataset is explained in Section \ref{sec:pcf} and it is referred as SPR dataset.
 Seven configurations were randomly selected for training both the GAN and the ANN, one configuration was held out for validation, and the last one is used for testing.
@@
 and outputs are ....} We have only used log of confinement loss as the output.
+This dataset is referred as \dszero.
+Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}.
 
@@
 In the following subsections, we have performed experiments to show the performance of the base ANN system by its own comparing with the state-of-the-art method in the literature, improvement gained by employing GAN phase, and finally the computational cost of the overall system compared to the simulator.
-All numeric comparison results are average of 10 executions.
+All numeric comparison results are averaged over multiple executions.
+
+\begin{table}
+\centering
+\caption{Datasets that are used in experiments}
+\begin{tabular}{l|l|l}
+	~ & SPR & \dszero \\\hline
+	Samples & 432 & 1117\\
+	Configurations & 9 & - \\
+	Parameters & 6 & 5 \\
+	Output & $log_{loss}$ & $log_{loss}$ \\
+	Testing & 48 (1 configuration) & 10\% \\
+	Testing method & 9-fold & 10-fold \\
+\end{tabular}
+\label{tbl:dataset}
+\end{table}
+
+\subsection{Performance of ANN}
+
+In this set of experiments, we have analyzed the performance of the proposed ANN design.
+The first experiment involves in training loss over SPR dataset.
+In this experiment, we have trained ANN model for up to 2000 epochs and reported the training loss in Figure \ref{chart:trainingmse}.
+According to this experiment, training our ANN architecture more than 1000 epochs does not yield any significant improvement.
+Therefore, we have set the training epoch limit to 1000 in subsequent experiments.
 
@@
 
-\subsection{Performance of ANN}
-
-We train the ANN model for more than 2000 epochs, starting from the original data set.
-Then we augment the latter set by 1000 generated samples by our WGAN-GP, which will be demonstrated in the next subsection, and train again with the new augmented data set.
-The following table summarizes the hyper-parameters chosen for the ANN model:
-\begin{table}[h]
+\begin{table*}[h]
 \centering
@@
 \caption{Hyper-parameters chosen for the ANN model, where $\beta_{1}$ and $\beta_{2}$ are a part of Adam parameters}
-\end{table}
+\end{table*}
 
-\newpage
 The MSE on the training sets ranged from 0.0030 to 0.0050.
-For all training data sets the MSE decreased in an acceptable manner.
+For all training datasets the MSE decreased in an acceptable manner.
 Next, we plot the predictions the ANN model made on the test set, after training using only the original set.
@@
 
-\begin{figure}[h]
-	\hspace*{-0.07\textwidth}
-	\begin{subfigure}{.5\textwidth}
+\begin{figure}
     \begin{tikzpicture}
 		\begin{axis}[
-		xlabel=$Epochs$, 
-		ylabel=$Training \space MSE$,
-		title={Training MSE of the ANN model},
+		xlabel=Epochs, 
+		ylabel=Training \space MSE,
+		width=0.48\textwidth,
 		grid=both,
@@
 		major grid style={gray!25},
-		width=1.1\linewidth,
 		no marks]
@@
 	\end{tikzpicture}
-	\end{subfigure}\hspace{0.1\textwidth}
-	\begin{subfigure}{.5\textwidth}
+	\caption{Training MSE of the ANN model}
+	\label{chart:trainingmse}
+\end{figure}
+
+\begin{figure}
 \begin{tikzpicture}
@@
 		major grid style={gray!25},
-			width=1.1\linewidth]
+		width=0.48\textwidth
+	]
 		\addplot[
 			only marks,
-			mark size=2.9pt, mark=o, color=red, fill=red] %
-			table{dataset_336.txt};
+			mark size=2.9pt, mark=o, color=red, fill=red
+		] table{dataset_336.txt};
 		\addlegendentry{$Predicted$}
-			\addplot[line width=1pt,solid,color=blue]  %
-			table{y.txt};
+
+		\addplot[
+			line width=1pt,
+			solid,color=blue
+		] table{y.txt};
 		\addlegendentry{$Actual$}
+
 	\end{axis}
 \end{tikzpicture}
-	\end{subfigure}
-	\caption{}
 \end{figure}
-
-    \newpage
 
@@
 During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in Figure(4).
-In this subsection we discuss the results of augmenting the real data set with generated samples.
-Figure(4) demonstrates the predictions made by the ANN model after training with different sizes of the data set.
+In this subsection we discuss the results of augmenting the real dataset with generated samples.
+Figure(4) demonstrates the predictions made by the ANN model after training with different sizes of the dataset.
 This might look paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data.
@@
 Or the sampling strategy adopted is poor.
-But the most convincing reason is the limited original training data set size of 336 samples, used to train the WGAN model in the first place.
+But the most convincing reason is the limited original training dataset size of 336 samples, used to train the WGAN model in the first place.
 After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved what we set out to accomplish at the beginning, to improve the accuracy of the ANN model by artificially expanding the original set.
 
-\hspace{-0.07\textwidth}
-\begin{figure}[h]
+\begin{figure}
     \begin{subfigure}{.5\textwidth}
@@
 \end{figure}
-\newpage
+
 It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(5).
@@
 \end{figure}
-\newpage
+
 \subsection{Computational performance}
@@
 \newline
-The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, mini batch size, data set size, number of epochs, the framework used to code the model, and of course the specifications of the machine.
+The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, mini batch size, dataset size, number of epochs, the framework used to code the model, and of course the specifications of the machine.
 In this work we fixed the number of epochs to 2000 and executed training using Tensorflow(Keras) and Pytorch frameworks.
@@
 It is worth mentioning the differences between training with full batch or mini batches.
-In full batch training, the whole data set is passed to the model for each iteration.
-In contrast, mini-batch-training, the data set is split into small mini batches of equal sizes, then passed to the model seperately, thus for each epoch there will be exactly length  of the data set devided by the mini batch size steps, and hence slowing down the training process.
+In full batch training, the whole dataset is passed to the model for each iteration.
+In contrast, mini-batch-training, the dataset is split into small mini batches of equal sizes, then passed to the model seperately, thus for each epoch there will be exactly length  of the dataset devided by the mini batch size steps, and hence slowing down the training process.
 Previous works \cite{masters2018revisiting, keskar2016large} have firmly proved the advantages of using the correct mini batch size as oppose to large batch sizes.
@@
 \begin{tabular}{lllll}
-    & data set size & mini batch size & Time elapsed (sec) \\
+    & dataset size & mini batch size & Time elapsed (sec) \\
 Mini batches    &336 + 0 & 8 & 214 & \\
@@
 \begin{tabular}{lllll}
-   & data set size & Time elapsed (sec) \\
+   & dataset size & Time elapsed (sec) \\
 Full batch    &336 + 0 &  23 & \\
@@
 \begin{tabular}{lllll}
- & data set size & mini batch size & Time elapsed (sec) \\
+ & dataset size & mini batch size & Time elapsed (sec) \\
 Mini batches    & 336 + 0 & 8 & 1315 & \\
@@
 \begin{tabular}{lllll}
-   &data set size & Time elapsed (sec) \\
+   &dataset size & Time elapsed (sec) \\
    Full batch &336 + 0 &  36  & \\

### 2020-04-12 src/basic_tf_ann.py
update: kfold_sys

@@ -1,122 +1,0 @@
-from __future__ import print_function
-import time
-import data_handler
-import initializer
-import matplotlib.pyplot as plt
-import tensorflow.compat.v1 as tf
-from tensorflow.python.client import device_lib
-
-tf.disable_eager_execution()
-
-FLAGS = initializer.init()
-
-# Print CPUs / GPUs available
-print(device_lib.list_local_devices())
-
-# Load data
-tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname='.\data\data.xlsx')
-
-# Augment
-tr_data, tr_labels = data_handler.augment_data(tr_data, tr_labels, FLAGS)
-
-# Parameters
-learning_rate = FLAGS.lr
-training_epochs = FLAGS.epochs
-batch_size = FLAGS.ANN_batch_size
-
-# Network Parameters
-n_hidden = FLAGS.num_neurons
-n_input = FLAGS.num_inputs
-n_outputs = FLAGS.num_outputs
-num_hidden_layers = FLAGS.num_layers
-
-# Initializers
-sigma = 1
-weight_initializer = tf.variance_scaling_initializer(mode="fan_avg", distribution="uniform", scale=sigma)
-bias_initializer = tf.zeros_initializer()
-
-weights = {
-    'h1': tf.Variable(weight_initializer([n_input, n_hidden])),
-    'out': tf.Variable(weight_initializer([n_hidden, n_outputs]))
-}
-biases = {
-    'b1': tf.Variable(bias_initializer([n_hidden])),
-    'out': tf.Variable(bias_initializer([n_outputs]))
-}
-
-# Create hidden layers
-for i in range(1, num_hidden_layers):
-    weights['h{}'.format(i + 1)] = tf.Variable(weight_initializer([n_hidden, n_hidden]))
-    biases['b{}'.format(i + 1)] = tf.Variable(bias_initializer([n_outputs]))
-
-
-# Create model
-def multilayer_perceptron(x):
-    in_x = tf.add(tf.matmul(x, weights['h1']), biases['b1'])
-    in_x = tf.nn.relu(in_x)
-    # in_x = tf.nn.dropout(in_x, keep_prob = 0.8)
-    # in_x = tf.layers.batch_normalization(in_x)
-
-    for i in range(1, num_hidden_layers):
-        in_x = tf.add(tf.matmul(in_x, weights['h{}'.format(i + 1)]), biases['b{}'.format(i + 1)])
-        in_x = tf.nn.relu(in_x)
[…]

### 2020-04-12 src/data_handler.py

@@ -3,37 +3,41 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 from sklearn.preprocessing import StandardScaler
+from sklearn.preprocessing import normalize
+from sklearn.preprocessing import PowerTransformer
+from sklearn.model_selection import train_test_split
 import initializer
 
 FLAGS = initializer.init()
 
 def split_data(x, y, kf=False):
     if kf:
-        x = x.reshape(8, 3, 16, 6)
+        x = x.reshape(8, 3, 16, FLAGS.num_inputs)
         y = y.reshape(8, 3, 16, 1)
     else:
-        x = x.reshape(9, 3, 16, 6)
+        x = x.reshape(9, 3, 16, FLAGS.num_inputs)
         y = y.reshape(9, 3, 16, 1)
 
     if FLAGS.k_fold and not kf:
         return [x,y]
 
-    tr_data = x[:7].reshape(7 * 16 * 3, 6)
+    tr_data = x[:7].reshape(7 * 16 * 3, FLAGS.num_inputs)
     tr_labels = y[:7].reshape(7 * 16 * 3, 1)
     #Shuffle tr data
+    '''
     merge = np.concatenate((tr_data, tr_labels), axis=1)
     sp.random.shuffle(merge)
     tr_data = merge[:, :6].reshape(7 * 16 * 3, 6)
     tr_labels = merge[:, -1].reshape(7 * 16 * 3, 1)
-
+    '''
     if kf:
-        va_data = x[-1].reshape(1 * 16 * 3, 6)
+        va_data = x[-1].reshape(1 * 16 * 3, FLAGS.num_inputs)
         va_labels = y[-1].reshape(1 * 16 * 3, 1)
         return [tr_data, tr_labels, va_data, va_labels]
     else:
-        va_data = x[-2].reshape(1 * 16 * 3, 6)
+        va_data = x[-2].reshape(1 * 16 * 3, FLAGS.num_inputs)
         va_labels = y[-2].reshape(1 * 16 * 3, 1)
-        test_data = x[-1].reshape(1 * 16 * 3, 6)
+        test_data = x[-1].reshape(1 * 16 * 3, FLAGS.num_inputs)
         test_labels = y[-1].reshape(1 * 16 * 3, 1)
         return [tr_data, tr_labels, va_data, va_labels, test_data, test_labels]
 
@@ -44,32 +48,52 @@ def load_data(fname):
[…]

### 2020-04-12 src/initializer.py

@@ -13,7 +13,8 @@ wgan_flags = params_dict[0]
 ann_flags = params_dict[1]
 data_flags = params_dict[2]
 
-tf.flags.DEFINE_bool('k_fold', False, 'Use Kfold')
+tf.flags.DEFINE_bool('k_fold_pcf2', False, 'Use Kfold for pcf2')
+tf.flags.DEFINE_bool('k_fold', False, 'Use Kfold for pcf-SPR')
 tf.flags.DEFINE_bool('train_wgan', False, 'train wgan, defaul:True')
 tf.flags.DEFINE_bool('generate', False, 'generate data, defaul:True')
 tf.flags.DEFINE_bool('train_ann', False, 'train ann, defaul:True')

### 2020-04-12 src/main.py

@@ -4,6 +4,8 @@ os.environ['TF_CPP_MIN_LOG_LEVEL'] = '3'
 import networks, data_handler, initializer
 from networks import Wgan_optim
 from sklearn.model_selection import KFold
+from sklearn.preprocessing import MinMaxScaler
+from basic_tf_ann import Ann
 
 # tf.config.experimental.set_visible_devices([], 'GPU')
 tf.config.threading.set_inter_op_parallelism_threads(16)
@@ -35,8 +37,11 @@ def train_ann_model(tr_data=[], tr_labels=[], va_data=[], va_labels=[]):
     ann_model = networks.make_model(FLAGS)
     # Load the same data used to train the WGAN
     # SPR-based PCF
+
     if not FLAGS.k_fold:
         tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname=FLAGS.data)
+        print(tr_data)
+        print(tr_labels)
     # PCF data
     # tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_pcf_data(fname=FLAGS.shuffled_pcf_data)
     # Augment data. To train with only the original real samples, set augment_size = 0.
@@ -52,7 +57,7 @@ def train_ann_model(tr_data=[], tr_labels=[], va_data=[], va_labels=[]):
                          )
 
 
-def test_model(test_data=[], test_labels=[], plot=False):
+def test_model(test_data=[], test_labels=[], plot=True):
     ann_model = networks.make_model(FLAGS)
     if not FLAGS.k_fold:
         _, __, _, ___, test_data, test_labels = data_handler.load_data(FLAGS.shuffled_data)
@@ -69,25 +74,60 @@ def test_model(test_data=[], test_labels=[], plot=False):
                                       plot=plot)
 
 
-def train_system_kf():
+def train_system_kf_pcf2():
+    kf = KFold(10)
+    x, y = data_handler.load_pcf_data(fname=FLAGS.pcf_data)
+    print(x.shape)
+    for tr_index, test_index in kf.split(x):
+        X_train, X_test = x[tr_index], x[test_index]
+        y_train, y_test = y[tr_index], y[test_index]
+
+        print(X_train.shape)
+
+        #train_wgan(tr_data, tr_labels, generate=True)
+        #train_ann_model(tr_data, tr_labels, va_data, va_labels)
+        #test_model(test_data, test_labels, False)
+
[…]

### 2020-04-12 src/networks.py

@@ -45,14 +45,17 @@ def make_model(flags):
     logger.info('\n[*] Number of outputs: {}'.format(num_outputs))
     logger.info('\n[*] Batch Normalization: {}'.format(batch_norm))
     # 1st layer
-    model.add(layers.Dense(num_neurons, input_shape=(num_inputs,)))
+    model.add(layers.Dense(num_neurons,input_shape=(num_inputs,)))
     if batch_norm:
-     model.add(layers.BatchNormalization())
+        pass
+        #model.add(layers.Dropout(0.3))
+        model.add(layers.BatchNormalization())
     model.add(layers.ReLU())
     # Hidden layers
     for _ in range(num_layers - 1):
         model.add(layers.Dense(num_neurons))
         if batch_norm:
+            #model.add(layers.Dropout(0.5))
             model.add(layers.BatchNormalization())
         model.add(layers.ReLU())
     # OUTPUT layer
@@ -78,7 +81,7 @@ def train_model(model, tr_data, tr_labels, va_data, va_labels, flags):
 
         save_dir = "./trained-kf-models/{}/model.h5".format(cur_time)
         chkdir = "./trained-kf-weights/{}/weights.hdf5".format(cur_time)
-        flags.model_to_test = chkdir
+        flags.model_to_test = save_dir
 
     if not flags.k_fold:
         save_dir = flags.save_dir
@@ -95,7 +98,7 @@ def train_model(model, tr_data, tr_labels, va_data, va_labels, flags):
     # TensorBoard
     tensorboard_callback = keras.callbacks.TensorBoard(log_dir=logdir)
     # Save the best va_loss file
-    checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=0,
+    checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=1,
                                                    save_best_only=True)
     # Define optimizers
     Adam = keras.optimizers.Adam(learning_rate=
@@ -103,11 +106,13 @@ def train_model(model, tr_data, tr_labels, va_data, va_labels, flags):
     RMSprop = keras.optimizers.RMSprop(learning_rate=1e-2, rho=0.9)
     # Train
     model.compile(optimizer=Adam, loss='mean_squared_error')
-    hist = model.fit(tr_data, tr_labels, epochs=epochs, verbose=1,
+    hist = model.fit(tr_data, tr_labels, epochs=epochs,
                      validation_data=(va_data, va_labels), callbacks=[checkpointer, tensorboard_callback],
[…]

### 2020-04-12 src/tf_ann.py

@@ -1,0 +1,92 @@
+from __future__ import print_function
+import time
+import data_handler
+import initializer
+import matplotlib.pyplot as plt
+import tensorflow.compat.v1 as tf
+from tensorflow.python.client import device_lib
+
+tf.disable_eager_execution()
+
+FLAGS = initializer.init()
+
+
+class Ann():
+    def __init__(self, session, flags, tr_data, tr_labels, va_data, va_labels, test_data):
+        self.learning_rate = flags.lr
+        self.training_epochs = flags.epochs
+        self.batch_size = flags.ANN_batch_size
+        self.n_hidden = flags.num_neurons
+        self.n_input = flags.num_inputs
+        self.n_outputs = flags.num_outputs
+        num_hidden_layers = flags.num_layers
+        self.sess = session
+        self._build_net()
+        self.tr_data , self.tr_labels, self.va_data, self.va_labels, self.test_data = \
+        tr_data , tr_labels, va_data, va_labels, test_data
+
+    def _build_net(self):
+        self.X = tf.placeholder("float", [None, self.n_input], name='X')
+        self.Y = tf.placeholder("float", [None, self.n_outputs], name='Y')
+        self.model = self.make_model
+        self.out = self.model(self.X)
+        # Define loss and optimizer
+        self.loss_op = tf.losses.mean_squared_error(self.Y, self.out)
+        self.optimizer = tf.train.AdamOptimizer(learning_rate=self.learning_rate)
+        self.train_op = self.optimizer.minimize(self.loss_op)
+
+
+    def make_model(self,data, name='m_'):
+        with tf.variable_scope(name):
+            x = tf.layers.Dense(self.n_hidden, name='l1', _reuse=tf.AUTO_REUSE)(data)
+            x = tf.layers.BatchNormalization(name='b1')(x)
+            x = tf.nn.relu(x, name='relu_1')
+
+            x1 = tf.layers.Dense(self.n_hidden, name='l2', _reuse=tf.AUTO_REUSE)(x)
+            x1 = tf.layers.BatchNormalization(name='b2')(x1)
+            x1 = tf.nn.relu(x1, name='relu_2')
+
+            x2 = tf.layers.Dense(self.n_hidden, name='l3', _reuse=tf.AUTO_REUSE)(x1)
+            x2 = tf.layers.BatchNormalization(name='b3')(x2)
+            x2 = tf.nn.relu(x2, name='relu_3')
+
[…]

### 2020-04-12 src/data_handler.py
comment: convert to micro meters

@@ -63,8 +63,11 @@ def load_data(fname):
     #print(scaler.mean_)
     #print(scaler.var_)
     #df = scaler.transform(df)
+
+    # Convert to micro meter
     df[:,2] /= 10
     df[:,4:8] /= 10
+
     '''
     scaler = StandardScaler(with_mean=False)
     df_temp = scaler.fit_transform(df)

### 2020-04-12 src/data_handler.py
fix: typo

@@ -80,11 +80,11 @@ def load_data(fname):
     #analytes = analytes.reshape(432, 1)
     #x = sp.concatenate((analytes, x), axis=1)
     #x /= 10
-    #scaler = StandardScaler()
-    #scaler.fit(x)
+    scaler = StandardScaler()
+    scaler.fit(x)
     #print(scaler.mean_)
     #print(scaler.var_)
-    #x = scaler.transform(x)
+    x = scaler.transform(x)
     #print(x)
     #x = normalize(x, norm='l2')
     #pt = PowerTransformer()

### 2020-04-12 src/data_handler.py
fix: typo

@@ -80,11 +80,11 @@ def load_data(fname):
     #analytes = analytes.reshape(432, 1)
     #x = sp.concatenate((analytes, x), axis=1)
     #x /= 10
-    scaler = StandardScaler()
-    scaler.fit(x)
+    #scaler = StandardScaler()
+    #scaler.fit(x)
     #print(scaler.mean_)
     #print(scaler.var_)
-    x = scaler.transform(x)
+    #x = scaler.transform(x)
     #print(x)
     #x = normalize(x, norm='l2')
     #pt = PowerTransformer()

### 2020-04-13 docs/paper/paper.tex
* Some graphs, rewrote experiments section

@@
 Table \ref{tbl:anndetails} summarizes the details of this model.
+
 We have adopted Adam \cite{kingma2014adam} as the optimizer and the mean squared error (MSE) as the loss/cost function.
-
-Due to the nature of the problem, over-fitting is an important issue.
-We have used early stopping method to reduce over-fitting.
-In this method, it is possible to terminate and go back to a previous state if overall validation error increases.
-Thus instead of being forced into a worse classifier, training is terminated earlier.
 In addition, we use Batch Normalization algorithm \cite{ioffe2015batch} to accelerate training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.
-
 In proposed system, the ANN is trained using the samples from the original dataset and the augmented samples generated by the GAN phase.
-Additionally, we use z-score normalization (standardization).
-The parameters to the normalizer is calculated through training samples and it is applied to all samples that will be used with the regressor.
-This includes testing and training samples.
-Please note that the samples that are selected to be used in training is not used in the training phase and any normalization that is applied to them are applied during testing phase.
 
@@
 
-\def\dszero{Zero}
+\def\dszero{PCF}
 
@@
 and collected using FV-FEM.} Details of this dataset is explained in Section \ref{sec:pcf} and it is referred as SPR dataset.
-Seven configurations were randomly selected for training both the GAN and the ANN, one configuration was held out for validation, and the last one is used for testing.
+Having nine configurations, we have performed 9-fold testing on this dataset.
+Each fold tests a single configuration using the other configurations as training data.
 Slicing the data this way allowed us to guide the network to predict the loss on a completely different configuration.
@@
 Additionally, we have used the dataset that has been used in \cite{paper0}.
-\hl{This dataset contains 1000 samples.
+\hl{This dataset contains over 1000 samples.
 Inputs to this data is ....
@@
 In this experiment, we have trained ANN model for up to 2000 epochs and reported the training loss in Figure \ref{chart:trainingmse}.
-According to this experiment, training our ANN architecture more than 1000 epochs does not yield any significant improvement.
+According to this experiment, training our ANN architecture more than 1000 epochs does not yield to any significant improvement.
 Therefore, we have set the training epoch limit to 1000 in subsequent experiments.
+Additionally, it is clear that the use of augmented samples from the GAN phase reduces the oscillations in the training error.
 
-\hl{CK: continue here.}
+We have performed experiements comparing the proposed ANN architecture with the state-of-the-art method proposed in \cite{paper0}.
+Results of this experiment is demonstrated in Figure \ref{chart:perfnoaug}.
+Please note that in the experiment involving SPR dataset, ANN models are predicting a new configuration and the number of samples available for training is lower.
+Therefore, they both have higher error rate compared to the \dszero{} dataset.
 
 \begin{table*}[h]
+\hl{Needs fixing}
+\caption{Hyper-parameters chosen for the ANN model, where $\beta_{1}$ and $\beta_{2}$ are a part of Adam parameters}
 \centering
@@
 }
-\caption{Hyper-parameters chosen for the ANN model, where $\beta_{1}$ and $\beta_{2}$ are a part of Adam parameters}
 \end{table*}
 
-The MSE on the training sets ranged from 0.0030 to 0.0050.
-For all training datasets the MSE decreased in an acceptable manner.
-Next, we plot the predictions the ANN model made on the test set, after training using only the original set.
-As shown in the following figure.
-
-\begin{figure}
+\begin{figure*}
+	\begin{subfigure}{.48\textwidth}
+	\centering
     \begin{tikzpicture}
@@
 		ylabel=Training \space MSE,
-		width=0.48\textwidth,
+		width=\textwidth,
 		grid=both,
@@
 		major grid style={gray!25},
+		ymax=2,
 		no marks]
 		\addplot[line width=1pt,solid,color=blue] %
-		table{tr_loss_ann.txt};
+		table{../../experiments_spr-pcf/va_loss_curves/With augmentation/ann/ann_tr_loss.txt};
 		\end{axis}
 	\end{tikzpicture}
-	\caption{Training MSE of the ANN model}
+	\caption{With augmentation}
+	\end{subfigure}	
+	\begin{subfigure}{.48\textwidth}
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+		xlabel=Epochs, 
+		ylabel=Training \space MSE,
+		width=\textwidth,
+		grid=both,
+		minor grid style={gray!25},
+		major grid style={gray!25},
+		ymax=2,
+		no marks]
+		\addplot[line width=1pt,solid,color=blue] %
+		table{../../experiments_spr-pcf/va_loss_curves/Without augmentation/ann_loss_without_augmt.txt};
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Without augmentation}
+	\end{subfigure}
+
+	\caption{Training MSE of the ANN model with (a) and without (b) GAN phase obtained from SPR dataset}
 	\label{chart:trainingmse}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
+\begin{subfigure}{0.48\textwidth}
 	\begin{tikzpicture}
@@
 			legend pos=north west,
-		xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
-		ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
-		title={Length of the training dataset = 336 + 0},
+			xlabel=Actual loss in $log(db/cm)$, 
+			ylabel=Predicted loss in $log(db/cm)$,
 			grid=both,
@@
 			major grid style={gray!25},
+			width=\textwidth
+		]
+			\addplot[
+				only marks,
+				mark size=2.9pt, mark=o, color=red, fill=red
+			] table{../../experiments_spr-pcf/Without_augmentation/kfold-predictions-vs-labels/1st/graph_data.txt};
+			\addlegendentry{$Proposed$}
+
+			\addplot[
+				only marks,
+				mark size=2.9pt, mark=x, color=green
+			] %table{??};
+			coordinates{(7.2, 6.8)};
+			\addlegendentry{\cite{paper0}}
+
+			\draw[
+				line width=1pt,
+				solid,color=blue
+			]
+			(axis cs:\pgfkeysvalueof{/pgfplots/xmin},\pgfkeysvalueof{/pgfplots/xmin}) -- 
+			(axis cs:\pgfkeysvalueof{/pgfplots/xmax},\pgfkeysvalueof{/pgfplots/xmax});
+			\addlegendimage{line legend, 
+				line width=1pt,
+				solid,color=blue}
+			\addlegendentry{$Actual$}
+
+		\end{axis}
+	\end{tikzpicture}
+	\caption{SPR dataset}
+\end{subfigure}
+\begin{subfigure}{0.48\textwidth}
+    \begin{tikzpicture}
+	\begin{axis}[
+		legend pos=north west,
+		xlabel=Actual loss in $log(db/cm)$, 
+		ylabel=Predicted loss in $log(db/cm)$,
+		grid=both,
+		minor grid style={gray!25},
+		major grid style={gray!25},
+		width=\textwidth
+	]
+		\addplot[
+			only marks,
+			mark size=2.9pt, mark=o, color=red, fill=red
+		] 
+		table{../../experiments_pcf2/Without_augmentation/kfold-predictions-vs-labels/8th/graph_data.txt};
+		\addlegendentry{$Proposed$}
+
+		\addplot[
+			only marks,
+			mark size=2.9pt, mark=x, color=green
+		] 
+		%table{??};
+		coordinates{(-5, -10)};
+		\addlegendentry{\cite{paper0}}
+
+		\draw[
+			line width=1pt,
+			solid,color=blue
+		]
+		(axis cs:\pgfkeysvalueof{/pgfplots/xmin},\pgfkeysvalueof{/pgfplots/xmin}) -- 
+		(axis cs:\pgfkeysvalueof{/pgfplots/xmax},\pgfkeysvalueof{/pgfplots/xmax});
+		\addlegendimage{line legend, 
+			line width=1pt,
+			solid,color=blue}
+		\addlegendentry{$Actual$}
+
+		\end{axis}
+    \end{tikzpicture}
+    \caption{\dszero{} dataset}
+\end{subfigure}
+\vspace{0.75cm}
+
+\begin{subfigure}{\textwidth}
+	\begin{tikzpicture}
+	\begin{axis}[
+		legend pos=north west,
+		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
+		ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
+		grid=both,
+		minor grid style={gray!25},
+		major grid style={gray!25},
+		title={$n_{analyte=1.34}$},
 		width=0.48\textwidth
@@
 		mark size=2.9pt, mark=o, color=red, fill=red
-		] table{dataset_336.txt};
-		\addlegendentry{$Predicted$}
+	]
+	table[x={wave},y={predicted}]{data/vswavelength134_fold1.txt};
+	\addlegendentry{$Proposed$}
 
 	\addplot[
-			line width=1pt,
-			solid,color=blue
-		] table{y.txt};
-		\addlegendentry{$Actual$}
+		only marks,
+		mark size=2.9pt, mark=x, color=green
+	] 
+	%table{??};
+	coordinates{(500, 7)};
+	\addlegendentry{\cite{paper0}}
+
+	\addplot[
+		color=blue
+	] 
+	table[x={wave},y={real}]{data/vswavelength134_fold1.txt};
+	coordinates{(6.8, 7.2)};
+	\addlegendentry{Actual}
 
@@
 	\end{tikzpicture}
-\end{figure}
+	\begin{tikzpicture}
+	\begin{axis}[
+		legend pos=north west,
+		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
+		ylabel=$~$,
+		grid=both,
+		minor grid style={gray!25},
+		major grid style={gray!25},
+		title={$n_{analyte=1.35}$},
+		width=0.48\textwidth
+	]
+	\addplot[
+		only marks,
+		mark size=2.9pt, mark=o, color=red, fill=red
+	] 
+	table[x={wave},y={predicted}]{data/vswavelength135_fold1.txt};
+	\addlegendentry{$Proposed$}
+
+     \addplot[
+		only marks,
+		mark size=2.9pt, mark=x, color=green
+     ]
+     %table{??};
+     coordinates{(500, 7.5)};
+     \addlegendentry{\cite{paper0}}
+
+	\addplot[
+		color=blue
+	] 
+	table[x={wave},y={real}]{data/vswavelength135_fold1.txt};
+	\addlegendentry{Actual}
+
+	\end{axis}
+	\end{tikzpicture}
+	\caption{Configuration estimation on SPR dataset}
+\end{subfigure}
+\caption{Testing results without GAN augmentation phase}
+\label{chart:perfnoaug}
+\end{figure*}
+
+\hl{CK: continue here..}
 
@@
 
-\begin{figure}
-    \begin{subfigure}{.5\textwidth}
-			\begin{tikzpicture}
-			\begin{axis}[
-			xlabel=$Epochs$, 
-			ylabel=$ Training $ $ MSE $,
-			title={Training loss function of the Critic network},
-			grid=both,
-			minor grid style={gray!25},
-			major grid style={gray!25},
-			width=1.1\linewidth]
-			\addplot[line width=1pt,solid,color=blue]  %
-			table{wgan_tr_loss.txt};
-			\end{axis}
-			\end{tikzpicture}
-\end{subfigure}\hspace{0.05\textwidth}
-    \begin{subfigure}{.5\textwidth}
-			\begin{tikzpicture}
-			\begin{axis}[
-			legend pos=north west,
-			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
-			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
-			title={Length of the training dataset = 336 + 1000},
-			grid=both,
-			minor grid style={gray!25},
-			major grid style={gray!25},
-			width=1.1\linewidth]
-			\addplot[
-			only marks,
-			mark size=2.9pt, mark=o, color=red, fill=red] %
-			table{dataset_1000.txt};
-			\addlegendentry{$Predicted$}
-			\addplot[line width=1pt,solid,color=blue]  %
-			table{y.txt};
-			\addlegendentry{$Actual$}
-			\end{axis}
-			\end{tikzpicture}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}
-			\begin{tikzpicture}
-			\begin{axis}[
-			legend pos=north west,
-			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
-			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
-			title={Length of the training dataset = 336 + 2000},
-			grid=both,
-			minor grid style={gray!25},
-			major grid style={gray!25},
-			width=1.1\linewidth]
-			\addplot[
-			only marks,
-			mark size=2.9pt, mark=o, color=red, fill=red] %
-			table{dataset_2000.txt};
-			\addlegendentry{$Predicted$}
-			\addplot[line width=1pt,solid,color=blue]  %
-			table{y.txt};
-			\addlegendentry{$Actual$}
-			\end{axis}
-			\end{tikzpicture}
-\end{subfigure}\hspace{0.05\textwidth}
-\begin{subfigure}{.5\textwidth}
-			\begin{tikzpicture}
-			\begin{axis}[
-			legend pos=north west,
-			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
-			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
-			title={Length of the training dataset = 336 + 3000},
-			grid=both,
-			minor grid style={gray!25},
-			major grid style={gray!25},
-			width=1.1\linewidth]
-			\addplot[
-			only marks,
-			mark size=2.9pt, mark=o, color=red, fill=red] %
-			table{dataset_3000.txt};
-			\addlegendentry{$Predicted$}
-			\addplot[line width=1pt,solid,color=blue]  %
-			table{y.txt};
-			\addlegendentry{$Actual$}
-			\end{axis}
-			\end{tikzpicture}
-\end{subfigure}
-\caption{}
-\end{figure}
-
 It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(5).
 The most important result in these experiments is that the ANN model predicted the correct location of the peak value of the confinement loss distributions for the three different analytes used.
-\begin{figure}
-    \begin{subfigure}{.5\textwidth}
-			\begin{tikzpicture}
-			\begin{axis}[
-			title={$n_{analyte=1.33}$},
-			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
-			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
-			grid=both,
-			minor grid style={gray!25},
-			major grid style={gray!25},
-			width=1.1\linewidth]
-			\addplot[
-			only marks,
-			mark size=2.9pt, mark=o, color=red, fill=red] %
-			table[x={X},y={Y_REAL}]{133.txt};
-			\addlegendentry{$Actual$}
-			\addplot[smooth, 
-			line width=1pt,solid,color=blue]  %
-			table[x={X},y={Predictions}]{133.txt};
-			\addlegendentry{$Predictions$}
-			\end{axis}
-			\end{tikzpicture}
-\end{subfigure}\hspace{0.05\textwidth}
- \begin{subfigure}{.5\textwidth}
-			\begin{tikzpicture}
-			\begin{axis}[
-			title={$n_{analyte=1.34}$},
-			xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
-			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
-			grid=both,
-			minor grid style={gray!25},
-			major grid style={gray!25},
-			width=1.1\linewidth]
-			\addplot[
-			only marks,
-			mark size=2.9pt, mark=o, color=red, fill=red] %
-			table[x={X},y={Y_REAL}]{134.txt};
-			\addlegendentry{$Actual$}
-			\addplot[smooth,
-			line width=1pt,solid,color=blue]  %
-			table[x={X},y={Predictions}]{134.txt};
-			\addlegendentry{$Predictions$}
-			\end{axis}
-			\end{tikzpicture}
-\end{subfigure}
- \begin{subfigure}{.5\textwidth}
-			\begin{tikzpicture}
-			\begin{axis}[
-			title={$n_{analyte=1.35}$},
-		    xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
-			ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
-			grid=both,
-			minor grid style={gray!25},
-			major grid style={gray!25},
-			width=1.1\linewidth]
-			\addplot[
-			only marks,
-			mark size=2.9pt, mark=o, color=red, fill=red] %
-			table[x={X},y={Y_REAL}]{135.txt};
-			\addlegendentry{$Actual$}
-			\addplot[smooth,line width=1pt,solid,color=blue]  %
-			table[x={X},y={Predictions}]{135.txt};
-			\addlegendentry{$Predictions$}
-			\end{axis}
-			\end{tikzpicture}
-\end{subfigure}
-\caption{}
-\end{figure}
 
@@
 \hl{Training and execution time of ANN versus simulation method}
-
-This work had been conduct on a  laptop:
-
-\begin{itemize}
-\item Intel(R) Core(TM) i7-5600 CPU @2.60GHz (4 CPUs)
-\item 8GB RAM
-\item No GPU on board
-\end{itemize}
-
-For comparaison purposes we ran the expirements on a machine with GPU on board:
-
-\hl{CEM PC SPECS}
 
@@
 The code for this work is available at: \url{https://github.com/Aimen-Zelaci/SPRPCF_ANN/}.
-\newline
+
 The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, mini batch size, dataset size, number of epochs, the framework used to code the model, and of course the specifications of the machine.
+
 In this work we fixed the number of epochs to 2000 and executed training using Tensorflow(Keras) and Pytorch frameworks.
@@
 
-\hl{WGAN EXCUTION WITH GPU VS CPU BY CEM}
-
-Next, we compare the testing runtime of the ANN model to that of simulation methods used to compute the confinement loss for 3 different analytes and 16 wavelenghts, i.e a total of 48 values of the confinement loss, demonstrated in Table(7).
-This result is absolutely staggering.
-The ANN model calculated 48 confinement losses in just 0.17 seconds, while simulations took about 2 hours.
-Therefore, a well trained ANN model can be used to accurately find the best PCF geometric properties set that maximisez the distance between the confinement loss distributions of each analyte in a matter of seconds to minutes.
-Hence, accelerate the search for the best PCF sensor.
-
 \begin{table}[h]

### 2020-04-13 docs/paper/paper.tex
* Few more fixes in the text * Framework for GAN experiments

@@
 Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}.
+As a final note, the range and domain of these datasets are different; therefore, all comparisons should be drawn within the same dataset.
 
@@
 		\begin{axis}[
-			legend pos=north west,
 			xlabel=Actual loss in $log(db/cm)$, 
@@
 			major grid style={gray!25},
-			width=\textwidth
+			width=\textwidth,
+			legend pos=south east
 		]
@@
 	\begin{axis}[
-		legend pos=north west,
 		xlabel=Actual loss in $log(db/cm)$, 
@@
 		major grid style={gray!25},
-		width=\textwidth
+		width=\textwidth,
+		legend pos=south east
 	]
@@
 	\begin{axis}[
-		legend pos=north west,
 		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
@@
 		title={$n_{analyte=1.34}$},
-		width=0.48\textwidth
+		width=0.48\textwidth,
+		legend pos=north east
 	]
@@
 		title={$n_{analyte=1.35}$},
-		width=0.48\textwidth
+		width=0.48\textwidth,
+		legend pos=north east
 	]
@@
 
-During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in Figure(4).
-In this subsection we discuss the results of augmenting the real dataset with generated samples.
-Figure(4) demonstrates the predictions made by the ANN model after training with different sizes of the dataset.
-This might look paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data.
-There are several reasons for why our ANN model is driven in the wrong direction.
-Even though our WGAN-GP seemed well trained, there still a domain gap between the real data and the generated data, or the expansion of data is growing in the wrong direction to that of entirely containing the real data.
-Furthermore, the generated data might lack realism.
-Or the sampling strategy adopted is poor.
-But the most convincing reason is the limited original training dataset size of 336 samples, used to train the WGAN model in the first place.
-After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved what we set out to accomplish at the beginning, to improve the accuracy of the ANN model by artificially expanding the original set.
+We have performed experiments to showcase the improvement gained by augmenting training samples using a GAN.
+In Figure ...
+the results of these experiments has shown.
+GAN does not only boost the score of the proposed ANN system, but also decreases the MSE on the method proposed in \cite{paper0}.
+An additional note to take away from this experiment is that the dataset with the least number of samples has the highest improvement, which is demonstrated in a clearer fashion in Table ....
+This is due the fact that the number of training samples in this dataset is insufficient to train the regressor networks.
 
-It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(5).
-The most important result in these experiments is that the ANN model predicted the correct location of the peak value of the confinement loss distributions for the three different analytes used.
+\hl{Information about the number of augmented samples.}
+
+The final set of experiments shows the stability that GAN phase adds.
+In Table ...
+we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing.
+It is clear that the GAN phase not only improves the average case but significantly improves the worst case, which is important in a live setting.
+This added stability can also be observed in Figure \ref{chart:trainingmse}, where the training loss has less fluctuations when the data augmentation is employed.
 
@@
 
-\begin{table}[h]
+\begin{table}
 \begin{tabular}{lllll}
@@
 \end{table}
-\begin{table}[h]
+\begin{table}
 \begin{tabular}{lllll}

### 2020-04-15 docs/paper/paper.tex
* Experimental results section finished with mock data

@@
 \usepackage{cite}
+\usepackage{multirow}
 
@@
 As stated in the previous works, artificial neural networks (ANN) can predict the result of numerical simulations much faster.
-However, there are two issues with the methods proposed previously.
-Namely, the required number of samples for training and the overall accuracy of these methods.
+However, there are two issues with the methods proposed previously: the required number of samples for training and the generality of these methods.
 In this paper, we  propose the use of generative adversarial networks (GAN) to augment the real dataset to train an ANN model.
 Experimental analysis suggest that the proposed combination not only accurately predicts the confinement loss even with limited amount of data but also GAN can be used to improve existing methods in the literature.
-Finally, it is shown that this system can predict the confinement loss over a range of analytes and wavelengths in a completely new set of geometric configuration.
+Finally, it is shown that this system can predict the confinement loss over a range of analytes and wavelengths in a completely new set of geometric configuration and generic enough not to require any additional tuning when used in a new dataset.
 \end{abstract}
@@
 
-It is possible to use different metrics for training in GAN [references here], for this project we have selected WGAN Wasserstein distance metric.
+It is possible to use different metrics for training in GAN \hl{[references here]}, for this project we have selected WGAN Wasserstein distance metric.
 This variant has been proposed by Arjovsky et al in \cite{arjovsky2017wasserstein}.
@@
 		Neurons in hidden layers & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ & 50 \\
+		Batch size & 32 & 32 & 48 \\
 		Activation function & ReLU & Leaky ReLU & ReLU \\
@@
 		Layer normalization & - & Batch \cite{ioffe2015batch} & Batch \\
-		Loss function & -Critic(generated) & Critic(generated) - Critic(collected) & MSE \\
+		Loss function & Critic(generated) & Critic(generated) - Critic(collected) & MSE \\
 	\end{tabular}
@@
 Table \ref{tbl:anndetails} summarizes the details of this model.
+
+In our model, we have used mini-batch training with 48 samples as the batch size.
+In contrast to full-batch training, mini-batch training allows more frequent gradient calculations, improving the stability and reliability of the training \cite{masters2018revisiting, keskar2016large}.
+The downside of using mini-batches are added computational complexity during training.
+However, it has no adverse effect on the testing phase.
 
@@
 In this experiment, we have trained ANN model for up to 2000 epochs and reported the training loss in Figure \ref{chart:trainingmse}.
-According to this experiment, training our ANN architecture more than 1000 epochs does not yield to any significant improvement.
-Therefore, we have set the training epoch limit to 1000 in subsequent experiments.
+We have additionally tested the accuracy with different number of epochs in training.
+According to this experiment, training our ANN architecture more than 2000 epochs does not yield to any improvement.
+Therefore, we have set the training epoch limit to 2000 in subsequent experiments.
+However, this number depends on dataset and at times additional training can improve the result.
 Additionally, it is clear that the use of augmented samples from the GAN phase reduces the oscillations in the training error.
@@
 Therefore, they both have higher error rate compared to the \dszero{} dataset.
-
-\begin{table*}[h]
-\hl{Needs fixing}
-\caption{Hyper-parameters chosen for the ANN model, where $\beta_{1}$ and $\beta_{2}$ are a part of Adam parameters}
-\centering
-\scalebox{1.5}{
-    \begin{tabular}{|l|l|l|l|l|}
-    \hline
-Length of the training data-set & Learning rate& Mini batch size & $\beta_{1}$ & $\beta_{2}$\\
-\hline
-336 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
-\hline
-336 + 1000 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
-\hline
-336 + 2000 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
-\hline
-336 + 3000 & $ 2.5\times10^{-04} $ & 20  & 0.9 & 0.999 \\
-\hline
-    \end{tabular}
-}
-\end{table*}
 
@@
 			ymax=2,
-		no marks]
+			no marks
+		]
 		\addplot[line width=1pt,solid,color=blue] %
-		table{../../experiments_spr-pcf/va_loss_curves/With augmentation/ann/ann_tr_loss.txt};
+		table{../../loss_curves_2k/ann_tr_loss_2k_with.txt};
 		\end{axis}
@@
 			xlabel=Epochs, 
-		ylabel=Training \space MSE,
 			width=\textwidth,
@@
 			ymax=2,
-		no marks]
+			no marks
+		]
 		\addplot[line width=1pt,solid,color=blue] %
-		table{../../experiments_spr-pcf/va_loss_curves/Without augmentation/ann_loss_without_augmt.txt};
+		table{../../loss_curves_2k/ann_tr_loss_2k_without.txt};
 		\end{axis}
@@
 		] 
-		table{../../experiments_pcf2/Without_augmentation/kfold-predictions-vs-labels/8th/graph_data.txt};
+		table{../../expirrements_pcf2/Our_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
 		\addlegendentry{$Proposed$}
@@
 		] 
-		%table{??};
-		coordinates{(-5, -10)};
+		table{../../expirrements_pcf2/Their_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
 		\addlegendentry{\cite{paper0}}
@@
 	]
-	table[x={wave},y={predicted}]{data/vswavelength134_fold1.txt};
+	table[x={wave},y={predicted}]{data/vswavelength134_fold9_noaug.txt};
 	\addlegendentry{$Proposed$}
@@
 	] 
-	table[x={wave},y={real}]{data/vswavelength134_fold1.txt};
+	table[x={wave},y={real}]{data/vswavelength134_fold9_noaug.txt};
 	coordinates{(6.8, 7.2)};
 	\addlegendentry{Actual}
-
 	\end{axis}
 	\end{tikzpicture}
+	%
 	\begin{tikzpicture}
@@
 	] 
-	table[x={wave},y={predicted}]{data/vswavelength135_fold1.txt};
+	table[x={wave},y={predicted}]{data/vswavelength135_fold9_noaug.txt};
 	\addlegendentry{$Proposed$}
@@
 	] 
-	table[x={wave},y={real}]{data/vswavelength135_fold1.txt};
+	table[x={wave},y={real}]{data/vswavelength135_fold9_noaug.txt};
 	\addlegendentry{Actual}
@@
 
+The first set of experiments performed on GAN phase is the number of the augmented samples.
+In these experiments we have started augmentation by using 500 samples, increasing it by another 500 per experiment.
+According to these experiments we have reached the minimum MSE at 1000 samples.
+Adding further samples reduces the performance and increases the training time.
+The results of this experiment is demonstrated in Figure \ref{chart:gansamples}.
+This number may depend on the dataset that is used.
+However, in our experiments 1000 augmented samples produce good results in both datasets.
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[]
+	\begin{axis}[
+	ybar, axis x line=bottom, xlabel=Augmented samples, 
+	xmin=-100,xmax=2100,
+	ymin=0,ymax=1,
+	width=0.48\textwidth, height=6cm,
+	axis y line=left, ylabel=MSE, 
+	legend cell align=left,
+	legend style={draw=none, at={(0.5,-0.25)},anchor=north,/tikz/every even column/.append style={column sep=1.0cm}}, 
+	ylabel near ticks, ylabel shift={-5pt},
+	grid = major, legend columns=4
+	]
+
+	\pgfplotsset{every axis/.append style={font=\small, thick, tick style={semithick}}}
+	\pgfplotsset{every axis label/.append style={font=\small\sffamily\it}}
+
+	\addplot[fill=black!90!white] 
+	coordinates {
+		(0, 0.89)
+		(500, 0.37)
+		(1000, 0.31)
+		(1500, 0.5)
+		(2000, 0.38)
+	};
+
+	\end{axis}
+	\end{tikzpicture}
+	\caption{Effect of increasing augmented samples on MSE.}
+	\label{chart:gansamples}
+\end{figure}
+
 We have performed experiments to showcase the improvement gained by augmenting training samples using a GAN.
-In Figure ...
-the results of these experiments has shown.
-GAN does not only boost the score of the proposed ANN system, but also decreases the MSE on the method proposed in \cite{paper0}.
-An additional note to take away from this experiment is that the dataset with the least number of samples has the highest improvement, which is demonstrated in a clearer fashion in Table ....
-This is due the fact that the number of training samples in this dataset is insufficient to train the regressor networks.
+In Figure \ref{chart:gan}, the results of these experiments has shown.
+An additional note to take away from this experiment is that the dataset with the least number of samples has the highest improvement, which is demonstrated in a clearer fashion in Table \ref{tbl:all}.
+This is due the fact that the number of training samples in this dataset is insufficient to train the regressor network.
 
-\hl{Information about the number of augmented samples.}
+\begin{figure*}
+\begin{subfigure}{0.48\textwidth}
+	\begin{tikzpicture}
+		\begin{axis}[
+			xlabel=Actual loss in $log(db/cm)$, 
+			ylabel=Predicted loss in $log(db/cm)$,
+			grid=both,
+			minor grid style={gray!25},
+			major grid style={gray!25},
+			width=\textwidth,
+			legend pos=south east
+		]
+			\addplot[
+				only marks,
+				mark size=2.9pt, mark=o, color=red, fill=red
+			] table{../../experiments_spr-pcf/Without_augmentation/kfold-predictions-vs-labels/1st/graph_data.txt};
+			\addlegendentry{With GAN}
+
+			\addplot[
+				only marks,
+				mark size=2.9pt, mark=x, color=green
+			] %table{??};
+			coordinates{(7.2, 6.8)};
+			\addlegendentry{Without GAN}
+
+			\draw[
+				line width=1pt,
+				solid,color=blue
+			]
+			(axis cs:\pgfkeysvalueof{/pgfplots/xmin},\pgfkeysvalueof{/pgfplots/xmin}) -- 
+			(axis cs:\pgfkeysvalueof{/pgfplots/xmax},\pgfkeysvalueof{/pgfplots/xmax});
+			\addlegendimage{line legend, 
+				line width=1pt,
+				solid,color=blue}
+			\addlegendentry{$Actual$}
+
+		\end{axis}
+	\end{tikzpicture}
+	\caption{SPR dataset}
+\end{subfigure}
+\begin{subfigure}{0.48\textwidth}
+    \begin{tikzpicture}
+	\begin{axis}[
+		xlabel=Actual loss in $log(db/cm)$, 
+		ylabel=Predicted loss in $log(db/cm)$,
+		grid=both,
+		minor grid style={gray!25},
+		major grid style={gray!25},
+		width=\textwidth,
+		legend pos=south east
+	]
+		\addplot[
+			only marks,
+			mark size=2.9pt, mark=o, color=red, fill=red
+		] 
+		table{../../expirrements_pcf2/Our_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
+		\addlegendentry{With GAN}
+
+		\addplot[
+		only marks,
+		mark size=2.9pt, mark=x, color=green
+		] 
+		table{../../expirrements_pcf2/Their_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
+		\addlegendentry{Without GAN}
+
+		\draw[
+			line width=1pt,
+			solid,color=blue
+		]
+		(axis cs:\pgfkeysvalueof{/pgfplots/xmin},\pgfkeysvalueof{/pgfplots/xmin}) -- 
+		(axis cs:\pgfkeysvalueof{/pgfplots/xmax},\pgfkeysvalueof{/pgfplots/xmax});
+		\addlegendimage{line legend, 
+			line width=1pt,
+			solid,color=blue}
+		\addlegendentry{$Actual$}
+
+		\end{axis}
+    \end{tikzpicture}
+    \caption{\dszero{} dataset}
+\end{subfigure}
+\vspace{0.75cm}
+
+\begin{subfigure}{\textwidth}
+	\begin{tikzpicture}
+	\begin{axis}[
+		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
+		ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
+		grid=both,
+		minor grid style={gray!25},
+		major grid style={gray!25},
+		title={$n_{analyte=1.34}$},
+		width=0.48\textwidth,
+		legend pos=north east
+	]
+	\addplot[
+		only marks,
+		mark size=2.9pt, mark=o, color=red, fill=red
+	]
+	table[x={wave},y={predicted}]{data/vswavelength134_fold9_noaug.txt};
+	\addlegendentry{With GAN}
+
+	\addplot[
+		only marks,
+		mark size=2.9pt, mark=x, color=green
+	] 
+	%table{??};
+	coordinates{(500, 7)};
+	\addlegendentry{Without GAN}
+
+	\addplot[
+		color=blue
+	] 
+	table[x={wave},y={real}]{data/vswavelength134_fold9_noaug.txt};
+	coordinates{(6.8, 7.2)};
+	\addlegendentry{Actual}
+	\end{axis}
+	\end{tikzpicture}
+	%
+	\begin{tikzpicture}
+	\begin{axis}[
+		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
+		ylabel=$~$,
+		grid=both,
+		minor grid style={gray!25},
+		major grid style={gray!25},
+		title={$n_{analyte=1.35}$},
+		width=0.48\textwidth,
+		legend pos=north east
+	]
+	\addplot[
+		only marks,
+		mark size=2.9pt, mark=o, color=red, fill=red
+	] 
+	table[x={wave},y={predicted}]{data/vswavelength135_fold9_noaug.txt};
+	\addlegendentry{With GAN}
+
+     \addplot[
+		only marks,
+		mark size=2.9pt, mark=x, color=green
+     ]
+     %table{??};
+     coordinates{(500, 7.5)};
+     \addlegendentry{Without GAN}
+
+	\addplot[
+		color=blue
+	] 
+	table[x={wave},y={real}]{data/vswavelength135_fold9_noaug.txt};
+	\addlegendentry{Actual}
+
+	\end{axis}
+	\end{tikzpicture}
+	\caption{Configuration estimation on SPR dataset}
+\end{subfigure}
+\label{chart:gan}
+\caption{GAN Phase experimental results}
+\end{figure*}
+
+We have also applied GAN phase to the network architecture proposed in \cite{paper0}.
+In this experiment, GAN phase reduced the performance slightly.
+However, as we have discussed earlier, due to increased number of samples, full batch training strategy is the cause of this.
+In fact, when we reduce the batch size down to 900 samples, GAN phase starts to improve the score of this architecture.
 
 The final set of experiments shows the stability that GAN phase adds.
-In Table ...
-we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing.
+In Table \ref{tbl:all}, we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing.
 It is clear that the GAN phase not only improves the average case but significantly improves the worst case, which is important in a live setting.
 This added stability can also be observed in Figure \ref{chart:trainingmse}, where the training loss has less fluctuations when the data augmentation is employed.
+
+\begin{table}
+\caption{Detailed performance analysis}
+\begin{tabular}{l|l|l|l|l|l|l}
+	Method & \multicolumn{4}{c|}{Proposed} & \multicolumn{2}{c}{\cite{paper0}} \\\hline
+	Dataset & \multicolumn{2}{c|}{SPR} & \multicolumn{2}{c|}{\dszero{}} & SPR & \dszero{} \\\hline
+	GAN Phase 			& Yes  & No   & Yes  & No   &  \multicolumn{2}{c}{No} \\\hline
+	Average   			& 0.31 & 0.89 & ???? & ???? & ???? & ???? \\
+	Best      			& ???? & ???? & ???? & ???? & ???? & ???? \\
+	Worst     			& ???? & ???? & ???? & ???? & ???? & ???? \\
+	Std. deviation  	& ???? & ???? & ???? & ???? & ???? & ???? \\
+	Training time (s)  	& ???? & ???? & ???? & ???? & ???? & ???? \\
+	Testing time  (ms) 	& ???? & ???? & ???? & ???? & ???? & ???? \\
+\end{tabular}
+\label{tbl:all}
+\end{table}
 
@@
 
-Epirements conducted on the latter machine will be labeled as GPU based, whereas on the former as CPU based.
-
-By taking advantage of Cloud Computing technology, one does not have to spend large amounts of money to obtain high-specs machine, rather, rent readily available deep learning instances in the cloud for pennies on the dollar.
-
-The code for this work is available at: \url{https://github.com/Aimen-Zelaci/SPRPCF_ANN/}.
-
-The elapsed training time of an ANN model depends on the parameters of the model, for example, the number of hidden layers and hidden neurons, mini batch size, dataset size, number of epochs, the framework used to code the model, and of course the specifications of the machine.
-
-In this work we fixed the number of epochs to 2000 and executed training using Tensorflow(Keras) and Pytorch frameworks.
-As demonstrated in Tables(5,6).
-It is worth mentioning the differences between training with full batch or mini batches.
-In full batch training, the whole dataset is passed to the model for each iteration.
-In contrast, mini-batch-training, the dataset is split into small mini batches of equal sizes, then passed to the model seperately, thus for each epoch there will be exactly length  of the dataset devided by the mini batch size steps, and hence slowing down the training process.
-Previous works \cite{masters2018revisiting, keskar2016large} have firmly proved the advantages of using the correct mini batch size as oppose to large batch sizes.
-Mini batches allow for more frequent gradient calculations, that results in more stable and reliable training.
-Perhaps one of the main downsides of using large batch size is the poor generalization resulting in a phenomena know as the "generalization gap".
-Active research \cite{hoffer2017train} is on going to actually use large batch sizes while mainting the performance of the model and shortning the training runtime.
-A closely related recent work \cite{paper0}, conducted their expirements using full batch to train the model.
-In this work we will use the latter paper availabe code on Github for Pytorch expirements, with slight modifications to fit our purposes.
-Finally, we compare the performance of the WGAN model, using Tensorflow(Keras) framework, of CPU based to that of GPU based.
+In this section we have determined both testing and training time of the proposed system in comparison to the simulation approach.
+In Table \ref{tbl:timing}, the result of these experiments are published.
+Training time is total training time while testing is per sample.
+Please note that he training time is considered offline time; i.e., it is the time that will only be used once before the system is deployed.
+Once trained, the ANN can work alone without the need for GAN or training again.
 
 \begin{table}
-\begin{tabular}{lllll}
-    & dataset size & mini batch size & Time elapsed (sec) \\
-Mini batches    &336 + 0 & 8 & 214 & \\
-    &336 + 1000 & 8 & 744 & \\
-    &336 + 2000 & 16 & 685  & \\ 
-    &336 + 3000 & 20 & 861  & \\
+\caption{Execution time of algorithms}
+\begin{tabular}{l|l|l}
+Method  &  Training & Testing \\
+Proposed ANN without GAN phase & ??? & ??? \\
+Proposed ANN with GAN phase    & ??? & ??? \\
+\cite{paper0}                  & ??? & ??? \\
+FV-FEM						   & -   & ???
 \end{tabular}
-\begin{tabular}{lllll}
-   & dataset size & Time elapsed (sec) \\
-Full batch    &336 + 0 &  23 & \\
-    &336 + 1000 &  34 & \\
-    &336 + 2000 &  45 & \\ 
-    &336 + 3000 &  57 & \\
-\end{tabular}
-\caption{Training performance using Tensorflow(Keras). CPU based training.}
+\label{table:timing}
 \end{table}
-\begin{table}
-\begin{tabular}{lllll}
- & dataset size & mini batch size & Time elapsed (sec) \\
-Mini batches    & 336 + 0 & 8 & 1315 & \\
-    & 336 + 1000 & 8 & 6453  & \\
-    & 336 + 2000 & 16 & 4751  & \\ 
-    & 336 + 3000 & 20 & 5132 & \\
-\end{tabular}
-\begin{tabular}{lllll}
-   &dataset size & Time elapsed (sec) \\
-   Full batch &336 + 0 &  36  & \\
-    & 336 + 1000 &  98  & \\
-    & 336 + 2000 &  195  & \\ 
-    & 336 + 3000 &  336  & \\
-\end{tabular}
-\caption{Training performance using Pytorch. CPU based training.}
-\end{table}
-
-\begin{table}[h]
-\centering
-\begin{tabular}{l|l}
-      & Time elapsed \\
-      \hline
-    ANN &  0.17 sec \\
-    \hline
-    Simulation &  7872 sec = 2.18 hours  \\
-\end{tabular}
-
-\caption{ANN vs Simulation test runtime performance}
-\end{table}
-\newpage
 
@@
 
+The code for this work is available at: \url{https://github.com/Aimen-Zelaci/SPRPCF_ANN/}.
+
 \bibliographystyle{IEEEtran}

### 2020-04-16 docs/paper/paper.tex
* Experimental results section is complete

@@
 		Hidden layers & 5 & 5 & 6 \\
-		Neurons in hidden layers & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ & 50 \\
+		Neurons in hidden layers & $ 128 $ & 1024 & 50 \\
 		Batch size & 32 & 32 & 48 \\
@@
 We have used mean square error as in the comparisons.
-All algorithms are implemented using TensorFlow library in Python and experiments are performed on laptop with Intel i7-5600 CPU and 8GB of RAM.
+All algorithms are implemented using TensorFlow with Keras library in Python and experiments are performed on laptop with Intel i7-5600 CPU and 8GB of RAM.
 TensorFlow library is set to use only CPU for the experiments.
 
-In the following subsections, we have performed experiments to show the performance of the base ANN system by its own comparing with the state-of-the-art method in the literature, improvement gained by employing GAN phase, and finally the computational cost of the overall system compared to the simulator.
-All numeric comparison results are averaged over multiple executions.
+In the following subsections, we have performed experiments to show the performance of the base ANN system by its own comparing with the state-of-the-art method in the literature \cite{paper0}, improvement gained by employing GAN phase, and finally the computational cost of the overall system compared to the simulator.
+5000 training epochs are used for the state-of-the-art method as suggested in the original paper.
+All numeric comparison results are averaged over multiple executions as listed in Table \ref{tbl:dataset}.
+Non-averaged data used in charts, such as configuration estimation, are selected from non-extreme cases for the compared methods.
 
@@
 Therefore, they both have higher error rate compared to the \dszero{} dataset.
+According to Figure \ref{chart:perfnoaug}-c $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength.
+This can be caused by the fact that this method uses full-batch learning \hl{[??]} and therefore under-fits the model.
+Regardless of this, both models have similar MSE due to the shift in the curve fit.
+This shift is caused because the network is never exposed to this particular geometric configuration.
 
@@
 			width=\textwidth,
+			ymin=5,ymax=7,xmin=5,xmax=7,
 			legend pos=south east
@@
 				mark size=2.9pt, mark=o, color=red, fill=red
-			] table{../../experiments_spr-pcf/Without_augmentation/kfold-predictions-vs-labels/1st/graph_data.txt};
+			] table{../../experiments_spr-pcf/Our_net/Without_augmentation/kfold-predictions-vs-labels/8th/graph_data.txt};
 			\addlegendentry{$Proposed$}
@@
 				mark size=2.9pt, mark=x, color=green
-			] %table{??};
-			coordinates{(7.2, 6.8)};
+			] 
+			table{../../experiments_spr-pcf/Their_net/without_augmentation/kfold-predictions-vs-labels/5th/graph_data.txt};
 			\addlegendentry{\cite{paper0}}
@@
 		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
-		ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
+		ylabel=$ Loss $ $ in $ $ Log(db/cm) $,
 		grid=both,
@@
 		width=0.48\textwidth,
-		legend pos=north east
+		legend pos=north west
 	]
@@
 	]
-	table[x={wave},y={predicted}]{data/vswavelength134_fold9_noaug.txt};
+	table[x={wave},y={predicted}]{data/wave_134_our.txt};
 	\addlegendentry{$Proposed$}
@@
 	] 
-	%table{??};
-	coordinates{(500, 7)};
+	table[x={wave},y={predicted}]{data/wave_134_their.txt};
 	\addlegendentry{\cite{paper0}}
@@
 	] 
-	table[x={wave},y={real}]{data/vswavelength134_fold9_noaug.txt};
-	coordinates{(6.8, 7.2)};
+	table[x={wave},y={real}]{data/wave_134_our.txt};
+
 	\addlegendentry{Actual}
@@
 	] 
-	table[x={wave},y={predicted}]{data/vswavelength135_fold9_noaug.txt};
+	table[x={wave},y={predicted}]{data/wave_135_our.txt};
 	\addlegendentry{$Proposed$}
@@
      ]
-     %table{??};
-     coordinates{(500, 7.5)};
+	table[x={wave},y={predicted}]{data/wave_135_their.txt};
      \addlegendentry{\cite{paper0}}
@@
 	] 
-	table[x={wave},y={real}]{data/vswavelength135_fold9_noaug.txt};
+	table[x={wave},y={real}]{data/wave_135_their.txt};
 	\addlegendentry{Actual}
@@
 \end{figure*}
-
-\hl{CK: continue here..}
 
@@
 In Figure \ref{chart:gan}, the results of these experiments has shown.
-An additional note to take away from this experiment is that the dataset with the least number of samples has the highest improvement, which is demonstrated in a clearer fashion in Table \ref{tbl:all}.
-This is due the fact that the number of training samples in this dataset is insufficient to train the regressor network.
+An additional note to take away from this experiment is that the dataset with the limited number of samples has highest improvement, which is demonstrated in a clearer fashion in Table \ref{tbl:all}.
+This is due the fact that the number of training samples in this dataset is insufficient to train the regressor network causing reduced performance.
+
+In Figure \ref{chart:gan}-c, prediction capabilities with and without GAN phase is compared.
+In the case with $n_{analyte} = 133$, the network without GAN phase has failed to predict the curve correctly.
+Even though GAN boosted network has predicted the curve lower than it is, the peak is in the correct wavelength, which could help PCF designers to pin-point highest loss.
 
@@
 				mark size=2.9pt, mark=o, color=red, fill=red
-			] table{../../experiments_spr-pcf/Without_augmentation/kfold-predictions-vs-labels/1st/graph_data.txt};
-			\addlegendentry{With GAN}
+			] 
+			table{../../experiments_spr-pcf/Our_net/Without_augmentation/kfold-predictions-vs-labels/3rd/graph_data.txt};
+			\addlegendentry{Without GAN}
 
@@
 				mark size=2.9pt, mark=x, color=green
-			] %table{??};
-			coordinates{(7.2, 6.8)};
-			\addlegendentry{Without GAN}
+			]
+			table{../../experiments_spr-pcf/Our_net/with_augmentation/kfold-predictions-vs-labels/3rd/graph_data.txt};
+			\addlegendentry{With GAN}
 
@@
 			\addlegendentry{$Actual$}
-
+			\legend{}
 		\end{axis}
@@
 		] 
-		table{../../expirrements_pcf2/Our_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
-		\addlegendentry{With GAN}
+		table{../../expirrements_pcf2/Our_net/without_augment/kfold-predictions-vs-labels/4th/graph_data.txt};
+		\addlegendentry{Without GAN}
 
@@
 		] 
-		table{../../expirrements_pcf2/Their_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
-		\addlegendentry{Without GAN}
+		table{../../expirrements_pcf2/Our_net/with_augment/kfold-predictions-vs-labels/4th/graph_data.txt};
+		\addlegendentry{With GAN}
 
@@
 		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
-		ylabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
+		ylabel=$Loss $ $ in $ $ Log(db/cm) $,
 		grid=both,
@@
 		width=0.48\textwidth,
-		legend pos=north east
+		legend pos=north east,
 	]
@@
 	]
-	table[x={wave},y={predicted}]{data/vswavelength134_fold9_noaug.txt};
-	\addlegendentry{With GAN}
+	table[x={wave},y={predicted}]{data/wave_134_our.txt};
+	\addlegendentry{Without GAN}
 
@@
 	] 
-	%table{??};
-	coordinates{(500, 7)};
-	\addlegendentry{Without GAN}
+	table[x={wave},y={predicted}]{data/wave_134_aug.txt};
+	\addlegendentry{With GAN}
 
@@
 	] 
-	table[x={wave},y={real}]{data/vswavelength134_fold9_noaug.txt};
-	coordinates{(6.8, 7.2)};
-	\addlegendentry{Actual}
+	table[x={wave},y={real}]{data/wave_134_our.txt};
+	\addlegendentry{Actual}\legend{};
 	\end{axis}
@@
 		major grid style={gray!25},
-		title={$n_{analyte=1.35}$},
+		title={$n_{analyte=1.33}$},
 		width=0.48\textwidth,
@@
 	] 
-	table[x={wave},y={predicted}]{data/vswavelength135_fold9_noaug.txt};
-	\addlegendentry{With GAN}
+	table[x={wave},y={predicted}]{data/wave_133_our.txt};
+	\addlegendentry{Without GAN}
 
@@
      ]
-     %table{??};
-     coordinates{(500, 7.5)};
-     \addlegendentry{Without GAN}
+     table[x={wave},y={predicted}]{data/wave_133_aug.txt};
+     \addlegendentry{With GAN}
 
@@
 	] 
-	table[x={wave},y={real}]{data/vswavelength135_fold9_noaug.txt};
+	table[x={wave},y={real}]{data/wave_133_aug.txt};
 	\addlegendentry{Actual}
-
+	\legend{}
 	\end{axis}
@@
 \end{subfigure}
+
 \label{chart:gan}
@@
 It is clear that the GAN phase not only improves the average case but significantly improves the worst case, which is important in a live setting.
+Even in a dataset with enough examples to train the network (\dszero), using GAN phase reduces the worst case error by 32\%.
 This added stability can also be observed in Figure \ref{chart:trainingmse}, where the training loss has less fluctuations when the data augmentation is employed.
@@
 \begin{tabular}{l|l|l|l|l|l|l}
-	Method & \multicolumn{4}{c|}{Proposed} & \multicolumn{2}{c}{\cite{paper0}} \\\hline
-	Dataset & \multicolumn{2}{c|}{SPR} & \multicolumn{2}{c|}{\dszero{}} & SPR & \dszero{} \\\hline
-	GAN Phase 			& Yes  & No   & Yes  & No   &  \multicolumn{2}{c}{No} \\\hline
-	Average   			& 0.31 & 0.89 & ???? & ???? & ???? & ???? \\
-	Best      			& ???? & ???? & ???? & ???? & ???? & ???? \\
-	Worst     			& ???? & ???? & ???? & ???? & ???? & ???? \\
-	Std. deviation  	& ???? & ???? & ???? & ???? & ???? & ???? \\
-	Training time (s)  	& ???? & ???? & ???? & ???? & ???? & ???? \\
-	Testing time  (ms) 	& ???? & ???? & ???? & ???? & ???? & ???? \\
+	Method & \multicolumn{3}{c|}{SPR} & \multicolumn{3}{c}{\dszero{}} \\\hline
+	Dataset & \multicolumn{2}{c|}{Proposed} & \cite{paper0}  & \multicolumn{2}{c|}{Proposed}   & \cite{paper0} \\\hline
+	GAN Phase 			& Yes            & No    &  No     &   Yes            & No             & No    \\\hline
+	Average   			& \textbf{0.314} & 0.894 & 0.987   &   \textbf{0.134} & 0.156          & 0.167 \\
+	Best      			& \textbf{0.006} & 0.042 & 0.047   &   0.095          & \textbf{0.093} & 0.106 \\
+	Worst     			& \textbf{1.102} & 6.792 & 5.955   &   \textbf{0.181} & 0.265          & 0.416 \\
+	Std. dev.       	& \textbf{0.437} & 2.213 & 1.940   &   \textbf{0.031} & 0.046          & 0.090 \\
 \end{tabular}
@@
 
-\hl{Training and execution time of ANN versus simulation method}
-
 In this section we have determined both testing and training time of the proposed system in comparison to the simulation approach.
@@
 Training time is total training time while testing is per sample.
-Please note that he training time is considered offline time; i.e., it is the time that will only be used once before the system is deployed.
+These tests are performed over SPR dataset.
+Please note that he training time is considered offline time; i.e., it is the time that will only be used once, before the system is deployed.
 Once trained, the ANN can work alone without the need for GAN or training again.
+With this information, it is evident that the ANN based methods are far faster than the simulation approach by several orders of magnitude.
+Even when training is included, total time spent to calculate the confinement loss will be faster on a GAN boosted ANN compared to FV-FEM simulator after only 5 samples.
+
+The training time difference between ANN systems is caused by the increased depth in the proposed architecture as well as mini-batch training strategy.
+Training time is dominated by GAN phase; however, this phase does not add any overhead to the testing time.
+The testing time difference between two networks are caused by the depth of the neural network (6 hidden layers instead of 3).
 
@@
 \begin{tabular}{l|l|l}
-Method  &  Training & Testing \\
-Proposed ANN without GAN phase & ??? & ??? \\
-Proposed ANN with GAN phase    & ??? & ??? \\
-\cite{paper0}                  & ??? & ??? \\
-FV-FEM						   & -   & ???
+Method    			  &  Training (s) & Testing (ms) \\\hline
+Proposed ANN 		  &  42 & 3.6 \\
+Proposed ANN with GAN & 449 & 3.6 \\
+GAN phase only        & 370 &  -  \\
+\cite{paper0}		  &  20 & 2.7 \\
+FV-FEM		   		  &  -  & 106958
 \end{tabular}
-\label{table:timing}
+\label{tbl:timing}
 \end{table}

### 2020-04-16 docs/paper/paper.tex
* Conclusion

@@
 
-\hl{about the improved speed}
+In this paper, we have demonstrated that the use of generative adversarial networks can benefit neural networks that are designed to compute photonic crystal fiber optical properties.
+Additionally, we have also proposed and demonstrated a superior neural network that is both more generic and more powerful to estimate of confinement loss.
+The GAN phase also reduces the required samples to fully train the ANN, reducing the work necessary to employ the proposed system.
+The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research; in the experiments, it surpassed the accuracy of the method proposed in \cite{paper0} on the dataset that this state-of-the-art method is optimized on.
 
-\hl{reduced amount of training samples}
+Another important aspect in this paper is the experiments performed on a dataset that is designed to test the ability of the neural networks to estimate the properties of a new configuration.
+For this purpose, we have built a database based on Surface Plasmon Resonance with varying geometric configurations.
+During testing a new configuration that is not used for the training is used.
+The proposed ANN, augmented with GAN phase is shown to estimate the new configuration to an acceptable error rate.
 
-\hl{increased generality of the system}
-
-\hl{This Idea is very important}
-In this work we built a feed forward ANN model that learned the confinement loss given the geometric properties of a SPR-based PCF sensor with fixed pattern and geometrical shape of the cladding air holes.
-For different types of sensors, Convolutional and Reccurent neural networks can be of great advantage, to discover the spatial insights of variety of patterns and  geometrical shape of the cladding air holes.
-The latter will be conducted in future work.
-
-Machine learning approaches has an inherit strength on top of classical simulation methods: they could model hidden parameters in a system which we have no knowledge about.
-Therefore, not only ANN can improve the speed of PCF simulation, but also accuracy of the simulations.
-However, this final claim requires further analysis and experimentation.
+The most important benefit of using machine learning methods instead of simulation is the speed factor.
+In the experiments it is shown that the machine learning methods works few orders of magnitude faster than the simulation methods.
+For different types of sensors, Convolutional and Recurrent neural networks can be of great advantage to discover the optimal patterns and geometrical shapes of the cladding air holes.
+This potential will be explored in a future work.
 

### 2020-04-17 docs/paper/paper.tex
* Fixes to the paper

@@
 However, the potential number of combinations possible for a single application is very large.
-This issue combined by the speed of the commonly used Full Vectorial Finite Element Method (FV-FEM) causes the task to take significant amount of time.
+This issue combined by the speed of the commonly used Full Vectorial Finite Element Method (FV-FEM) simulators causes the task to take significant amount of time.
 As stated in the previous works, artificial neural networks (ANN) can predict the result of numerical simulations much faster.
@@
 Experimental analysis suggest that the proposed combination not only accurately predicts the confinement loss even with limited amount of data but also GAN can be used to improve existing methods in the literature.
-Finally, it is shown that this system can predict the confinement loss over a range of analytes and wavelengths in a completely new set of geometric configuration and generic enough not to require any additional tuning when used in a new dataset.
+Finally, it is shown that this system can predict the confinement loss over a range of analytes and wavelengths in a completely new geometric configuration and generic enough not to require any additional tuning when used in a new dataset.
 \end{abstract}
@@
 
-Machine Learning (ML) techniques are becoming a common tool in many fields, surpassing human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
-Additionally, ANN can approximate any function proven by Universality theorem \cite{HORNIK1991251}.
+Machine Learning (ML) techniques are becoming a common tool in many fields and surpassing human performance in many tasks, such as automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology.
+Additionally, ANN can approximate any function proven by the Universality theorem \cite{HORNIK1991251}.
 This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a photonic crystal fiber \cite{paper0}.
 
-One of the most difficult challenges that deep learning models face is that they benefit from large amounts of data to train, which may be costly to acquire.
+One of the most difficult challenges that deep learning models face is that they benefit from large amounts of data to train, which is often costly and/or difficult to acquire.
 One of the solutions to overcome this issue is to artificially expand the original training dataset by the means of generative networks.
@@
 In this paper, we focus on estimating confinement loss, one of the propagation features of multi-channel Photonic Crystal Fiber (PCF) sensors, using artificial neural networks.
-Specifically, we have based our system on Surface Plasmon Resonance (SPR).
-However, in the experiments section we have demonstrated that the designed system is generic enough to apply to multiple PCF designs.
+\hl{Specifically, we have based our system on Surface Plasmon Resonance (SPR)}.
+However, in the experiments section we have demonstrated that the designed system is generic enough to be applied to multiple PCF designs.
 The most important contribution of this research is the use of GAN phase, where the available data is expanded to be used in the training phase.
@@
 Detailed analysis of the experimental results are discussed in section \ref{sec:exp}.
-Finally, concluding remarks are made in section \ref{sec:conc}.
+Finally, concluding remarks are made in Section \ref{sec:conc}.
 
@@
 
-In this section details of the proposed method is discussed.
+In this section, details of the proposed method is discussed.
 Training of the system contains two phases: a GAN phase and regression training phase.
@@
 These generated samples are filtered to ensure they fall within the applicable range.
-Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network.
-At the end of the training, the ANN that is trained for the regression task will be used to decide the containment loss  of a set of input parameters.
+Original training samples and generated samples are joined to train a fully-connected feed-forward multi-layer perceptron (MLP) neural network for the regression ask of estimating confinement loss.
+At the end of the training, the ANN will be used to decide the containment loss of a previously unseen set of input parameters.
 This architecture is illustrated in Figure \ref{fig:overall}.
@@
 The aim of the generator is to transform fully randomized data into data that follows the distribution of the original dataset.
-Discriminator assesses the performance of the generator and provides feedback for training.
+The discriminator assesses the performance of the generator and provides feedback for training.
 Instead of directly training generator, it is trained through this feedback.
@@
 
-It is possible to use different metrics for training in GAN \hl{[references here]}, for this project we have selected WGAN Wasserstein distance metric.
-This variant has been proposed by Arjovsky et al in \cite{arjovsky2017wasserstein}.
-In this system, discriminator is named as critic and it measures the distance between the generated data and the real data.
+It is possible to use different metrics for training a GAN \cite{goodfellow2014generative, mao2017least, lucic2018gans}; for this project we have selected Wasserstein distance metric called as WGAN.
+This variant is proposed by Arjovsky et al in \cite{arjovsky2017wasserstein}.
+In this system, discriminator is named as critic and it measures the distance between the generated  and the real data.
 The reason behind choosing WGAN over other methods is to be able to determine a stopping criteria.
@@
 WGAN uses an adaptive stopping criteria that does not have the issue mentioned above.
-Additionally, we have selected to incorporate Gradient penalty to improve WGAN proposed in \cite{gulrajani2017improved}.
+Additionally, we have selected to incorporate Gradient penalty to improve WGAN as proposed in \cite{gulrajani2017improved}.
 This improved WGAN system converges in a stable manner without having to fine tune hyper-parameters of the system.
@@
 The output from this system should be input and output pairs that will be used to train ANN part of the system.
-In our PCF system we have 6 input parameters and a single output parameter making a total of 7 parameters that will be used in the GAN phase.
+In our SPR system, we have 7 input parameters and a single output parameter, making a total of 8 parameters that will be used in the GAN phase.
 In Section \ref{sec:exp}, we have experimented using a different PCF system with different inputs, resulting a different number of parameters for the system.
-The generator is supplied with the same number of parameters as its expected output, that is 7 for our PCF system.
+The generator is supplied with the same number of parameters as its expected output, that is 8 for our dataset.
 These parameters are generated using Gaussian noise and is called latent variable.
-Once the training phase is complete, the generator and the filter is used to augment the number of training samples that are available for ANN.
 
@@
 In the proposed system, we have included a filtering step for the generated data.
-This step uses a simple condition to discard the values that fall out of the desired range, for both the independent variables ($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss.
+This step uses a simple condition to discard the values that fall out of the desired range, for both the independent variables ($n_{analyte}, \lambda, \Lambda, d1, d2, d3, n_c$), and the confinement loss.
+Once the training phase is complete, the generator and the filter is used to augment the number of training samples that are available for ANN to train on.
 
@@
 		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} & \textbf{Regressor} \\\hline
-		Hidden layers & 5 & 5 & 6 \\
-		Neurons in hidden layers & $ 128 $ & 1024 & 50 \\
+		Hidden layers & 5 & 5 & 5 \\
+		Neurons in hidden layers & $ 128 $ & $2^{layer\_index} \times 32$ & 50 \\
 		Batch size & 32 & 32 & 48 \\
@@
 		Optimizer & Adam \cite{kingma2014adam} & Adam & Adam \\
-		Input normalization & None & Z-score (for collected samples) & Z-score \\
+		Input normalization & None & None & None \\
 		Layer normalization & - & Batch \cite{ioffe2015batch} & Batch \\
-		Loss function & Critic(generated) & Critic(generated) - Critic(collected) & MSE \\
+		Loss function & $-Critic(generated)$ & $Critic(gen) - Critic(col) + Penalty_{gradient}$ & MSE \\
 	\end{tabular}
@@
 
-The ANN model employed in this research is a fully-connected feed-forward Multi Layer Perceptron (MLP) consists of an input layer, an output layer, and 5 hidden layers.
+The ANN model employed in this research is a fully-connected feed-forward Multi Layer Perceptron network consists of an input layer, an output layer, and 5 hidden layers.
 The ANN is designed and trained to estimate containment loss in a regression configuration.
-We have applied $log_{10}$ to confinement loss in order to keep its numeric stability across a wide range.
+We have applied $log_{10}$ to confinement loss in order to keep its numeric stability across a wide range \cite{paper0}.
 Each hidden layer contains 50 neurons and uses Rectified Linear Unit (ReLU) activation function.
@@
 
-We have adopted Adam \cite{kingma2014adam} as the optimizer and the mean squared error (MSE) as the loss/cost function.
+We have adopted Adam \cite{kingma2014adam} as the optimizer and mean squared error (MSE) as the loss/cost function.
 In addition, we use Batch Normalization algorithm \cite{ioffe2015batch} to accelerate training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.
-In proposed system, the ANN is trained using the samples from the original dataset and the augmented samples generated by the GAN phase.
+In the proposed system, the ANN is trained using the training samples from the original dataset and the augmented samples generated by the GAN phase.
 
@@
 
-A labelled dataset of only 432 samples was collected in this work, through simulations using FV-FEM.
-This dataset consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables.
+\hl{PCF design details, written by AY. Following is only for reference}
+
+A labelled dataset of 432 samples was collected in this work, through simulations using FV-FEM.
+This dataset consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, and real part of the refractive index ($n_c$) taken as our independent variables.
 The labels are the confinement loss of the PCF.
@@
 }
-
-\hl{PCF design details, written by AY}
 
@@
 Each fold tests a single configuration using the other configurations as training data.
-Slicing the data this way allowed us to guide the network to predict the loss on a completely different configuration.
+Slicing the data this way allowed us to guide the network to predict the loss on a configuration that has not used in training.
 Please note that we have applied $log_{10}$ to confinement loss to scale it.
+
+We have used mean square error (MSE) in the comparisons.
+All algorithms are implemented using TensorFlow with Keras library in Python and experiments are performed on laptop with Intel i7-5600 CPU and 8GB of RAM.
+TensorFlow library is set to use only CPU for the experiments.
 
@@
 Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}.
-As a final note, the range and domain of these datasets are different; therefore, all comparisons should be drawn within the same dataset.
+As a final note, the range and domain of these datasets are different; therefore, all numeric comparisons should be drawn within the same dataset.
 
-We have used mean square error as in the comparisons.
-All algorithms are implemented using TensorFlow with Keras library in Python and experiments are performed on laptop with Intel i7-5600 CPU and 8GB of RAM.
-TensorFlow library is set to use only CPU for the experiments.
-
-In the following subsections, we have performed experiments to show the performance of the base ANN system by its own comparing with the state-of-the-art method in the literature \cite{paper0}, improvement gained by employing GAN phase, and finally the computational cost of the overall system compared to the simulator.
-5000 training epochs are used for the state-of-the-art method as suggested in the original paper.
+In the following subsections, we have performed experiments to show the performance of the base ANN system by its own comparing with the state-of-the-art method in the literature \cite{paper0}, improvement gained by employing GAN phase, and finally the computational advantages of using ANN over the simulator.
+5000 training epochs are used for \cite{paper0} as suggested in the original paper.
 All numeric comparison results are averaged over multiple executions as listed in Table \ref{tbl:dataset}.
-Non-averaged data used in charts, such as configuration estimation, are selected from non-extreme cases for the compared methods.
+Non-averaged data used in figures, such as configuration estimation, are selected from non-extreme cases for the compared methods.
 
@@
 	Configurations & 9 & - \\
-	Parameters & 6 & 5 \\
+	Parameters & 7 & 5 \\
 	Output & $log_{loss}$ & $log_{loss}$ \\
@@
 The first experiment involves in training loss over SPR dataset.
-In this experiment, we have trained ANN model for up to 2000 epochs and reported the training loss in Figure \ref{chart:trainingmse}.
-We have additionally tested the accuracy with different number of epochs in training.
-According to this experiment, training our ANN architecture more than 2000 epochs does not yield to any improvement.
-Therefore, we have set the training epoch limit to 2000 in subsequent experiments.
-However, this number depends on dataset and at times additional training can improve the result.
-Additionally, it is clear that the use of augmented samples from the GAN phase reduces the oscillations in the training error.
+In this experiment, we have trained ANN model for up to 3000 epochs and reported the training loss in Figure \ref{chart:trainingmse}.
+According to this experiment, training our ANN architecture more than 2500 epochs does not yield to any improvement.
+Therefore, we have set the training epoch limit to 2500 in all subsequent experiments.
+However, this number depends on the dataset and at times additional training can improve the result.
+Additionally, the benefit of augmented samples from the GAN phase is evident even at the training as they reduce the oscillations in the training loss.
 
@@
 Results of this experiment is demonstrated in Figure \ref{chart:perfnoaug}.
-Please note that in the experiment involving SPR dataset, ANN models are predicting a new configuration and the number of samples available for training is lower.
+In the experiment using SPR dataset, ANN models are predicting a new configuration and the number of samples available for training is lower.
 Therefore, they both have higher error rate compared to the \dszero{} dataset.
-According to Figure \ref{chart:perfnoaug}-c $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength.
-This can be caused by the fact that this method uses full-batch learning \hl{[??]} and therefore under-fits the model.
+According to Figure \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength.
+This can be caused by the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}.
 Regardless of this, both models have similar MSE due to the shift in the curve fit.
@@
 			major grid style={gray!25},
-			ymax=2,
+			ymax=3,
 			no marks
@@
 		\addplot[line width=1pt,solid,color=blue] %
-		table{../../loss_curves_2k/ann_tr_loss_2k_with.txt};
+		table{../../loss_curves_3k/ann_tr_loss_3k_their_data_without.txt};
 		\end{axis}
@@
 		\addplot[line width=1pt,solid,color=blue] %
-		table{../../loss_curves_2k/ann_tr_loss_2k_without.txt};
+		table{../../loss_curves_3k/ann_tr_loss_3k_their_data_with.txt};
 		\end{axis}
@@
 				mark size=2.9pt, mark=o, color=red, fill=red
-			] table{../../experiments_spr-pcf/Our_net/Without_augmentation/kfold-predictions-vs-labels/8th/graph_data.txt};
-			\addlegendentry{$Proposed$}
+			] 
+			table{../../experiments_spr-pcf/Their_net/without_augmentation/kfold-predictions-vs-labels/5th/graph_data.txt};
+			\addlegendentry{\cite{paper0}}
 
@@
 				only marks,
-				mark size=2.9pt, mark=x, color=green
+				mark size=2.9pt, mark=x, color=green!50!black
 			] 
-			table{../../experiments_spr-pcf/Their_net/without_augmentation/kfold-predictions-vs-labels/5th/graph_data.txt};
-			\addlegendentry{\cite{paper0}}
+			table{../../experiments_spr-pcf/Our_net/Without_augmentation/kfold-predictions-vs-labels/8th/graph_data.txt};
+			\addlegendentry{$Proposed$}
 
@@
 			\addlegendentry{$Actual$}
+				\legend{}
 
@@
 		] 
-		table{../../expirrements_pcf2/Our_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
-		\addlegendentry{$Proposed$}
+		table{../../expirrements_pcf2/Their_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
+		\addlegendentry{\cite{paper0}}
 
@@
 		only marks,
-		mark size=2.9pt, mark=x, color=green
+		mark size=2.9pt, mark=x, color=green!50!black
 		] 
-		table{../../expirrements_pcf2/Their_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
-		\addlegendentry{\cite{paper0}}
+		table{../../expirrements_pcf2/Our_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
+		\addlegendentry{$Proposed$}
 
@@
 	]
-	table[x={wave},y={predicted}]{data/wave_134_our.txt};
-	\addlegendentry{$Proposed$}
+	table[x={wave},y={predicted}]{data/wave_134_their.txt};
+	\addlegendentry{\cite{paper0}}
 
@@
 		only marks,
-		mark size=2.9pt, mark=x, color=green
+		mark size=2.9pt, mark=x, color=green!50!black
 	]
-	table[x={wave},y={predicted}]{data/wave_134_their.txt};
-	\addlegendentry{\cite{paper0}}
+	table[x={wave},y={predicted}]{data/wave_134_our.txt};
+	\addlegendentry{$Proposed$}
 
@@
 	\addlegendentry{Actual}
+	\legend{}
 	\end{axis}
@@
 	] 
-	table[x={wave},y={predicted}]{data/wave_135_our.txt};
-	\addlegendentry{$Proposed$}
+	table[x={wave},y={predicted}]{data/wave_135_their.txt};
+  	\addlegendentry{\cite{paper0}}
 
@@
 		only marks,
-		mark size=2.9pt, mark=x, color=green
+		mark size=2.9pt, mark=x, color=green!50!black
      ]
-	table[x={wave},y={predicted}]{data/wave_135_their.txt};
-     \addlegendentry{\cite{paper0}}
+   	table[x={wave},y={predicted}]{data/wave_135_our.txt};
+   	\addlegendentry{$Proposed$}
 
@@
 	\addlegendentry{Actual}
+		\legend{}
 
@@
 The first set of experiments performed on GAN phase is the number of the augmented samples.
-In these experiments we have started augmentation by using 500 samples, increasing it by another 500 per experiment.
+In these experiments, we have augmented the proposed ANN system with varying number of samples.
 According to these experiments we have reached the minimum MSE at 1000 samples.
-Adding further samples reduces the performance and increases the training time.
+Adding further samples slightly reduces the performance while increasing the training time.
 The results of this experiment is demonstrated in Figure \ref{chart:gansamples}.
-This number may depend on the dataset that is used.
+The number of augmented samples may depend on the dataset that is used.
 However, in our experiments 1000 augmented samples produce good results in both datasets.
@@
 
-We have performed experiments to showcase the improvement gained by augmenting training samples using a GAN.
-In Figure \ref{chart:gan}, the results of these experiments has shown.
-An additional note to take away from this experiment is that the dataset with the limited number of samples has highest improvement, which is demonstrated in a clearer fashion in Table \ref{tbl:all}.
-This is due the fact that the number of training samples in this dataset is insufficient to train the regressor network causing reduced performance.
+We have performed experiments to showcase the improvement gained by augmenting training samples using GAN phase.
+In Figure \ref{chart:ganperf}, the results of these experiments has shown.
+An additional note to take away from this experiment is that the dataset with the limited number of samples has the highest improvement, which is demonstrated in a clearer fashion in Table \ref{tbl:all}.
+This difference is due the fact that the number of training samples in this dataset is insufficient to train the regressor network causing reduced performance.
 
-In Figure \ref{chart:gan}-c, prediction capabilities with and without GAN phase is compared.
-In the case with $n_{analyte} = 133$, the network without GAN phase has failed to predict the curve correctly.
+In Figure \ref{chart:ganperf}c, prediction of new configuration with and without GAN phase is compared.
+In the case with $n_{analyte} = 1.33$, the network without GAN phase has failed to predict the curve correctly.
 Even though GAN boosted network has predicted the curve lower than it is, the peak is in the correct wavelength, which could help PCF designers to pin-point highest loss.
@@
 				only marks,
-				mark size=2.9pt, mark=x, color=green
+				mark size=2.9pt, mark=x, color=green!50!black
 			]
@@
 		only marks,
-		mark size=2.9pt, mark=x, color=green
+		mark size=2.9pt, mark=x, color=green!50!black
 		] 
@@
 		only marks,
-		mark size=2.9pt, mark=x, color=green
+		mark size=2.9pt, mark=x, color=green!50!black
 	] 
@@
 		only marks,
-		mark size=2.9pt, mark=x, color=green
+		mark size=2.9pt, mark=x, color=green!50!black
      ]
@@
 \end{subfigure}
-
-\label{chart:gan}
 \caption{GAN Phase experimental results}
+\label{chart:ganperf}
 \end{figure*}
@@
 In this experiment, GAN phase reduced the performance slightly.
-However, as we have discussed earlier, due to increased number of samples, full batch training strategy is the cause of this.
+However, as we have discussed earlier, full batch training strategy is the cause of this due to increased number of samples.
 In fact, when we reduce the batch size down to 900 samples, GAN phase starts to improve the score of this architecture.
@@
 In Table \ref{tbl:all}, we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing.
-It is clear that the GAN phase not only improves the average case but significantly improves the worst case, which is important in a live setting.
+It is clear that the GAN phase not only improves the average case but significantly improves the worst case while reducing the deviation, which is important in a live setting.
 Even in a dataset with enough examples to train the network (\dszero), using GAN phase reduces the worst case error by 32\%.
@@
 These tests are performed over SPR dataset.
-Please note that he training time is considered offline time; i.e., it is the time that will only be used once, before the system is deployed.
+Please note that the training time is considered offline time; i.e., it is the time that will only be used once, before the system is deployed.
 Once trained, the ANN can work alone without the need for GAN or training again.
 With this information, it is evident that the ANN based methods are far faster than the simulation approach by several orders of magnitude.
-Even when training is included, total time spent to calculate the confinement loss will be faster on a GAN boosted ANN compared to FV-FEM simulator after only 5 samples.
+Even when training time is included, total time spent to calculate the confinement loss will be faster on a GAN boosted ANN compared to an FV-FEM simulator after only 5 samples.
 
@@
 Training time is dominated by GAN phase; however, this phase does not add any overhead to the testing time.
-The testing time difference between two networks are caused by the depth of the neural network (6 hidden layers instead of 3).
+The testing time difference between two networks are caused by the depth of the neural network (5 hidden layers instead of 3).
+
+We have also experimented with TensorFlow using GPU via an additional system that contains NVidia GTX 1660Ti GPU.
+However, due to the relatively small size of the network, using GPU slightly reduced the computational performance instead of increasing it.
 
@@
 In this paper, we have demonstrated that the use of generative adversarial networks can benefit neural networks that are designed to compute photonic crystal fiber optical properties.
-Additionally, we have also proposed and demonstrated a superior neural network that is both more generic and more powerful to estimate of confinement loss.
+Additionally, we have also proposed and demonstrated a neural network that is both more generic and more accurate to estimate the confinement loss compared to the state-of-the-art network.
 The GAN phase also reduces the required samples to fully train the ANN, reducing the work necessary to employ the proposed system.
-The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research; in the experiments, it surpassed the accuracy of the method proposed in \cite{paper0} on the dataset that this state-of-the-art method is optimized on.
+The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research; in the experiments, it surpassed the accuracy of the method proposed in \cite{paper0} on the dataset this method is optimized on.
 
-Another important aspect in this paper is the experiments performed on a dataset that is designed to test the ability of the neural networks to estimate the properties of a new configuration.
+Another important aspect in this paper is the experiments performed on a dataset that is designed to test the ability of artificial neural networks to estimate the properties of a new configuration.
 For this purpose, we have built a database based on Surface Plasmon Resonance with varying geometric configurations.
-During testing a new configuration that is not used for the training is used.
+During the testing, a new configuration that is not used for the training is used.
 The proposed ANN, augmented with GAN phase is shown to estimate the new configuration to an acceptable error rate.
@@
 The most important benefit of using machine learning methods instead of simulation is the speed factor.
-In the experiments it is shown that the machine learning methods works few orders of magnitude faster than the simulation methods.
+In the experiments it is shown that the machine learning methods work few orders of magnitude faster than the simulation method.
 For different types of sensors, Convolutional and Recurrent neural networks can be of great advantage to discover the optimal patterns and geometrical shapes of the cladding air holes.

### 2020-04-28 docs/paper/paper.tex
* fixed graph
* Literature review * Integrated SPR PCF design

@@
-\documentclass[draft, 10pt]{IEEEtran}
+\documentclass[10pt]{IEEEtran}
 
@@
 
-\hl{Importance of PCF and SPR, written by AY or HA}
+\hl{Importance of PCF and SPR, written by HA}
 
@@
 
-\hl{!! Literature survey !!}
+One of the first works on using artificial neural networks in photonic crystal fibers (PCF) design is presented in \cite{hameed2008accurate}.
+The results demonstrated the accuracy of the network on a specific PCF design.
+Another ANN method is employed in \cite{rodriguez2010efficient} to calculate chromatic dispersion of photonic crystal fiber.
+In \cite{mescia2011refinement}, authors employed a neural network for the refinement and design of Erbium doped photonic crystal fiber.
+Results showed that conventional methods consume large amount of time compared to the runtime of the neural network.
+Perhaps the most rigorous experiments about neural network use in PCF design is presented in \cite{paper0}.
+In this paper, a feed-forward multi-layer perceptron neural network is used to calculate multiple properties of a PCF design.
+The authors shown that the network can achieve both acceptable accuracy and superior speed compared to the existing numerical methods.
 
-\hl{Use of ANN in PCF}
+Authors in \cite{perez2017effectiveness} has explored the possibility of using GAN to boost neural networks, finding it is possible to improve the accuracy of existing image classifiers.
+Frid-Adar, et.
+al.
+\cite{frid2018synthetic} has applied the same method to improve the accuracy of liver lesion classification.
+The authors has found that balancing the training data using GAN has a higher improvement in accuracy compared to classical data generation strategies.
+Finally, in \cite{shin2018medical}, authors used the same technique to both augment and anonymize the training data with brain MRI with the similar success of the previous papers.
 
-\hl{SPR in PCF}
+\hl{Literature survey requires expansion related with SPR and PCF}
 
@@
 
-\hl{PCF design details, written by AY. Following is only for reference}
+\hl{to HA: This section has been written by two different people, should be merged!}
+
+\hl{Aimen:}
 
@@
 
+\hl{AY:}
+
+The numerical investigation to build the SPR dataset have been simulated with Comsol Multiphysics software~\cite{comsol_help}, where  the Full Vectorial Finite Element Method (FV-FEM) with perfectly matched layers (PMLs)~\cite{koshiba2002full,saitoh2001full} are used for numerical analysis.
+
+\begin{figure}[]
+	\centering
+	\includegraphics[width=.6\linewidth]{figures/Figx}
+	\caption{The cross-section of proposed  PCF based SPR sensor.}
+	\label{Figx}
+\end{figure}
+
+The cross section of proposed PCF based SPR sensor has been shown in Figure~\ref{Figx}.
+As can be seen from this figure, the sensor consists of analyte channel (sensing medium), metallic layer(Au) and PCF sections.
+The PCF section consists of nineteen various sized air holes, placed on silica background with hexagonal arrangement.
+The diameter of air holes are initially set as; $d_1$ is $0.45 \mu m$, $d_2$ is $0.75 \mu m$ and $d_3$ is $0.35 \mu m$, and  $d_c$ is $0.15$.
+The distance between air holes ($\Lambda$) also initially  set to be $2 \mu m$.
+The aim of using different size air holes is, while trapping the light in the core region of PCF (fundamental mode), at the same time allow some amount of light to leak from the bridges between air holes toward the plasmonic layer.
+Which will match the surface plasmon waves propagating along the metallic surface.
+Gold (Au) used as plasmonic layer and set to be $40 nm$, where Johnson and Christy Data~\cite{johnson1972optical} used for its permittivity.
+The Sellmeier Equation (Eq.(\ref{eqn1})) is used for calculating the refractive index of Silica  \cite{bjarklev2003PCF}.
+
+\begin{equation}
+n^2(\lambda)=1+\frac{ B_1 (\lambda)^2} {(\lambda)^2-C_1} + \frac{ B_2 (\lambda)^2} {(\lambda)^2-C_2} + \frac{ B_3 (\lambda)^2} {(\lambda)^2-C_3}
+\label{eqn1}
+\end{equation}
+%%
+
+where $\lambda$ is the operating wavelength, $n$ is the RI, $B_{1,2,3}$ and  $C_{1,2,3}$ are the  Sellmeier constants~\cite{bjarklev2003PCF}.
+
+The aim of SPR based sensor are sensing the RI changes at the resonance conditions.
+The resonace condition is the phase matching between SPWs propagating along metal layer (Au) and the fundamental mode of ligt that is propagating along the PCF core.
+At that specific time the confinement loss is reaches the highest peak point.
+Therefore, in SPR based PCF sensors the key parameter is the confinement loss and it is so important to precisely calculate the confinement losses.
+The Equation~\ref{eqn2} is used in this study for that purpose~\cite{yasli2019effect}.
+
+%%
+\begin{equation}
+\frac{40\pi}{ln(10) \lambda} Im(n_{eff}) \times 10^{4} [dB/cm]
+\label{eqn2}
+\end{equation}
+%%
+
+where the imaginary part of the effective RI shown with Im($n_{eff}$).
+
 \section{Experiments}
@@
 We have built the first dataset that is used in the experiments.
-This is \hl{an SPR PCF configuration ...
-and collected using FV-FEM.} Details of this dataset is explained in Section \ref{sec:pcf} and it is referred as SPR dataset.
+Details of this dataset is explained in Section \ref{sec:pcf} and it is referred as SPR dataset.
 Having nine configurations, we have performed 9-fold testing on this dataset.
@@
 Additionally, we have used the dataset that has been used in \cite{paper0}.
-\hl{This dataset contains over 1000 samples.
-Inputs to this data is ....
-and outputs are ....} We have only used log of confinement loss as the output.
+This dataset contains over 1000 samples.
+Inputs are refractive index of the core ($n_c$), wavelength ($\lambda$), hole diameter ($d$), pitch ($\Lambda$), and number of rings ($N_r$);  and outputs are effective index ($n_{eff}$), effective mode area ($A_{eff}$), dispersion ($D$), and the confinement loss ($\alpha_c$).
+We have only used confinement loss as the output.
 This dataset is referred as \dszero.
@@
 	\end{tikzpicture}
-	\caption{With augmentation}
+	\caption{Without augmentation}
 	\end{subfigure}	
@@
 	\end{tikzpicture}
-	\caption{Without augmentation}
+	\caption{With augmentation}
 	\end{subfigure}

### 2020-06-07 docs/paper/paper.tex
* Changes incoming from HA

@@
 
-\author{Aimen Zelaci, Ahmet Yaşlı, Cem Kalyoncu, and Hüseyin Ademgil}
+\author{Aimen Zelaci, Ahmet Yasli, Cem Kalyoncu, and Huseyin Ademgil}
 
@@
 
-\hl{Importance of PCF and SPR, written by HA}
+Due to their unique propagation features, Photonic Crystal Fibers (PCFs) have been integrated into a number of optical based devices and applications.
+Design flexibilities and precise light guidance abilities has made them more promising in comparison to conventional step index fibers in various optical applications including sensing \cite{wang2011selectively}.
+
+In the last decade, PCF based structures extensively employed as sensing devices.
+Possibility of filling the cladding holes with gas and liquid analytes makes them favourable in both chemical and biological sensing applications \cite{wang2011selectively,rifat2016highly,caucheteur2015review,dash2014spr}.
+Moreover, due to adaptable light guidance with possibilities of controlling the confinement loss and the chromatic dispersion at any operating wavelength are distinguishing features of PCF based structures in the literature.
+These charming propagation features can be achieved by employing, circular, cylindrical and even square and rectangular shaped \cite{wang2015simulation} air holes in the cladding and in the core region of the structures.
+Furthermore, the cladding pattern arrangements such as hexagonal, octagonal, decagonal square and circular \cite{wang2011selectively,bouk2004dispersion,ademgil2014highly,razzak2007chromatic}  can be engaged to achieve the desired features for preferred applications.
+The hole-to hole spacing (pitch) and the air hole sizes are critical parameters of tuning the aforementioned propagation characteristics.
+On the other hand, surface plasmon resonance (SPR) is a unique technique that occurs with light and free electrons interaction at metallic boundaries.
+This interaction results with excitement of surface plasmon polarition (SPP).
+Relative permittivity variations of the analytes will change the characteristics of the SPP wave, where sensing is triggered.
+Kretschamann Raether prism geometry is the fundamental construction principle of SPR based sensors \cite{kretschmann1968radiative}.
+This geometry practises Snell's Total Internal Reflection rule, where still very small amount of light refracts from the metallic layer into the evanescent field.
+The refracted photons are coupling with electron charge oscillations (plasmon) at the surface of metallic layer, which are known as surface plasmon waves (SPW).
+The maximum energy transfer from core mode to SPWs occurs with the effective index equalisation of this corresponding modes.
+This phenomenon is known as resonance phase matching, where losses are reaching the maximum levels.
+The possible changes in the analyte index will directly affect the resonance matching wavelengths.
+These possible variations are the main parameters for sensitivity calculations.
+The deep research on SPR based sensors have shown that Kretschmann Raether’s prism geometry fails satisfying the remote sensing and miniaturization requirements of critical detecting applications.
+One of the most common solution of overcoming these limitations are replacing the prism with the core of an optical fiber.
+Considering the recent technological developments, PCF are offering tremendous amount of design flexibility with the possibilities of complete control of light guidance.
+Hence, SPR technique can be integrated to this unique microstructured fibers for developing comprehensive multi-purpose sensor \cite{rifat2016highly,yasli2019effect}.
+Following the exclusive study by Hassani and Skorobogatiy \cite{hassani2006design}, number of structures have reported the merits of PCF based SPR sensors.
+In the past, structures that contains features such as multi-channel single analyte and multi-channel multi analyte have been investigated \cite{rifat2016highly,yasli2019effect,zhang2011wagon,yasli2019multi,azzam2016multichannel}.
+Aslo, the effects of various metallic layers such as Au, Ag \cite{yasli2019multi}, Ag- Graphene \cite{rifat2016highly}, Ta2TO5 \cite{otupiri2015multi}, ITO \cite{dash2014spr}, TiO2 \cite{rifat2016highly} with various design paraeters have also been investigated in detailed.
+Several design parameters such as plasmonic material, thickness of the layers, air hole size and positions are decisive on resonance matching wavelength of the SPR based structures.
+Optimizing and refinement of these parameters are extremely time consuming process with considerable computational time \cite{fornarelli2009neural,abdelaziz2012photonic,paper0}.
+In the past, genetic algorithms \cite{abdelaziz2012photonic,borel2004topology} method was used to optimize the structural design parameters to achieve better propagation features of photonic devices\cite{rifat2016highly,caucheteur2015review}.
+Nowadays, in order to optimize such structures, artificial neural networks (ANN) and other machine learning (ML) algorithms are being applied \cite{fornarelli2009neural,paper0,hameed2008accurate}.
+Although ANNs and ML have been applied to PCFs \cite{fornarelli2009neural,paper0} and SPR structures \cite{fu2018optimization,mcatee2019artificial} independently, to the best of our knowledge, there seems to have been no published papers that investigated the PCF based SPR structures with this well tested methods.
 
@@
 Another ANN method is employed in \cite{rodriguez2010efficient} to calculate chromatic dispersion of photonic crystal fiber.
-In \cite{mescia2011refinement}, authors employed a neural network for the refinement and design of Erbium doped photonic crystal fiber.
+In Ref.
+\cite{mescia2011refinement}, authors employed a neural network for the refinement and design of Erbium doped photonic crystal fiber.
 Results showed that conventional methods consume large amount of time compared to the runtime of the neural network.
@@
 
-\section{Proposed method}
+\section{Network Architecture}
 \label{sec:prop}
@@
 At the start of the training, a GAN is trained to generate additional data by using training samples.
-These generated samples are filtered to ensure they fall within the applicable range.
-Original training samples and generated samples are joined to train a fully-connected feed-forward multi-layer perceptron (MLP) neural network for the regression ask of estimating confinement loss.
-At the end of the training, the ANN will be used to decide the containment loss of a previously unseen set of input parameters.
-This architecture is illustrated in Figure \ref{fig:overall}.
+These generated samples are filtered to ensure the range of application.
+Original training samples and generated samples are joined to train a fully-connected feedforward multi-layer perceptron (MLP) neural network.
+This satisfies the regression need for estimating the confinement loss.
+At the end of the training, the ANN will be used to decide the confinement loss of a previously unexperienced set of input parameters.
+The illustration of the proposed architecture is presented in  Figure \ref{fig:overall}.
 The details of the proposed GAN and ANN architecture is discussed in the following subsections.
@@
 
-Generative adversarial networks are introduced in \cite{goodfellow2014generative}.
-We have employed GAN to augment the number of samples that are used in training.
+In our study, GAN is employed to augment the number of samples that are used in training  \cite{goodfellow2014generative}.
 A GAN is composed of two neural networks: generator and discriminator.
@@
 The discriminator assesses the performance of the generator and provides feedback for training.
-Instead of directly training generator, it is trained through this feedback.
+Instead of using the direct training generator, it is trained through this feedback.
 This paradigm avoids over-fitting the data.
 
-It is possible to use different metrics for training a GAN \cite{goodfellow2014generative, mao2017least, lucic2018gans}; for this project we have selected Wasserstein distance metric called as WGAN.
-This variant is proposed by Arjovsky et al in \cite{arjovsky2017wasserstein}.
+The GAN can be trained by diverse metrics  \cite{goodfellow2014generative, mao2017least, lucic2018gans}].
+In this work Wasserstein distance metric (WGAN) is selected \cite{arjovsky2017wasserstein}.
 In this system, discriminator is named as critic and it measures the distance between the generated  and the real data.
@@
 In a regular GAN system, training is stopped when the generated data is deemed viable by an observer.
-Since GAN is often used in generation of image, video or audio, using a human in the loop is effective.
-However, in our problem, it is not viable for a human to judge the generated data.
-Automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which in turn degrades the performance.
-WGAN uses an adaptive stopping criteria that does not have the issue mentioned above.
-Additionally, we have selected to incorporate Gradient penalty to improve WGAN as proposed in \cite{gulrajani2017improved}.
-This improved WGAN system converges in a stable manner without having to fine tune hyper-parameters of the system.
-The flowchart of this system is given in Figure \ref{fig:gan}.
+Since GAN is frequently used in image, video or audio generation, where human is used effectively in the loop.
+In our case, it is not viable for a human to judge the generated data, therefore, automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which may degrade the performance.
+On the other hand, WGAN uses an adaptive stopping criteria that can easily overcome the aforementioned disadvantages.
+Additionally, Gradient penalty is incorporated to improve the WGAN as described in \cite{gulrajani2017improved}.
+This proposed enhanced WGAN system converges in a stable manner without requiring further fine tuning the hyper-parameters of the system.
+The flowchart of this proposed system is illustrated in Figure  \ref{fig:gan}.
 
@@
 In our SPR system, we have 7 input parameters and a single output parameter, making a total of 8 parameters that will be used in the GAN phase.
-In Section \ref{sec:exp}, we have experimented using a different PCF system with different inputs, resulting a different number of parameters for the system.
-The generator is supplied with the same number of parameters as its expected output, that is 8 for our dataset.
+In Section \ref{sec:exp}, various PCF structures are tested with different inputs, resulting a different number of system parameters.
+The generator is supplied with the same number of parameters.
 These parameters are generated using Gaussian noise and is called latent variable.
@@
 Hence, it is important to sample the generated data in way to prevent performance degradation \cite{bhattarai2019sampling}.
-In the proposed system, we have included a filtering step for the generated data.
-This step uses a simple condition to discard the values that fall out of the desired range, for both the independent variables ($n_{analyte}, \lambda, \Lambda, d1, d2, d3, n_c$), and the confinement loss.
+In our proposed system, we have included a filtering step for the generated data.
+This step uses a simple condition to discard the values that fall out of the desired range of both the independent variables  ($n_{analyte}, \lambda, \Lambda, d1, d2, d3, n_c$), and the confinement loss.
 Once the training phase is complete, the generator and the filter is used to augment the number of training samples that are available for ANN to train on.
@@
 In addition, we use Batch Normalization algorithm \cite{ioffe2015batch} to accelerate training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.
-In the proposed system, the ANN is trained using the training samples from the original dataset and the augmented samples generated by the GAN phase.
+Also, the ANN is trained using the training samples from the original dataset and the augmented samples generated by the GAN phase.
 
 \section{Photonic crystal fiber design}
-\label{sec:pcf}
 
-\hl{to HA: This section has been written by two different people, should be merged!}
+In order to build the desired dataset, the numerical analysis of the proposed sensor structure is carried out with the commercial software package Comsol Multiphysics \cite{comsol_help}.
+The Full Vectorial Finite Element Method (FV-FEM) with the perfectly matched layers (PMLs) \cite{koshiba2002full,saitoh2001full} are employed.
 
-\hl{Aimen:}
-
-A labelled dataset of 432 samples was collected in this work, through simulations using FV-FEM.
-This dataset consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, and real part of the refractive index ($n_c$) taken as our independent variables.
-The labels are the confinement loss of the PCF.
-The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36)).
-
-\hl{We will fix the pattern and geometrical shape of the cladding air holes, and vary the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$.
-Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional neural networks.
-}
-
-\hl{AY:}
-
-The numerical investigation to build the SPR dataset have been simulated with Comsol Multiphysics software~\cite{comsol_help}, where  the Full Vectorial Finite Element Method (FV-FEM) with perfectly matched layers (PMLs)~\cite{koshiba2002full,saitoh2001full} are used for numerical analysis.
+The cross section of the proposed structure is illustrated in Figure 3.
+As can be seen from this figure, the sensor consists of analyte channel (sensing medium), plasmonic layer (Au) and various sized cladding air holes.
+The cladding region is formed by nineteen various sized air holes, sited on silica background with hexagonal lattice arrangement.
+The diameter of the air holes are set to;  $d_1$= $0.45 \mu m$, $d_2$= $0.75 \mu m$, $d_3$= $0.35 \mu m$, and  $d_c$= $0.15$.
+The distance between air holes ($\lambda$) are set to $2 \mu m$.
+Initially, trapping the light (fundamental mode) in to the core region is vital for mode quality.
+On the other hand, some amount of light needs to be leak towards the plasmonic layer, where the sensitivity measurement occurs.
+This is the key phenomenon for resonance phase matching occurrence.
+In this respect, the various sized cladding holes are employed for controlling the light guidance, where each set of air holes are effecting different propagation characteristic of the sensor.
+The Gold (Au) material is used as plasmonic layer and set to be$40 \mu m$.
+The Johnson and Christy Data \cite{johnson1972optical} are used the permittivity values.
+The Sellmeier Equation (Eq.(\ref{eqn1})) is used for calculating the refractive index of Silica material \cite{bjarklev2003PCF}.
 
@@
 \end{figure}
-
-The cross section of proposed PCF based SPR sensor has been shown in Figure~\ref{Figx}.
-As can be seen from this figure, the sensor consists of analyte channel (sensing medium), metallic layer(Au) and PCF sections.
-The PCF section consists of nineteen various sized air holes, placed on silica background with hexagonal arrangement.
-The diameter of air holes are initially set as; $d_1$ is $0.45 \mu m$, $d_2$ is $0.75 \mu m$ and $d_3$ is $0.35 \mu m$, and  $d_c$ is $0.15$.
-The distance between air holes ($\Lambda$) also initially  set to be $2 \mu m$.
-The aim of using different size air holes is, while trapping the light in the core region of PCF (fundamental mode), at the same time allow some amount of light to leak from the bridges between air holes toward the plasmonic layer.
-Which will match the surface plasmon waves propagating along the metallic surface.
-Gold (Au) used as plasmonic layer and set to be $40 nm$, where Johnson and Christy Data~\cite{johnson1972optical} used for its permittivity.
-The Sellmeier Equation (Eq.(\ref{eqn1})) is used for calculating the refractive index of Silica  \cite{bjarklev2003PCF}.
 
@@
 
-The aim of SPR based sensor are sensing the RI changes at the resonance conditions.
-The resonace condition is the phase matching between SPWs propagating along metal layer (Au) and the fundamental mode of ligt that is propagating along the PCF core.
-At that specific time the confinement loss is reaches the highest peak point.
-Therefore, in SPR based PCF sensors the key parameter is the confinement loss and it is so important to precisely calculate the confinement losses.
-The Equation~\ref{eqn2} is used in this study for that purpose~\cite{yasli2019effect}.
+As mentioned in the introductory part, during the resonance phase matching condition, the confinement losses are reaching the highest rate.
+Therefore, precise calculation of the confinement losses are critical.
+The Equation~\ref{eqn2} is used in this study for that purpose \cite{yasli2019effect}.
 
@@
 where the imaginary part of the effective RI shown with Im($n_{eff}$).
+
+A labelled dataset of 432 samples was provided by FV-FEM numerical analysis.
+Our dataset contains a number of independent variables such as the operating wavelength $\lambda$, analyte index $n_{analyte}$, hole to hole distance $\Lambda$, the air holes sizes ($d_1$, $d_2$ and $d_3$), and the real part of the refractive index ($n_c$).
+The labels are specified as the confinement loss of the sensor structure.
+The set consists of nine different configurations of the geometric properties ($\Lambda$, $d_1$, $d_2$, $d_3$), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36)).
+
+The optimizing and refinement of these above parameters are extremely time-consuming and requires considerable computational time.
+In order to optimize the structural design parameters and achieve the desired propagation features, we have fixed the geometry of the sensor structure (hexagonal arrangement with circular air holes) and vary the operating wavelength $\lambda$, index of refraction $n_{analyte}$, hole to hole spacing $\Lambda$, and the size of the cladding holes ($d_1$, $d_2$ and $d_3$).
+
+\hl {Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional Neural Networks.
+(Bu paragrafa cem baksin, sonuc kisminda kullanabiliriz)}
 
@@
 		\addplot[line width=1pt,solid,color=blue] %
-		table{../../loss_curves_3k/ann_tr_loss_3k_their_data_without.txt};
+		table{data/ann_tr_loss_3k_their_data_without.txt};
 		\end{axis}
@@
 		\addplot[line width=1pt,solid,color=blue] %
-		table{../../loss_curves_3k/ann_tr_loss_3k_their_data_with.txt};
+		table{data/ann_tr_loss_3k_their_data_with.txt};
 		\end{axis}
@@
 			] 
-			table{../../experiments_spr-pcf/Their_net/without_augmentation/kfold-predictions-vs-labels/5th/graph_data.txt};
+			table{data/spr_their_without_5.txt};
 			\addlegendentry{\cite{paper0}}
@@
 			] 
-			table{../../experiments_spr-pcf/Our_net/Without_augmentation/kfold-predictions-vs-labels/8th/graph_data.txt};
+			table{data/spr_our_without_8.txt};
 			\addlegendentry{$Proposed$}
@@
 		] 
-		table{../../expirrements_pcf2/Their_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
+		table{data/pcf_their_without_2.txt};
 		\addlegendentry{\cite{paper0}}
@@
 		] 
-		table{../../expirrements_pcf2/Our_net/without_augment/kfold-predictions-vs-labels/2nd/graph_data.txt};
+		table{data/pcf_our_without_2.txt};
 		\addlegendentry{$Proposed$}
@@
 			] 
-			table{../../experiments_spr-pcf/Our_net/Without_augmentation/kfold-predictions-vs-labels/3rd/graph_data.txt};
+			table{data/spr_our_without_3.txt};
 			\addlegendentry{Without GAN}
@@
 			]
-			table{../../experiments_spr-pcf/Our_net/with_augmentation/kfold-predictions-vs-labels/3rd/graph_data.txt};
+			table{data/spr_our_with_3.txt};
 			\addlegendentry{With GAN}
@@
 		] 
-		table{../../expirrements_pcf2/Our_net/without_augment/kfold-predictions-vs-labels/4th/graph_data.txt};
+		table{data/pcf_our_without_4.txt};
 		\addlegendentry{Without GAN}
@@
 		] 
-		table{../../expirrements_pcf2/Our_net/with_augment/kfold-predictions-vs-labels/4th/graph_data.txt};
+		table{data/pcf_our_with_4.txt};
 		\addlegendentry{With GAN}

### 2020-06-07 docs/paper/paper.tex
* Few fixes

@@
 At the start of the training, a GAN is trained to generate additional data by using training samples.
-These generated samples are filtered to ensure the range of application.
+These generated samples are filtered to ensure they fall within the numerical range of the application.
 Original training samples and generated samples are joined to train a fully-connected feedforward multi-layer perceptron (MLP) neural network.
 This satisfies the regression need for estimating the confinement loss.
-At the end of the training, the ANN will be used to decide the confinement loss of a previously unexperienced set of input parameters.
+At the end of the training, the ANN will be used to decide the confinement loss of a previously unseen set of input parameters.
 The illustration of the proposed architecture is presented in  Figure \ref{fig:overall}.
@@
 The discriminator assesses the performance of the generator and provides feedback for training.
-Instead of using the direct training generator, it is trained through this feedback.
+Instead of directly training the generator, it is trained through this feedback.
 This paradigm avoids over-fitting the data.
@@
 Since GAN is frequently used in image, video or audio generation, where human is used effectively in the loop.
-In our case, it is not viable for a human to judge the generated data, therefore, automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which may degrade the performance.
+In our case, it is not viable for a human to judge the generated data.
+Simply removing the human in-the-loop from GAN can lead to over or under-fitting, which may degrade the performance.
 On the other hand, WGAN uses an adaptive stopping criteria that can easily overcome the aforementioned disadvantages.
@@
 In addition, we use Batch Normalization algorithm \cite{ioffe2015batch} to accelerate training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.
-Also, the ANN is trained using the training samples from the original dataset and the augmented samples generated by the GAN phase.
+Finally, the ANN is trained using the training samples from the original dataset and the augmented samples generated by the GAN phase.
 
@@
 A labelled dataset of 432 samples was provided by FV-FEM numerical analysis.
-Our dataset contains a number of independent variables such as the operating wavelength $\lambda$, analyte index $n_{analyte}$, hole to hole distance $\Lambda$, the air holes sizes ($d_1$, $d_2$ and $d_3$), and the real part of the refractive index ($n_c$).
+Our dataset contains a number of independent variables, \hl{these are} the operating wavelength $\lambda$, analyte index $n_{analyte}$, hole to hole distance $\Lambda$, the air holes sizes ($d_1$, $d_2$ and $d_3$), and the real part of the refractive index ($n_c$).
 The labels are specified as the confinement loss of the sensor structure.
@@
 In order to optimize the structural design parameters and achieve the desired propagation features, we have fixed the geometry of the sensor structure (hexagonal arrangement with circular air holes) and vary the operating wavelength $\lambda$, index of refraction $n_{analyte}$, hole to hole spacing $\Lambda$, and the size of the cladding holes ($d_1$, $d_2$ and $d_3$).
-
-\hl {Then the results of this study can be carried to different types of SPR-based PCF sensors, using other suitable deep learning approaches such as Recurrent and Convolutional Neural Networks.
-(Bu paragrafa cem baksin, sonuc kisminda kullanabiliriz)}
 

### 2020-06-22 docs/paper/paper.tex
Second round of fixes

@@
 
-\title{\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}}
+\title{\hl{Generative adversarial neural networks
+		model of photonic crystal fiber based Surface Plasmon Resonance Sensor
+}}
 
@@
 Additionally, ANN can approximate any function proven by the Universality theorem  \cite{HORNIK1991251}.
-This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a photonic crystal fiber \cite{paper0}.
+This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures  \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a PCFs  \cite{paper0} and SPR structures \cite{fu2018optimization,mcatee2019artificial}.
 
-One of the most difficult challenges that deep learning models face is that they benefit from large amounts of data to train, which is often costly and/or difficult to acquire.
-One of the solutions to overcome this issue is to artificially expand the original training dataset by the means of generative networks.
-Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) \cite{goodfellow2014generative}, proved to be successful in data generation \cite{schlegl2017unsupervised, zheng2017unlabeled, frid2018synthetic, tanaka2019data, perez2017effectiveness}.
+One of the most difficult challenges that deep learning models are facing is that they benefit from large amounts of data to train, which is often costly and/or difficult to acquire.
+An alternative solution is to artificially expand the original training dataset by the means of generative networks.
+In this regard, Generative Adversarial Networks (GAN) introduced by Goodfellow et al  \cite{goodfellow2014generative}, has proven to be successful in data generation \cite{schlegl2017unsupervised, zheng2017unlabeled, frid2018synthetic, tanaka2019data, perez2017effectiveness}.
 
-In this paper, we focus on estimating confinement loss, one of the propagation features of multi-channel Photonic Crystal Fiber (PCF) sensors, using artificial neural networks.
-\hl{Specifically, we have based our system on Surface Plasmon Resonance (SPR)}.
-However, in the experiments section we have demonstrated that the designed system is generic enough to be applied to multiple PCF designs.
+In this work, we focus on estimating the confinement loss behaviour of multichannel PCF based SPR sensor by employing the artificial neural networks.
+Specifically, we have constructed our system on PCF based SPR model.
+However, in the experiments section we have demonstrated that the designed system is generic enough to be applied to multiple similar PCF based designs.
 The most important contribution of this research is the use of GAN phase, where the available data is expanded to be used in the training phase.
 
-One of the first works on using artificial neural networks in photonic crystal fibers (PCF) design is presented in \cite{hameed2008accurate}.
-The results demonstrated the accuracy of the network on a specific PCF design.
-Another ANN method is employed in \cite{rodriguez2010efficient} to calculate chromatic dispersion of photonic crystal fiber.
+To our knowledge, Ref.~\cite{hameed2008accurate} was the first work proposed ANN technique on PCF structures.
+The results demonstrated the accuracy of the network on a specific PCF structure.
+On the other hand, ANN method was employed for predicting the chromatic dispersion of conventional hexagonal lattice PCF structure  \cite{rodriguez2010efficient}.
 In Ref.
-\cite{mescia2011refinement}, authors employed a neural network for the refinement and design of Erbium doped photonic crystal fiber.
-Results showed that conventional methods consume large amount of time compared to the runtime of the neural network.
+\cite{mescia2011refinement}, authors employed a neural network for the refinement and design of Erbium doped PCF.
+Presented results have shown that conventional methods consume large amount of time compared to the runtime of the neural network.
 Perhaps the most rigorous experiments about neural network use in PCF design is presented in  \cite{paper0}.
-In this paper, a feed-forward multi-layer perceptron neural network is used to calculate multiple properties of a PCF design.
-The authors shown that the network can achieve both acceptable accuracy and superior speed compared to the existing numerical methods.
+In this work, a feed-forward multi-layer perceptron neural network is used to calculate multiple propagation features of a PCF design.
+It can be evidently seen that this proposed network can achieve both acceptable accuracy and superior speed compared to the existing numerical methods.
+On the other hand, genetic algorithm and ANN method have also been tested on SPR sensor structures \cite{fu2018optimization,mcatee2019artificial}.
+It can be seen that robust performances can be achieved with these methods.
 
-Authors in \cite{perez2017effectiveness} has explored the possibility of using GAN to boost neural networks, finding it is possible to improve the accuracy of existing image classifiers.
+The accuracy of existing image classifiers of the neural networks can be improved by using GAN  \cite{perez2017effectiveness}.
 Frid-Adar, et.
 al.
-\cite{frid2018synthetic} has applied the same method to improve the accuracy of liver lesion classification.
-The authors has found that balancing the training data using GAN has a higher improvement in accuracy compared to classical data generation strategies.
-Finally, in \cite{shin2018medical}, authors used the same technique to both augment and anonymize the training data with brain MRI with the similar success of the previous papers.
+\cite{frid2018synthetic} have applied the same method to improve the accuracy of liver lesion classification.
+It is found that balancing the training data with GAN has a higher improvement in accuracy compared to classical data generation strategies.
+The same technique was applied to augment and anonymize the training data of the brain MRI  \cite{shin2018medical}.
 
-\hl{Literature survey requires expansion related with SPR and PCF}
-
-This paper is organized as follows.
-Section \ref{sec:prop} details the use of GAN to generate additional training samples for ANN as well as the proposed neural network architecture.
-Photonic crystal fiber design that is used for testing is described in details in section \ref{sec:pcf}.
-Detailed analysis of the experimental results are discussed in section \ref{sec:exp}.
-Finally, concluding remarks are made in Section \ref{sec:conc}.
+This paper is organized as follows.This paper is organized as follows.
+The details of GAN procedure to generate additional training samples for ANN as well as the proposed neural network architecture is presented in Section \ref{sec:prop}.
+The design parameters and details of PCF based SPR structure is described in section \ref{sec:pcf}.
+Detailed analysis of the numerical results is discussed in section \ref{sec:exp}.
+Finally, concluding remarks are presented in Section \ref{sec:conc}.
 
@@
 
-In this section, details of the proposed method is discussed.
+In this section, details of the proposed method are discussed.
 Training of the system contains two phases: a GAN phase and regression training phase.
-At the start of the training, a GAN is trained to generate additional data by using training samples.
-These generated samples are filtered to ensure they fall within the numerical range of the application.
+At the beginning of the training, a GAN is trained to generate additional data by using training samples.
+These generated samples are filtered to ensure they are within the range of the original feature space.
 Original training samples and generated samples are joined to train a fully-connected feedforward multi-layer perceptron (MLP) neural network.
@@
 The illustration of the proposed architecture is presented in  Figure \ref{fig:overall}.
-The details of the proposed GAN and ANN architecture is discussed in the following subsections.
+The details of the proposed GAN and ANN architecture is discussed in the following sub-sections.
 
@@
 The GAN can be trained by diverse metrics \cite{goodfellow2014generative, mao2017least, lucic2018gans}].
-In this work Wasserstein distance metric (WGAN) is selected \cite{arjovsky2017wasserstein}.
-In this system, discriminator is named as critic and it measures the distance between the generated  and the real data.
-The reason behind choosing WGAN over other methods is to be able to determine a stopping criteria.
+In this work Wasserstein distance metric (WGAN) is selected \cite{arjovsky2017wasserstein}.In this system, discriminator is named as critic and it measures the distance between the generated and the real data.
+The distinguishing feature of the WGAN compared other methods is the ability to determine a stopping criteria.
 In a regular GAN system, training is stopped when the generated data is deemed viable by an observer.
@@
 In our case, it is not viable for a human to judge the generated data.
-Simply removing the human in-the-loop from GAN can lead to over or under-fitting, which may degrade the performance.
+In an ordinary GAN system, removing human in-the-loop can lead to over or under-fitting, which may degrade the performance.
 On the other hand, WGAN uses an adaptive stopping criteria that can easily overcome the aforementioned disadvantages.
@@
 
-In this work, both the Critic and the generator are fully connected feed forward MLP models.
+In this work, both the critic and the generator are fully-connected feed-forward MLP models.
 The details of the networks are given in Table  \ref{tbl:anndetails}.
-The output from this system should be input and output pairs that will be used to train ANN part of the system.
-In our SPR system, we have 7 input parameters and a single output parameter, making a total of 8 parameters that will be used in the GAN phase.
+The output of the system would be input and output pairs that are used to train ANN part of the system.
+In our sensor structure, we have 7 input parameters and a single output parameter, making a total of 8 that will be used in the GAN phase.
 In Section  \ref{sec:exp}, various PCF structures are tested with different inputs, resulting a different number of system parameters.
@@
 This step uses a simple condition to discard the values that fall out of the desired range of both the independent variables  ($n_{analyte}, \lambda, \Lambda, d1, d2, d3, n_c$), and the confinement loss.
-Once the training phase is complete, the generator and the filter is used to augment the number of training samples that are available for ANN to train on.
+Once the training phase is completed, the generator and the filter is used to augment the number of training samples that are available for ANN to train on.
 
@@
 
-The ANN model employed in this research is a fully-connected feed-forward Multi Layer Perceptron network consists of an input layer, an output layer, and 5 hidden layers.
-The ANN is designed and trained to estimate containment loss in a regression configuration.
-We have applied $log_{10}$ to confinement loss in order to keep its numeric stability across a wide range \cite{paper0}.
+The ANN model employed in this work is a fully connected feed-forward MLP network consists of an input layer, an output layer, and 5 hidden layers.
+The ANN is designed and trained to estimate the confinement loss in a regression configuration.
+We have applied  $log_{10}$ to confinement loss calculation in order to keep its numeric stability across a wide range \cite{paper0}.
 Each hidden layer contains 50 neurons and uses Rectified Linear Unit (ReLU) activation function.
@@
 We have adopted Adam \cite{kingma2014adam} as the optimizer and mean squared error (MSE) as the loss/cost function.
-In addition, we use Batch Normalization algorithm \cite{ioffe2015batch} to accelerate training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.
-Finally, the ANN is trained using the training samples from the original dataset and the augmented samples generated by the GAN phase.
+In addition, Batch Normalization algorithm \cite{ioffe2015batch} is employed to accelerate the training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.
+Also, the ANN is trained using the training samples from the original dataset and the augmented samples generated by the GAN phase.
 
 \section{Photonic crystal fiber design}
+\label{sec:pcf}
 

### 2020-07-24 docs/paper/paper.tex
Incoming changes from HA

@@
 
-\title{\hl{Generative adversarial neural networks
-		model of photonic crystal fiber based Surface Plasmon Resonance Sensor
+\title{\hl{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor
 }}
@@
 Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches.
-However, the potential number of combinations possible for a single application is very large.
+However, the potential number of design combinations and flexible propagation features are offering a wide range of application areas.
 This issue combined by the speed of the commonly used Full Vectorial Finite Element Method (FV-FEM) simulators causes the task to take significant amount of time.
-As stated in the previous works, artificial neural networks (ANN) can predict the result of numerical simulations much faster.
+As stated in the previous works, artificial neural networks (ANN) can be employed to predict the result of numerical simulations much faster.
 However, there are two issues with the methods proposed previously: the required number of samples for training and the generality of these methods.
 In this paper, we propose the use of generative adversarial networks (GAN) to augment the real dataset to train an ANN model.
-Experimental analysis suggest that the proposed combination not only accurately predicts the confinement loss even with limited amount of data but also GAN can be used to improve existing methods in the literature.
-Finally, it is shown that this system can predict the confinement loss over a range of analytes and wavelengths in a completely new geometric configuration and generic enough not to require any additional tuning when used in a new dataset.
+The experimental analysis suggested that the proposed combination not only accurately predicts the confinement loss even with limited amount of data but also GAN can be used to improve existing methods in the literature.
+Moreover, proposed system can also predict the confinement loss over a range of analytes and wavelengths in a completely new geometric configuration and generic enough not to require any additional tuning when used in a new dataset.
 \end{abstract}
@@
 In the last decade, PCF based structures extensively employed as sensing devices.
-Possibility of filling the cladding holes with gas and liquid analytes makes them favourable in both chemical and biological sensing applications \cite{wang2011selectively,rifat2016highly,caucheteur2015review,dash2014spr}.
+Possibility of filling the cladding holes with gas and liquid analytes makes them favorable in both chemical and biological sensing applications  \cite{wang2011selectively,rifat2016highly,caucheteur2015review,dash2014spr}.
 Moreover, due to adaptable light guidance with possibilities of controlling the confinement loss and the chromatic dispersion at any operating wavelength are distinguishing features of PCF based structures in the literature.
 These charming propagation features can be achieved by employing, circular, cylindrical and even square and rectangular shaped \cite{wang2015simulation} air holes in the cladding and in the core region of the structures.
-Furthermore, the cladding pattern arrangements such as hexagonal, octagonal, decagonal square and circular \cite{wang2011selectively,bouk2004dispersion,ademgil2014highly,razzak2007chromatic}  can be engaged to achieve the desired features for preferred applications.
+Furthermore, the cladding pattern arrangements such as hexagonal, octagonal, decagonal, square and circular \cite{wang2011selectively,bouk2004dispersion,ademgil2014highly,razzak2007chromatic} can be engaged to achieve the desired features for preferred applications.
 The hole-to hole spacing (pitch) and the air hole sizes are critical parameters of tuning the aforementioned propagation characteristics.
@@
 Kretschamann Raether prism geometry is the fundamental construction principle of SPR based sensors  \cite{kretschmann1968radiative}.
-This geometry practises Snell's Total Internal Reflection rule, where still very small amount of light refracts from the metallic layer into the evanescent field.
+This geometry practices Snell’s Total Internal Reflection rule, where still very small amount of light refracts from the metallic layer into the evanescent field.
 The refracted photons are coupling with electron charge oscillations (plasmon) at the surface of metallic layer, which are known as surface plasmon waves (SPW).
-The maximum energy transfer from core mode to SPWs occurs with the effective index equalisation of this corresponding modes.
+The maximum energy transfer from core mode to SPWs occurs with the effective index equalization of this corresponding modes.
 This phenomenon is known as resonance phase matching, where losses are reaching the maximum levels.
@@
 In the past, structures that contains features such as multi-channel single analyte and multi-channel multi analyte have been investigated \cite{rifat2016highly,yasli2019effect,zhang2011wagon,yasli2019multi,azzam2016multichannel}.
-Aslo, the effects of various metallic layers such as Au, Ag \cite{yasli2019multi}, Ag- Graphene \cite{rifat2016highly}, Ta2TO5 \cite{otupiri2015multi}, ITO \cite{dash2014spr}, TiO2 \cite{rifat2016highly} with various design paraeters have also been investigated in detailed.
+Also, the effects of various metallic layers such as Au, Ag \cite{yasli2019multi}, Ag- Graphene \cite{rifat2016highly}, Ta2TO5 \cite{otupiri2015multi}, ITO \cite{dash2014spr}, TiO2 \cite{rifat2016highly} with various design parameters have also been investigated in detailed.
 Several design parameters such as plasmonic material, thickness of the layers, air hole size and positions are decisive on resonance matching wavelength of the SPR based structures.
 Optimizing and refinement of these parameters are extremely time consuming process with considerable computational time \cite{fornarelli2009neural,abdelaziz2012photonic,paper0}.
-In the past, genetic algorithms \cite{abdelaziz2012photonic,borel2004topology} method was used to optimize the structural design parameters to achieve better propagation features of photonic devices\cite{rifat2016highly,caucheteur2015review}.
+In the past, genetic algorithms \cite{abdelaziz2012photonic,borel2004topology} method was used to optimize the structural design parameters to achieve better propagation features of photonic devices \cite{rifat2016highly,caucheteur2015review}.
 Nowadays, in order to optimize such structures, artificial neural networks (ANN) and other machine learning (ML) algorithms are being applied \cite{fornarelli2009neural,paper0,hameed2008accurate}.
@@
 Additionally, ANN can approximate any function proven by the Universality theorem  \cite{HORNIK1991251}.
-This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures  \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nanocavities \cite{asano2018optimization}, and more recently, computing optical properties of a PCFs  \cite{paper0} and SPR structures \cite{fu2018optimization,mcatee2019artificial}.
+This fact propelled researchers to widen the applications of ANN even further, including the study of nano-photonic structures   \cite{kiarashinejad2020knowledge}, optimization of photonic crystal nano-cavities \cite{asano2018optimization}, and more recently, computing optical properties of a PCFs  \cite{paper0} and SPR structures \cite{fu2018optimization,mcatee2019artificial}.
 
@@
 
-In this work, we focus on estimating the confinement loss behaviour of multichannel PCF based SPR sensor by employing the artificial neural networks.
+In this work, we focused on estimating the confinement loss behavior of multichannel PCF based SPR sensor by employing the ANNs.
 Specifically, we have constructed our system on PCF based SPR model.
@@
 In Ref.
-\cite{mescia2011refinement}, authors employed a neural network for the refinement and design of Erbium doped PCF.
+\cite{mescia2011refinement},authors employed a neural network for the refinement and design of Erbium doped PCF.
 Presented results have shown that conventional methods consume large amount of time compared to the runtime of the neural network.
-Perhaps the most rigorous experiments about neural network use in PCF design is presented in  \cite{paper0}.
-In this work, a feed-forward multi-layer perceptron neural network is used to calculate multiple propagation features of a PCF design.
-It can be evidently seen that this proposed network can achieve both acceptable accuracy and superior speed compared to the existing numerical methods.
+Perhaps the most rigorous experiments about neural network use in PCF design is presented in  \cite{paper0}.In this work, a feed-forward multi-layer perceptron neural network is used to calculate multiple propagation features of a PCF design.
+It can be evidently seen that this proposed network can be achieved both acceptable accuracy and superior speed compared to the existing numerical methods.
 On the other hand, genetic algorithm and ANN method have also been tested on SPR sensor structures \cite{fu2018optimization,mcatee2019artificial}.
@@
 
-This paper is organized as follows.This paper is organized as follows.
-The details of GAN procedure to generate additional training samples for ANN as well as the proposed neural network architecture is presented in Section \ref{sec:prop}.
+This paper is organized as follows.The details of GAN procedure to generate additional training samples for ANN as well as the proposed neural network architecture is presented in Section \ref{sec:prop}.
 The design parameters and details of PCF based SPR structure is described in section \ref{sec:pcf}.
@@
 At the beginning of the training, a GAN is trained to generate additional data by using training samples.
-These generated samples are filtered to ensure they are within the range of the original feature space.
+These generated samples are filtered to ensure the range of application.
 Original training samples and generated samples are joined to train a fully-connected feedforward multi-layer perceptron (MLP) neural network.
 This satisfies the regression need for estimating the confinement loss.
-At the end of the training, the ANN will be used to decide the confinement loss of a previously unseen set of input parameters.
+At the end of the training, the ANN will be used to decide the confinement loss of a previously unexperienced set of input parameters.
 The illustration of the proposed architecture is presented in Figure \ref{fig:overall}.
@@
 A GAN is composed of two neural networks: generator and discriminator.
-The aim of the generator is to transform fully randomized data into data that follows the distribution of the original dataset.
+The aim of the generator is to transform fully randomized data into form that follows the distribution of the original dataset.
 The discriminator assesses the performance of the generator and provides feedback for training.
-Instead of directly training the generator, it is trained through this feedback.
+Instead of using the direct training generator, it is trained through this feedback.
 This paradigm avoids over-fitting the data.
@@
 The GAN can be trained by diverse metrics \cite{goodfellow2014generative, mao2017least, lucic2018gans}].
-In this work Wasserstein distance metric (WGAN) is selected \cite{arjovsky2017wasserstein}.In this system, discriminator is named as critic and it measures the distance between the generated and the real data.
+In this work Wasserstein distance metric (WGAN) is employed \cite{arjovsky2017wasserstein}.
+In this system, discriminator is named as critic and it measures the distance between the generated and the real data.
 The distinguishing feature of the WGAN compared other methods is the ability to determine a stopping criteria.
 In a regular GAN system, training is stopped when the generated data is deemed viable by an observer.
-Since GAN is frequently used in image, video or audio generation, where human is used effectively in the loop.
-In our case, it is not viable for a human to judge the generated data.
-In an ordinary GAN system, removing human in-the-loop can lead to over or under-fitting, which may degrade the performance.
+GAN is frequently used in image, video or audio generation, where human is used effectively in the loop.
+In our case, it is not viable for a human to judge the generated data, therefore, automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which may degrade the performance.
 On the other hand, WGAN uses an adaptive stopping criteria that can easily overcome the aforementioned disadvantages.
@@
 
-In this work, both the critic and the generator are fully-connected feed-forward MLP models.
-The details of the networks are given in Table  \ref{tbl:anndetails}.
+In our work, both the critic and the generator are fully connected to feed forward MLP models.
+The detailed parameters of the networks are given in Table  \ref{tbl:anndetails}.
 The output of the system would be input and output pairs that are used to train ANN part of the system.
-In our sensor structure, we have 7 input parameters and a single output parameter, making a total of 8 that will be used in the GAN phase.
+In our proposed model, we have 7 input parameters and a single output parameter, making a total of 8 that will be used in the GAN phase.
 In Section  \ref{sec:exp}, various PCF structures are tested with different inputs, resulting a different number of system parameters.
@@
 Previous works \cite{ravuri2019seeing, shmelkov2018good}, demonstrated that it is possible for random data augmentation to weaken the performance of the model.
-Hence, it is important to sample the generated data in way to prevent performance degradation  \cite{bhattarai2019sampling}.
+Hence, it is important to sample the generated data in a way to prevent performance degradation  \cite{bhattarai2019sampling}.
 In our proposed system, we have included a filtering step for the generated data.
@@
 In contrast to full-batch training, mini-batch training allows more frequent gradient calculations, improving the stability and reliability of the training \cite{masters2018revisiting, keskar2016large}.
-The downside of using mini-batches are added computational complexity during training.
+The weakness of using mini-batches are added computational complexity during training.
 However, it has no adverse effect on the testing phase.
 
-We have adopted Adam \cite{kingma2014adam} as the optimizer and mean squared error (MSE) as the loss/cost function.
+We have adopted Adam \cite{kingma2014adam}as the optimizer and mean squared error (MSE) as the loss/cost function.
 In addition, Batch Normalization algorithm \cite{ioffe2015batch} is employed to accelerate the training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.
@@
 The cross section of the proposed structure is illustrated in Figure 3.
-As can be seen from this figure, the sensor consists of analyte channel (sensing medium), plasmonic layer (Au) and various sized cladding air holes.
+As can be seen from this figure, the sensor consists of analyte channel (sensing medium), plasmonic layer (Au)and various sized cladding air holes.
 The cladding region is formed by nineteen various sized air holes, sited on silica background with hexagonal lattice arrangement.
-The diameter of the air holes are set to;  $d_1$= $0.45 \mu m$, $d_2$= $0.75 \mu m$, $d_3$= $0.35 \mu m$, and  $d_c$= $0.15$.
-The distance between air holes ($\lambda$) are set to $2 \mu m$.
+The air hole diameters are set to;  $d_1$= $0.45 \mu m$, $d_2$= $0.75 \mu m$, $d_3$= $0.35 \mu m$, and  $d_c$= $0.15$.
+The distance between air holes ($\lambda$) are fixed to $2 \mu m$.
 Initially, trapping the light (fundamental mode) in to the core region is vital for mode quality.
@@
 In this respect, the various sized cladding holes are employed for controlling the light guidance, where each set of air holes are effecting different propagation characteristic of the sensor.
-The Gold (Au) material is used as plasmonic layer and set to be$40 \mu m$.
+The Gold (Au) material is used as plasmonic layer and set to be $40 \mu m$.
 The Johnson and Christy Data \cite{johnson1972optical} are used the permittivity values.
@@
 Therefore, precise calculation of the confinement losses are critical.
-The Equation~\ref{eqn2} is used in this study for that purpose \cite{yasli2019effect}.
+The Equation \ref{eqn2} is used in this study for that purpose \cite{yasli2019effect}.
 
@@
 
-A labelled dataset of 432 samples was provided by FV-FEM numerical analysis.
-Our dataset contains a number of independent variables, \hl{these are} the operating wavelength $\lambda$, analyte index $n_{analyte}$, hole to hole distance $\Lambda$, the air holes sizes ($d_1$, $d_2$ and $d_3$), and the real part of the refractive index ($n_c$).
+A labelled dataset of 432 samples was provided by FVFEM numerical analysis.
+Our dataset contains a number of independent variables, such as the operating wavelength  $\lambda$, analyte index $n_{analyte}$, hole to hole distance $\Lambda$, the air holes sizes ($d_1$, $d_2$ and $d_3$), and the real part of the refractive index ($n_c$).
 The labels are specified as the confinement loss of the sensor structure.
@@
 Details of this dataset is explained in Section \ref{sec:pcf} and it is referred as SPR dataset.
-Having nine configurations, we have performed 9-fold testing on this dataset.
+We have performed 9-fold testing on this dataset, where nine configurations are existing.
 Each fold tests a single configuration using the other configurations as training data.
-Slicing the data this way allowed us to guide the network to predict the loss on a configuration that has not used in training.
-Please note that we have applied $log_{10}$ to confinement loss to scale it.
+Slicing the data allows us to guide the network to predict the loss on a configuration that has not been used in training.
+Please note that we have applied $log_{10}$ to confinement loss for scaling.
 
-We have used mean square error (MSE) in the comparisons.
-All algorithms are implemented using TensorFlow with Keras library in Python and experiments are performed on laptop with Intel i7-5600 CPU and 8GB of RAM.
+Also, mean square error (MSE) is used for the comparisons.
+All algorithms are implemented using TensorFlow with Keras library in Python and experiments are performed on device with Intel i7-5600 CPU and 8GB of RAM.
 TensorFlow library is set to use only CPU for the experiments.
@@
 We have only used confinement loss as the output.
-This dataset is referred as \dszero.
+This dataset is referred as PCF.
 Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}.
@@
 According to this experiment, training our ANN architecture more than 2500 epochs does not yield to any improvement.
-Therefore, we have set the training epoch limit to 2500 in all subsequent experiments.
-However, this number depends on the dataset and at times additional training can improve the result.
+Therefore, the training epoch limit is set to 2500 in all subsequent experiments.
+However, this number depends on the dataset and additional training may improve the results.
 Additionally, the benefit of augmented samples from the GAN phase is evident even at the training as they reduce the oscillations in the training loss.
@@
 Results of this experiment is demonstrated in Figure \ref{chart:perfnoaug}.
-In the experiment using SPR dataset, ANN models are predicting a new configuration and the number of samples available for training is lower.
-Therefore, they both have higher error rate compared to the \dszero{} dataset.
+In SPR dataset experiment, ANN models are predicting a new configuration and the number of samples available for training is lower.
+Therefore, they both have higher error rate compared to the PCF dataset.
 According to Figure \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength.
-This can be caused by the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}.
+This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}.
 Regardless of this, both models have similar MSE due to the shift in the curve fit.
-This shift is caused because the network is never exposed to this particular geometric configuration.
+Since the network is never exposed to this particular geometric configuration shift in the curve fit occurs.
 
@@
 The final set of experiments shows the stability that GAN phase adds.
-In Table \ref{tbl:all}, we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing.
+In Table \ref{tbl:all},we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing.
 It is clear that the GAN phase not only improves the average case but significantly improves the worst case while reducing the deviation, which is important in a live setting.
-Even in a dataset with enough examples to train the network (\dszero), using GAN phase reduces the worst case error by 32\%.
+Even in a dataset with enough examples to train the network (PCF), using GAN phase reduces the worst case error by  32\%.
 This added stability can also be observed in Figure \ref{chart:trainingmse}, where the training loss has less fluctuations when the data augmentation is employed.
@@
 
-In this paper, we have demonstrated that the use of generative adversarial networks can benefit neural networks that are designed to compute photonic crystal fiber optical properties.
+In this paper, we have demonstrated that the use of generative adversarial networks can be beneficial to neural networks that are designed to compute propagation characteristics of PCF devices.
 Additionally, we have also proposed and demonstrated a neural network that is both more generic and more accurate to estimate the confinement loss compared to the state-of-the-art network.
 The GAN phase also reduces the required samples to fully train the ANN, reducing the work necessary to employ the proposed system.
-The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research; in the experiments, it surpassed the accuracy of the method proposed in \cite{paper0} on the dataset this method is optimized on.
+The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research article.
+In our experiments, due to optimized dataset the accuracy of the method proposed in Ref.
+\cite{paper0} is also improved.
 
-Another important aspect in this paper is the experiments performed on a dataset that is designed to test the ability of artificial neural networks to estimate the properties of a new configuration.
+Another important aspect in this work is the experiments performed on a dataset that is designed to test the ability of artificial neural networks to estimate the properties of a new configuration.
 For this purpose, we have built a database based on Surface Plasmon Resonance with varying geometric configurations.
-During the testing, a new configuration that is not used for the training is used.
+During the testing, a new configuration that is not used for the training is employed.
 The proposed ANN, augmented with GAN phase is shown to estimate the new configuration to an acceptable error rate.
 
-The most important benefit of using machine learning methods instead of simulation is the speed factor.
+The most vital advantage of using machine learning methods instead of numerical simulation is the speed factor.
 In the experiments it is shown that the machine learning methods work few orders of magnitude faster than the simulation method.

### 2020-07-24 docs/paper/paper.tex
Languages fixes

@@
 Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches.
-However, the potential number of design combinations and flexible propagation features are offering a wide range of application areas.
-This issue combined by the speed of the commonly used Full Vectorial Finite Element Method (FV-FEM) simulators causes the task to take significant amount of time.
+However, the potential number of design combinations and flexible propagation features are offering a wide range of application areas, resulting in an exponential increase in the search space.
+This issue combined with the speed of the commonly used Full Vectorial Finite Element Method (FV-FEM) simulators causes the task to take a significant amount of time.
 As stated in the previous works, artificial neural networks (ANN) can be employed to predict the result of numerical simulations much faster.
@@
 In this paper, we propose the use of generative adversarial networks (GAN) to augment the real dataset to train an ANN model.
-The experimental analysis suggested that the proposed combination not only accurately predicts the confinement loss even with limited amount of data but also GAN can be used to improve existing methods in the literature.
-Moreover, proposed system can also predict the confinement loss over a range of analytes and wavelengths in a completely new geometric configuration and generic enough not to require any additional tuning when used in a new dataset.
+The experimental analysis suggested that the proposed combination not only accurately predicts the confinement loss even with limited amounts of data but also GAN can be used to improve existing methods in the literature.
+Moreover, the proposed system can also predict the confinement loss over a range of analytes and wavelengths in a completely new geometric configuration and generic enough not to require any additional tuning when used in a new dataset.
+This property is demonstrated by experimenting on an existing PCF dataset, which the proposed system surpassed the accuracy of the method proposed for it.
 \end{abstract}
@@
 \section{Introduction}
-
 Due to their unique propagation features, Photonic Crystal Fibers (PCFs) have been integrated into a number of optical based devices and applications.
@@
 
-In the last decade, PCF based structures extensively employed as sensing devices.
+In the last decade, PCF based structures are extensively employed as sensing devices.
 Possibility of filling the cladding holes with gas and liquid analytes makes them favorable in both chemical and biological sensing applications  \cite{wang2011selectively,rifat2016highly,caucheteur2015review,dash2014spr}.
@@
 Kretschamann Raether prism geometry is the fundamental construction principle of SPR based sensors  \cite{kretschmann1968radiative}.
-This geometry practices Snell’s Total Internal Reflection rule, where still very small amount of light refracts from the metallic layer into the evanescent field.
-The refracted photons are coupling with electron charge oscillations (plasmon) at the surface of metallic layer, which are known as surface plasmon waves (SPW).
-The maximum energy transfer from core mode to SPWs occurs with the effective index equalization of this corresponding modes.
+This geometry practices Snell’s Total Internal Reflection rule, where still a very small amount of light refracts from the metallic layer into the evanescent field.
+The refracted photons are coupling with electron charge oscillations (plasmon) at the surface of the metallic layer, which are known as surface plasmon waves (SPW).
+The maximum energy transfer from core mode to SPWs occurs with the effective index equalization of these corresponding modes.
 This phenomenon is known as resonance phase matching, where losses are reaching the maximum levels.
@@
 These possible variations are the main parameters for sensitivity calculations.
-The deep research on SPR based sensors have shown that Kretschmann Raether’s prism geometry fails satisfying the remote sensing and miniaturization requirements of critical detecting applications.
-One of the most common solution of overcoming these limitations are replacing the prism with the core of an optical fiber.
-Considering the recent technological developments, PCF are offering tremendous amount of design flexibility with the possibilities of complete control of light guidance.
+The deep research on SPR based sensors have shown that Kretschmann Raether’s prism geometry fails to satisfy the remote sensing and miniaturization requirements of critical detecting applications.
+One of the most common solutions of overcoming these limitations is replacing the prism with the core of an optical fiber.
+Considering the recent technological developments, PCF are offering a tremendous amount of design flexibility with the possibilities of complete control of light guidance.
 Hence, SPR technique can be integrated to this unique microstructured fibers for developing comprehensive multi-purpose sensor \cite{rifat2016highly,yasli2019effect}.
-Following the exclusive study by Hassani and Skorobogatiy \cite{hassani2006design}, number of structures have reported the merits of PCF based SPR sensors.
+Following the exclusive study by Hassani and Skorobogatiy \cite{hassani2006design}, a number of structures have reported the merits of PCF based SPR sensors.
 In the past, structures that contains features such as multi-channel single analyte and multi-channel multi analyte have been investigated \cite{rifat2016highly,yasli2019effect,zhang2011wagon,yasli2019multi,azzam2016multichannel}.
@@
 Several design parameters such as plasmonic material, thickness of the layers, air hole size and positions are decisive on resonance matching wavelength of the SPR based structures.
-Optimizing and refinement of these parameters are extremely time consuming process with considerable computational time \cite{fornarelli2009neural,abdelaziz2012photonic,paper0}.
+Optimizing and refinement of these parameters is an extremely time consuming process with considerable computational time \cite{fornarelli2009neural,abdelaziz2012photonic,paper0}.
 In the past, genetic algorithms \cite{abdelaziz2012photonic,borel2004topology} method was used to optimize the structural design parameters to achieve better propagation features of photonic devices \cite{rifat2016highly,caucheteur2015review}.
@@
 
-In this work, we focused on estimating the confinement loss behavior of multichannel PCF based SPR sensor by employing the ANNs.
-Specifically, we have constructed our system on PCF based SPR model.
+In this work, we focused on estimating the confinement loss behavior of multichannel PCF based SPR sensors by employing the ANNs.
+Specifically, we have constructed our system on a PCF based SPR model.
 However, in the experiments section we have demonstrated that the designed system is generic enough to be applied to multiple similar PCF based designs.
-The most important contribution of this research is the use of GAN phase, where the available data is expanded to be used in the training phase.
+The most important contribution of this research is the use of the GAN phase, where the available data is expanded to be used in the training phase.
 
@@
 \cite{mescia2011refinement},authors employed a neural network for the refinement and design of Erbium doped PCF.
-Presented results have shown that conventional methods consume large amount of time compared to the runtime of the neural network.
+Presented results have shown that conventional methods consume large amounts of time compared to the runtime of the neural network.
 Perhaps the most rigorous experiments about neural network use in PCF design is presented in  \cite{paper0}.In this work, a feed-forward multi-layer perceptron neural network is used to calculate multiple propagation features of a PCF design.
-It can be evidently seen that this proposed network can be achieved both acceptable accuracy and superior speed compared to the existing numerical methods.
-On the other hand, genetic algorithm and ANN method have also been tested on SPR sensor structures \cite{fu2018optimization,mcatee2019artificial}.
-It can be seen that robust performances can be achieved with these methods.
+It can be seen that this proposed network can achieve both acceptable accuracy and superior speed compared to the existing numerical methods.
+On the other hand, genetic algorithms and ANN methods have also been tested on SPR sensor structures \cite{fu2018optimization,mcatee2019artificial}.
+These methods also deliver robust performances.
 
@@
 At the beginning of the training, a GAN is trained to generate additional data by using training samples.
-These generated samples are filtered to ensure the range of application.
+These generated samples are filtered to ensure they are within the numeric range of application.
 Original training samples and generated samples are joined to train a fully-connected feedforward multi-layer perceptron (MLP) neural network.
 This satisfies the regression need for estimating the confinement loss.
-At the end of the training, the ANN will be used to decide the confinement loss of a previously unexperienced set of input parameters.
+At the end of the training, the ANN will be used to decide the confinement loss of a previously unseen set of input parameters.
 The illustration of the proposed architecture is presented in Figure \ref{fig:overall}.
@@
 \label{ssec:gan}
-
 In our study, GAN is employed to augment the number of samples that are used in training  \cite{goodfellow2014generative}.
@@
 The discriminator assesses the performance of the generator and provides feedback for training.
-Instead of using the direct training generator, it is trained through this feedback.
-This paradigm avoids over-fitting the data.
+Instead of directly training the generator, it is trained through this feedback.
+This paradigm avoids overfitting the data.
 
@@
 In this system, discriminator is named as critic and it measures the distance between the generated and the real data.
-The distinguishing feature of the WGAN compared other methods is the ability to determine a stopping criteria.
+The distinguishing feature of the WGAN compared to other methods is the ability to determine a stopping criteria.
 In a regular GAN system, training is stopped when the generated data is deemed viable by an observer.
@@
 In our proposed model, we have 7 input parameters and a single output parameter, making a total of 8 that will be used in the GAN phase.
-In Section  \ref{sec:exp}, various PCF structures are tested with different inputs, resulting a different number of system parameters.
+In Section  \ref{sec:exp}, various PCF structures are tested with different inputs, resulting in a different number of system parameters.
 The generator is supplied with the same number of parameters.
-These parameters are generated using Gaussian noise and is called latent variable.
+These parameters are generated using Gaussian noise and this input is called latent variable.
 
@@
 
-The ANN model employed in this work is a fully connected feed-forward MLP network consists of an input layer, an output layer, and 5 hidden layers.
+The ANN model employed in this work is a fully connected feed-forward MLP network consisting of an input layer, an output layer, and 5 hidden layers.
 The ANN is designed and trained to estimate the confinement loss in a regression configuration.
@@
 In contrast to full-batch training, mini-batch training allows more frequent gradient calculations, improving the stability and reliability of the training \cite{masters2018revisiting, keskar2016large}.
-The weakness of using mini-batches are added computational complexity during training.
+The weakness of using mini-batches is added computational complexity during training.
 However, it has no adverse effect on the testing phase.
@@
 The cross section of the proposed structure is illustrated in Figure 3.
-As can be seen from this figure, the sensor consists of analyte channel (sensing medium), plasmonic layer (Au)and various sized cladding air holes.
+As can be seen from this figure, the sensor consists of an analyte channel (sensing medium), plasmonic layer (Au)and various sized cladding air holes.
 The cladding region is formed by nineteen various sized air holes, sited on silica background with hexagonal lattice arrangement.
@@
 The distance between air holes ($\lambda$) are fixed to $2 \mu m$.
-Initially, trapping the light (fundamental mode) in to the core region is vital for mode quality.
-On the other hand, some amount of light needs to be leak towards the plasmonic layer, where the sensitivity measurement occurs.
+Initially, trapping the light (fundamental mode) into the core region is vital for mode quality.
+On the other hand, some amount of light needs to be leaked towards the plasmonic layer, where the sensitivity measurement occurs.
 This is the key phenomenon for resonance phase matching occurrence.
-In this respect, the various sized cladding holes are employed for controlling the light guidance, where each set of air holes are effecting different propagation characteristic of the sensor.
-The Gold (Au) material is used as plasmonic layer and set to be $40 \mu m$.
-The Johnson and Christy Data \cite{johnson1972optical} are used the permittivity values.
+In this respect, the various sized cladding holes are employed for controlling the light guidance, where each set of air holes are affecting different propagation characteristics of the sensor.
+The Gold (Au) material is used as a plasmonic layer and set to be $40 \mu m$.
+The Johnson and Christy Data \cite{johnson1972optical} are used for the permittivity values.
 The Sellmeier Equation (Eq.(\ref{eqn1})) is used for calculating the refractive index of Silica material \cite{bjarklev2003PCF}.
@@
 \def\dszero{PCF}
-
 In order to prove the effectiveness of the proposed setup, we have performed multiple experiments over two datasets.
 We have built the first dataset that is used in the experiments.
-Details of this dataset is explained in Section \ref{sec:pcf} and it is referred as SPR dataset.
-We have performed 9-fold testing on this dataset, where nine configurations are existing.
+Details of this dataset is explained in Section \ref{sec:pcf} and it is referred to as SPR dataset.
+We have performed 9-fold testing on this dataset, due to having nine configurations.
 Each fold tests a single configuration using the other configurations as training data.
@@
 We have only used confinement loss as the output.
-This dataset is referred as PCF.
+This dataset is referred to as PCF.
 Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}.
@@
 In this set of experiments, we have analyzed the performance of the proposed ANN design.
-The first experiment involves in training loss over SPR dataset.
-In this experiment, we have trained ANN model for up to 3000 epochs and reported the training loss in Figure \ref{chart:trainingmse}.
-According to this experiment, training our ANN architecture more than 2500 epochs does not yield to any improvement.
+The first experiment involves training loss over the SPR dataset.
+In this experiment, we have trained the ANN model for up to 3000 epochs and reported the training loss in Figure \ref{chart:trainingmse}.
+According to this experiment, training our ANN architecture more than 2500 epochs does not yield any improvement.
 Therefore, the training epoch limit is set to 2500 in all subsequent experiments.
@@
 
-We have performed experiements comparing the proposed ANN architecture with the state-of-the-art method proposed in \cite{paper0}.
-Results of this experiment is demonstrated in Figure \ref{chart:perfnoaug}.
-In SPR dataset experiment, ANN models are predicting a new configuration and the number of samples available for training is lower.
-Therefore, they both have higher error rate compared to the PCF dataset.
+We have performed experiments comparing the proposed ANN architecture with the state-of-the-art method proposed in \cite{paper0}.
+Results of this experiment are demonstrated in Figure \ref{chart:perfnoaug}.
+In the SPR dataset experiment, ANN models are predicting a new configuration and the number of samples available for training is lower.
+Therefore, they both have higher error rates compared to the PCF dataset.
 According to Figure \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength.
@@
 
-The first set of experiments performed on GAN phase is the number of the augmented samples.
-In these experiments, we have augmented the proposed ANN system with varying number of samples.
+The first set of experiments performed on the GAN phase is the number of the augmented samples.
+In these experiments, we have augmented the proposed ANN system with a varying number of samples.
 According to these experiments we have reached the minimum MSE at 1000 samples.
@@
 An additional note to take away from this experiment is that the dataset with the limited number of samples has the highest improvement, which is demonstrated in a clearer fashion in Table \ref{tbl:all}.
-This difference is due the fact that the number of training samples in this dataset is insufficient to train the regressor network causing reduced performance.
+This difference is due to the fact that the number of training samples in this dataset is insufficient to train the regressor network causing reduced performance.
 
 In Figure \ref{chart:ganperf}c, prediction of new configuration with and without GAN phase is compared.
-In the case with $n_{analyte} = 1.33$, the network without GAN phase has failed to predict the curve correctly.
-Even though GAN boosted network has predicted the curve lower than it is, the peak is in the correct wavelength, which could help PCF designers to pin-point highest loss.
+In the case with $n_{analyte} = 1.33$, the network without the GAN phase has failed to predict the curve correctly.
+Even though the GAN boosted network has predicted the curve lower than it is, the peak is in the correct wavelength, which could help PCF designers to pin-point highest loss.
 
@@
 
-We have also applied GAN phase to the network architecture proposed in \cite{paper0}.
-In this experiment, GAN phase reduced the performance slightly.
+We have also applied the GAN phase to the network architecture proposed in \cite{paper0}.
+In this experiment, the GAN phase reduced the performance slightly.
 However, as we have discussed earlier, full batch training strategy is the cause of this due to increased number of samples.
-In fact, when we reduce the batch size down to 900 samples, GAN phase starts to improve the score of this architecture.
+In fact, when we reduce the batch size down to 900 samples, the GAN phase starts to improve the score of this architecture.
 
-The final set of experiments shows the stability that GAN phase adds.
+The final set of experiments shows the stability that the GAN phase adds.
 In Table \ref{tbl:all},we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing.
 It is clear that the GAN phase not only improves the average case but significantly improves the worst case while reducing the deviation, which is important in a live setting.
-Even in a dataset with enough examples to train the network (PCF), using GAN phase reduces the worst case error by  32\%.
+Even in a dataset with enough examples to train the network (PCF), using the GAN phase reduces the worst case error by  32\%.
 This added stability can also be observed in Figure \ref{chart:trainingmse}, where the training loss has less fluctuations when the data augmentation is employed.
@@
 Training time is total training time while testing is per sample.
-These tests are performed over SPR dataset.
+These tests are performed over the SPR dataset.
 Please note that the training time is considered offline time; i.e., it is the time that will only be used once, before the system is deployed.
@@
 The training time difference between ANN systems is caused by the increased depth in the proposed architecture as well as mini-batch training strategy.
-Training time is dominated by GAN phase; however, this phase does not add any overhead to the testing time.
-The testing time difference between two networks are caused by the depth of the neural network (5 hidden layers instead of 3).
+Training time is dominated by the GAN phase; however, this phase does not add any overhead to the testing time.
+The testing time difference between two networks is caused by the depth of the neural network (5 hidden layers instead of 3).
 
@@
 During the testing, a new configuration that is not used for the training is employed.
-The proposed ANN, augmented with GAN phase is shown to estimate the new configuration to an acceptable error rate.
+The proposed ANN, augmented with the GAN phase is shown to estimate the new configuration to an acceptable error rate.
 

### 2020-08-10 docs/paper/paper.tex
IEEE formatted

@@
 
-\title{\hl{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor
-}}
+\title{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor}
 
@@
 		Input normalization & None & None & None \\
-		Layer normalization & - & Batch \cite{ioffe2015batch} & Batch \\
-		Loss function & $-Critic(generated)$ & $Critic(gen) - Critic(col) + Penalty_{gradient}$ & MSE \\
+		Layer normalization & None & Batch \cite{ioffe2015batch} & Batch \\
+		Loss function & $-Critic\left[gen\right]$ & $Critic\left[gen\right] - Critic\left[col\right] + Penalty_{grad}$ & MSE \\\hline
+		\multicolumn{4}{l}{gen: generated, col: collected, grad: gradient}
 	\end{tabular}

### 2020-08-12 docs/paper/paper.tex
Format update

@@
-\documentclass[10pt]{IEEEtran}
+\documentclass[journal,twoside,web]{ieeecolor}
+\usepackage{jsen}
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{wrapfig}
+\usepackage{placeins}
+\usepackage[outdir=./]{epstopdf}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\markboth{\journalname, VOL. XX, NO. XX, XXXX 2017}
+{Author \MakeLowercase{\textit{et al.}}: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS (February 2017)}
+\definecolor{abstractbg}{rgb}{0.89804,0.94510,0.83137}
+\setlength{\fboxrule}{0pt}
+\setlength{\fboxsep}{0pt}
 
@@
 \begin{document}
+\title{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor}
+\author{
+	Aimen Zelaci, Ahmet Yasli, Cem Kalyoncu, and Huseyin Ademgil, \IEEEmembership{Senior Member, IEEE}
+	\thanks{A. Z. Author is with 
+		the European University of Lefke, Faculty of Engineering, Electrical and Electronics Engineering Department, Lefke, TR-10, Turkey (e-mail: aimen.zelaci@gmail.com).
+	}
+	\thanks{A. Y. Author is with 
+		the European University of Lefke, Faculty of Engineering, Electrical and Electronics Engineering Department, Lefke, TR-10, Turkey (e-mail: ayasli@eul.edu.tr).
+	}
+	\thanks{C. K. Author is with 
+		the European University of Lefke, Faculty of Engineering, Computer Engineering Department, Lefke, TR-10, Turkey (e-mail: ckalyoncu@eul.edu.tr).
+	}
+	\thanks{H. A. Author is with 
+		the European University of Lefke, Faculty of Engineering, Computer Engineering Department, Lefke, TR-10, Turkey (e-mail: hademgil@eul.edu.tr).
+	}
+}
 
-\title{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor}
-
-\author{Aimen Zelaci, Ahmet Yasli, Cem Kalyoncu, and Huseyin Ademgil}
-
-\maketitle
-
+\IEEEtitleabstractindextext{%
+\fcolorbox{abstractbg}{abstractbg}{%
+\begin{minipage}{\textwidth}%
+%\begin{wrapfigure}[12]{r}{3in}%
+%\includegraphics[width=3in]{jsenga.png}%
+%\end{wrapfigure}%
 \begin{abstract}
@@
 \end{abstract}
+
+\begin{IEEEkeywords}
+Artificial neural network (ANN), fiber optic sensor, generative adversarial networks (GAN), machine learning, photonic crystal fiber (PCF), surface plasmon resonance (SPR).
+\end{IEEEkeywords}
+\end{minipage}}}
+
+\maketitle
 
@@
 
-\begin{figure*}
+\begin{figure}
 	\begin{subfigure}{.48\textwidth}
@@
 			ymax=3,
+			height=6cm,
 			no marks
@@
 			xlabel=Epochs, 
+			ylabel=Training \space MSE,
 			width=\textwidth,
@@
 	\label{chart:trainingmse}
-\end{figure*}
+\end{figure}
 
@@
 			width=\textwidth,			
+			height=8cm,
 			ymin=5,ymax=7,xmin=5,xmax=7,
@@
 		width=\textwidth,
+		height=8cm,
 		legend pos=south east
@@
 		width=0.48\textwidth,
+		height=8cm,
 		legend pos=north west
@@
 			width=\textwidth,
+%			height=6cm,
 			legend pos=south east
@@
 		width=\textwidth,
+%		height=6cm,
 		legend pos=south east
@@
 		legend pos=north east,
+%		height=6cm
 	]
@@
 		width=0.48\textwidth,
-		legend pos=north east
+		legend pos=north east,
+%		height=6cm
 	]
@@
 \caption{Detailed performance analysis}
+\centering
 \begin{tabular}{l|l|l|l|l|l|l}
@@
 \caption{Execution time of algorithms}
+\centering
 \begin{tabular}{l|l|l}

### 2020-09-27 src/data_handler.py
cleanup

@@ -9,95 +9,77 @@ from sklearn.model_selection import train_test_split
 import initializer
 
 FLAGS = initializer.init()
+num_inputs  = FLAGS.num_inputs
+no_spr_samples = FLAGS.no_spr_samples
+no_spr_analytes = FLAGS.no_spr_analytes
+no_spr_configs = FLAGS.no_spr_configs
 
 def split_data(x, y, kf=False):
     if kf:
-        x = x.reshape(8, 3, 16, FLAGS.num_inputs)
-        y = y.reshape(8, 3, 16, 1)
+        x = x.reshape(no_spr_configs -  1, no_spr_analytes, no_spr_samples, num_inputs)
+        y = y.reshape(no_spr_configs - 1, no_spr_analytes, no_spr_samples, 1)
     else:
-        x = x.reshape(9, 3, 16, FLAGS.num_inputs)
-        y = y.reshape(9, 3, 16, 1)
+        x = x.reshape(no_spr_configs, no_spr_analytes, no_spr_samples, num_inputs)
+        y = y.reshape(no_spr_configs, no_spr_analytes, no_spr_samples, 1)
 
     if FLAGS.k_fold and not kf:
         return [x,y]
 
-    tr_data = x[:7].reshape(7 * 16 * 3, FLAGS.num_inputs)
-    tr_labels = y[:7].reshape(7 * 16 * 3, 1)
-    #Shuffle tr data
-    '''
-    merge = np.concatenate((tr_data, tr_labels), axis=1)
-    sp.random.shuffle(merge)
-    tr_data = merge[:, :6].reshape(7 * 16 * 3, 6)
-    tr_labels = merge[:, -1].reshape(7 * 16 * 3, 1)
-    '''
+    tr_data = x[: no_spr_configs -  2].reshape((no_spr_configs -  2) * no_spr_samples * no_spr_analytes, num_inputs)
+    tr_labels = y[: no_spr_configs -  2].reshape((no_spr_configs -  2) * no_spr_samples * no_spr_analytes, 1)
+
     if kf:
-        va_data = x[-1].reshape(1 * 16 * 3, FLAGS.num_inputs)
-        va_labels = y[-1].reshape(1 * 16 * 3, 1)
+        va_data = x[-1].reshape(1 * no_spr_samples * no_spr_analytes, num_inputs)
+        va_labels = y[-1].reshape(1 * no_spr_samples * no_spr_analytes, 1)
         return [tr_data, tr_labels, va_data, va_labels]
     else:
[…]

### 2020-09-27 src/initializer.py

@@ -48,6 +48,12 @@ tf.flags.DEFINE_string('model_to_test', ann_flags['model_to_test'], 'Test model 
 tf.flags.DEFINE_integer('augment_size', ann_flags['augment_size'], 'data augmentation size, default:1000')
 tf.flags.DEFINE_integer('gen_iterations', wgan_flags['gen_iterations'], 'iteration of data generation, default:1000')
 
+tf.flags.DEFINE_integer('no_spr_samples_per_analyte',data_flags['no_spr_samples_per_analyte'], 'Number of samples per analyte')
+tf.flags.DEFINE_integer('no_spr_samples',data_flags['no_spr_samples_per_analyte'], 'Number of samples per analyte')
+tf.flags.DEFINE_integer('no_spr_analytes',data_flags['no_spr_analytes'], 'Number of Analytes')
+tf.flags.DEFINE_integer('no_spr_configs',data_flags['no_spr_configs'], 'Number of SPR geometric configurations')
+
+tf.flags.DEFINE_string('data_set', data_flags['data_set'], 'The dataset used to train the system: PCF or SPR')
 tf.flags.DEFINE_string('gen_data_dir', data_flags['gen_data_dir'],
                        'generated data directory,default:gen_data/gen_data.txt')
 tf.flags.DEFINE_string('data', data_flags['data'], 'SPR-PCF data directory')

### 2020-09-27 src/main.py

@@ -5,20 +5,19 @@ import networks, data_handler, initializer
 from networks import Wgan_optim
 from sklearn.model_selection import KFold
 from sklearn.preprocessing import MinMaxScaler
-from basic_tf_ann import Ann
-
+from sklearn.model_selection import train_test_split
+import time
 # tf.config.experimental.set_visible_devices([], 'GPU')
 tf.config.threading.set_inter_op_parallelism_threads(16)
 FLAGS = initializer.init()
-#tr_data, tr_labels, va_data, va_labels, test_data, test_labels = [],[],[],[],[],[]
 
 def train_wgan(tr_data=[], tr_labels=[],generate=False):
     run_config = tf.ConfigProto()
     run_config.gpu_options.allow_growth = True
     sess = tf.Session(config=run_config)
-    if not FLAGS.k_fold:
-        tr_data, tr_labels, __, _, __, _ = data_handler.load_data(fname=FLAGS.data)
-    #tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_pcf_data(fname=FLAGS.pcf_data)
+    if not FLAGS.k_fold and not FLAGS.k_fold_pcf2:
+        tr_data, tr_labels, __, _, __, _ = data_handler.load_spr_data(fname=FLAGS.data)
+        #tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_pcf_data(fname=FLAGS.pcf_data)
     wgan = Wgan_optim(sess, FLAGS, tr_data, tr_labels)
     sess.run(tf.global_variables_initializer())
     wgan.train_wgan()
@@ -39,7 +38,7 @@ def train_ann_model(tr_data=[], tr_labels=[], va_data=[], va_labels=[]):
     # SPR-based PCF
 
     if not FLAGS.k_fold:
-        tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_data(fname=FLAGS.data)
+        tr_data, tr_labels, va_data, va_labels, test_data, test_labels = data_handler.load_spr_data(fname=FLAGS.data)
         print(tr_data)
         print(tr_labels)
     # PCF data
@@ -60,7 +59,7 @@ def train_ann_model(tr_data=[], tr_labels=[], va_data=[], va_labels=[]):
 def test_model(test_data=[], test_labels=[], plot=True):
     ann_model = networks.make_model(FLAGS)
     if not FLAGS.k_fold:
[…]

### 2020-09-27 src/networks.py

@@ -98,8 +98,7 @@ def train_model(model, tr_data, tr_labels, va_data, va_labels, flags):
     # TensorBoard
     tensorboard_callback = keras.callbacks.TensorBoard(log_dir=logdir)
     # Save the best va_loss file
-    checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=1,
-                                                   save_best_only=True)
+    #checkpointer = keras.callbacks.ModelCheckpoint(filepath=chkdir, verbose=1, save_best_only=True)
     # Define optimizers
     Adam = keras.optimizers.Adam(learning_rate=
                                  lr, beta_1=0.9, beta_2=0.999)
@@ -107,7 +106,7 @@ def train_model(model, tr_data, tr_labels, va_data, va_labels, flags):
     # Train
     model.compile(optimizer=Adam, loss='mean_squared_error')
     hist = model.fit(tr_data, tr_labels, epochs=epochs,
-                     validation_data=(va_data, va_labels), callbacks=[checkpointer, tensorboard_callback],
+                     validation_data=(va_data, va_labels), callbacks=[tensorboard_callback],
                      batch_size=batch_size)
     # Post training
     model.save(save_dir)
@@ -357,16 +356,17 @@ class Wgan_optim(object):
 
     @staticmethod
     def filter_1(data):
-        # Noise filter
-        pve = sum(int(o <= 0.0) for o in data[:7])
-        #nve = sum(int(t <= 0.0) for t in p[1:6])
-        return pve
+        # Noise filter for the SPR set
+        cd1 = sum(int(o >= 1.0) for o in data[3:7])
+        cd2 = sum(int(t <= 0.0) for t in p)
+        return [cd1, cd2]
 
     @staticmethod
     def filter_2(data):
-        pve = sum(int(o <= 0.0) for o in data[:6])
+        # Noise filter for PCF set
+        cd1 = sum(int(o <= 0.0) for o in data[:6])
         #nve = sum(int(t <= 0.0) for t in p[1:6])
-        return pve
+        return cd1
 
     def generate_data(self,load=True):
         logger.info('\n*****\n GENERATING DATA ... \n****\n')
@@ -379,11 +379,16 @@ class Wgan_optim(object):
         for _ in tqdm(range(self.flags.gen_iterations)):
             predictions = self.sess.run(self.g_samples,
                                         feed_dict={self.z: self.sample_z(num=self.num_examples_to_generate)})
-            # print(predictions)
             for p in predictions:
[…]

### 2020-09-28 src/data_handler.py
fix: typo

@@ -54,8 +54,7 @@ def load_spr_data(fname):
 
     df = df.reshape(no_spr_configs, no_spr_analytes, no_spr_samples,  -1)
     sp.random.shuffle(df)
-    df = df.reshape(no_spr_configs * no_spr_samples * no_spr_analytes, no_spr_configs, -1)
-    print(df.shape)
+    df = df.reshape(no_spr_configs * no_spr_samples * no_spr_analytes, -1)
     '''
     Tried different normalization techniques
     scaler = StandardScaler()

### 2020-09-28 src/networks.py

@@ -380,11 +380,11 @@ class Wgan_optim(object):
             predictions = self.sess.run(self.g_samples,
                                         feed_dict={self.z: self.sample_z(num=self.num_examples_to_generate)})
             for p in predictions:
-                if(elf.flags.data_set = "SPR"):
+                if(self.flags.data_set == "SPR"):
                     cd1, cd2 = self.filter_1(p)
                     if not cd1 and not cd2:
                         _df = np.concatenate((_df, p.reshape(1, self.noise_dim)), axis=0)
-                if(self.flags.data_set = "PCF"):
+                if(self.flags.data_set == "PCF"):
                     cd1 = self.filter_2(p)
                     if not cd1:
                         _df = np.concatenate((_df, p.reshape(1, self.noise_dim)), axis=0)

### 2020-09-30 docs/revision/review.tex
add: revision folder

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{pgfplots}

\title{Review questions list}

\begin{document}
\begin{enumerate}
	\item \textbf{-TRIVIAL-} Page 4, Line 43, Right Column- The paper cited [18] doesn't have 7 inputs as looking from the dataset file (from github) and the mauscript itself. It looks to me that there are 5 inputs. Can you recheck this?

\textcolor{green}{ANSWER: } In line 91 in their code: \\
$ scaler_datafile_1 = scaler1.transform(datafile_1) $  \\
 $X = scaler_datafile_1[:,range(0,6)]$                 input variables columns\\
$y = scaler_datafile_1[:,range(6,11)] $                  output variables columns\\

Shows that they have used 6 inputs.

It is a typo in our paper, "7" should be changed to "6". And the we should add "the clad-ref-index".	\\
\textcolor{red}{ CK's comment: We should be much more careful about these. Mistakes like these damage our projection of surety.}

	\item \textbf{-TRIVIAL-} Also, have you used the dataset of [18] along with your own data making it finally as 1117+432 data samples. If yes, how did you merge both datasets as proposed manuscript (d1,d2,d3,etc) data sets has different inputs parameters than [18]. What happens to non-common columns like number of rings input feature as mentioned in [18].     \\
	\textcolor{green}{ANSWER: } No, we have not. \textcolor{red}{ CK's comment: Don't do that yet. We will talk about it later.}

\item \textbf{-TRIVIAL-} Page 7, Line 43, Right Column- Github link for the code is broken. I hope you will correct it. Looking forward to check your code along with data samples you have used  to obtain results in this manuscript. \\
\textcolor{green}{ANSWER: } I forgot to make the repo public. I will make it public as soon as we finish with the revision.

    \item \textbf{-TRIVIAL-} Please, reread the paper to correct some misspelling words. For example, Abstract (line 3): should it be "researchers"? Another example in "Introduction", page 1, column 2, line 35: "Snell's Total" instead of "Snell?s Total". \\
    \textcolor{green}{ANSWER AZ: To be resolved by HA} \\ \textcolor{red}{ CK's comment: HA will not be able to do this as this is a word to latex issue.}

\item \textbf{-TRIVIAL-} Which kind of performance metric the authors are measuring in Table II? Is it MSE? Please, define it.  \\
\textcolor{green}{ANSWER: } Yes, we should indicate in the table that it is indeed the MSE. \textcolor{red}{ CK's comment: Just add the necessary bit.}

\item \textbf{-TRIVIAL-} Please, define which is RI (page 4, column 1, line 38). \\
\textcolor{green}{ANSWER: } TO be answered by AY or HA.

\item  \textbf{-EASY-} How do the authors know the ANN is not overfitting in Fig. 3? Have the authors employed any validation during training? Please, provide the ANN models' performance on the validation by showing the validation MSE during training. \\
\textcolor{green}{ANSWER: } Yes, we have employed validation. I have prepared validation curves: with and without augmentation with epochs set to 3000.\\ \textcolor{green}{ Following CK comment: I believe we should include the plots; He will still ask for the plots even if we choose to just mention it. The plots also show that data augmentation reduced fluctuations on the va set which is a very important result in our work.} \\ \textcolor{red}{CK's comment: We don't have space for another graph.}

\textcolor{blue}{AZ: Finally, CK, Please rename the tables files used for the loss curves (should be "our data" not "their data"), also in the corresponding latex code.}

\item \textbf{-EASY-} Please provide the test MSEs for comparison between the proposed method and the ref. [18] (illustrated in Fig. 4).   \\
\textcolor{green}{ANSWER: }  \textcolor{red}{To be calculated by CK using the data used to plot the graphs.}

    \item \textbf{-EASY-} Page 3, Line 13, Right Column- Why you have specifically used 5 hidden layers? What will be the impact on performance when using less or more hidden layers and neurons?\\
    \textcolor{green}{ANSWER: } After several experiments, we noticed that using less than 5 hidden layers will cause the model to under fit, while using more increased the training runtime of the model. Also, using more hideen layers led the model over fit as the number of parameters was very high compared to the number of variables in the feature space.  \\ \textcolor{red}{ CK's comment: Sure, we will need to reword this, and others too.}

	\item \textbf{-EASY-} Page 5, Line 46, Left Column- "This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model[46]"- There is no surity of this reason if the above comment/query in line 43 is logical. So reframe/reconsider this statement. \\

	\textcolor{green}{ANSWER: } We can safely drop this argument, or reframe in a way that we are not absolutely sure as more research is required on this topic. \textcolor{red}{Following CK comment: Will be reframed as to what we have seen.}

	\item \textbf{-EASY-} I suggest that the authors give more information about the stopping criteria of the GAN. As the author pointed out, human judgment has an important role in the generation of images and audio. So, could the known physical laws about PCF and SPR be used to replace the human role in the GAN system to improve the performance? How does the author verify the validity of the augmented samples? \\
	\textcolor{green}{ANSWER: } When it comes to physical quantities it is difficult to visually interpret the generated samples. I can not answer the first question. However, this is the mainpoint why we chose the WGAN, because the loss function is interpretable as it measures the distance between the distrubutions of real and generated data in a stable manner. I can provide the loss curve of the WGAN which shows that it is indeed converging and that to a high degree of certainty (probabilistically speaking) that our generated data is valid. In a future research it is possible that we implement a system that validates the generated samples according to the physical laws. \textcolor{red}{CK's comment: We explained this in the paper. We will rephrase it in the reply. } \\ \textcolor{blue}{AZ: The loss curve of the wgan is ready.}

\item \textbf{-EASY-} In GAN and ANN, how many training samples and test samples are used respectively? How are the test samples selected? \\
\textcolor{green}{ANSWER: } For the SPR set: for the 9 folds, we used 336 samples to train the gan and the ann, 48 for validation and 48 for testing. For the PCF set: for the 10 folds, we used about 10\% for testing, about 10\% for validation and the rest for training. \textcolor{red}{CK's comment: We had a table containing this, we removed it to save space.}

\item \textbf{-MEDIUM-} Figure 4c, Figure 6- Give more details about the paramaters (d1,d2,d3,refrative index,etc) at which this particular actual blue line graph is obtained.\\
\textcolor{green}{ANSWER: } \textcolor{red}{Following CK comment: } The reviewer is asking for the input planes used; \\
\begin{enumerate}
\item Figure 4c, analyte 1.34: \\
$Re(neff) = 1.46; Pitch = 0.24 um ; d1 = 0.45 um; d2= 0.75um; d3 = 0.35um $ \\
\item Figure 4c, analyte 1.35: \\
$Re(neff) = 1.45; Pitch = 0.15 um ; d1 = 0.25 um; d2= 0.75um; d3 = 0.35um $ \\
\item Figure 6, analyte 1.34: \\
$Re(neff) = 1.46; Pitch = 0.24 um ; d1 = 0.45 um; d2= 0.75um; d3 = 0.35um $ \\
\item Figure 6, analyte 1.35: \\
$Re(neff) = 1.45; Pitch = 0.15 um ; d1 = 0.25 um; d2= 0.55um; d3 = 0.15um $ \\

\end{enumerate}

 \item \textbf{-MEDIUM-} Page 5, Line 43, Left Column- You have stated that [18]'s model has been failing in Figure 4c. It looks to me that the blue line in Figure 4c is for your proposed PCF structure design, while [18]'s PCF design was a simple hexagonal structure with varying rings. Also, there was no analyte (but you have used refractive index 1.35 as shown in this manuscript) in [18]. So if you compare ML models (your's and [18]) only on the criteria of wavelength as stated in Figure 4c, then [18] model is supposed to fail. This comparison doesn't make much sense as both designs and input features are different. If you disagree, then explain this comparison in more detail and mention the design specification values.
The similar comparison (your's and [18]) explanation is required for Figure 6. //
\textcolor{green}{ANSWER:} \textcolor{red}{Following CK comment: } \\ AZ: Even if we say that we changed the number of inputs in [18], our argument is still very weak, because [18]'s model is designed specifically for one dataset. We can definitely compare our model to [18] on their data, but on our data I believe we should just say: \textcolor{red} {We have changed the number of inputs and trained [18]'s on our dataset. Figure 4c indeed proves that their model is specifically designed for one dataset and it is normal and very natural, actually it is supposed to fail on other datasets.} \\ \textcolor{red}{CK's comment: We will have to reword this, it is not supposed to fail, it is not designed to succeed. However, we need to show that the design of the ANN is important for generality. .} \\ \textcolor{blue}{AZ: I still have my doubts. The thing is they did not claim generality in their paper, their ANN is designed specifically for that dataset ...}

\item \textbf{-MEDIUM-} Page 7, Line 45, Left Column- "In our experiments, due to optimized dataset the accuracy of the method proposed in Ref. [18] is also improved."- Following from the previous comments- if the comparison is not for the similar designs then you can't state this improvement. So please elaborate on this. \\
\textcolor{red}{Following CK comment: A fix added by HA, to be unfixed}

\item \textbf{-MEDIUM-} Page 7, Line 40, Right Column- Recurrent Neural Networks (RNN) generally rely memory to recognise patterns like in speech recognition or text generation and tells what should/will come after. How do you state/propose here than RNN can be used to discover optimal geometrical shapes?- because all the geometrical shapes might be independent of each other. \\
\textcolor{green}{ANSWER: } I believe we should drop this argument. The reviewer is right, if the shapes are independent then an RNN won't be of advantage in this case. \\

\textcolor{red}{Following CK comment: The argument will be dropped}

\item \textbf{-HARD-} How did the authors find the ANN architectures? How long did it take to find the ANN designs suitable for the problem being addressed? \\
\textcolor{green}{ANSWER: } The choice for this regression problem given the type of data we have in the feature space was quite trivial: Multi Layer Perceptron was chosen over other architechtures such as CNN and RNN which might not be suitable for this particular problem. Relying on the results attained in [18] and after efficiently training different MLPs (with different layers, tuning the other parameters ... etc) we were able to find an adequate ANN. As to how long; this is unclear as I do not remember and I believe it should be considered as an offline time.\\

\textcolor{red}{CK: Not really that hard. We can state we have started using the state-of-the-art as the base and made modifications that are deemed beneficial to this particular domain. We should tell him that the ANN structure may not be the most optimal}

\item \textbf{-HARD-} The authors wrote, "The most important contribution of this research is the use of
the GAN phase, where the available data is expanded to be
used in the training phase". Why use a Generative adversarial network? What would be the advantages and disadvantages of a GAN approach over other possible data generators, such as evolutionary mutation functions? The authors should provide a comparison methodology and discuss differences between GAN and other data generators. \\
\textcolor{green}{ANSWER: } To be investigated in future research.\\ \textcolor{red}{CK comment: We can talk about this in here and maybe in paper. I am not sure he is requesting experiments. We can avoid experiments by adding it to future works.}

\item \textbf{-HARD-} In Fig 5, the MSE increase when the augmented samples exceed 1000. Why does more samples cause performance degradation? \\ 
\textcolor{green}{ANSWER: AZ I agree with CK's comment}\\ \textcolor{red}{CK comment: This is simple. Augmentation is not perfect. If we keep adding more augmented data, it dialutes the importance of the real data. Initially this is not a problem as the low number of samples is a larger issue. Therefore, there is a balance to be struck here.}

\item \textbf{-NOT CLEAR-} In Fig 6, in the case of SPR, the calculated loss spectrum has a large deviation under some specific parameters. Could the authors discuss the reasons for the deviation and how to judge the validity of the calculation result?
\textcolor{green}{ANSWER: AZ: I could not really understand this question} \\
\textcolor{red}{CK comment: We should explain (in reply) the reason behind this is estimating a new structure rather than interpolating missing values within the same configuration.}

\end{enumerate}

\end{document}

### 2020-10-01 docs/paper/paper.tex
* Partial revision

@@
-\documentclass[journal,twoside,web]{ieeecolor}
-\usepackage{jsen}
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{wrapfig}
-\usepackage{placeins}
-\usepackage[outdir=./]{epstopdf}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\markboth{\journalname, VOL. XX, NO. XX, XXXX 2017}
-{Author \MakeLowercase{\textit{et al.}}: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS (February 2017)}
-\definecolor{abstractbg}{rgb}{0.89804,0.94510,0.83137}
+\documentclass[journal]{IEEEtran}
+
 \setlength{\fboxrule}{0pt}
 \setlength{\fboxsep}{0pt}
-
 \usepackage{color,soul}
@@
 
+\hyphenation{op-tical net-works semi-conduc-tor}
 \usepackage[english]{babel}
@@
 \begin{document}
+
 \title{Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor}
@@
 
-\IEEEtitleabstractindextext{%
-\fcolorbox{abstractbg}{abstractbg}{%
-\begin{minipage}{\textwidth}%
-%\begin{wrapfigure}[12]{r}{3in}%
-%\includegraphics[width=3in]{jsenga.png}%
-%\end{wrapfigure}%
+% The paper headers
+\markboth{Journal of Journal of Lightwave Technology,~Vol.~14, No.~8, August~2015}%
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
+
+% make the title area
+\maketitle
+
 \begin{abstract}
-Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches.
+	Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researchers.
 However, the potential number of design combinations and flexible propagation features are offering a wide range of application areas, resulting in an exponential increase in the search space.
@@
 \end{IEEEkeywords}
-\end{minipage}}}
 
-\maketitle
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
@@
 Kretschamann Raether prism geometry is the fundamental construction principle of SPR based sensors  \cite{kretschmann1968radiative}.
-This geometry practices Snell’s Total Internal Reflection rule, where still a very small amount of light refracts from the metallic layer into the evanescent field.
+This geometry practices Snell's Total Internal Reflection rule, where still a very small amount of light refracts from the metallic layer into the evanescent field.
 The refracted photons are coupling with electron charge oscillations (plasmon) at the surface of the metallic layer, which are known as surface plasmon waves (SPW).
@@
 These possible variations are the main parameters for sensitivity calculations.
-The deep research on SPR based sensors have shown that Kretschmann Raether’s prism geometry fails to satisfy the remote sensing and miniaturization requirements of critical detecting applications.
+The deep research on SPR based sensors have shown that Kretschmann Raether's prism geometry fails to satisfy the remote sensing and miniaturization requirements of critical detecting applications.
 One of the most common solutions of overcoming these limitations is replacing the prism with the core of an optical fiber.
@@
 This proposed enhanced WGAN system converges in a stable manner without requiring further fine tuning the hyper-parameters of the system.
-The flowchart of this proposed system is illustrated in Figure \ref{fig:gan}.
+% The flowchart of this proposed system is illustrated in Figure \ref{fig:gan}.
 
@@
 Once the training phase is completed, the generator and the filter is used to augment the number of training samples that are available for ANN to train on.
-
-\begin{figure}
-	\centering
-	\begin{tikzpicture}[node distance=2cm]
-		\node(latent) 	[filter,text width=1.4cm] 		{\baselineskip=10pt Noise generator\par};
-		\node(generator)[operation,below of=latent] 	{Generator};
-		\node(generated)[data, below of=generator,
-						 text width=1.4cm]				{\baselineskip=10pt Generated samples\par};
-		\node(collected)[data, right of=generated,
-						 xshift=1cm,text width=1.4cm]	{\baselineskip=10pt Collected samples\par};
-		\node(critic)	[operation,below of=generated,
-						 xshift=1.5cm]					{Critic};
-		\node(metric)   [metric,below of=critic,
-						 text width=1.4cm, yshift=-.2cm]{\baselineskip=10pt{}Wasserstein distance\par};
-
-		\draw [training] (latent) -- (generator) node [pos=.5, left, xshift=-0.1cm] (z) {Latent variable};
-		\draw [training] (generator) -- (generated);
-		\draw [training] (generated) -| (critic);
-		\draw [training] (collected) -| (critic);
-		\draw [training] (critic) -- (metric);
-		\draw [testing]  (metric.east) - ++(1,0) |-  (critic.east);
-		\draw [testing]  (metric.west) - ++(-2.2,0) |-  (generator.west);
-	\end{tikzpicture}
-	\caption{WGAN training}
-	\label{fig:gan}
-\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\begin{tikzpicture}[node distance=2cm]
+%	\node(latent) 	[filter,text width=1.4cm] 		{\baselineskip=10pt Noise generator\par};
+%	\node(generator)[operation,below of=latent] 	{Generator};
+%	\node(generated)[data, below of=generator,
+%	text width=1.4cm]				{\baselineskip=10pt Generated samples\par};
+%	\node(collected)[data, right of=generated,
+%	xshift=1cm,text width=1.4cm]	{\baselineskip=10pt Collected samples\par};
+%	\node(critic)	[operation,below of=generated,
+%	xshift=1.5cm]					{Critic};
+%	\node(metric)   [metric,below of=critic,
+%	text width=1.4cm, yshift=-.2cm]{\baselineskip=10pt{}Wasserstein distance\par};
+%	
+%	\draw [training] (latent) -- (generator) node [pos=.5, left, xshift=-0.1cm] (z) {Latent variable};
+%	\draw [training] (generator) -- (generated);
+%	\draw [training] (generated) -| (critic);
+%	\draw [training] (collected) -| (critic);
+%	\draw [training] (critic) -- (metric);
+%	\draw [testing]  (metric.east) - ++(1,0) |-  (critic.east);
+%	\draw [testing]  (metric.west) - ++(-2.2,0) |-  (generator.west);
+%	\end{tikzpicture}
+%	\caption{WGAN training}
+%	\label{fig:gan}
+%\end{figure}
 
@@
 	\centering
-	\includegraphics[width=.6\linewidth]{figures/Figx}
+	\includegraphics[width=.7\linewidth]{figures/Figx}
 	\caption{The cross-section of proposed  PCF based SPR sensor.}
@@
 
-where $\lambda$ is the operating wavelength, $n$ is the RI, $B_{1,2,3}$ and  $C_{1,2,3}$ are the  Sellmeier constants~\cite{bjarklev2003PCF}.
+where $\lambda$ is the operating wavelength, $n$ is the Refractive Index (RI), $B_{1,2,3}$ and  $C_{1,2,3}$ are the  Sellmeier constants~\cite{bjarklev2003PCF}.
 
@@
 Additionally, we have used the dataset that has been used in \cite{paper0}.
-This dataset contains over 1000 samples.
-Inputs are refractive index of the core ($n_c$), wavelength ($\lambda$), hole diameter ($d$), pitch ($\Lambda$), and number of rings ($N_r$);  and outputs are effective index ($n_{eff}$), effective mode area ($A_{eff}$), dispersion ($D$), and the confinement loss ($\alpha_c$).
+This dataset contains 1117 samples.
+There are 7 inputs: refractive index of the core ($n_c$), wavelength ($\lambda$), hole diameter ($d$), pitch ($\Lambda$), and number of rings ($N_r$);  and outputs are effective index ($n_{eff}$), effective mode area ($A_{eff}$), dispersion ($D$), and the confinement loss ($\alpha_c$).
 We have only used confinement loss as the output.
 This dataset is referred to as PCF.
-Details of the datasets that are used in the experiments are given in Table \ref{tbl:dataset}.
 As a final note, the range and domain of these datasets are different; therefore, all numeric comparisons should be drawn within the same dataset.
@@
 5000 training epochs are used for  \cite{paper0} as suggested in the original paper.
-All numeric comparison results are averaged over multiple executions as listed in Table \ref{tbl:dataset}.
+All numeric comparison results are averaged over multiple executions: 9-fold testing for SPR dataset and 10-fold testing for \dszero.
 Non-averaged data used in figures, such as configuration estimation, are selected from non-extreme cases for the compared methods.
-
-\begin{table}
-\centering
-\caption{Datasets that are used in experiments}
-\begin{tabular}{l|l|l}
-	~ & SPR & \dszero \\\hline
-	Samples & 432 & 1117\\
-	Configurations & 9 & - \\
-	Parameters & 7 & 5 \\
-	Output & $log_{loss}$ & $log_{loss}$ \\
-	Testing & 48 (1 configuration) & 10\% \\
-	Testing method & 9-fold & 10-fold \\
-\end{tabular}
-\label{tbl:dataset}
-\end{table}
+%
+%\begin{table}
+%	\centering
+%	\caption{Datasets that are used in experiments}
+%	\begin{tabular}{l|l|l}
+%		~ & SPR & \dszero \\\hline
+%		Samples & 432 & 1117\\
+%		Configurations & 9 & - \\
+%		Parameters & 7 & 5 \\
+%		Output & $log_{loss}$ & $log_{loss}$ \\
+%		Testing & 48 (1 configuration) & 10\% \\
+%		Testing method & 9-fold & 10-fold \\
+%	\end{tabular}
+%	\label{tbl:dataset}
+%\end{table}
+%
 
@@
 		table{data/ann_tr_loss_3k_their_data_without.txt};
+		\addlegendentry{Without GAN}
+
+		\addplot[line width=1pt,solid,color=red] %
+		table{data/ann_tr_loss_3k_their_data_with.txt};
+		\addlegendentry{With GAN}
 		\end{axis}
 		\end{tikzpicture}
-	\caption{Without augmentation}
-	\end{subfigure}	
-	\begin{subfigure}{.48\textwidth}
-	\centering
-	\begin{tikzpicture}
-		\begin{axis}[
-			xlabel=Epochs, 
-			ylabel=Training \space MSE,
-			width=\textwidth,
-			grid=both,
-			minor grid style={gray!25},
-			major grid style={gray!25},
-			ymax=3,
-			height=6cm,
-			no marks
-		]
-		\addplot[line width=1pt,solid,color=blue] %
-		table{data/ann_tr_loss_3k_their_data_with.txt};
-		\end{axis}
-	\end{tikzpicture}
-	\caption{With augmentation}
 	\end{subfigure}
 
-	\caption{Training MSE of the ANN model with (a) and without (b) GAN phase obtained from SPR dataset}
+	\caption{Training MSE of the ANN model}
 	\label{chart:trainingmse}
@@
 		width=\textwidth,			
-			height=8cm,
+		height=6cm,
 		ymin=5,ymax=7,xmin=5,xmax=7,
@@
 		width=\textwidth,
-		height=8cm,
+		height=6cm,
 		legend pos=south east
@@
 		\begin{axis}[
-		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
+		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $ ({$n_{analyte=1.34}$}), 
 		ylabel=$ Loss $ $ in $ $ Log(db/cm) $,
@@
 		major grid style={gray!25},
-		title={$n_{analyte=1.34}$},
 		width=0.48\textwidth,
-		height=8cm,
+		height=6cm,
 		legend pos=north west
@@
 
+		% their mse: 0.08721
+		% our mse: 0.18869
+
 		\addlegendentry{Actual}
@@
 		\begin{axis}[
-		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
+		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $ ($n_{analyte=1.35}$), 
 		ylabel=$~$,
@@
 		major grid style={gray!25},
-		title={$n_{analyte=1.35}$},
 		width=0.48\textwidth,
-		height=8cm,
+		height=6cm,
 		legend pos=north west
@@
 		\legend{}
-
+		% our: 0.37049
+		% their: 0.17491
 		\end{axis}
 		\end{tikzpicture}
-	\caption{Configuration estimation on SPR dataset}
+		\caption{Configuration estimation on SPR dataset.}
 	\end{subfigure}
@@
 	ymin=0,ymax=1,
-	width=0.48\textwidth, height=6cm,
+	width=0.48\textwidth, height=5cm,
 	axis y line=left, ylabel=MSE, 
@@
 		width=\textwidth,
-%			height=6cm,
+		height=6cm,
 		legend pos=south east
@@
 		width=\textwidth,
-%		height=6cm,
+		height=6cm,
 		legend pos=south east
@@
 		legend pos=north east,
-%		height=6cm
+		height=6cm
 		]
@@
 		\addlegendentry{Actual}\legend{};
+
+		%w/o: 0.18869
+		%w/g: 0.11670
+
 		\end{axis}
@@
 		\addlegendentry{With GAN}
+
+		%w/o: 0.32373
+		%w/g: 0.08664
 
@@
 The final set of experiments shows the stability that the GAN phase adds.
-In Table \ref{tbl:all},we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing.
+In Table \ref{tbl:all}, we have listed minimum, maximum, average MSE along with the standard deviation between folds in the testing.
 It is clear that the GAN phase not only improves the average case but significantly improves the worst case while reducing the deviation, which is important in a live setting.
@@
 \begin{table}
-\caption{Detailed performance analysis}
+	\caption{Detailed performance analysis in MSE}
 	\centering
 	\begin{tabular}{l|l|l|l|l|l|l}
-	Method & \multicolumn{3}{c|}{SPR} & \multicolumn{3}{c}{\dszero{}} \\\hline
-	Dataset & \multicolumn{2}{c|}{Proposed} & \cite{paper0}  & \multicolumn{2}{c|}{Proposed}   & \cite{paper0} \\\hline
+		Dataset & \multicolumn{3}{c|}{SPR} & \multicolumn{3}{c}{\dszero{}} \\\hline
+		Method & \multicolumn{2}{c|}{Proposed} & \cite{paper0}  & \multicolumn{2}{c|}{Proposed}   & \cite{paper0} \\\hline
 		GAN Phase 			& Yes            & No    &  No     &   Yes            & No             & No    \\\hline

### 2020-10-01 docs/revision/review.tex
update: review list
* Partial revision

@@
 
+\definecolor{darkgreen}{RGB}{0, 128, 0}
+\definecolor{purple}{RGB}{128, 0, 128}
+
+\newcommand{\fix}{\large \textcolor{blue}{ \textbf{Fix:} }}
+\newcommand{\fixed}{\Large \textcolor{purple}{ \underline{\textbf{Fixed}} }}
+\newcommand{\reply}{\large \textcolor{blue}{ \textbf{Reply will be written} }}
+
 \title{Review questions list}
-
 \begin{document}
@@
 
-\textcolor{green}{ANSWER: } In line 91 in their code: \\
-$ scaler_datafile_1 = scaler1.transform(datafile_1) $  \\
- $X = scaler_datafile_1[:,range(0,6)]$                 input variables columns\\
-$y = scaler_datafile_1[:,range(6,11)] $                  output variables columns\\
+\textcolor{darkgreen}{ANSWER: } In line 91 in their code:
+\begin{verbatim}
+scaler_datafile_1 = scaler1.transform(datafile_1) 
+X = scaler_datafile_1[:,range(0,6)]   # input variables
+y = scaler_datafile_1[:,range(6,11)]  # output variables
+
+\end{verbatim}
+
+Line 130:
+\begin{verbatim}
+input_dim = 6   # no. of input variables columns
+output_dim = no_of_output_nodes #no. of output variables columns
+from collections import OrderedDict
+\end{verbatim}
 
@@
 It is a typo in our paper, "7" should be changed to "6". And the we should add "the clad-ref-index".	\\
-\textcolor{red}{ CK's comment: We should be much more careful about these. Mistakes like these damage our projection of surety.}
+\textcolor{red}{ CK's comment: We should be much more careful about these. Mistakes like these damage our projection of surety.}\\
+
+\textcolor{darkgreen}{ AZ: I am sure that I used the same inputs in our experiments.}
+
+\fix AZ (double check first and update the paper)
 
@@
 \\
-	\textcolor{green}{ANSWER: } No, we have not. \textcolor{red}{ CK's comment: Don't do that yet. We will talk about it later.}
+	\textcolor{darkgreen}{ANSWER: } No, we have not.
+
+	\reply
 
@@
 \\
-\textcolor{green}{ANSWER: } I forgot to make the repo public. I will make it public as soon as we finish with the revision.
+\textcolor{darkgreen}{ANSWER: } I forgot to make the repo public. I will make it public as soon as we finish with the revision. \\ 
+\textcolor{red}{ CK's comment: Don't do that yet. We will talk about it later.}
+\reply
 
@@
 \\
-    \textcolor{green}{ANSWER AZ: To be resolved by HA} \\ \textcolor{red}{ CK's comment: HA will not be able to do this as this is a word to latex issue.}
+\textcolor{darkgreen}{ANSWER AZ: To be resolved by HA} \\ \textcolor{red}{ CK's comment: HA will not be able to do this as this is a word to latex issue.}
+
+\fix I have fixed the ones mentioned, we have to re-read the paper before submission.
 
 \item \textbf{-TRIVIAL-} Which kind of performance metric the authors are measuring in Table II? Is it MSE? Please, define it.  \\
-\textcolor{green}{ANSWER: } Yes, we should indicate in the table that it is indeed the MSE. \textcolor{red}{ CK's comment: Just add the necessary bit.}
+\textcolor{darkgreen}{ANSWER: } Yes, we should indicate in the table that it is indeed the MSE. \textcolor{red}{ CK's comment: Just add the necessary bit.}
+
+It was also mentioned in the text.
+
+\fixed
 
 \item \textbf{-TRIVIAL-} Please, define which is RI (page 4, column 1, line 38). \\
-\textcolor{green}{ANSWER: } TO be answered by AY or HA.
+\textcolor{darkgreen}{ANSWER: } TO be answered by AY or HA.
+
+\fixed
 
@@
 \\
-\textcolor{green}{ANSWER: } Yes, we have employed validation.
-I have prepared validation curves: with and without augmentation with epochs set to 3000.\\ \textcolor{green}{ Following CK comment: I believe we should include the plots; He will still ask for the plots even if we choose to just mention it.
+\textcolor{darkgreen}{ANSWER: } Yes, we have employed validation.
+I have prepared validation curves: with and without augmentation with epochs set to 3000.\\ \textcolor{darkgreen}{ Following CK comment: I believe we should include the plots; He will still ask for the plots even if we choose to just mention it.
 The plots also show that data augmentation reduced fluctuations on the va set which is a very important result in our work.} \\ \textcolor{red}{CK's comment: We don't have space for another graph.}
@@
 
+\fix The names should be checked
+
 \item \textbf{-EASY-} Please provide the test MSEs for comparison between the proposed method and the ref. [18] (illustrated in Fig. 4).   \\
-\textcolor{green}{ANSWER: }  \textcolor{red}{To be calculated by CK using the data used to plot the graphs.}
+\textcolor{darkgreen}{ANSWER: }  \textcolor{red}{To be calculated by CK using the data used to plot the graphs.}
+
+\fix Calculation is done AY will place values on graph.
 
     \item \textbf{-EASY-} Page 3, Line 13, Right Column- Why you have specifically used 5 hidden layers? What will be the impact on performance when using less or more hidden layers and neurons?\\
-    \textcolor{green}{ANSWER: } After several experiments, we noticed that using less than 5 hidden layers will cause the model to under fit, while using more increased the training runtime of the model.
-Also, using more hideen layers led the model over fit as the number of parameters was very high compared to the number of variables in the feature space.
+    \textcolor{darkgreen}{ANSWER: } After several experiments, we noticed that using less than 5 hidden layers will cause the model to under fit, while using more increased the training run-time of the model.
+Also, using more hidden layers led the model over fit as the number of parameters was very high compared to the number of variables in the feature space.
 \\ \textcolor{red}{ CK's comment: Sure, we will need to reword this, and others too.}
+
+    \reply
 
@@
 
-	\textcolor{green}{ANSWER: } We can safely drop this argument, or reframe in a way that we are not absolutely sure as more research is required on this topic.
+	\textcolor{darkgreen}{ANSWER: } We can safely drop this argument, or reframe in a way that we are not absolutely sure as more research is required on this topic.
 \textcolor{red}{Following CK comment: Will be reframed as to what we have seen.}
@@
 \\
-	\textcolor{green}{ANSWER: } When it comes to physical quantities it is difficult to visually interpret the generated samples.
+	\textcolor{darkgreen}{ANSWER: } When it comes to physical quantities it is difficult to visually interpret the generated samples.
 I can not answer the first question.
@@
 \item \textbf{-EASY-} In GAN and ANN, how many training samples and test samples are used respectively? How are the test samples selected? \\
-\textcolor{green}{ANSWER: } For the SPR set: for the 9 folds, we used 336 samples to train the gan and the ann, 48 for validation and 48 for testing.
+\textcolor{darkgreen}{ANSWER: } For the SPR set: for the 9 folds, we used 336 samples to train the gan and the ann, 48 for validation and 48 for testing.
 For the PCF set: for the 10 folds, we used about 10\% for testing, about 10\% for validation and the rest for training.
@@
 \item \textbf{-MEDIUM-} Figure 4c, Figure 6- Give more details about the paramaters (d1,d2,d3,refrative index,etc) at which this particular actual blue line graph is obtained.\\
-\textcolor{green}{ANSWER: } \textcolor{red}{Following CK comment: } The reviewer is asking for the input planes used; \\
+\textcolor{darkgreen}{ANSWER: } \textcolor{red}{Following CK comment: } The reviewer is asking for the input planes used; \\
 \begin{enumerate}
@@
 The similar comparison (your's and [18]) explanation is required for Figure 6. //
-\textcolor{green}{ANSWER:} \textcolor{red}{Following CK comment: } \\ AZ: Even if we say that we changed the number of inputs in [18], our argument is still very weak, because [18]'s model is designed specifically for one dataset.
+\textcolor{darkgreen}{ANSWER:} \textcolor{red}{Following CK comment: } \\ AZ: Even if we say that we changed the number of inputs in [18], our argument is still very weak, because [18]'s model is designed specifically for one dataset.
 We can definitely compare our model to [18] on their data, but on our data I believe we should just say: \textcolor{red} {We have changed the number of inputs and trained [18]'s on our dataset.
@@
 \\
-\textcolor{green}{ANSWER: } I believe we should drop this argument. The reviewer is right, if the shapes are independent then an RNN won't be of advantage in this case. \\
+\textcolor{darkgreen}{ANSWER: } I believe we should drop this argument. The reviewer is right, if the shapes are independent then an RNN won't be of advantage in this case. \\
 
@@
 \item \textbf{-HARD-} How did the authors find the ANN architectures? How long did it take to find the ANN designs suitable for the problem being addressed? \\
-\textcolor{green}{ANSWER: } The choice for this regression problem given the type of data we have in the feature space was quite trivial: Multi Layer Perceptron was chosen over other architechtures such as CNN and RNN which might not be suitable for this particular problem.
+\textcolor{darkgreen}{ANSWER: } The choice for this regression problem given the type of data we have in the feature space was quite trivial: Multi Layer Perceptron was chosen over other architechtures such as CNN and RNN which might not be suitable for this particular problem.
 Relying on the results attained in [18] and after efficiently training different MLPs (with different layers, tuning the other parameters ...
@@
 \\
-\textcolor{green}{ANSWER: } To be investigated in future research.\\ \textcolor{red}{CK comment: We can talk about this in here and maybe in paper.
+\textcolor{darkgreen}{ANSWER: } To be investigated in future research.\\ \textcolor{red}{CK comment: We can talk about this in here and maybe in paper.
 I am not sure he is requesting experiments.
@@
 \item \textbf{-HARD-} In Fig 5, the MSE increase when the augmented samples exceed 1000. Why does more samples cause performance degradation? \\ 
-\textcolor{green}{ANSWER: AZ I agree with CK's comment}\\ \textcolor{red}{CK comment: This is simple.
+\textcolor{darkgreen}{ANSWER: AZ I agree with CK's comment}\\ \textcolor{red}{CK comment: This is simple.
 Augmentation is not perfect.
@@
 Could the authors discuss the reasons for the deviation and how to judge the validity of the calculation result?
-\textcolor{green}{ANSWER: AZ: I could not really understand this question} \\
+\textcolor{darkgreen}{ANSWER: AZ: I could not really understand this question} \\
 \textcolor{red}{CK comment: We should explain (in reply) the reason behind this is estimating a new structure rather than interpolating missing values within the same configuration.}

### 2020-10-03 docs/paper/paper.tex
update: loss_curve::Bar-chart

@@
 		major grid style={gray!25},
-		ymax=3,
+		ymax=0.2,
 		height=6cm,
@@
 		\addplot[line width=1pt,solid,color=blue] %
-		table{data/ann_tr_loss_3k_their_data_without.txt};
+		table{data/ann_tr_loss_3k_our_data_without.txt};
 		\addlegendentry{Without GAN}
@@
 		\addplot[line width=1pt,solid,color=red] %
-		table{data/ann_tr_loss_3k_their_data_with.txt};
+		table{data/ann_tr_loss_3k_our_data_with.txt};
 		\addlegendentry{With GAN}
@@
 	ybar, axis x line=bottom, xlabel=Augmented samples, 
-	xmin=-100,xmax=2100,
+	xmin=-100,xmax=3100,
 	ymin=0,ymax=1,
@@
 		(0, 0.89)
+		(250, 0.72)
 		(500, 0.37)
+		(750, 0.43)
 		(1000, 0.31)
+		(1250, 0.37)
 		(1500, 0.5)
 		(2000, 0.38)
+		(2500, 0.53)
+		(3000, 0.92)
 	};

### 2020-10-06 docs/paper/paper.tex
update: revision list

--- 2020-10-01 docs/paper/paper.tex
@@
 \usepackage{multirow}
+
+\tikzstyle directed=[postaction={decorate,decoration={markings, 
+		mark=at position 1 with {\arrow[arrowstyle]{stealth}}}}]
+
+\tikzstyle arrowstyle=[scale=1]
 
@@
 % The paper headers
-\markboth{Journal of Journal of Lightwave Technology,~Vol.~14, No.~8, August~2015}%
+\markboth{ Journal of Lightwave Technology,~Vol.~14, No.~8, August~2015}%
 {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
@@
 The air hole diameters are set to;  $d_1$= $0.45 \mu m$, $d_2$= $0.75 \mu m$, $d_3$= $0.35 \mu m$, and  $d_c$= $0.15$.
-The distance between air holes ($\lambda$) are fixed to $2 \mu m$.
+The distance between air holes ($\Lambda$) are fixed to $2 \mu m$.
 Initially, trapping the light (fundamental mode) into the core region is vital for mode quality.
@@
 
-		\addlegendentry{Actual}
 		\legend{}
+				legend style={anchor=north east,draw=none,fill=none,font=\tiny, at={(axis cs:670,1.55)}},
+
+		]
+
+		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE: 0.08721}
+		\addlegendimage{second}\addlegendentry{Proposed MSE: 0.18869 }
+
 		\end{axis}
@@
 		% their: 0.17491
+		legend style={anchor=north west,draw=none,fill=none,font=\tiny, at={(axis cs:670,1.55)}},
+		legend cell align=left,
+		]
+
+		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE:0.17491}
+		\addlegendimage{second}\addlegendentry{Proposed MSE:0.37049 }
+
 		\end{axis}
@@
 		%w/g: 0.11670
+		legend style={anchor=north west,draw=none,fill=none,font=\tiny, at={(axis cs:690,1.55)}},
+
+		]
+
+		\addlegendimage{first}\addlegendentry{Without GAN:0.18869}
+		\addlegendimage{second}\addlegendentry{With GAN:0.11670 }
 
@@
 		\legend{}
+				legend style={anchor=north west,draw=none,fill=none,font=\small, at={(axis cs:690,1.55)}},
+
+		]
+
+		\addlegendimage{first}\addlegendentry{Without GAN:0.32373}
+		\addlegendimage{second}\addlegendentry{With GAN:0.08664 }
 		\end{axis}

### 2020-10-06 docs/paper/paper.tex
fix: paper.tex

--- 2020-10-03 docs/paper/paper.tex
@@
 
-In our work, both the critic and the generator are fully connected to feed forward MLP models.
+In our work, both the critic and the generator are fully connected feed forward MLP models.
 The detailed parameters of the networks are given in Table \ref{tbl:anndetails}.

### 2020-10-10 docs/paper/paper.tex
* more fixes

@@
 According to Figure \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength.
-This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}.
-Regardless of this, both models have similar MSE due to the shift in the curve fit.
-Since the network is never exposed to this particular geometric configuration shift in the curve fit occurs.
+%This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}.
+Regardless of this, both models have similar MSE due to the shift in the curve fit. Since the network is never exposed to this particular geometric configuration shift in the curve fit occurs.
 
@@
 Adding further samples slightly reduces the performance while increasing the training time.
-The results of this experiment is demonstrated in Figure \ref{chart:gansamples}.
-The number of augmented samples may depend on the dataset that is used.
-However, in our experiments 1000 augmented samples produce good results in both datasets.
+The results of this experiment is demonstrated in Figure \ref{chart:gansamples} \hl{showing that the increasing number of augmented samples increases the performance to a point where it will start hurting the performance (>3000 samples).
+The reason behind this augmented samples are not perfect.
+They deviate from the actual data.
+However, up to a point, the performance impact of having low number of training samples out-weighs the imperfect data generated by GAN.} The number of augmented samples depends on the training samples that are available and can vary depending on the dataset used.
 
@@
 The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research article.
-In our experiments, due to optimized dataset the accuracy of the method proposed in Ref.
-\cite{paper0} is also improved.
+\hl{The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research; in the experiments, it surpassed the accuracy of the method proposed in }\cite{paper0}\hl{ on the dataset that method is optimized on.}
 

### 2020-10-10 docs/revision/review.tex
update: revision list
update: review-list
* reply

@@
 \fix AZ (double check first and update the paper)
+
+\fixed
 
@@
 
-\fix The names should be checked
+\fix The names should be checked ... \fixed
+
+\reply regarding the validation curves if we do not have space.
 
@@
 
-\fix Calculation is done AY will place values on graph.
+\fix Calculation is done AY will place values on graph... \fixed
 
@@
 	\textcolor{darkgreen}{ANSWER: } We can safely drop this argument, or reframe in a way that we are not absolutely sure as more research is required on this topic.
-\textcolor{red}{Following CK comment: Will be reframed as to what we have seen.}
+\textcolor{red}{Following CK comment: Will be reframed as to what we have seen.} CK: I have removed the sentence as the explanation could have easily extended to 4-5 lines.
+In the reply we can talk about doing experiments about this.
+\fixed
 
@@
 
+\textcolor{red}{CK: That is our claim.
+We are saying any random ANN cannot generalize to other planes, ours can.
+Also, in real life you don't have a dataset to design your ANN for.
+Optimizing an ANN for a single database is considered cheating as this never happens in reality.}
+
 \item \textbf{-MEDIUM-} Page 7, Line 45, Left Column- "In our experiments, due to optimized dataset the accuracy of the method proposed in Ref.
@@
 \textcolor{red}{Following CK comment: A fix added by HA, to be unfixed}
+\fixed{} We have to explain the problem in the reply.
 
@@
 We should tell him that the ANN structure may not be the most optimal}
+
+\reply
 
@@
 
+\fixed
+
 \item \textbf{-NOT CLEAR-} In Fig 6, in the case of SPR, the calculated loss spectrum has a large deviation under some specific parameters.

### 2020-10-10 docs/revision/review.tex
fix::16 - update::18

@@
 \textcolor{red}{Following CK comment: The argument will be dropped}
+\textcolor{darkgreen}{AZ: The argument is dropped; commented out in the latex file 'paper.tex' line 860}
+
+\fixed{}
 
@@
 I am not sure he is requesting experiments.
-We can avoid experiments by adding it to future works.}
+We can avoid experiments by adding it to future works.} \\
+\textcolor{blue}{AZ: We already mentioned and gave references demonstrating the effectiveness and flexibility of GANs.
+As they are becoming very common method in data augmentation, we have investigated its power to solve the problem at hand.
+Furthermore, our study was not comparative in nature with regards to data augmentation methods.
+\\
+Concerning other methods, more experiments , which are beyond the scope of this study, will be conducted to select the the optimal technique.}
 
@@
 
-\fixed
+\fixed{}
 

### 2020-10-14 docs/paper/paper.tex
fix::16 - update::18
* Replies for first 3 comments

@@
 Table  \ref{tbl:anndetails} summarizes the details of this model.
+\hl{The number of hidden layers and neurons are empirically determined to be able to estimate the loss curve while keeping the complexity of the network to minimum.}
 
@@
 This dataset contains 1117 samples.
-There are 7 inputs: refractive index of the core ($n_c$), wavelength ($\lambda$), hole diameter ($d$), pitch ($\Lambda$), and number of rings ($N_r$);  and outputs are effective index ($n_{eff}$), effective mode area ($A_{eff}$), dispersion ($D$), and the confinement loss ($\alpha_c$).
+\hl{There are 5 inputs}: refractive index of the core ($n_c$), wavelength ($\lambda$), hole diameter ($d$), pitch ($\Lambda$), and number of rings ($N_r$);  and outputs are effective index ($n_{eff}$), effective mode area ($A_{eff}$), dispersion ($D$), and the confinement loss ($\alpha_c$).
 We have only used confinement loss as the output.
@@
 In the experiments it is shown that the machine learning methods work few orders of magnitude faster than the simulation method.
-For different types of sensors, Convolutional and Recurrent neural networks can be of great advantage to discover the optimal patterns and geometrical shapes of the cladding air holes.
+
+%For different types of sensors, Convolutional and Recurrent neural networks can be of great advantage to discover the optimal patterns and geometrical shapes of the cladding air holes.
 This potential will be explored in a future work.

### 2020-10-14 docs/paper/paper.tex
update: va_curves: fixes

@@
 However, this number depends on the dataset and additional training may improve the results.
-Additionally, the benefit of augmented samples from the GAN phase is evident even at the training as they reduce the oscillations in the training loss.
+Additionally, the benefit of augmented samples from the GAN phase is evident even at the training as they reduce the \hl{fluctuations in the training loss and validation MSE}.
 
@@
 
+\begin{figure}
+	\begin{subfigure}{.48\textwidth}
+		\centering
+		\begin{tikzpicture}
+		\begin{axis}[
+		xlabel=Epochs, 
+		ylabel=Validation \space MSE,
+		width=\textwidth,
+		grid=both,
+		minor grid style={gray!25},
+		major grid style={gray!25},
+		ymax=3,
+		height=6cm,
+		no marks
+		]
+		\addplot[line width=1pt,solid,color=blue] %
+		table{data/va_loss_3k_our_data_without.txt};
+		\addlegendentry{Without GAN}
+
+		\addplot[line width=1pt,solid,color=red] %
+		table{data/va_loss_3k_our_data_with.txt};
+		\addlegendentry{With GAN}
+		\end{axis}
+		\end{tikzpicture}
+	\end{subfigure}
+
+	\caption{\hl{Validation MSE of the ANN model}}
+	\label{chart:validationmse}
+\end{figure}
+
 \begin{figure*}
@@
 		\end{tikzpicture}
-		\caption{Configuration estimation on SPR dataset.}
+		\captionsetup{justification=centering}
+		\caption{Configuration estimation on SPR dataset.
+		\\\hl{$ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 $ $ d1 = 0.45 um $ $ d2= 0.75 um$ $ d3 = 0.35 um $.}\\ \hl{ $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.75um $ $ d3 = 0.35um $.}
+		  }
 	\end{subfigure}
@@
 		\end{tikzpicture}
-		\caption{Configuration estimation on SPR dataset}
+		\captionsetup{justification=centering}
+		\caption{Configuration estimation on SPR dataset. 
+		\\ \hl{$n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 um $ $ d1 = 0.45 um $ $ d2= 0.75um $ $ d3 = 0.35um $.} \\ \hl{$n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.55um $ $ d3 = 0.15um $.}
+		}
 	\end{subfigure}

### 2020-10-14 docs/paper/jsen.tex
* Reviewer 1 reply is finished

\documentclass[journal,twoside,web]{ieeecolor}
\usepackage{jsen}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{wrapfig}
\usepackage[outdir=./]{epstopdf}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\markboth{\journalname, VOL. XX, NO. XX, XXXX 2017}
{Author \MakeLowercase{\textit{et al.}}: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS (February 2017)}
\definecolor{abstractbg}{rgb}{0.89804,0.94510,0.83137}
\setlength{\fboxrule}{0pt}
\setlength{\fboxsep}{0pt}
\begin{document}
\title{Preparation of Papers for IEEE TRANSACTIONS and JOURNALS (February 2017)}
\author{First A. Author, \IEEEmembership{Fellow, IEEE}, Second B. Author, and Third C. Author, Jr., \IEEEmembership{Member, IEEE}
\thanks{This paragraph of the first footnote will contain the date on 
which you submitted your paper for review. It will also contain support 
information, including sponsor and financial support acknowledgment. For 
example, ``This work was supported in part by the U.S. Department of 
Commerce under Grant BS123456.'' }
\thanks{The next few paragraphs should contain 
the authors' current affiliations, including current address and e-mail. For 
example, F. A. Author is with the National Institute of Standards and 
Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov). }
\thanks{S. B. Author, Jr., was with Rice University, Houston, TX 77005 USA. He is 
now with the Department of Physics, Colorado State University, Fort Collins, 
CO 80523 USA (e-mail: author@lamar.colostate.edu).}
\thanks{T. C. Author is with 
the Electrical Engineering Department, University of Colorado, Boulder, CO 
80309 USA, on leave from the National Research Institute for Metals, 
Tsukuba, Japan (e-mail: author@nrim.go.jp).}}

\IEEEtitleabstractindextext{%
\fcolorbox{abstractbg}{abstractbg}{%
\begin{minipage}{\textwidth}%
\begin{wrapfigure}[12]{r}{3in}%
\includegraphics[width=3in]{jsenga.png}%
\end{wrapfigure}%
\begin{abstract}
These instructions give you guidelines for preparing papers for 
IEEE Transactions and Journals. Use this document as a template if you are 
using \LaTeX. Otherwise, use this document as an 
instruction set. The electronic file of your paper will be formatted further 
at IEEE. Paper titles should be written in uppercase and lowercase letters, 
not all uppercase. Avoid writing long formulas with subscripts in the title; 
short formulas that identify the elements are fine (e.g., "Nd--Fe--B"). Do 
not write ``(Invited)'' in the title. Full names of authors are preferred in 
the author field, but are not required. Put a space between authors' 
initials. The abstract must be a concise yet comprehensive reflection of 
what is in your article. In particular, the abstract must be self-contained, 
without abbreviations, footnotes, or references. It should be a microcosm of 
the full article. The abstract must be between 150--250 words. Be sure that 
you adhere to these limits; otherwise, you will need to edit your abstract 
accordingly. The abstract must be written as one paragraph, and should not 
contain displayed mathematical equations or tabular material. The abstract 
should include three or four different keywords or phrases, as this will 
help readers to find it. It is important to avoid over-repetition of such 
phrases as this can result in a page being rejected by search engines. 
Ensure that your abstract reads well and is grammatically correct.
\end{abstract}

\begin{IEEEkeywords}
Enter key words or phrases in alphabetical 
order, separated by commas. For a list of suggested keywords, send a blank 
e-mail to keywords@ieee.org or visit \underline
{http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
\end{IEEEkeywords}
\end{minipage}}}

\maketitle

\section{Introduction}
\label{sec:introduction}
\IEEEPARstart{T}{his} document is a template for \LaTeX. If you are 
reading a paper or PDF version of this document, please download the 
electronic file, trans\_jour.tex, from the IEEE Web site at \underline
{http://www.ieee.org/authortools/trans\_jour.tex} so you can use it to prepare your manuscript. If 
you would prefer to use LaTeX, download IEEE's LaTeX style and sample files 
from the same Web page. You can also explore using the Overleaf editor at 
\underline
{https://www.overleaf.com/blog/278-how-to-use-overleaf-with-}\discretionary{}{}{}\underline
{ieee-collabratec-your-quick-guide-to-getting-started\#.}\discretionary{}{}{}\underline{xsVp6tpPkrKM9}

If your paper is intended for a conference, please contact your conference 
editor concerning acceptable word processor formats for your particular 
conference.

IEEE will do the final formatting of your paper. If your paper is intended 
for a conference, please observe the conference page limits.

\subsection{Abbreviations and Acronyms}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have already been defined in the abstract. Abbreviations 
such as IEEE, SI, ac, and dc do not have to be defined. Abbreviations that 
incorporate periods should not have spaces: write ``C.N.R.S.,'' not ``C. N. 
R. S.'' Do not use abbreviations in the title unless they are unavoidable 
(for example, ``IEEE'' in the title of this article).

\subsection{Other Recommendations}
Use one space after periods and colons. Hyphenate complex modifiers: 
``zero-field-cooled magnetization.'' Avoid dangling participles, such as, 
``Using \eqref{eq}, the potential was calculated.'' [It is not clear who or what 
used \eqref{eq}.] Write instead, ``The potential was calculated by using \eqref{eq},'' or 
``Using \eqref{eq}, we calculated the potential.''

Use a zero before decimal points: ``0.25,'' not ``.25.'' Use 
``cm$^{3}$,'' not ``cc.'' Indicate sample dimensions as ``0.1 cm 
$\times $ 0.2 cm,'' not ``0.1 $\times $ 0.2 cm$^{2}$.'' The 
abbreviation for ``seconds'' is ``s,'' not ``sec.'' Use 
``Wb/m$^{2}$'' or ``webers per square meter,'' not 
``webers/m$^{2}$.'' When expressing a range of values, write ``7 to 
9'' or ``7--9,'' not ``7$\sim $9.''

A parenthetical statement at the end of a sentence is punctuated outside of 
the closing parenthesis (like this). (A parenthetical sentence is punctuated 
within the parentheses.) In American English, periods and commas are within 
quotation marks, like ``this period.'' Other punctuation is ``outside''! 
Avoid contractions; for example, write ``do not'' instead of ``don't.'' The 
serial comma is preferred: ``A, B, and C'' instead of ``A, B and C.''

If you wish, you may write in the first person singular or plural and use 
the active voice (``I observed that $\ldots$'' or ``We observed that $\ldots$'' 
instead of ``It was observed that $\ldots$''). Remember to check spelling. If 
your native language is not English, please get a native English-speaking 
colleague to carefully proofread your paper.

Try not to use too many typefaces in the same article. You're writing
scholarly papers, not ransom notes. Also please remember that MathJax
can't handle really weird typefaces.

\subsection{Equations}
Number equations consecutively with equation numbers in parentheses flush 
with the right margin, as in \eqref{eq}. To make your equations more 
compact, you may use the solidus (~/~), the exp function, or appropriate 
exponents. Use parentheses to avoid ambiguities in denominators. Punctuate 
equations when they are part of a sentence, as in
\begin{equation}E=mc^2.\label{eq}\end{equation}

Be sure that the symbols in your equation have been defined before the 
equation appears or immediately following. Italicize symbols ($T$ might refer 
to temperature, but T is the unit tesla). Refer to ``\eqref{eq},'' not ``Eq. \eqref{eq}'' 
or ``equation \eqref{eq},'' except at the beginning of a sentence: ``Equation \eqref{eq} 
is $\ldots$ .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

If you are submitting your paper to a colorized journal, you can use
the following two lines at the start of the article to ensure its
appearance resembles the final copy:

\smallskip\noindent
\begin{small}
\begin{tabular}{l}
\verb+\+\texttt{documentclass[journal,twoside,web]\{ieeecolor\}}\\
\verb+\+\texttt{usepackage\{\textit{Journal\_Name}\}}
\end{tabular}
\end{small}

\section{Units}
Use either SI (MKS) or CGS as primary units. (SI units are strongly 
encouraged.) English units may be used as secondary units (in parentheses). 
This applies to papers in data storage. For example, write ``15 
Gb/cm$^{2}$ (100 Gb/in$^{2})$.'' An exception is when 
English units are used as identifiers in trade, such as ``3\textonehalf-in 
disk drive.'' Avoid combining SI and CGS units, such as current in amperes 
and magnetic field in oersteds. This often leads to confusion because 
equations do not balance dimensionally. If you must use mixed units, clearly 
state the units for each quantity in an equation.

The SI unit for magnetic field strength $H$ is A/m. However, if you wish to use 
units of T, either refer to magnetic flux density $B$ or magnetic field 
strength symbolized as $\mu _{0}H$. Use the center dot to separate 
compound units, e.g., ``A$\cdot $m$^{2}$.''

\section{Some Common Mistakes}
The word ``data'' is plural, not singular. The subscript for the 
permeability of vacuum $\mu _{0}$ is zero, not a lowercase letter 
``o.'' The term for residual magnetization is ``remanence''; the adjective 
is ``remanent''; do not write ``remnance'' or ``remnant.'' Use the word 
``micrometer'' instead of ``micron.'' A graph within a graph is an 
``inset,'' not an ``insert.'' The word ``alternatively'' is preferred to the 
word ``alternately'' (unless you really mean something that alternates). Use 
the word ``whereas'' instead of ``while'' (unless you are referring to 
simultaneous events). Do not use the word ``essentially'' to mean 
``approximately'' or ``effectively.'' Do not use the word ``issue'' as a 
euphemism for ``problem.'' When compositions are not specified, separate 
chemical symbols by en-dashes; for example, ``NiMn'' indicates the 
intermetallic compound Ni$_{0.5}$Mn$_{0.5}$ whereas 
``Ni--Mn'' indicates an alloy of some composition 
Ni$_{x}$Mn$_{1-x}$.

\begin{figure}[!t]
\centerline{\includegraphics[width=\columnwidth]{fig1.png}}
\caption{Magnetization as a function of applied field.
It is good practice to explain the significance of the figure in the caption.}
\label{fig1}
\end{figure}

Be aware of the different meanings of the homophones ``affect'' (usually a 
verb) and ``effect'' (usually a noun), ``complement'' and ``compliment,'' 
``discreet'' and ``discrete,'' ``principal'' (e.g., ``principal 
investigator'') and ``principle'' (e.g., ``principle of measurement''). Do 
not confuse ``imply'' and ``infer.''

Prefixes such as ``non,'' ``sub,'' ``micro,'' ``multi,'' and ``ultra'' are 
not independent words; they should be joined to the words they modify, 
usually without a hyphen. There is no period after the ``et'' in the Latin 
abbreviation ``\emph{et al.}'' (it is also italicized). The abbreviation ``i.e.,'' means 
``that is,'' and the abbreviation ``e.g.,'' means ``for example'' (these 
abbreviations are not italicized).

A general IEEE styleguide is available at \underline{http://www.ieee.org/authortools}.

\section{Guidelines for Graphics Preparation and Submission}
\label{sec:guidelines}

\subsection{Types of Graphics}
The following list outlines the different types of graphics published in 
IEEE journals. They are categorized based on their construction, and use of 
color/shades of gray:

\subsubsection{Color/Grayscale figures}
{Figures that are meant to appear in color, or shades of black/gray. Such 
figures may include photographs, illustrations, multicolor graphs, and 
flowcharts.}

\subsubsection{Line Art figures}
{Figures that are composed of only black lines and shapes. These figures 
should have no shades or half-tones of gray, only black and white.}

\subsubsection{Author photos}
{Head and shoulders shots of authors that appear at the end of our papers. }

\subsubsection{Tables}
{Data charts which are typically black and white, but sometimes include 
color.}

\begin{table}
\caption{Units for Magnetic Properties}
\label{table}
\setlength{\tabcolsep}{3pt}
\begin{tabular}{|p{25pt}|p{75pt}|p{115pt}|}
\hline
Symbol& 
Quantity& 
Conversion from Gaussian and \par CGS EMU to SI $^{\mathrm{a}}$ \\
\hline
$\Phi $& 
magnetic flux& 
1 Mx $\to  10^{-8}$ Wb $= 10^{-8}$ V$\cdot $s \\
$B$& 
magnetic flux density, \par magnetic induction& 
1 G $\to  10^{-4}$ T $= 10^{-4}$ Wb/m$^{2}$ \\
$H$& 
magnetic field strength& 
1 Oe $\to  10^{3}/(4\pi )$ A/m \\
$m$& 
magnetic moment& 
1 erg/G $=$ 1 emu \par $\to 10^{-3}$ A$\cdot $m$^{2} = 10^{-3}$ J/T \\
$M$& 
magnetization& 
1 erg/(G$\cdot $cm$^{3}) =$ 1 emu/cm$^{3}$ \par $\to 10^{3}$ A/m \\
4$\pi M$& 
magnetization& 
1 G $\to  10^{3}/(4\pi )$ A/m \\
$\sigma $& 
specific magnetization& 
1 erg/(G$\cdot $g) $=$ 1 emu/g $\to $ 1 A$\cdot $m$^{2}$/kg \\
$j$& 
magnetic dipole \par moment& 
1 erg/G $=$ 1 emu \par $\to 4\pi \times  10^{-10}$ Wb$\cdot $m \\
$J$& 
magnetic polarization& 
1 erg/(G$\cdot $cm$^{3}) =$ 1 emu/cm$^{3}$ \par $\to 4\pi \times  10^{-4}$ T \\
$\chi , \kappa $& 
susceptibility& 
1 $\to  4\pi $ \\
$\chi_{\rho }$& 
mass susceptibility& 
1 cm$^{3}$/g $\to  4\pi \times  10^{-3}$ m$^{3}$/kg \\
$\mu $& 
permeability& 
1 $\to  4\pi \times  10^{-7}$ H/m \par $= 4\pi \times  10^{-7}$ Wb/(A$\cdot $m) \\
$\mu_{r}$& 
relative permeability& 
$\mu \to \mu_{r}$ \\
$w, W$& 
energy density& 
1 erg/cm$^{3} \to  10^{-1}$ J/m$^{3}$ \\
$N, D$& 
demagnetizing factor& 
1 $\to  1/(4\pi )$ \\
\hline
\multicolumn{3}{p{251pt}}{Vertical lines are optional in tables. Statements that serve as captions for 
the entire table do not need footnote letters. }\\
\multicolumn{3}{p{251pt}}{$^{\mathrm{a}}$Gaussian units are the same as cg emu for magnetostatics; Mx 
$=$ maxwell, G $=$ gauss, Oe $=$ oersted; Wb $=$ weber, V $=$ volt, s $=$ 
second, T $=$ tesla, m $=$ meter, A $=$ ampere, J $=$ joule, kg $=$ 
kilogram, H $=$ henry.}
\end{tabular}
\label{tab1}
\end{table}

\subsection{Multipart figures}
Figures compiled of more than one sub-figure presented side-by-side, or 
stacked. If a multipart figure is made up of multiple figure
types (one part is lineart, and another is grayscale or color) the figure 
should meet the stricter guidelines.

\subsection{File Formats For Graphics}\label{formats}
Format and save your graphics using a suitable graphics processing program 
that will allow you to create the images as PostScript (PS), Encapsulated 
PostScript (.EPS), Tagged Image File Format (.TIFF), Portable Document 
Format (.PDF), Portable Network Graphics (.PNG), or Metapost (.MPS), sizes them, and adjusts 
the resolution settings. When 
submitting your final paper, your graphics should all be submitted 
individually in one of these formats along with the manuscript.

\subsection{Sizing of Graphics}
Most charts, graphs, and tables are one column wide (3.5 inches/88 
millimeters/21 picas) or page wide (7.16 inches/181 millimeters/43 
picas). The maximum depth a graphic can be is 8.5 inches (216 millimeters/54
picas). When choosing the depth of a graphic, please allow space for a 
caption. Figures can be sized between column and page widths if the author 
chooses, however it is recommended that figures are not sized less than 
column width unless when necessary.

There is currently one publication with column measurements that do not 
coincide with those listed above. Proceedings of the IEEE has a column 
measurement of 3.25 inches (82.5 millimeters/19.5 picas).

The final printed size of author photographs is exactly
1 inch wide by 1.25 inches tall (25.4 millimeters$\,\times\,$31.75 millimeters/6 
picas$\,\times\,$7.5 picas). Author photos printed in editorials measure 1.59 inches 
wide by 2 inches tall (40 millimeters$\,\times\,$50 millimeters/9.5 picas$\,\times\,$12 
picas).

\subsection{Resolution }
The proper resolution of your figures will depend on the type of figure it 
is as defined in the ``Types of Figures'' section. Author photographs, 
color, and grayscale figures should be at least 300dpi. Line art, including 
tables should be a minimum of 600dpi.

\subsection{Vector Art}
In order to preserve the figures' integrity across multiple computer 
platforms, we accept files in the following formats: .EPS/.PDF/.PS. All 
fonts must be embedded or text converted to outlines in order to achieve the 
best-quality results.

\subsection{Color Space}
The term color space refers to the entire sum of colors that can be 
represented within the said medium. For our purposes, the three main color 
spaces are Grayscale, RGB (red/green/blue) and CMYK 
(cyan/magenta/yellow/black). RGB is generally used with on-screen graphics, 
whereas CMYK is used for printing purposes.

All color figures should be generated in RGB or CMYK color space. Grayscale 
images should be submitted in Grayscale color space. Line art may be 
provided in grayscale OR bitmap colorspace. Note that ``bitmap colorspace'' 
and ``bitmap file format'' are not the same thing. When bitmap color space 
is selected, .TIF/.TIFF/.PNG are the recommended file formats.

\subsection{Accepted Fonts Within Figures}
When preparing your graphics IEEE suggests that you use of one of the 
following Open Type fonts: Times New Roman, Helvetica, Arial, Cambria, and 
Symbol. If you are supplying EPS, PS, or PDF files all fonts must be 
embedded. Some fonts may only be native to your operating system; without 
the fonts embedded, parts of the graphic may be distorted or missing.

A safe option when finalizing your figures is to strip out the fonts before 
you save the files, creating ``outline'' type. This converts fonts to 
artwork what will appear uniformly on any screen.

\subsection{Using Labels Within Figures}

\subsubsection{Figure Axis labels }
Figure axis labels are often a source of confusion. Use words rather than 
symbols. As an example, write the quantity ``Magnetization,'' or 
``Magnetization M,'' not just ``M.'' Put units in parentheses. Do not label 
axes only with units. As in Fig. 1, for example, write ``Magnetization 
(A/m)'' or ``Magnetization (A$\cdot$m$^{-1}$),'' not just ``A/m.'' Do not label axes with a ratio of quantities and 
units. For example, write ``Temperature (K),'' not ``Temperature/K.''

Multipliers can be especially confusing. Write ``Magnetization (kA/m)'' or 
``Magnetization (10$^{3}$ A/m).'' Do not write ``Magnetization 
(A/m)$\,\times\,$1000'' because the reader would not know whether the top 
axis label in Fig. 1 meant 16000 A/m or 0.016 A/m. Figure labels should be 
legible, approximately 8 to 10 point type.

\subsubsection{Subfigure Labels in Multipart Figures and Tables}
Multipart figures should be combined and labeled before final submission. 
Labels should appear centered below each subfigure in 8 point Times New 
Roman font in the format of (a) (b) (c).

\subsection{File Naming}
Figures (line artwork or photographs) should be named starting with the 
first 5 letters of the author's last name. The next characters in the 
filename should be the number that represents the sequential 
location of this image in your article. For example, in author 
``Anderson's'' paper, the first three figures would be named ander1.tif, 
ander2.tif, and ander3.ps.

Tables should contain only the body of the table (not the caption) and 
should be named similarly to figures, except that `.t' is inserted 
in-between the author's name and the table number. For example, author 
Anderson's first three tables would be named ander.t1.tif, ander.t2.ps, 
ander.t3.eps.

Author photographs should be named using the first five characters of the 
pictured author's last name. For example, four author photographs for a 
paper may be named: oppen.ps, moshc.tif, chen.eps, and duran.pdf.

If two authors or more have the same last name, their first initial(s) can 
be substituted for the fifth, fourth, third$\ldots$ letters of their surname 
until the degree where there is differentiation. For example, two authors 
Michael and Monica Oppenheimer's photos would be named oppmi.tif, and 
oppmo.eps.

\subsection{Referencing a Figure or Table Within Your Paper}
When referencing your figures and tables within your paper, use the 
abbreviation ``Fig.'' even at the beginning of a sentence. Do not abbreviate 
``Table.'' Tables should be numbered with Roman Numerals.

\subsection{Checking Your Figures: The IEEE Graphics Analyzer}
The IEEE Graphics Analyzer enables authors to pre-screen their graphics for 
compliance with IEEE Transactions and Journals standards before submission. 
The online tool, located at
\underline{http://graphicsqc.ieee.org/}, allows authors to 
upload their graphics in order to check that each file is the correct file 
format, resolution, size and colorspace; that no fonts are missing or 
corrupt; that figures are not compiled in layers or have transparency, and 
that they are named according to the IEEE Transactions and Journals naming 
convention. At the end of this automated process, authors are provided with 
a detailed report on each graphic within the web applet, as well as by 
email.

For more information on using the Graphics Analyzer or any other graphics 
related topic, contact the IEEE Graphics Help Desk by e-mail at 
graphics@ieee.org.

\subsection{Submitting Your Graphics}
Because IEEE will do the final formatting of your paper,
you do not need to position figures and tables at the top and bottom of each 
column. In fact, all figures, figure captions, and tables can be placed at 
the end of your paper. In addition to, or even in lieu of submitting figures 
within your final manuscript, figures should be submitted individually, 
separate from the manuscript in one of the file formats listed above in 
Section \ref{formats}. Place figure captions below the figures; place table titles 
above the tables. Please do not include captions as part of the figures, or 
put them in ``text boxes'' linked to the figures. Also, do not place borders 
around the outside of your figures.

\subsection{Color Processing/Printing in IEEE Journals}
All IEEE Transactions, Journals, and Letters allow an author to publish 
color figures on IEEE Xplore\textregistered\ at no charge, and automatically 
convert them to grayscale for print versions. In most journals, figures and 
tables may alternatively be printed in color if an author chooses to do so. 
Please note that this service comes at an extra expense to the author. If 
you intend to have print color graphics, include a note with your final 
paper indicating which figures or tables you would like to be handled that 
way, and stating that you are willing to pay the additional fee.

\section{Conclusion}
A conclusion section is not required. Although a conclusion may review the 
main points of the paper, do not replicate the abstract as the conclusion. A 
conclusion might elaborate on the importance of the work or suggest 
applications and extensions.

\appendices

Appendixes, if needed, appear before the acknowledgment.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in American English is 
without an ``e'' after the ``g.'' Use the singular heading even if you have 
many acknowledgments. Avoid expressions such as ``One of us (S.B.A.) would 
like to thank $\ldots$ .'' Instead, write ``F. A. Author thanks $\ldots$ .'' In most 
cases, sponsor and financial support acknowledgments are placed in the 
unnumbered footnote on the first page, not here.

\section*{References and Footnotes}

\subsection{References}
References need not be cited in text. When they are, they appear on the 
line, in square brackets, inside the punctuation. Multiple references are 
each numbered with separate brackets. When citing a section in a book, 
please give the relevant page numbers. In text, refer simply to the 
reference number. Do not use ``Ref.'' or ``reference'' except at the 
beginning of a sentence: ``Reference \cite{b3} shows $\ldots$ .'' Please do not use 
automatic endnotes in \emph{Word}, rather, type the reference list at the end of the 
paper using the ``References'' style.

Reference numbers are set flush left and form a column of their own, hanging 
out beyond the body of the reference. The reference numbers are on the line, 
enclosed in square brackets. In all references, the given name of the author 
or editor is abbreviated to the initial only and precedes the last name. Use 
them all; use \emph{et al.} only if names are not given. Use commas around Jr., 
Sr., and III in names. Abbreviate conference titles. When citing IEEE 
transactions, provide the issue number, page range, volume number, year, 
and/or month if available. When referencing a patent, provide the day and 
the month of issue, or application. References may not include all 
information; please obtain and include relevant information. Do not combine 
references. There must be only one reference with each number. If there is a 
URL included with the print reference, it can be included at the end of the 
reference.

Other than books, capitalize only the first word in a paper title, except 
for proper nouns and element symbols. For papers published in translation 
journals, please give the English citation first, followed by the original 
foreign-language citation See the end of this document for formats and 
examples of common references. For a complete discussion of references and 
their formats, see the IEEE style manual at
\underline{http://www.ieee.org/authortools}.

\subsection{Footnotes}
Number footnotes separately in superscript numbers.\footnote{It is recommended that footnotes be avoided (except for 
the unnumbered footnote with the receipt date on the first page). Instead, 
try to integrate the footnote information into the text.} Place the actual 
footnote at the bottom of the column in which it is cited; do not put 
footnotes in the reference list (endnotes). Use letters for table footnotes 
(see Table \ref{table}).

\section{Submitting Your Paper for Review}

\subsection{Final Stage}
When you submit your final version (after your paper has been accepted), 
print it in two-column format, including figures and tables. You must also 
send your final manuscript on a disk, via e-mail, or through a Web 
manuscript submission system as directed by the society contact. You may use 
\emph{Zip} for large files, or compress files using \emph{Compress, Pkzip, Stuffit,} or \emph{Gzip.}

Also, send a sheet of paper or PDF with complete contact information for all 
authors. Include full mailing addresses, telephone numbers, fax numbers, and 
e-mail addresses. This information will be used to send each author a 
complimentary copy of the journal in which the paper appears. In addition, 
designate one author as the ``corresponding author.'' This is the author to 
whom proofs of the paper will be sent. Proofs are sent to the corresponding 
author only.

\subsection{Review Stage Using ScholarOne\textregistered\ Manuscripts}
Contributions to the Transactions, Journals, and Letters may be submitted 
electronically on IEEE's on-line manuscript submission and peer-review 
system, ScholarOne\textregistered\ Manuscripts. You can get a listing of the 
publications that participate in ScholarOne at 
\underline{http://www.ieee.org/publications\_standards/publications/}\discretionary{}{}{}\underline{authors/authors\_submission.html}.
First check if you have an existing account. If there is none, please create 
a new account. After logging in, go to your Author Center and click ``Submit 
First Draft of a New Manuscript.''

Along with other information, you will be asked to select the subject from a 
pull-down list. Depending on the journal, there are various steps to the 
submission process; you must complete all steps for a complete submission. 
At the end of each step you must click ``Save and Continue''; just uploading 
the paper is not sufficient. After the last step, you should see a 
confirmation that the submission is complete. You should also receive an 
e-mail confirmation. For inquiries regarding the submission of your paper on 
ScholarOne Manuscripts, please contact oprs-support@ieee.org or call +1 732 
465 5861.

ScholarOne Manuscripts will accept files for review in various formats. 
Please check the guidelines of the specific journal for which you plan to 
submit.

You will be asked to file an electronic copyright form immediately upon 
completing the submission process (authors are responsible for obtaining any 
security clearances). Failure to submit the electronic copyright could 
result in publishing delays later. You will also have the opportunity to 
designate your article as ``open access'' if you agree to pay the IEEE open 
access fee.

\subsection{Final Stage Using ScholarOne Manuscripts}
Upon acceptance, you will receive an email with specific instructions 
regarding the submission of your final files. To avoid any delays in 
publication, please be sure to follow these instructions. Most journals 
require that final submissions be uploaded through ScholarOne Manuscripts, 
although some may still accept final submissions via email. Final 
submissions should include source files of your accepted manuscript, high 
quality graphic files, and a formatted pdf file. If you have any questions 
regarding the final submission process, please contact the administrative 
contact for the journal.

In addition to this, upload a file with complete contact information for all 
authors. Include full mailing addresses, telephone numbers, fax numbers, and 
e-mail addresses. Designate the author who submitted the manuscript on 
ScholarOne Manuscripts as the ``corresponding author.'' This is the only 
author to whom proofs of the paper will be sent.

\subsection{Copyright Form}
Authors must submit an electronic IEEE Copyright Form (eCF) upon submitting 
their final manuscript files. You can access the eCF system through your 
manuscript submission system or through the Author Gateway. You are 
responsible for obtaining any necessary approvals and/or security 
clearances. For additional information on intellectual property rights, 
visit the IEEE Intellectual Property Rights department web page at 
\underline{http://www.ieee.org/publications\_standards/publications/rights/}\discretionary{}{}{}\underline{index.html}.

\section{IEEE Publishing Policy}
The general IEEE policy requires that authors should only submit original 
work that has neither appeared elsewhere for publication, nor is under 
review for another refereed publication. The submitting author must disclose 
all prior publication(s) and current submissions when submitting a 
manuscript. Do not publish ``preliminary'' data or results. The submitting 
author is responsible for obtaining agreement of all coauthors and any 
consent required from employers or sponsors before submitting an article. 
The IEEE Transactions and Journals Department strongly discourages courtesy 
authorship; it is the obligation of the authors to cite only relevant prior 
work.

The IEEE Transactions and Journals Department does not publish conference 
records or proceedings, but can publish articles related to conferences that 
have undergone rigorous peer review. Minimally, two reviews are required for 
every article submitted for peer review.

\section{Publication Principles}
The two types of contents of that are published are; 1) peer-reviewed and 2) 
archival. The Transactions and Journals Department publishes scholarly 
articles of archival value as well as tutorial expositions and critical 
reviews of classical subjects and topics of current interest.

Authors should consider the following points:

\begin{enumerate}
\item Technical papers submitted for publication must advance the state of knowledge and must cite relevant prior work. 
\item The length of a submitted paper should be commensurate with the importance, or appropriate to the complexity, of the work. For example, an obvious extension of previously published work might not be appropriate for publication or might be adequately treated in just a few pages.
\item Authors must convince both peer reviewers and the editors of the scientific and technical merit of a paper; the standards of proof are higher when extraordinary or unexpected results are reported. 
\item Because replication is required for scientific progress, papers submitted for publication must provide sufficient information to allow readers to perform similar experiments or calculations and 
use the reported results. Although not everything need be disclosed, a paper 
must contain new, useable, and fully described information. For example, a 
specimen's chemical composition need not be reported if the main purpose of 
a paper is to introduce a new measurement technique. Authors should expect 
to be challenged by reviewers if the results are not supported by adequate 
data and critical details.
\item Papers that describe ongoing work or announce the latest technical achievement, which are suitable for presentation at a professional conference, may not be appropriate for publication.
\end{enumerate}

\section{Reference Examples}

\begin{itemize}

\item \emph{Basic format for books:}\\
J. K. Author, ``Title of chapter in the book,'' in \emph{Title of His Published Book, x}th ed. City of Publisher, (only U.S. State), Country: Abbrev. of Publisher, year, ch. $x$, sec. $x$, pp. \emph{xxx--xxx.}\\
See \cite{b1,b2}.

\item \emph{Basic format for periodicals:}\\
J. K. Author, ``Name of paper,'' \emph{Abbrev. Title of Periodical}, vol. \emph{x, no}. $x, $pp\emph{. xxx--xxx, }Abbrev. Month, year, DOI. 10.1109.\emph{XXX}.123456.\\
See \cite{b3}--\cite{b5}.

\item \emph{Basic format for reports:}\\
J. K. Author, ``Title of report,'' Abbrev. Name of Co., City of Co., Abbrev. State, Country, Rep. \emph{xxx}, year.\\
See \cite{b6,b7}.

\item \emph{Basic format for handbooks:}\\
\emph{Name of Manual/Handbook, x} ed., Abbrev. Name of Co., City of Co., Abbrev. State, Country, year, pp. \emph{xxx--xxx.}\\
See \cite{b8,b9}.

\item \emph{Basic format for books (when available online):}\\
J. K. Author, ``Title of chapter in the book,'' in \emph{Title of
Published Book}, $x$th ed. City of Publisher, State, Country: Abbrev.
of Publisher, year, ch. $x$, sec. $x$, pp. \emph{xxx--xxx}. [Online].
Available: \underline{http://www.web.com}\\
See \cite{b10}--\cite{b13}.

\item \emph{Basic format for journals (when available online):}\\
J. K. Author, ``Name of paper,'' \emph{Abbrev. Title of Periodical}, vol. $x$, no. $x$, pp. \emph{xxx--xxx}, Abbrev. Month, year. Accessed on: Month, Day, year, DOI: 10.1109.\emph{XXX}.123456, [Online].\\
See \cite{b14}--\cite{b16}.

\item \emph{Basic format for papers presented at conferences (when available online): }\\
J.K. Author. (year, month). Title. presented at abbrev. conference title. [Type of Medium]. Available: site/path/file\\
See \cite{b17}.

\item \emph{Basic format for reports and handbooks (when available online):}\\
J. K. Author. ``Title of report,'' Company. City, State, Country. Rep. no., (optional: vol./issue), Date. [Online] Available: site/path/file\\
See \cite{b18,b19}.

\item \emph{Basic format for computer programs and electronic documents (when available online): }\\
Legislative body. Number of Congress, Session. (year, month day). \emph{Number of bill or resolution}, \emph{Title}. [Type of medium]. Available: site/path/file\\
\textbf{\emph{NOTE: }ISO recommends that capitalization follow the accepted practice for the language or script in which the information is given.}\\
See \cite{b20}.

\item \emph{Basic format for patents (when available online):}\\
Name of the invention, by inventor's name. (year, month day). Patent Number [Type of medium]. Available: site/path/file\\
See \cite{b21}.

\item \emph{Basic format}\emph{for conference proceedings (published):}\\
J. K. Author, ``Title of paper,'' in \emph{Abbreviated Name of Conf.}, City of Conf., Abbrev. State (if given), Country, year, pp. \emph{xxxxxx.}\\
See \cite{b22}.

\item \emph{Example for papers presented at conferences (unpublished):}\\
See \cite{b23}.

\item \emph{Basic format for patents}$:$\\
J. K. Author, ``Title of patent,'' U.S. Patent \emph{x xxx xxx}, Abbrev. Month, day, year.\\
See \cite{b24}.

\item \emph{Basic format for theses (M.S.) and dissertations (Ph.D.):}
\begin{enumerate}
\item J. K. Author, ``Title of thesis,'' M.S. thesis, Abbrev. Dept., Abbrev. Univ., City of Univ., Abbrev. State, year.
\item J. K. Author, ``Title of dissertation,'' Ph.D. dissertation, Abbrev. Dept., Abbrev. Univ., City of Univ., Abbrev. State, year.
\end{enumerate}
See \cite{b25,b26}.

\item \emph{Basic format for the most common types of unpublished references:}
\begin{enumerate}
\item J. K. Author, private communication, Abbrev. Month, year.
\item J. K. Author, ``Title of paper,'' unpublished.
\item J. K. Author, ``Title of paper,'' to be published.
\end{enumerate}
See \cite{b27}--\cite{b29}.

\item \emph{Basic formats for standards:}
\begin{enumerate}
\item \emph{Title of Standard}, Standard number, date.
\item \emph{Title of Standard}, Standard number, Corporate author, location, date.
\end{enumerate}
See \cite{b30,b31}.

\item \emph{Article number in~reference examples:}\\
See \cite{b32,b33}.

\item \emph{Example when using et al.:}\\
See \cite{b34}.

\end{itemize}

\begin{thebibliography}{00}

\bibitem{b1} G. O. Young, ``Synthetic structure of industrial plastics,'' in \emph{Plastics,} 2\textsuperscript{nd} ed., vol. 3, J. Peters, Ed. New York, NY, USA: McGraw-Hill, 1964, pp. 15--64.

\bibitem{b2} W.-K. Chen, \emph{Linear Networks and Systems.} Belmont, CA, USA: Wadsworth, 1993, pp. 123--135.

\bibitem{b3} J. U. Duncombe, ``Infrared navigation---Part I: An assessment of feasibility,'' \emph{IEEE Trans. Electron Devices}, vol. ED-11, no. 1, pp. 34--39, Jan. 1959, 10.1109/TED.2016.2628402.

\bibitem{b4} E. P. Wigner, ``Theory of traveling-wave optical laser,'' \emph{Phys. Rev}., vol. 134, pp. A635--A646, Dec. 1965.

\bibitem{b5} E. H. Miller, ``A note on reflector arrays,'' \emph{IEEE Trans. Antennas Propagat}., to be published.

\bibitem{b6} E. E. Reber, R. L. Michell, and C. J. Carter, ``Oxygen absorption in the earth's atmosphere,'' Aerospace Corp., Los Angeles, CA, USA, Tech. Rep. TR-0200 (4230-46)-3, Nov. 1988.

\bibitem{b7} J. H. Davis and J. R. Cogdell, ``Calibration program for the 16-foot antenna,'' Elect. Eng. Res. Lab., Univ. Texas, Austin, TX, USA, Tech. Memo. NGL-006-69-3, Nov. 15, 1987.

\bibitem{b8} \emph{Transmission Systems for Communications}, 3\textsuperscript{rd} ed., Western Electric Co., Winston-Salem, NC, USA, 1985, pp. 44--60.

\bibitem{b9} \emph{Motorola Semiconductor Data Manual}, Motorola Semiconductor Products Inc., Phoenix, AZ, USA, 1989.

\bibitem{b10} G. O. Young, ``Synthetic structure of industrial
plastics,'' in Plastics, vol. 3, Polymers of Hexadromicon, J. Peters,
Ed., 2\textsuperscript{nd} ed. New York, NY, USA: McGraw-Hill, 1964, pp. 15-64.
[Online]. Available:
\underline{http://www.bookref.com}.

\bibitem{b11} \emph{The Founders' Constitution}, Philip B. Kurland
and Ralph Lerner, eds., Chicago, IL, USA: Univ. Chicago Press, 1987.
[Online]. Available: \underline{http://press-pubs.uchicago.edu/founders/}

\bibitem{b12} The Terahertz Wave eBook. ZOmega Terahertz Corp., 2014.
[Online]. Available:
\underline{http://dl.z-thz.com/eBook/zomega\_ebook\_pdf\_1206\_sr.pdf}. Accessed on: May 19, 2014.

\bibitem{b13} Philip B. Kurland and Ralph Lerner, eds., \emph{The
Founders' Constitution.} Chicago, IL, USA: Univ. of Chicago Press,
1987, Accessed on: Feb. 28, 2010, [Online] Available:
\underline{http://press-pubs.uchicago.edu/founders/}

\bibitem{b14} J. S. Turner, ``New directions in communications,'' \emph{IEEE J. Sel. Areas Commun}., vol. 13, no. 1, pp. 11-23, Jan. 1995.

\bibitem{b15} W. P. Risk, G. S. Kino, and H. J. Shaw, ``Fiber-optic frequency shifter using a surface acoustic wave incident at an oblique angle,'' \emph{Opt. Lett.}, vol. 11, no. 2, pp. 115--117, Feb. 1986.

\bibitem{b16} P. Kopyt \emph{et al., ``}Electric properties of graphene-based conductive layers from DC up to terahertz range,'' \emph{IEEE THz Sci. Technol.,} to be published. DOI: 10.1109/TTHZ.2016.2544142.

\bibitem{b17} PROCESS Corporation, Boston, MA, USA. Intranets:
Internet technologies deployed behind the firewall for corporate
productivity. Presented at INET96 Annual Meeting. [Online].
Available: \underline{http://home.process.com/Intranets/wp2.htp}

\bibitem{b18} R. J. Hijmans and J. van Etten, ``Raster: Geographic analysis and modeling with raster data,'' R Package Version 2.0-12, Jan. 12, 2012. [Online]. Available: \underline {http://CRAN.R-project.org/package=raster}

\bibitem{b19} Teralyzer. Lytera UG, Kirchhain, Germany [Online].
Available:
\underline{http://www.lytera.de/Terahertz\_THz\_Spectroscopy.php?id=home}, Accessed on: Jun. 5, 2014

\bibitem{b20} U.S. House. 102\textsuperscript{nd} Congress, 1\textsuperscript{st} Session. (1991, Jan. 11). \emph{H. Con. Res. 1, Sense of the Congress on Approval of}  \emph{Military Action}. [Online]. Available: LEXIS Library: GENFED File: BILLS

\bibitem{b21} Musical toothbrush with mirror, by L.M.R. Brooks. (1992, May 19). Patent D 326 189 [Online]. Available: NEXIS Library: LEXPAT File: DES

\bibitem{b22} D. B. Payne and J. R. Stern, ``Wavelength-switched pas- sively coupled single-mode optical network,'' in \emph{Proc. IOOC-ECOC,} Boston, MA, USA, 1985, pp. 585--590.

\bibitem{b23} D. Ebehard and E. Voges, ``Digital single sideband detection for interferometric sensors,'' presented at the \emph{2\textsuperscript{nd} Int. Conf. Optical Fiber Sensors,} Stuttgart, Germany, Jan. 2-5, 1984.

\bibitem{b24} G. Brandli and M. Dick, ``Alternating current fed power supply,'' U.S. Patent 4 084 217, Nov. 4, 1978.

\bibitem{b25} J. O. Williams, ``Narrow-band analyzer,'' Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, USA, 1993.

\bibitem{b26} N. Kawasaki, ``Parametric study of thermal and chemical nonequilibrium nozzle flow,'' M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.

\bibitem{b27} A. Harrison, private communication, May 1995.

\bibitem{b28} B. Smith, ``An approach to graphs of linear forms,'' unpublished.

\bibitem{b29} A. Brahms, ``Representation error for real numbers in binary computer arithmetic,'' IEEE Computer Group Repository, Paper R-67-85.

\bibitem{b30} IEEE Criteria for Class IE Electric Systems, IEEE Standard 308, 1969.

\bibitem{b31} Letter Symbols for Quantities, ANSI Standard Y10.5-1968.

\bibitem{b32} R. Fardel, M. Nagel, F. Nuesch, T. Lippert, and A. Wokaun, ``Fabrication of organic light emitting diode pixels by laser-assisted forward transfer,'' \emph{Appl. Phys. Lett.}, vol. 91, no. 6, Aug. 2007, Art. no. 061103.~

\bibitem{b33} J. Zhang and N. Tansu, ``Optical gain and laser characteristics of InGaN quantum wells on ternary InGaN substrates,'' \emph{IEEE Photon. J.}, vol. 5, no. 2, Apr. 2013, Art. no. 2600111

\bibitem{b34} S. Azodolmolky~\emph{et al.}, Experimental demonstration of an impairment aware network planning and operation tool for transparent/translucent optical networks,''~\emph{J. Lightw. Technol.}, vol. 29, no. 4, pp. 439--448, Sep. 2011.

\end{thebibliography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.png}}]{First A. Author} (M'76--SM'81--F'87) and all authors may include 
biographies. Biographies are often not included in conference-related
papers. This author became a Member (M) of IEEE in 1976, a Senior
Member (SM) in 1981, and a Fellow (F) in 1987. The first paragraph may
contain a place and/or date of birth (list place, then date). Next,
the author's educational background is listed. The degrees should be
listed with type of degree in what field, which institution, city,
state, and country, and year the degree was earned. The author's major
field of study should be lower-cased.

The second paragraph uses the pronoun of the person (he or she) and not the 
author's last name. It lists military and work experience, including summer 
and fellowship jobs. Job titles are capitalized. The current job must have a 
location; previous positions may be listed 
without one. Information concerning previous publications may be included. 
Try not to list more than three books or published articles. The format for 
listing publishers of a book within the biography is: title of book 
(publisher name, year) similar to a reference. Current and previous research 
interests end the paragraph. The third paragraph begins with the author's 
title and last name (e.g., Dr.\ Smith, Prof.\ Jones, Mr.\ Kajor, Ms.\ Hunter). 
List any memberships in professional societies other than the IEEE. Finally, 
list any awards and work for IEEE committees and publications. If a 
photograph is provided, it should be of good quality, and 
professional-looking. Following are two examples of an author's biography.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.png}}]{Second B. Author} was born in Greenwich Village, New York, NY, USA in 
1977. He received the B.S. and M.S. degrees in aerospace engineering from 
the University of Virginia, Charlottesville, in 2001 and the Ph.D. degree in 
mechanical engineering from Drexel University, Philadelphia, PA, in 2008.

From 2001 to 2004, he was a Research Assistant with the Princeton Plasma 
Physics Laboratory. Since 2009, he has been an Assistant Professor with the 
Mechanical Engineering Department, Texas A{\&}M University, College Station. 
He is the author of three books, more than 150 articles, and more than 70 
inventions. His research interests include high-pressure and high-density 
nonthermal plasma discharge processes and applications, microscale plasma 
discharges, discharges in liquids, spectroscopic diagnostics, plasma 
propulsion, and innovation plasma applications. He is an Associate Editor of 
the journal \emph{Earth, Moon, Planets}, and holds two patents.

Dr. Author was a recipient of the International Association of Geomagnetism 
and Aeronomy Young Scientist Award for Excellence in 2008, and the IEEE 
Electromagnetic Compatibility Society Best Symposium Paper Award in 2011. 
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a3.png}}]{Third C. Author, Jr.} (M'87) received the B.S. degree in mechanical 
engineering from National Chung Cheng University, Chiayi, Taiwan, in 2004 
and the M.S. degree in mechanical engineering from National Tsing Hua 
University, Hsinchu, Taiwan, in 2006. He is currently pursuing the Ph.D. 
degree in mechanical engineering at Texas A{\&}M University, College 
Station, TX, USA.

From 2008 to 2009, he was a Research Assistant with the Institute of 
Physics, Academia Sinica, Tapei, Taiwan. His research interest includes the 
development of surface processing and biological/medical treatment 
techniques using nonthermal atmospheric pressure plasmas, fundamental study 
of plasma sources, and fabrication of micro- or nanostructured surfaces.

Mr. Author's awards and honors include the Frew Fellowship (Australian 
Academy of Science), the I. I. Rabi Prize (APS), the European Frequency and 
Time Forum Award, the Carl Zeiss Research Award, the William F. Meggers 
Award and the Adolph Lomb Medal (OSA).
\end{IEEEbiography}

\end{document}

### 2020-10-14 docs/paper/paper.tex
* Reviewer 1 reply is finished

@@
 		\caption{Configuration estimation on SPR dataset.
-		\\\hl{$ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 $ $ d1 = 0.45 um $ $ d2= 0.75 um$ $ d3 = 0.35 um $.}\\ \hl{ $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.75um $ $ d3 = 0.35um $.}
+		\\\hl{Left: $ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 $ $ d1 = 0.45 um $ $ d2= 0.75 um$ $ d3 = 0.35 um $.}\\ \hl{Right: $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.75um $ $ d3 = 0.35um $.}
 		  }
@@
 		\caption{Configuration estimation on SPR dataset. 
-		\\ \hl{$n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 um $ $ d1 = 0.45 um $ $ d2= 0.75um $ $ d3 = 0.35um $.} \\ \hl{$n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.55um $ $ d3 = 0.15um $.}
+		\\ \hl{Left: $n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 um $ $ d1 = 0.45 um $ $ d2= 0.75um $ $ d3 = 0.35um $.} \\ \hl{Right: $n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.55um $ $ d3 = 0.15um $.}
 		}
@@
 The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research article.
-\hl{The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research; in the experiments, it surpassed the accuracy of the method proposed in }\cite{paper0}\hl{ on the dataset that method is optimized on.}
+\hl{The proposed combination is shown to be general enough that even though it is designed and optimized for the SPR dataset; in the experiments, it surpassed the accuracy of the method proposed in }\cite{paper0}\hl{ on the dataset that method is optimized on.}
 

### 2020-10-14 docs/revision/reply.tex
* Reviewer 1 reply is finished

\documentclass{article}
\usepackage[utf8]{inputenc}

\begin{document}

	We would like to thank the respected reviewer for their valuable comments that helped us to improve the quality of this article. We would also like to state that we were unable to add all the requested details directly to the paper due to the page limitation. However, in this reply, we have tried to address all points that are raised by the reviewers to the best of our ability. Also due to small changes in the manuscript, reference numbers have shifted. We have used the reference numbers as discussed by the reviewers and offered the new reference number at the end of each reply.

	~

	{\bfseries\large Reviewer 1}

	\begin{quote}
	Page 3, Line 13, Right Column- Why you have specifically used 5 hidden layers? What will be the impact on performance when using less or more hidden layers and neurons?
	\end{quote}

	During our initial studies, we have studied the effect of the network architecture on the accuracy. During these studies we have found 5 layers are necessary for ANN to be able estimate the loss curve. Specifically, in SPR dataset, this requirement is evident. Higher number of layers increases the required number of samples to train causing further problems. Similar situation exists for the number of neurons. However, it is possible that there might be a better combination of layers and neurons as we have not performed any exhaustive optimization on the neural network.

	A summary of this reply has been added to the paper in Section II-B at the end of the first paragraph.

	\begin{quote}
	Page 4, Line 43, Right Column- The paper cited [18] doesn't have 7 inputs as looking from the dataset file (from github) and the mauscript itself. It looks to me that there are 5 inputs. Can you recheck this?
	\end{quote}

	We want to thank the reviewer for his keen eyes. Indeed the number of features were wrongly listed in the paper even though there were 5 features listed in that sentence. The mistake is fixed and highlighted in the revised manuscript.

	\begin{quote}
	Also, have you used the dataset of [18] along with your own data making it finally as 1117+432 data samples. If yes, how did you merge both datasets as proposed manuscript (d1,d2,d3,etc) data sets has different inputs parameters than [18]. What happens to non-common columns like number of rings input feature as mentioned in [18].
	\end{quote}

	Both datasets are treated separately during experiments. Input neurons of the ANN systems are adjusted depending on the dataset used in a particular experiment without altering the rest of the architecture.

	\begin{quote}
	Figure 4c, Figure 6- Give more details about the paramaters (d1,d2,d3,refrative index,etc) at which this particular actual blue line graph is obtained.
	\end{quote}

	Requested information is added to the respective figures.

	\begin{quote}
	Page 5, Line 43, Left Column- You have stated that [18]'s model has been failing in Figure 4c. It looks to me that the blue line in Figure 4c is for your proposed PCF structure design, while [18]'s PCF design was a simple hexagonal structure with varying rings. Also, there was no analyte (but you have used refractive index 1.35 as shown in this manuscript) in [18]. So if you compare ML models (your's and [18]) only on the criteria of wavelength as stated in Figure 4c, then [18] model is supposed to fail. This comparison doesn't make much sense as both designs and input features are different. If you disagree, then explain this comparison in more detail and mention the design specification values.
	The similar comparison (your's and [18]) explanation is required for Figure 6.
	\end{quote}

	As the respected reviewer pointed out, we have used our SPR dataset in Figure 4c as well as Figure 4a which includes all configurations. The aim here is to show that the changes in the state-of-the-art is necessary to enable the ANN architecture to handle more complex systems. We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle the this more difficult problem. In Figure 6, the comparison is drawn using the proposed architecture with and without GAN phases. The method in [18] is excluded in this graph as the improvement that can obtained by applying GAN phase to the network proposed in [18] does not yield any net benefit. In the text below we would like to explain our rationale for modifying the state-of-the-art to the proposed architecture.

	The newly added average MSE values in the Figure 4 shows that the method in [18] is actually better at minimizing the error in these particular cases. Additionally, in the detailed performance analysis table (Table II), it is evident that the method at [18] and proposed method without the GAN phase has comparable results. However, Figure 4c shows that the error rate of both methods are accumulated differently. Even with the limited samples, the method at [18] is a good predictor of the real curve, except the shape of the curve does not actually model the real output; but a very rough estimation of it. The proposed ANN structure predicts the shape of the curve much better, however, it clearly requires more samples to fit that curve to the real output. Therefore, method at [18] cannot be refined further with less-than-ideal generated samples, on the other hand, the proposed architecture can benefit from increased number of samples. This was our aim when designing the proposed architecture. In fact, in our experiments, we have found that GAN phase has nearly no positive effect on the method proposed in [18]. We have excluded these experiments from the paper as it is already over the page limit. One last point we would like to show is that in Table II, in the SPR dataset, the reduction in error achieved by changing the network is less than 10\%, however, when GAN phase is also included, reduction reaches 68\%.

	\begin{quote}
	Page 5, Line 46, Left Column- "This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model[46]"- There is no surity of this reason if the above comment/query in line 43 is logical. So reframe/reconsider this statement.
	\end{quote}

	We have tried both full-batch and mini-batch learning models during our experiments. Mini-batch training generally had an edge over the full-batch training during these experiments. However, we agree with the reviewer that without a comprehensive experiment and its reported results, this claim has no basis. Therefore, we have decided to retract this statement.

	\begin{quote}
	Page 7, Line 45, Left Column- "In our experiments, due to optimized dataset the accuracy of the method proposed in Ref. [18] is also improved."- Following from the previous comments- if the comparison is not for the similar designs then you can't state this improvement. So please elaborate on this.
	\end{quote}

	We thank the respected reviewer for catching this sentence. We believe the meaning of this sentence has been completely altered during language editing. We have fixed this mix up.

	\begin{quote}
	Page 7, Line 40, Right Column- Recurrent Neural Networks (RNN) generally rely memory to recognise patterns like in speech recognition or text generation and tells what should/will come after. How do you state/propose here than RNN can be used to discover optimal geometrical shapes?- because all the geometrical shapes might be independent of each other.
	\end{quote}

	After an internal debate, we have understood the concern of the respected reviewer and decided to drop this claim.

	\begin{quote}
	Page 7, Line 43, Right Column- Github link for the code is broken. I hope you will correct it. Looking forward to check your code along with data samples you have used  to obtain results in this manuscript.
	\end{quote}

	The given link is our current working repository that includes the paper. We will alter and publish the repository after the acceptance according to the requirements of the journal preprint policies.

\end{document}

### 2020-10-14 docs/paper/paper.tex
fixed: typo

@@
 Table  \ref{tbl:anndetails} summarizes the details of this model.
-\hl{The number of hidden layers and neurons are empirically determined to be able to estimate the loss curve while keeping the complexity of the network to minimum.}
+\hl{The number of hidden layers and neurons are empirically determined to be able to estimate the loss curve while keeping the complexity of the network to a minimum.}
 

### 2020-10-14 docs/revision/reply.tex
update: fixed-typos:: update-first-argument

@@
 \usepackage[utf8]{inputenc}
+\usepackage{color,soul}
 
@@
 
-	During our initial studies, we have studied the effect of the network architecture on the accuracy.
+	During our initial \hl{systematic experiments; instead of "studies"}, we have studied the effect of the network architecture on the accuracy.
 During these studies we have found 5 layers are necessary for ANN to be able estimate the loss curve.
 Specifically, in SPR dataset, this requirement is evident.
-Higher number of layers increases the required number of samples to train causing further problems.
+Higher number of layers \hl{not only potentially leads to overfitting, but also to an  increase in} the required number of samples to train causing further problems.
 Similar situation exists for the number of neurons.
@@
 The aim here is to show that the changes in the state-of-the-art is necessary to enable the ANN architecture to handle more complex systems.
-We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle the this more difficult problem.
+We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle the more difficult problem.
 In Figure 6, the comparison is drawn using the proposed architecture with and without GAN phases.

### 2020-10-14 docs/revision/reply.tex
added all quotes: reviewer 2and3

@@
 
+	~
+
+	{\bfseries\large Reviewer 2}
+
+	\begin{quote}
+	 Please, reread the paper to correct some misspelling words.
+For example, Abstract (line 3): should it be "researchers"?
+Another example in "Introduction", page 1, column 2, line 35: "Snell's Total" instead of "Snell?s Total".
+	\end{quote}
+
+	\begin{quote}
+	The authors wrote, "The most important contribution of this research is the use of
+the GAN phase, where the available data is expanded to be
+used in the training phase".
+Why use a Generative adversarial network?
+What would be the advantages and disadvantages of a GAN approach over other possible data generators, such as evolutionary mutation functions?
+The authors should provide a comparison methodology and discuss differences between GAN and other data generators.
+	\end{quote}
+
+	\begin{quote}
+	How did the authors find the ANN architectures? How long did it take to find the ANN designs suitable for the problem being addressed?
+	\end{quote}
+
+	\begin{quote}
+	Which kind of performance metric the authors are measuring in Table II? Is it MSE? Please, define it.
+	\end{quote}
+
+	\begin{quote}
+	Please, define which is RI (page 4, column 1, line 38).
+	\end{quote}
+
+	\begin{quote}
+	How do the authors know the ANN is not overfitting in Fig.
+3?
+Have the authors employed any validation during training?
+Please, provide the ANN models' performance on the validation by showing the validation MSE during training.
+	\end{quote}
+
+	\begin{quote}
+	Please provide the test MSEs for comparison between the proposed method and the ref. [18] (illustrated in Fig. 4).
+	\end{quote}
+
+	~
+
+	{\bfseries\large Reviewer 3}
+
+	\begin{quote}
+	I suggest that the authors give more information about the stopping criteria of the GAN.
+As the author pointed out, human judgment has an important role in the generation of images and audio.
+So, could the known physical laws about PCF and SPR be used to replace the human role in the GAN system to improve the performance?
+How does the author verify the validity of the augmented samples?
+	\end{quote}
+
+	\begin{quote}
+	 In GAN and ANN, how many training samples and test samples are used respectively? How are the test samples selected?
+	\end{quote}
+
+	\begin{quote}
+	In Fig 5, the MSE increase when the augmented samples exceed 1000. Why does more samples cause performance degradation?
+	\end{quote}
+
+	\begin{quote}
+	In Fig 6, in the case of SPR, the calculated loss spectrum has a large deviation under some specific parameters.
+Could the authors discuss the reasons for the deviation and how to judge the validity of the calculation result?
+	\end{quote}
+
 \end{document}

### 2020-10-15 docs/revision/reply.tex
replied: reviewer 2 :: reviewer 3 except last Q

@@
 
+	\hl{We would to thank the respected reviewer for his sharpness. We have reread the manuscript and corrected spelling errors as well as grammatical errors, as much as we could. }
+
 	\begin{quote}
@@
 
+	\hl{Though the respected reviewer makes a valid point regarding data augmentation techniques, however, our study was not comparative in nature, thus, other data augmentation techniques will be investigated in future work.
+Furthermore, we have chosen GAN due to its effectiveness and popularity, as we the references we provided demonstrate.}
+
 	\begin{quote}
@@
 	\end{quote}
+
+	\hl{By using [18] as a starting point and carrying systematic experimentations, the ANN architecture was structured as the one which stabilized the loss curve and general enough to have acceptable validation errors on both data sets.}
 
@@
 
+	\hl{We would like to thank the reviewer for noticing the ill defined Table. Yes, the metric is the MSE, as shown in the tilte of Table II in the new manuscript.}
+
 	\begin{quote}
@@
 	\end{quote}
+
+	\hl{We very much appreciate the reviewer's remark on the missing the full form of RI. RI referes to the Refractive Index as it is indicated in the same line in the new manuscript. }
 
@@
 
+	\hl{During our experiments we used part of the data to validate training. In an attempt to stay within the maximum page limits, we had decided to not include the validation curves.
+	 The ANN's performance on the validation is provided in Figure 4 in the new manuscript.}
+
 	\begin{quote}
@@
 	\end{quote}
+
+	\hl{The requested MSEs are provided on the graphs in the new manuscript.} \\
+	\textcolor{red}{AZ: CK Should we discuss the MSEs here? I think you provided the same answer for Reviewer 1 - Q5.}
 
@@
 
+	\hl{We strongly agree with the reviewer's valuable suggestion.
+In fact the very reason that propelled us to choose WGAN is its stopping criteria.
+The loss curve of the WGAN converges in a stable manner indicating the end of the training phase, as it measures the distance between the distrubutions of real and generated data, which in return, to a high degree of certainty - probabilistically speaking-, validates our generated data.
+Due to the number of pages limitation, we decided not to include the loss graph of the WGAN, however, experiments showed that the curve converges in a stable manner to 0.}
+
 	\begin{quote}
@@
 
+	\hl{For the purpose of saving space we have not included the corresponding table, which includes detailed information about the data sets. 
+	For the SPR set,  for the 9 folds, we used 336 samples to train the GAN and the ANN, 48 for validation and 48 for testing.
+Please note that each geometric configuration has 16 data point per analyte making up to 48 for the 3 analytes used.
+	For the PCF set: for the 10 folds, we used about 10$\%$ for testing, about 10$\%$ for validation and the rest for training the ANN and GAN.}
+
 	\begin{quote}
@@
 	\end{quote}
+
+	\hl{The importance of real data dilutes as the number of generated data increases, thus, there is a balance to strive for.
+To support our claim we conducted further experiments and added the correspoding MSEs to the bar chart of Fugure 6.}
 

### 2020-10-15 docs/paper/paper.tex
fix:: styling-parameter vals-micro_meter
fixes::by Ahmet

@@
 In the last decade, PCF based structures are extensively employed as sensing devices.
-Possibility of filling the cladding holes with gas and liquid analytes makes them favorable in both chemical and biological sensing applications  \cite{wang2011selectively,rifat2016highly,caucheteur2015review,dash2014spr}.
+Possibility of filling the cladding holes with gas and liquid analytes makes them favorable in both chemical and biological sensing applications  \cite{wang2011selectively,rifat2016highly,dash2014spr}.
 Moreover, due to adaptable light guidance with possibilities of controlling the confinement loss and the chromatic dispersion at any operating wavelength are distinguishing features of PCF based structures in the literature.
-These charming propagation features can be achieved by employing, circular, cylindrical and even square and rectangular shaped \cite{wang2015simulation} air holes in the cladding and in the core region of the structures.
-Furthermore, the cladding pattern arrangements such as hexagonal, octagonal, decagonal, square and circular \cite{wang2011selectively,bouk2004dispersion,ademgil2014highly,razzak2007chromatic} can be engaged to achieve the desired features for preferred applications.
+These charming propagation features can be achieved by employing, circular, cylindrical and even square and rectangular shaped   air holes in the cladding and in the core region of the structures.
+Furthermore, the cladding pattern arrangements such as hexagonal, octagonal, decagonal, square and circular \cite{wang2011selectively,ademgil2014highly} can be engaged to achieve the desired features for preferred applications.
 The hole-to hole spacing (pitch) and the air hole sizes are critical parameters of tuning the aforementioned propagation characteristics.
@@
 Following the exclusive study by Hassani and Skorobogatiy \cite{hassani2006design}, a number of structures have reported the merits of PCF based SPR sensors.
-In the past, structures that contains features such as multi-channel single analyte and multi-channel multi analyte have been investigated \cite{rifat2016highly,yasli2019effect,zhang2011wagon,yasli2019multi,azzam2016multichannel}.
+In the past, structures that contains features such as multi-channel single analyte and multi-channel multi analyte have been investigated \cite{rifat2016highly,yasli2019effect,yasli2019multi,azzam2016multichannel}.
 Also, the effects of various metallic layers such as Au, Ag \cite{yasli2019multi}, Ag- Graphene \cite{rifat2016highly}, Ta2TO5 \cite{otupiri2015multi}, ITO \cite{dash2014spr}, TiO2 \cite{rifat2016highly} with various design parameters have also been investigated in detailed.
@@
 Optimizing and refinement of these parameters is an extremely time consuming process with considerable computational time \cite{fornarelli2009neural,abdelaziz2012photonic,paper0}.
-In the past, genetic algorithms \cite{abdelaziz2012photonic,borel2004topology} method was used to optimize the structural design parameters to achieve better propagation features of photonic devices \cite{rifat2016highly,caucheteur2015review}.
+In the past, genetic algorithms \cite{abdelaziz2012photonic,borel2004topology} method was used to optimize the structural design parameters to achieve better propagation features of photonic devices \cite{rifat2016highly}.
 Nowadays, in order to optimize such structures, artificial neural networks (ANN) and other machine learning (ML) algorithms are being applied \cite{fornarelli2009neural,paper0,hameed2008accurate}.
@@
 An alternative solution is to artificially expand the original training dataset by the means of generative networks.
-In this regard, Generative Adversarial Networks (GAN) introduced by Goodfellow et al  \cite{goodfellow2014generative}, has proven to be successful in data generation  \cite{schlegl2017unsupervised, zheng2017unlabeled, frid2018synthetic, tanaka2019data, perez2017effectiveness}.
+In this regard, Generative Adversarial Networks (GAN) introduced by Goodfellow et al  \cite{goodfellow2014generative}, has proven to be successful in data generation  \cite{schlegl2017unsupervised,  frid2018synthetic,  perez2017effectiveness}.
 
@@
 
-The GAN can be trained by diverse metrics \cite{goodfellow2014generative, mao2017least, lucic2018gans}].
+The GAN can be trained by diverse metrics \cite{goodfellow2014generative, lucic2018gans}].
 In this work Wasserstein distance metric (WGAN) is employed \cite{arjovsky2017wasserstein}.
@@
 
-In order to build the desired dataset, the numerical analysis of the proposed sensor structure is carried out with the commercial software package Comsol Multiphysics  \cite{comsol_help}.
-The Full Vectorial Finite Element Method (FV-FEM) with the perfectly matched layers (PMLs) \cite{koshiba2002full,saitoh2001full} are employed.
+In order to build the desired dataset, the numerical analysis of the proposed sensor structure is carried out with the commercial software package Comsol Multiphysics.
+The Full Vectorial Finite Element Method (FV-FEM) with the perfectly matched layers (PMLs) \cite{koshiba2002full} are employed.
 
@@
 		\caption{Configuration estimation on SPR dataset.
-		\\\hl{Left: $ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 $ $ d1 = 0.45 um $ $ d2= 0.75 um$ $ d3 = 0.35 um $.}\\ \hl{Right: $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.75um $ $ d3 = 0.35um $.}
+		\\\hl{Left: $ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 \mu m$ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m$ $ d_3 = 0.35 \mu m $.}\\ \hl{Right: $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m  $.}
 		  }
@@
 		\caption{Configuration estimation on SPR dataset. 
-		\\ \hl{Left: $n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 um $ $ d1 = 0.45 um $ $ d2= 0.75um $ $ d3 = 0.35um $.} \\ \hl{Right: $n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.55um $ $ d3 = 0.15um $.}
+		\\ \hl{Left: $n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 \mu m $ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m $.} \\ \hl{Right: $n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.55 \mu m $ $ d_3 = 0.15 \mu m $.}
 		}

### 2020-10-15 docs/revision/reply.tex
fixes:: reply

@@
 
-	\hl{We would to thank the respected reviewer for his sharpness. We have reread the manuscript and corrected spelling errors as well as grammatical errors, as much as we could. }
+	\hl{We would like to thank the respected reviewer for his sharpness. We have reread the manuscript and corrected spelling errors as well as grammatical errors, as much as we could. }
 
@@
 
+	\textcolor{red}{AZ: the second question makes no sense to me. The time to train an ANN is not something that we consider while building the ANN. Queite frankly I don't know how to reply.}
+
 	\begin{quote}
@@
 
-	\hl{We very much appreciate the reviewer's remark on the missing the full form of RI. RI referes to the Refractive Index as it is indicated in the same line in the new manuscript. }
+	\hl{We very much appreciate the reviewer's remark on the missing full form of RI. RI referes to the Refractive Index as it is indicated in the same line in the new manuscript. }
 

### 2020-10-17 docs/paper/paper.tex
Fixed the replies for Reviewer 2 and 3

@@
 The distinguishing feature of the WGAN compared to other methods is the ability to determine a stopping criteria.
-In a regular GAN system, training is stopped when the generated data is deemed viable by an observer.
+\hl{In a regular GAN system, training is stopped when the generated data is deemed viable by an observer.
 GAN is frequently used in image, video or audio generation, where human is used effectively in the loop.
 In our case, it is not viable for a human to judge the generated data, therefore, automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which may degrade the performance.
-On the other hand, WGAN uses an adaptive stopping criteria that can easily overcome the aforementioned disadvantages.
-Additionally, Gradient penalty is incorporated to improve the WGAN as described in \cite{gulrajani2017improved}.
+On the other hand, WGAN uses an adaptive stopping criteria that can easily overcome the aforementioned disadvantages.} Additionally, Gradient penalty is incorporated to improve the WGAN as described in \cite{gulrajani2017improved}.
 This proposed enhanced WGAN system converges in a stable manner without requiring further fine tuning the hyper-parameters of the system.
@@
 
-where $\lambda$ is the operating wavelength, $n$ is the Refractive Index (RI), $B_{1,2,3}$ and  $C_{1,2,3}$ are the  Sellmeier constants~\cite{bjarklev2003PCF}.
+where $\lambda$ is the operating wavelength, $n$ is the \hl{Refractive Index (RI)}, $B_{1,2,3}$ and  $C_{1,2,3}$ are the  Sellmeier constants~\cite{bjarklev2003PCF}.
 
@@
 All numeric comparison results are averaged over multiple executions: 9-fold testing for SPR dataset and 10-fold testing for \dszero.
-Non-averaged data used in figures, such as configuration estimation, are selected from non-extreme cases for the compared methods.
+\hl{The number of testing samples used in SPR dataset experiments is 48, \dszero{} experiments is 112.} Non-averaged data used in figures, such as configuration estimation, are selected from non-extreme cases for the compared methods.
 %
@@
 \begin{table}
-	\caption{Detailed performance analysis in MSE}
+	\caption{\hl{Detailed performance analysis in MSE}}
 	\centering

### 2020-10-17 docs/revision/reply.tex
Fixed the replies for Reviewer 2 and 3

--- 2020-10-14 docs/revision/reply.tex
@@
 
-	We would like to thank the respected reviewer for their valuable comments that helped us to improve the quality of this article.
+	We would like to thank the respected reviewers for their valuable comments that helped us to improve the quality of this article.
 We would also like to state that we were unable to add all the requested details directly to the paper due to the page limitation.
 However, in this reply, we have tried to address all points that are raised by the reviewers to the best of our ability.
-Also due to small changes in the manuscript, reference numbers have shifted.
-We have used the reference numbers as discussed by the reviewers and offered the new reference number at the end of each reply.
+Also due to small changes in the manuscript, reference and figure numbers are shifted.
+We have used these numbers as discussed by the reviewers and offered the new numbers at the end of each reply.
 
@@
 
-	During our initial \hl{systematic experiments; instead of "studies"}, we have studied the effect of the network architecture on the accuracy.
+	During our initial experiments, we have studied the effect of the network architecture on the accuracy.
 During these studies we have found 5 layers are necessary for ANN to be able estimate the loss curve.
 Specifically, in SPR dataset, this requirement is evident.
-Higher number of layers \hl{not only potentially leads to overfitting, but also to an  increase in} the required number of samples to train causing further problems.
+Higher number of layers increases both the risk of overfitting and the required number of samples to train the network, causing further problems.
 Similar situation exists for the number of neurons.
@@
 The aim here is to show that the changes in the state-of-the-art is necessary to enable the ANN architecture to handle more complex systems.
-We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle the more difficult problem.
+We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle this more difficult problem.
 In Figure 6, the comparison is drawn using the proposed architecture with and without GAN phases.
@@
 
+	We would like to thank the respected reviewer for his help in finding these problems. We have carefully reread the manuscript and corrected spelling and grammatical errors
+
 	\begin{quote}
-	The authors wrote, "The most important contribution of this research is the use of
-the GAN phase, where the available data is expanded to be
-used in the training phase".
+	The authors wrote, "The most important contribution of this research is the use of the GAN phase, where the available data is expanded to be used in the training phase".
 Why use a Generative adversarial network?
@@
 
+	Respected reviewer poses a very important remark.
+Our primary aim in this paper is to introduce data augmentation to this field as data augmentation has never used in this field before.
+This also means that there are no prior experiments to draw comparisons to.
+We have selected GAN as it is shown to be effective in many fields.
+We do believe the alternative generative methods may have similar results and should be explored.
+However, each of these methods should be explained, implemented and optimized for this problem.
+This will increase the scope of this study substantially and will require us to expand the paper further.
+Even though the former is possible; due to the page limit put forth by the journal, the latter is not.
+
 	\begin{quote}
@@
 	\end{quote}
+
+	We have used the networks described in [18] as a starting point and applied changes that are known to solve the issues that are surfaced when this method is applied to a more difficult dataset.
+While we cannot give an exact time frame to the solution, we have spent at least several weeks adapting the ANN for this difficult problem.
 
@@
 
+	We would like to thank the reviewer for noticing the missing metric in the table, it is indeed MSE. We have updated the table title to include the metric.
+
 	\begin{quote}
@@
 	\end{quote}
+
+	We have added the definition of RI in the manuscript.
 
@@
 
+	In original manuscript we have omitted the validation graph to save space. We have included the validation curve in the revised manuscript as Fig. 4.
+
 	\begin{quote}
@@
 	\end{quote}
+
+	The requested MSEs are provided on the graphs in the new manuscript. \\
 
@@
 
+	We are thankful for the reviewer's valuable comment.
+This is the exact reason we have used WGAN.
+WGAN does not require human judgment, instead, it uses an adaptive stopping criteria.
+It might be possible to embed simulation approach into GAN training phase to offload judgment duty.
+This approach requires an extensive study of simulation systems and further experiments to test the viability of this approach.
+However, authors will consider respected reviewer's suggestion for a future study.
+
+	WGAN features its own loss function to determine stopping criteria.
+During the experiments, we have observed that the loss curve of WGAN converges to zero during the training.
+In addition to this observation, to ensure the generated data is relevant, we have filtered out the generated samples that fall outside the bounding box of the actual samples.
+
 	\begin{quote}
@@
 
+	We are sorry for not openly stating the requested information in the manuscript.
+We have expanded the information regarding the training and test samples in the fourth paragraph of the Experimental setup section.
+We include this information below for easy access:
+
+	For the SPR set: we have used 9 fold testing, we used 336 samples for training, 48 for validation and 48 for testing.
+Please note that each geometric configuration has 16 data point per analyte making up to 48 for the 3 analytes used.
+In this experimental setup, each configuration set (48 samples) are tested separately in its own fold and the reported results are the average of these 9 folds.
+
+	For the PCF set: we have used 10 fold testing, 112 samples are used for testing, 101 (10\% of training) samples are used for validation and the rest is used for training.
+For this 10 fold testing, we have randomly shuffled the samples into 10 bins, each bin is used for testing over these folds and reported results are the average of these 10 folds.
+
 	\begin{quote}
@@
 	\end{quote}
+
+	Data augmentation is not perfect, the augmented data contains some degree of error.
+When the number of samples are too low, such is the state in SPR dataset, the performance loss due to low number of samples massively out-weighs the error introduced by the augmented samples.
+However, as the number of generated samples increase, this error accumulates and starts to reduce the performance of the overall system.
+We would like to point out that while 1000 augmented samples achieve the best result, it requires 3000 or more augmented samples to perform worse than no augmentation.
+We have also added more data points to Fig 5 to answer this question with surety.
 
@@
 
+	There are two reasons for the deviation in Fig 6a.
+The first and most important is the fact that SPR dataset experiments is much more difficult compared to PCF dataset experiments.
+The most important difference here is the testing strategy.
+In PCF dataset, the testing samples are selected randomly from all the samples in the dataset.
+However, in SPR dataset, testing samples are from a completely new geometric configuration, in other words, we never show the testing configuration to the ANN system and expect it to estimate its loss function.
+Additionally, SPR dataset contains far fewer samples.
+The second reason for the variation is the range of the experiments, SPR experiment output is constrained in a small region, accentuating the deviation.
+There is certainly more variation the SPR dataset, however, the difference is not as high as Fig 6 suggests.
+
+	Finally, it is possible to verify the results from Fig 6c as these are two of the individual geometric configurations that the ANN systems estimated.
+Even though there still is a deviation from the ground truth, ANN trained with the help of augmented samples is good at estimating the location of the peak.
+
 \end{document}

### 2020-10-17 docs/paper/paper.tex
fix: typo

@@
 Adding further samples slightly reduces the performance while increasing the training time.
-The results of this experiment is demonstrated in Figure \ref{chart:gansamples} \hl{showing that the increasing number of augmented samples increases the performance to a point where it will start hurting the performance (>3000 samples).
+The results of this experiment is demonstrated in Figure \ref{chart:gansamples} \hl{showing that the increasing number of augmented samples increases the performance to a point where it will start hurting the performance ($>$ 3000 samples).
 The reason behind this augmented samples are not perfect.

### 2020-10-17 docs/revision/reply.tex
add: note to the shifted ref and figures

@@
 The mistake is fixed and highlighted in the revised manuscript.
+\\
+	\textbf{NB: [18] has been shifted to [13] in the revised manuscript}
 
@@
 	Both datasets are treated separately during experiments.
-Input neurons of the ANN systems are adjusted depending on the dataset used in a particular experiment without altering the rest of the architecture.
+Input neurons of the ANN systems are adjusted depending on the dataset used in a particular experiment without altering the rest of the architecture.\\
+	\textbf{NB: [18] has been shifted to [13] in the revised manuscript.}
 
@@
 
-	Requested information is added to the respective figures.
+	Requested information is added to the respective figures.\\
+	\textbf{NB: Fig. 4c, Fig. 6 have been shifted to Fig. 5c, Fig. 7 respectively in the revised manuscript.}
 
@@
 One last point we would like to show is that in Table II, in the SPR dataset, the reduction in error achieved by changing the network is less than 10\%, however, when GAN phase is also included, reduction reaches 68\%.
+\\
+
+	\textbf{NB: [18], Fig. 4c, Fig. 6 has been shifted to [13], Fig. 5c, Fig. 7 respectively in the revised manuscript.}
 
@@
 
-	We thank the respected reviewer for catching this sentence. We believe the meaning of this sentence has been completely altered during language editing. We have fixed this mix up.
+	We thank the respected reviewer for catching this sentence. We believe the meaning of this sentence has been completely altered during language editing. We have fixed this mix up. \\
+	\textbf{NB: [18] has been shifted to [13] in the revised manuscript.}
 
@@
 While we cannot give an exact time frame to the solution, we have spent at least several weeks adapting the ANN for this difficult problem.
+\\
+
+	\textbf{NB: [18] has been shifted to [13] in the revised manuscript.}
 
@@
 
-	We would like to thank the reviewer for noticing the missing metric in the table, it is indeed MSE. We have updated the table title to include the metric.
+	We would like to thank the reviewer for noticing the missing metric in the table, it is indeed the MSE. We have updated the table title to include the metric.
 
@@
 
-	The requested MSEs are provided on the graphs in the new manuscript. \\
+	The requested MSEs are provided on the graphs in the revised manuscript. \\
+
+	\textbf{NB: [18], Fig. 4 has been shifted to [13], Fig. 5 respectively in the revised manuscript.}
 
@@
 Even though there still is a deviation from the ground truth, ANN trained with the help of augmented samples is good at estimating the location of the peak.
+\\
 
+	\textbf{NB: Fig. 6 has been shifted to Fig. 7 in the revised manuscript.}
 \end{document}

### 2020-10-20 docs/paper/paper.tex
Reply fixes by HA

@@
 Table  \ref{tbl:anndetails} summarizes the details of this model.
-\hl{The number of hidden layers and neurons are empirically determined to be able to estimate the loss curve while keeping the complexity of the network to a minimum.}
+\hl{The number of hidden layers and neurons are empirically determined to be able to estimate the loss curve while keeping the complexity of the network to a minimum.
+With these changes, the proposed network is able to predict more complex functions, however, it will also require more training samples.}
 
@@
 Therefore, they both have higher error rates compared to the PCF dataset.
-According to Figure \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength.
+\hl{According to Figure} \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ \hl{case, the ANN method proposed in }\cite{paper0}\hl{ is not a good predictor of the shape of the curve caused by the change in the wavelength, even though it fits this curve much better than the proposed method, showing that the proposed method requires more samples for training.}
 %This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}.
@@
 	\end{subfigure}
-	\vspace{0.75cm}
+	\vspace{0.5cm}
 
@@
 		\begin{axis}[
-		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $ ({$n_{analyte=1.34}$}), 
+		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
 		ylabel=$ Loss $ $ in $ $ Log(db/cm) $,
@@
 		height=6cm,
-		legend pos=north west
+		legend pos=north east,
+		legend style={font=\footnotesize}
 		]
@@
 		table[x={wave},y={predicted}]{data/wave_134_their.txt};
-		\addlegendentry{\cite{paper0}}
 
@@
 		table[x={wave},y={predicted}]{data/wave_134_our.txt};
-		\addlegendentry{$Proposed$}
 
@@
 
-		\legend{}
-				legend style={anchor=north east,draw=none,fill=none,font=\tiny, at={(axis cs:670,1.55)}},
-
-		]
-
-		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE: 0.08721}
-		\addlegendimage{second}\addlegendentry{Proposed MSE: 0.18869 }
+		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE: 0.09}
+		\addlegendimage{second}\addlegendentry{Proposed MSE: 0.19 }
+
+		]
 
@@
 		\begin{axis}[
-		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $ ($n_{analyte=1.35}$), 
+		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
 		ylabel=$~$,
@@
 		height=6cm,
-		legend pos=north west
+		legend pos=north west,
+		legend style={font=\footnotesize}
 		]
@@
 
-		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE:0.17491}
-		\addlegendimage{second}\addlegendentry{Proposed MSE:0.37049 }
+		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE:0.17}
+		\addlegendimage{second}\addlegendentry{Proposed MSE:0.37 }
 
@@
 		\caption{Configuration estimation on SPR dataset.
-		\\\hl{Left: $ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 \mu m$ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m$ $ d_3 = 0.35 \mu m $.}\\ \hl{Right: $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m  $.}
+\hl{Left: $ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 \mu m$ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m$ $ d_3 = 0.35 \mu m $.} \hl{Right: $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m  $.}
 		  }
@@
 		major grid style={gray!25},
-		title={$n_{analyte=1.34}$},
 		width=0.48\textwidth,
 		legend pos=north east,
-		height=6cm
+		height=6cm,
+		legend style={font=\footnotesize}
 		]
@@
 
-		\addlegendimage{first}\addlegendentry{Without GAN:0.18869}
-		\addlegendimage{second}\addlegendentry{With GAN:0.11670 }
+		\addlegendimage{first}\addlegendentry{Without GAN:0.19}
+		\addlegendimage{second}\addlegendentry{With GAN:0.12 }
 
@@
 		major grid style={gray!25},
-		title={$n_{analyte=1.33}$},
 		width=0.48\textwidth,
 		legend pos=north east,
-		height=6cm
+		height=6cm,
+		legend style={font=\footnotesize}
 		]
@@
 
-		\addlegendimage{first}\addlegendentry{Without GAN:0.32373}
-		\addlegendimage{second}\addlegendentry{With GAN:0.08664 }
+		\addlegendimage{first}\addlegendentry{Without GAN:0.32}
+		\addlegendimage{second}\addlegendentry{With GAN:0.09 }
 		\end{axis}
@@
 		\caption{Configuration estimation on SPR dataset.
-		\\ \hl{Left: $n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 \mu m $ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m $.} \\ \hl{Right: $n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.55 \mu m $ $ d_3 = 0.15 \mu m $.}
+\hl{Left: $n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 \mu m $ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m $.} \hl{Right: $n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.55 \mu m $ $ d_3 = 0.15 \mu m $.}
 		}

### 2020-10-20 docs/revision/reply.tex
fix: note to the shifted ref and figures
Reply fixes by HA

@@
 	We would like to thank the respected reviewers for their valuable comments that helped us to improve the quality of this article.
-We would also like to state that we were unable to add all the requested details directly to the paper due to the page limitation.
+We would also like to state that we were unable to add all the requested details directly to the manuscript due to the page limitation.
 However, in this reply, we have tried to address all points that are raised by the reviewers to the best of our ability.
@@
 	\begin{quote}
-	Page 3, Line 13, Right Column- Why you have specifically used 5 hidden layers? What will be the impact on performance when using less or more hidden layers and neurons?
+		\textbf{1: }Page 3, Line 13, Right Column- Why you have specifically used 5 hidden layers? What will be the impact on performance when using less or more hidden layers and neurons?
 	\end{quote}
 
-	During our initial experiments, we have studied the effect of the network architecture on the accuracy.
+	\textbf{Reponse: }During our initial experiments, we have studied the effect of the network architecture on the accuracy.
 During these studies we have found 5 layers are necessary for ANN to be able estimate the loss curve.
-Specifically, in SPR dataset, this requirement is evident.
+Specifically, in the SPR dataset, this requirement is evident.
 Higher number of layers increases both the risk of overfitting and the required number of samples to train the network, causing further problems.
@@
 
-	A summary of this reply has been added to the paper in Section II-B at the end of the first paragraph.
+	A summary of this reply has been added to the manuscript in Section II-B at the end of the first paragraph.
 
 	\begin{quote}
-	Page 4, Line 43, Right Column- The paper cited [18] doesn't have 7 inputs as looking from the dataset file (from github) and the mauscript itself.
+		\textbf{2: }Page 4, Line 43, Right Column- The manuscript cited [18] doesn't have 7 inputs as looking from the dataset file (from github) and the manuscript itself.
 It looks to me that there are 5 inputs.
@@
 
-	We want to thank the reviewer for his keen eyes.
-Indeed the number of features were wrongly listed in the paper even though there were 5 features listed in that sentence.
-The mistake is fixed and highlighted in the revised manuscript.
+	\textbf{Response:} Indeed the number of features were wrongly listed in the manuscript even though there were 5 features listed in that sentence.
+The mistake is corrected and highlighted in the revised manuscript.
 \\
-	\textbf{NB: [18] has been shifted to [13] in the revised manuscript}
+	\textit{[18] has been shifted to [13] in the revised manuscript}
 
 	\begin{quote}
-	Also, have you used the dataset of [18] along with your own data making it finally as 1117+432 data samples.
+		\textbf{3: }Also, have you used the dataset of [18] along with your own data making it finally as 1117+432 data samples.
 If yes, how did you merge both datasets as proposed manuscript (d1,d2,d3,etc) data sets has different inputs parameters than [18].
@@
 
-	Both datasets are treated separately during experiments.
+	\textbf{Response: }Both datasets are treated separately during experiments.
 Input neurons of the ANN systems are adjusted depending on the dataset used in a particular experiment without altering the rest of the architecture.\\
-	\textbf{NB: [18] has been shifted to [13] in the revised manuscript.}
+	\textit{Reference [18] has been shifted to [13] in the revised manuscript.}
 
 	\begin{quote}
-	Figure 4c, Figure 6- Give more details about the paramaters (d1,d2,d3,refrative index,etc) at which this particular actual blue line graph is obtained.
+		\textbf{4: }Figure 4c, Figure 6- Give more details about the paramaters (d1,d2,d3,refrative index,etc) at which this particular actual blue line graph is obtained.
 	\end{quote}
 
-	Requested information is added to the respective figures.\\
-	\textbf{NB: Fig. 4c, Fig. 6 have been shifted to Fig. 5c, Fig. 7 respectively in the revised manuscript.}
+	\textbf{Response: } Requested information is added to the respective figures.\\
+	\textit{Fig. 4c, Fig. 6 have been shifted to Fig. 5c, Fig. 7 respectively in the revised manuscript.}
 
 	\begin{quote}
-	Page 5, Line 43, Left Column- You have stated that [18]'s model has been failing in Figure 4c.
+		\textbf{5: }Page 5, Line 43, Left Column- You have stated that [18]'s model has been failing in Figure 4c.
 It looks to me that the blue line in Figure 4c is for your proposed PCF structure design, while [18]'s PCF design was a simple hexagonal structure with varying rings.
@@
 
-	As the respected reviewer pointed out, we have used our SPR dataset in Figure 4c as well as Figure 4a which includes all configurations.
+	\textbf{Reponse: }As the respected reviewer pointed out, we have used our SPR dataset in \textbf{Figure 4c} as well as \textbf{Figure 4a} which includes all configurations.
 The aim here is to show that the changes in the state-of-the-art is necessary to enable the ANN architecture to handle more complex systems.
-We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle this more difficult problem.
-In Figure 6, the comparison is drawn using the proposed architecture with and without GAN phases.
-The method in [18] is excluded in this graph as the improvement that can obtained by applying GAN phase to the network proposed in [18] does not yield any net benefit.
+We should point out here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of the GAN phase, which in turn allows us to tackle this more difficult problem.
+In \textbf{Figure 6}, the comparison is drawn using the proposed architecture with and without GAN phases.
+The method in [18] is excluded in this graph as the improvement that can be obtained by applying the GAN phase to the network proposed in [18] does not yield any net benefit.
 In the text below we would like to explain our rationale for modifying the state-of-the-art to the proposed architecture.
+A summary of this explanation is included in the modified manuscript at the end of the first paragraph in Section II-B and the last paragraph of first column in page 5.
 
-	The newly added average MSE values in the Figure 4 shows that the method in [18] is actually better at minimizing the error in these particular cases.
+	The newly added average MSE values in the \textbf{Figure 4} shows that the method in [18] is actually better at minimizing the error in these particular cases.
 Additionally, in the detailed performance analysis table (Table II), it is evident that the method at [18] and proposed method without the GAN phase has comparable results.
-However, Figure 4c shows that the error rate of both methods are accumulated differently.
+However, \textbf{Figure 4c} shows that the error rate of both methods are accumulated differently.
 Even with the limited samples, the method at [18] is a good predictor of the real curve, except the shape of the curve does not actually model the real output; but a very rough estimation of it.
 The proposed ANN structure predicts the shape of the curve much better, however, it clearly requires more samples to fit that curve to the real output.
-Therefore, method at [18] cannot be refined further with less-than-ideal generated samples, on the other hand, the proposed architecture can benefit from increased number of samples.
+Therefore, the method at [18] cannot be refined further with less-than-ideal generated samples, on the other hand, the proposed architecture can benefit from increased number of samples.
 This was our aim when designing the proposed architecture.
-In fact, in our experiments, we have found that GAN phase has nearly no positive effect on the method proposed in [18].
-We have excluded these experiments from the paper as it is already over the page limit.
+In fact, in our experiments, we have found that the GAN phase has nearly no positive effect on the method proposed in [18].
+We have excluded these experiments from the manuscript as it is already over the page limit.
 One last point we would like to show is that in Table II, in the SPR dataset, the reduction in error achieved by changing the network is less than 10\%, however, when GAN phase is also included, reduction reaches 68\%.
-\\
 
-	\textbf{NB: [18], Fig. 4c, Fig. 6 has been shifted to [13], Fig. 5c, Fig. 7 respectively in the revised manuscript.}
+	\textit{[18], Fig. 4c, Fig. 6 has been shifted to [13], Fig. 5c, Fig. 7 respectively in the revised manuscript.}
 
 	\begin{quote}
-	Page 5, Line 46, Left Column- "This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model[46]"- There is no surity of this reason if the above comment/query in line 43 is logical.
+		\textbf{6: }Page 5, Line 46, Left Column- "This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model[46]"- There is no surity of this reason if the above comment/query in line 43 is logical.
 So reframe/reconsider this statement.
@@
 
-	We have tried both full-batch and mini-batch learning models during our experiments.
+	\textbf{Response: }We have tried both full-batch and mini-batch learning models during our experiments.
 Mini-batch training generally had an edge over the full-batch training during these experiments.
@@
 	\begin{quote}
-	Page 7, Line 45, Left Column- "In our experiments, due to optimized dataset the accuracy of the method proposed in Ref.
+		\textbf{7: }Page 7, Line 45, Left Column- "In our experiments, due to optimized dataset the accuracy of the method proposed in Ref.
 [18] is also improved."- Following from the previous comments- if the comparison is not for the similar designs then you can't state this improvement.
@@
 
-	We thank the respected reviewer for catching this sentence. We believe the meaning of this sentence has been completely altered during language editing. We have fixed this mix up. \\
-	\textbf{NB: [18] has been shifted to [13] in the revised manuscript.}
+	\textbf{Response: }We believe the meaning of this sentence has been completely altered during language editing. We have corrected the sentence. \\
+	\textit{[18] has been shifted to [13] in the revised manuscript.}
 
 	\begin{quote}
-	Page 7, Line 40, Right Column- Recurrent Neural Networks (RNN) generally rely memory to recognise patterns like in speech recognition or text generation and tells what should/will come after.
+		\textbf{8: }Page 7, Line 40, Right Column- Recurrent Neural Networks (RNN) generally rely memory to recognise patterns like in speech recognition or text generation and tells what should/will come after.
 How do you state/propose here than RNN can be used to discover optimal geometrical shapes?- because all the geometrical shapes might be independent of each other.
@@
 
-	After an internal debate, we have understood the concern of the respected reviewer and decided to drop this claim.
+	\textbf{Response: }After an internal debate, we have understood the concern of the respected reviewer and decided to retract this claim.
 
 	\begin{quote}
-	Page 7, Line 43, Right Column- Github link for the code is broken.
+		\textbf{9: }Page 7, Line 43, Right Column- Github link for the code is broken.
 I hope you will correct it.
@@
 
-	The given link is our current working repository that includes the paper. We will alter and publish the repository after the acceptance according to the requirements of the journal preprint policies.
+	\textbf{Response: }The given link is our current working repository that includes the manuscript.
+We will alter and publish the repository after the acceptance according to the requirements of the journal preprint policies.
 
@@
 	\begin{quote}
-	 Please, reread the paper to correct some misspelling words.
+		\textbf{1: }Please, reread the manuscript to correct some misspelling words.
 For example, Abstract (line 3): should it be "researchers"?
@@
 
-	We would like to thank the respected reviewer for his help in finding these problems. We have carefully reread the manuscript and corrected spelling and grammatical errors
+	\textbf{Response: }We would like to thank the respected reviewer for his help in finding these problems. We have carefully reread the manuscript and corrected spelling and grammatical errors.
 
 	\begin{quote}
-	The authors wrote, "The most important contribution of this research is the use of the GAN phase, where the available data is expanded to be used in the training phase".
+		\textbf{2: }The authors wrote, "The most important contribution of this research is the use of the GAN phase, where the available data is expanded to be used in the training phase".
 Why use a Generative adversarial network?
@@
 
-	Respected reviewer poses a very important remark.
-Our primary aim in this paper is to introduce data augmentation to this field as data augmentation has never used in this field before.
+	\textbf{Response: }Respected reviewer poses a very important remark.
+Our primary aim in this manuscript is to introduce data augmentation to this field as it has never been used in this field before.
 This also means that there are no prior experiments to draw comparisons to.
@@
 However, each of these methods should be explained, implemented and optimized for this problem.
-This will increase the scope of this study substantially and will require us to expand the paper further.
+This will increase the scope of this study substantially and will require us to expand the manuscript further.
 Even though the former is possible; due to the page limit put forth by the journal, the latter is not.
@@
 	\begin{quote}
-	How did the authors find the ANN architectures? How long did it take to find the ANN designs suitable for the problem being addressed?
+		\textbf{3: }How did the authors find the ANN architectures? How long did it take to find the ANN designs suitable for the problem being addressed?
 	\end{quote}
 
-	We have used the networks described in [18] as a starting point and applied changes that are known to solve the issues that are surfaced when this method is applied to a more difficult dataset.
+	\textbf{Response: }We have used the network described in [18] as a starting point and applied changes that are known to solve the issues that are surfaced when this method is applied to a more difficult dataset.
 While we cannot give an exact time frame to the solution, we have spent at least several weeks adapting the ANN for this difficult problem.
@@
 
-	\textbf{NB: [18] has been shifted to [13] in the revised manuscript.}
+	\textit{[18] has been shifted to [13] in the revised manuscript.}
 
 	\begin{quote}
-	Which kind of performance metric the authors are measuring in Table II? Is it MSE? Please, define it.
+		\textbf{4: }Which kind of performance metric the authors are measuring in Table II? Is it MSE? Please, define it.
 	\end{quote}
 
-	We would like to thank the reviewer for noticing the missing metric in the table, it is indeed the MSE. We have updated the table title to include the metric.
+	\textbf{Response: }We would like to thank the reviewer for noticing the missing metric in the table, it is indeed the MSE.
+We have updated the table title to include the metric as suggested by the reviewer.
 
 	\begin{quote}
-	Please, define which is RI (page 4, column 1, line 38).
+		\textbf{5: }Please, define which is RI (page 4, column 1, line 38).
 	\end{quote}
 
-	We have added the definition of RI in the manuscript.
+	\textbf{Response: }We have added the definition of RI in the manuscript.
 
 	\begin{quote}
-	How do the authors know the ANN is not overfitting in Fig.
+		\textbf{6: }How do the authors know the ANN is not overfitting in Fig.
 3?
@@
 
-	In original manuscript we have omitted the validation graph to save space. We have included the validation curve in the revised manuscript as Fig. 4.
+	\textbf{Response: }In original manuscript we have omitted the validation graph to save space. We have included the validation curve in the revised manuscript as \textbf{Figure 4}.
 
 	\begin{quote}
-	Please provide the test MSEs for comparison between the proposed method and the ref. [18] (illustrated in Fig. 4).
+		\textbf{7: }Please provide the test MSEs for comparison between the proposed method and the ref. [18] (illustrated in Fig. 4).
 	\end{quote}
 
-	The requested MSEs are provided on the graphs in the revised manuscript. \\
+	\textbf{Response: }As suggested by the reviewer, MSEs are provided on the graphs in the revised manuscript. \\
 
-	\textbf{NB: [18], Fig. 4 has been shifted to [13], Fig. 5 respectively in the revised manuscript.}
+	\textit{[18], Fig. 4 has been shifted to [13], Fig. 5 respectively in the revised manuscript.}
 
@@
 	\begin{quote}
-	I suggest that the authors give more information about the stopping criteria of the GAN.
+		\textbf{1: }I suggest that the authors give more information about the stopping criteria of the GAN.
 As the author pointed out, human judgment has an important role in the generation of images and audio.
@@
 
-	We are thankful for the reviewer's valuable comment.
-This is the exact reason we have used WGAN.
+	\textbf{Response: }This is the exact reason we have used WGAN.
 WGAN does not require human judgment, instead, it uses an adaptive stopping criteria.
-It might be possible to embed simulation approach into GAN training phase to offload judgment duty.
+We have highlighted related section in the manuscript in page 4, first paragraph.
+
+	It might be possible to embed the simulation approach into the GAN training phase to offload judgment duty.
 This approach requires an extensive study of simulation systems and further experiments to test the viability of this approach.
-However, authors will consider respected reviewer's suggestion for a future study.
+However, authors will consider the respected reviewer's suggestion for a future study.
 
@@
 	\begin{quote}
-	 In GAN and ANN, how many training samples and test samples are used respectively? How are the test samples selected?
+		\textbf{2: }In GAN and ANN, how many training samples and test samples are used respectively? How are the test samples selected?
 	\end{quote}
 
-	We are sorry for not openly stating the requested information in the manuscript.
-We have expanded the information regarding the training and test samples in the fourth paragraph of the Experimental setup section.
+	\textbf{Response: }As suggested by the reviewer we have expanded the information regarding the training and test samples in the fourth paragraph of the Experimental setup section.
 We include this information below for easy access:
@@
 	For the SPR set: we have used 9 fold testing, we used 336 samples for training, 48 for validation and 48 for testing.
-Please note that each geometric configuration has 16 data point per analyte making up to 48 for the 3 analytes used.
+Please note that each geometric configuration has 16 data points per analyte making up to 48 for the 3 analytes used.
 In this experimental setup, each configuration set (48 samples) are tested separately in its own fold and the reported results are the average of these 9 folds.
@@
 	\begin{quote}
-	In Fig 5, the MSE increase when the augmented samples exceed 1000. Why does more samples cause performance degradation?
+		\textbf{3: }In Fig 5, the MSE increase when the augmented samples exceed 1000. Why does more samples cause performance degradation?
 	\end{quote}
 
-	Data augmentation is not perfect, the augmented data contains some degree of error.
-When the number of samples are too low, such is the state in SPR dataset, the performance loss due to low number of samples massively out-weighs the error introduced by the augmented samples.
+	\textbf{Response: }Data augmentation is not perfect, the augmented data contains some degree of error.
+When the number of samples are too low, such as the state in SPR dataset, the performance loss due to low number of samples massively out-weighs the error introduced by the augmented samples.
 However, as the number of generated samples increase, this error accumulates and starts to reduce the performance of the overall system.
 We would like to point out that while 1000 augmented samples achieve the best result, it requires 3000 or more augmented samples to perform worse than no augmentation.
-We have also added more data points to Fig 5 to answer this question with surety.
+We have also added more data points to \textbf{Figure 5} to support this reply.\\
+
+	\textit{Fig. 5 has been shifted to Fig. 6 in the revised manuscript.}
 
 	\begin{quote}
-	In Fig 6, in the case of SPR, the calculated loss spectrum has a large deviation under some specific parameters.
+		\textbf{4: }In Fig 6, in the case of SPR, the calculated loss spectrum has a large deviation under some specific parameters.
 Could the authors discuss the reasons for the deviation and how to judge the validity of the calculation result?
@@
 
-	There are two reasons for the deviation in Fig 6a.
-The first and most important is the fact that SPR dataset experiments is much more difficult compared to PCF dataset experiments.
+	\textbf{Response: }There are two reasons for the deviation in \textbf{Figure 6a}.
+The first and most important is the fact that SPR dataset experiments are much more difficult compared to PCF dataset experiments.
 The most important difference here is the testing strategy.
-In PCF dataset, the testing samples are selected randomly from all the samples in the dataset.
+In the PCF dataset, the testing samples are selected randomly from all the samples in the dataset.
 However, in SPR dataset, testing samples are from a completely new geometric configuration, in other words, we never show the testing configuration to the ANN system and expect it to estimate its loss function.
@@
 The second reason for the variation is the range of the experiments, SPR experiment output is constrained in a small region, accentuating the deviation.
-There is certainly more variation the SPR dataset, however, the difference is not as high as Fig 6 suggests.
+There is certainly more deviation in the SPR dataset, however, the difference is not as high as \textbf{Figure 6a} suggests.
 
-	Finally, it is possible to verify the results from Fig 6c as these are two of the individual geometric configurations that the ANN systems estimated.
+	Finally, it is possible to verify the results from \textbf{Figure 6c} as these are two of the individual geometric configurations that the ANN systems estimated.
 Even though there still is a deviation from the ground truth, ANN trained with the help of augmented samples is good at estimating the location of the peak.
@@
 
-	\textbf{NB: Fig. 6 has been shifted to Fig. 7 in the revised manuscript.}
+	\textit{Fig. 6 has been shifted to Fig. 7 in the revised manuscript.}
 \end{document}

### 2020-10-20 docs/paper/paper.tex
Final fixes before submission of revised manuscript

@@
 Due to their unique propagation features, Photonic Crystal Fibers (PCFs) have been integrated into a number of optical based devices and applications.
-Design flexibilities and precise light guidance abilities has made them more promising in comparison to conventional step index fibers in various optical applications including sensing \cite{wang2011selectively}.
+Design flexibilities and precise light guidance abilities have made them more promising in comparison to conventional step index fibers in various optical applications including sensing \cite{wang2011selectively}.
 
@@
 Furthermore, the cladding pattern arrangements such as hexagonal, octagonal, decagonal, square and circular \cite{wang2011selectively,ademgil2014highly} can be engaged to achieve the desired features for preferred applications.
-The hole-to hole spacing (pitch) and the air hole sizes are critical parameters of tuning the aforementioned propagation characteristics.
+The hole-to-hole spacing (pitch) and the air hole sizes are critical parameters of tuning the aforementioned propagation characteristics.
 On the other hand, surface plasmon resonance (SPR) is a unique technique that occurs with light and free electrons interaction at metallic boundaries.
-This interaction results with excitement of surface plasmon polarition (SPP).
+This interaction results in the excitement of surface plasmon polariton (SPP).
 Relative permittivity variations of the analytes will change the characteristics of the SPP wave, where sensing is triggered.
-Kretschamann Raether prism geometry is the fundamental construction principle of SPR based sensors  \cite{kretschmann1968radiative}.
+Kretschmann Raether prism geometry is the fundamental construction principle of SPR based sensors  \cite{kretschmann1968radiative}.
 This geometry practices Snell's Total Internal Reflection rule, where still a very small amount of light refracts from the metallic layer into the evanescent field.
@@
 The deep research on SPR based sensors have shown that Kretschmann Raether's prism geometry fails to satisfy the remote sensing and miniaturization requirements of critical detecting applications.
-One of the most common solutions of overcoming these limitations is replacing the prism with the core of an optical fiber.
-Considering the recent technological developments, PCF are offering a tremendous amount of design flexibility with the possibilities of complete control of light guidance.
-Hence, SPR technique can be integrated to this unique microstructured fibers for developing comprehensive multi-purpose sensor \cite{rifat2016highly,yasli2019effect}.
+One of the most common solutions for overcoming these limitations is replacing the prism with the core of an optical fiber.
+Considering the recent technological developments, PCF is offering a tremendous amount of design flexibility with the possibility of complete control of light guidance.
+Hence, SPR technique can be integrated into this unique microstructured fibers for developing a comprehensive multi-purpose sensor \cite{rifat2016highly,yasli2019effect}.
 Following the exclusive study by Hassani and Skorobogatiy \cite{hassani2006design}, a number of structures have reported the merits of PCF based SPR sensors.
-In the past, structures that contains features such as multi-channel single analyte and multi-channel multi analyte have been investigated \cite{rifat2016highly,yasli2019effect,yasli2019multi,azzam2016multichannel}.
-Also, the effects of various metallic layers such as Au, Ag \cite{yasli2019multi}, Ag- Graphene \cite{rifat2016highly}, Ta2TO5 \cite{otupiri2015multi}, ITO \cite{dash2014spr}, TiO2 \cite{rifat2016highly} with various design parameters have also been investigated in detailed.
-Several design parameters such as plasmonic material, thickness of the layers, air hole size and positions are decisive on resonance matching wavelength of the SPR based structures.
+In the past, structures that contain features such as multi-channel single analyte and multi-channel multi-analyte have been investigated \cite{rifat2016highly,yasli2019effect,yasli2019multi,azzam2016multichannel}.
+Also, the effects of various metallic layers such as Au, Ag \cite{yasli2019multi}, Ag- Graphene \cite{rifat2016highly}, Ta2TO5 \cite{otupiri2015multi}, ITO \cite{dash2014spr}, TiO2 \cite{rifat2016highly} with various design parameters have also been investigated in detail.
+Several design parameters such as plasmonic material, the thickness of the layers, air hole size and positions are decisive on resonance matching wavelength of the SPR based structures.
 Optimizing and refinement of these parameters is an extremely time consuming process with considerable computational time \cite{fornarelli2009neural,abdelaziz2012photonic,paper0}.
 In the past, genetic algorithms \cite{abdelaziz2012photonic,borel2004topology} method was used to optimize the structural design parameters to achieve better propagation features of photonic devices \cite{rifat2016highly}.
-Nowadays, in order to optimize such structures, artificial neural networks (ANN) and other machine learning (ML) algorithms are being applied \cite{fornarelli2009neural,paper0,hameed2008accurate}.
+Nowadays, in order to optimize such structures, artificial neural networks (ANN), and other machine learning (ML) algorithms are being applied \cite{fornarelli2009neural,paper0,hameed2008accurate}.
 Although ANNs and ML have been applied to PCFs \cite{fornarelli2009neural,paper0} and SPR structures \cite{fu2018optimization,mcatee2019artificial} independently, to the best of our knowledge, there seems to have been no published papers that investigated the PCF based SPR structures with this well tested methods.
@@
 Specifically, we have constructed our system on a PCF based SPR model.
-However, in the experiments section we have demonstrated that the designed system is generic enough to be applied to multiple similar PCF based designs.
+However, in the experiments section, we have demonstrated that the designed system is generic enough to be applied to multiple similar PCF based designs.
 The most important contribution of this research is the use of the GAN phase, where the available data is expanded to be used in the training phase.
@@
 The results demonstrated the accuracy of the network on a specific PCF structure.
-On the other hand, ANN method was employed for predicting the chromatic dispersion of conventional hexagonal lattice PCF structure \cite{rodriguez2010efficient}.
+On the other hand, the ANN method was employed for predicting the chromatic dispersion of conventional hexagonal lattice PCF structure \cite{rodriguez2010efficient}.
 In Ref.
@@
 
-This paper is organized as follows.The details of GAN procedure to generate additional training samples for ANN as well as the proposed neural network architecture is presented in Section \ref{sec:prop}.
+This paper is organized as follows.
+The details of GAN procedure to generate additional training samples for ANN as well as the proposed neural network architecture is presented in Section \ref{sec:prop}.
 The design parameters and details of PCF based SPR structure is described in section \ref{sec:pcf}.
@@
 In this section, details of the proposed method are discussed.
-Training of the system contains two phases: a GAN phase and regression training phase.
+Training of the system contains two phases: a GAN phase and a regression training phase.
 At the beginning of the training, a GAN is trained to generate additional data by using training samples.
-These generated samples are filtered to ensure they are within the numeric range of application.
+These generated samples are filtered to ensure they are within the numeric range of the application.
 Original training samples and generated samples are joined to train a fully-connected feedforward multi-layer perceptron (MLP) neural network.
@@
 The GAN can be trained by diverse metrics \cite{goodfellow2014generative, lucic2018gans}].
-In this work Wasserstein distance metric (WGAN) is employed \cite{arjovsky2017wasserstein}.
-In this system, discriminator is named as critic and it measures the distance between the generated and the real data.
-The distinguishing feature of the WGAN compared to other methods is the ability to determine a stopping criteria.
+In this work, Wasserstein distance metric (WGAN) is employed \cite{arjovsky2017wasserstein}.
+In this system, the discriminator is named as critic and it measures the distance between the generated and the real data.
+The distinguishing feature of the WGAN compared to other methods is the ability to determine stopping criteria.
 \hl{In a regular GAN system, training is stopped when the generated data is deemed viable by an observer.
@@
 The generator is supplied with the same number of parameters.
-These parameters are generated using Gaussian noise and this input is called latent variable.
+These parameters are generated using Gaussian noise and this input is called a latent variable.
 
@@
 This step uses a simple condition to discard the values that fall out of the desired range of both the independent variables  ($n_{analyte}, \lambda, \Lambda, d1, d2, d3, n_c$), and the confinement loss.
-Once the training phase is completed, the generator and the filter is used to augment the number of training samples that are available for ANN to train on.
+Once the training phase is completed, the generator and the filter are used to augment the number of training samples that are available for ANN to train on.
 %
@@
 
-The cross section of the proposed structure is illustrated in Figure 3.
-As can be seen from this figure, the sensor consists of an analyte channel (sensing medium), plasmonic layer (Au)and various sized cladding air holes.
-The cladding region is formed by nineteen various sized air holes, sited on silica background with hexagonal lattice arrangement.
+The cross-section of the proposed structure is illustrated in Figure 3.
+As can be seen from this figure, the sensor consists of an analyte channel (sensing medium), plasmonic layer (Au) and various sized cladding air holes.
+The cladding region is formed by nineteen various sized air holes, sited on a silica background with a hexagonal lattice arrangement.
 The air hole diameters are set to;  $d_1$= $0.45 \mu m$, $d_2$= $0.75 \mu m$, $d_3$= $0.35 \mu m$, and  $d_c$= $0.15$.
-The distance between air holes ($\Lambda$) are fixed to $2 \mu m$.
+The distance between air holes ($\Lambda$) is fixed to $2 \mu m$.
 Initially, trapping the light (fundamental mode) into the core region is vital for mode quality.
@@
 The Gold (Au) material is used as a plasmonic layer and set to be $40 \mu m$.
-The Johnson and Christy Data \cite{johnson1972optical} are used for the permittivity values.
+The Johnson and Christy Data \cite{johnson1972optical} is used for the permittivity values.
 The Sellmeier Equation (Eq.(\ref{eqn1})) is used for calculating the refractive index of Silica material \cite{bjarklev2003PCF}.
@@
 As mentioned in the introductory part, during the resonance phase matching condition, the confinement losses are reaching the highest rate.
-Therefore, precise calculation of the confinement losses are critical.
-The Equation \ref{eqn2} is used in this study for that purpose \cite{yasli2019effect}.
+Therefore, the precise calculation of the confinement losses is critical.
+Equation \ref{eqn2} is used in this study for that purpose \cite{yasli2019effect}.
 
@@
 
-A labelled dataset of 432 samples was provided by FVFEM numerical analysis.
+A labeled dataset of 432 samples was provided by FVFEM numerical analysis.
 Our dataset contains a number of independent variables, such as the operating wavelength  $\lambda$, analyte index $n_{analyte}$, hole to hole distance $\Lambda$, the air holes sizes ($d_1$, $d_2$ and $d_3$), and the real part of the refractive index ($n_c$).
@@
 
-Also, mean square error (MSE) is used for the comparisons.
-All algorithms are implemented using TensorFlow with Keras library in Python and experiments are performed on device with Intel i7-5600 CPU and 8GB of RAM.
+Also, the mean square error (MSE) metric is used for the comparisons.
+All algorithms are implemented using TensorFlow with Keras library in Python and experiments are performed on a device with Intel i7-5600 CPU and 8GB of RAM.
 TensorFlow library is set to use only CPU for the experiments.
@@
 All numeric comparison results are averaged over multiple executions: 9-fold testing for SPR dataset and 10-fold testing for \dszero.
-\hl{The number of testing samples used in SPR dataset experiments is 48, \dszero{} experiments is 112.} Non-averaged data used in figures, such as configuration estimation, are selected from non-extreme cases for the compared methods.
+\hl{The number of testing samples used in SPR dataset experiments is 48, \dszero{} experiments are 112.} Non-averaged data used in figures, such as configuration estimation, are selected from non-extreme cases for the compared methods.
 %
@@
 They deviate from the actual data.
-However, up to a point, the performance impact of having low number of training samples out-weighs the imperfect data generated by GAN.} The number of augmented samples depends on the training samples that are available and can vary depending on the dataset used.
+However, up to a point, the performance impact of having a low number of training samples out-weighs the imperfect data generated by GAN.} The number of augmented samples depends on the training samples that are available and can vary depending on the dataset used.
 
@@
 
-We have performed experiments to showcase the improvement gained by augmenting training samples using GAN phase.
-In Figure \ref{chart:ganperf}, the results of these experiments has shown.
+We have performed experiments to showcase the improvement gained by augmenting training samples using the GAN phase.
+In Figure \ref{chart:ganperf}, the results of these experiments are shown.
 An additional note to take away from this experiment is that the dataset with the limited number of samples has the highest improvement, which is demonstrated in a clearer fashion in Table \ref{tbl:all}.
@@
 
-In Figure \ref{chart:ganperf}c, prediction of new configuration with and without GAN phase is compared.
+In Figure \ref{chart:ganperf}c, prediction of a new configuration with and without GAN phase is compared.
 In the case with $n_{analyte} = 1.33$, the network without the GAN phase has failed to predict the curve correctly.
@@
 
-In this section we have determined both testing and training time of the proposed system in comparison to the simulation approach.
-In Table \ref{tbl:timing}, the result of these experiments are published.
+In this section, we have determined both testing and training time of the proposed system in comparison to the simulation approach.
+In Table \ref{tbl:timing}, the results of these experiments are published.
 Training time is total training time while testing is per sample.
@@
 Once trained, the ANN can work alone without the need for GAN or training again.
-With this information, it is evident that the ANN based methods are far faster than the simulation approach by several orders of magnitude.
+With this information, it is evident that the ANN-based methods are far faster than the simulation approach by several orders of magnitude.
 Even when training time is included, total time spent to calculate the confinement loss will be faster on a GAN boosted ANN compared to an FV-FEM simulator after only 5 samples.
 
-The training time difference between ANN systems is caused by the increased depth in the proposed architecture as well as mini-batch training strategy.
+The training time difference between ANN systems is caused by the increased depth in the proposed architecture as well as the mini-batch training strategy.
 Training time is dominated by the GAN phase; however, this phase does not add any overhead to the testing time.
@@
 
-In this paper, we have demonstrated that the use of generative adversarial networks can be beneficial to neural networks that are designed to compute propagation characteristics of PCF devices.
+In this paper, we have demonstrated that the use of generative adversarial networks can be beneficial to neural networks that are designed to compute the propagation characteristics of PCF devices.
 Additionally, we have also proposed and demonstrated a neural network that is both more generic and more accurate to estimate the confinement loss compared to the state-of-the-art network.
@@
 The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research article.
-\hl{The proposed combination is shown to be general enough that even though it is designed and optimized for the SPR dataset; in the experiments, it surpassed the accuracy of the method proposed in }\cite{paper0}\hl{ on the dataset that method is optimized on.}
-
-Another important aspect in this work is the experiments performed on a dataset that is designed to test the ability of artificial neural networks to estimate the properties of a new configuration.
+\hl{The proposed combination is shown to be general enough that even though it is designed and optimized for the SPR dataset; in the experiments, it surpassed the accuracy of the method proposed in }\cite{paper0}\hl{ on the dataset that the method is optimized on.}
+
+Another important aspect of this work is the experiments performed on a dataset that is designed to test the ability of artificial neural networks to estimate the properties of a new configuration.
 For this purpose, we have built a database based on Surface Plasmon Resonance with varying geometric configurations.
@@
 The most vital advantage of using machine learning methods instead of numerical simulation is the speed factor.
-In the experiments it is shown that the machine learning methods work few orders of magnitude faster than the simulation method.
+In the experiments, it is shown that the machine learning methods work few orders of magnitude faster than the simulation method.
 

### 2020-10-20 docs/revision/reply.tex
Final fixes before submission of revised manuscript

@@
 We would also like to state that we were unable to add all the requested details directly to the manuscript due to the page limitation.
-However, in this reply, we have tried to address all points that are raised by the reviewers to the best of our ability.
-Also due to small changes in the manuscript, reference and figure numbers are shifted.
-We have used these numbers as discussed by the reviewers and offered the new numbers at the end of each reply.
+However, in this reply, we have addressed all points that are raised by the reviewers.
+Also due to minor changes in the manuscript, reference and figure numbers are shifted.
+We have used these numbers as discussed by the reviewers and stated the new numbers at the end of each reply.
 
